### 2021-08-09 Manuscript.Rmd
Create Manuscript.Rmd
First commit of the RMarkdown file for analysing the data and writing the manuscript

---
title             : "NFC and burnout in teachers - A replication and extension study"
shorttitle        : "NFC and burnout in teachers"

author: 
  - name          : "Josephine Zerna"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Nicole Engelmann"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
      - Writing - review & editing
  - name          : "Anja Strobel"
    affiliation   : "3"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing
  - name          : "Alexander Strobel"
    affiliation   : "1"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing

affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden"
  - id            : "2"
    institution   : "Faculty of Education, Technische Universität Dresden"
  - id            : "3"
    institution   : "Institute of Psychology, Chemnitz University of Technology"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
wordcount         : "X"

bibliography      : references.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
---

```{r setup, include = FALSE}
library(papaja)
library(bibtex)

r_refs("r_references.bib") # creates bib to cite the used R packages

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables
#install.packages("knitr")      # for knitting documents and tables

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)

```

```{r analysis-preferences, echo=FALSE, message=FALSE, warning=FALSE}

  # Seed for random number generation
  set.seed(13)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

  # Set a number for the bootstrapping procedures
  bootnum <- 300

```

# Introduction

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities [@Cacioppo1982].
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait [@Stumm2013], and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984].
While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020], recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020].
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005].

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly [@Schaufeli2014].
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer [@GrayStanley2011; @Lloyd2002].
Lackritz [-@Lackritz2004] found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced self-efficacy.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady 2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper is to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expect NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we would like to extend the analysis to other possible mediators.
These mediators are motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery [@Salanova2006].
We would therefore like to investigate whether the association of NFC and burnout is mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
Using the same data as for the replication, we compute a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expect NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
And since burnout results from constant unpleasant activation by high demands, we expect it to be positively associated with DTH and negatively associated with DRF.
However, we have no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].

*The Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021].*

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript are available at [https://osf.io/36ep9/](https://osf.io/36ep9/).

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Please set your working directory using the drop down menu above
  # Then put this file in this directory, as well as the data.Rda file

  here::i_am("Manuscript.Rmd")

  # Load the data file

  load(here("data.Rda"))
```

## Participants
Teachers were recruited via social media, emails to colleagues of N.E. and to Saxon schools with the request to pass on the information.
All teachers were eligible, no payment was issued.
Of the $N=$ 278 participants, who started filling out the online survey, $N=$ `r nrow(data)` (`r round((table(data$gender)[1]/nrow(data))*100, digits = 1)`% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
Data was collected between the 12th of June and the 24th of July 2020.
At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.

## Material
All questionnaires were used in their German form. Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC was assessed using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control was assessed using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression were assessed using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently have a higher workload.
The Covid-19 items can be found in the **Supplementary Material**.
The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.

## Procedure
The questionnaires were provided online using SoSci Survey [@Leiner2019].
Participants were informed about aims and duration of the study and data security, then they provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.

## Data analysis
We used `r cite_r("r_references.bib")` for all our analyses.
### Multiple mediation model
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
### Structural equation model
Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.
### Exploratory analysis
We preregistered two exploratory analyses.
Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales [@Grass2018; @Naderi2018].
And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.

```{r splitandrecode, echo=FALSE, message=FALSE, warning=FALSE}

  # Put questionnaire data into different data frames for easy access

  mbi <- data[,10:30]             # Maslach Burnout Inventory
  erq <- data[,31:40]             # Emotion Regulation Questionnaire
  scs <- data[,41:53]             # Self Control Scale
  ws <- data[,54:90]              # Work Satisfaction
  ncs <- data[,c(91:98,100:107)]  # Need for Cognition Scale (without the dummy item)
  covb <- data[,108:118]          # Covid Burden Items
  dth <- ws[,c(4,8,9)]            # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]         # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]         # the Work Satisfaction items for the latent variable Demand-Resource-Fit

  # Create a list with keys for the questionnaire subscales/latent variables/item parcels

  keylist <- list(mbi_ee = c(5,7,10,11,14,18,19,20,21), mbi_dp = c(1,6,9,15,17), mbi_rpe = c(2,3,4,8,12,13,16),
                  erq_supp = c(2,4,6,9), erq_reap = c(1,3,5,7,8,10),
                  scs = c(2,3,4,5,6,7,8,10,11),
                  ncs = c(4,6,7,8,9,10,11,12,15,16),
                  ws = c(4,5,6,8,9,10,11,13,16,19,20,33))

  # Recode all the reverse coded items

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
  dtl <- 6 - dtl                                      # Recode from 1-5 to to 5-1
  dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
  drf <- drf -3                                       # Recode all from 1-5 to to -2-+2

```

```{r parcelling, echo=FALSE, message=FALSE, warning=FALSE}

  # Parcelling preparation: Compute factor loadings on the first PCA component

  ncs_pca <- princomp(ncs, cor = FALSE, scores = TRUE)
  ncs_load <- ncs_pca$loadings[,1]

  # Parcelling function

  parcel.gen <- function(loadings, parcels = 4,seed = 242,iterations = 10000) {

    p = parcels                   # number of parcels
    l = length(loadings)          # number of items
    set.seed(seed)              # seed for reproducibility

    out = parcels = NULL            # set up containers
    for (k in 1:iterations) {

      s = sample(1:l,l,replace = F) # random item order
      m = matrix(s,ncol = 4)        # separate into parcels

      # temporarily convert item numbers per parcel to concatenated strings
      parcels.i = NULL
      for (i in 1:p) {
        parcels.i = c(parcels.i,paste0(sort(m[,i]),collapse = ","))
      }
      # write to container
      parcels = rbind(parcels,parcels.i)

      # compute average item loadings per parcel
      avg.h = colMeans(matrix(loadings[m],ncol = 4))

      # compute differences between all average item loadings
      h.diff = NULL
      for (i in 1:(p-1)) {
        for (j in (i+1):p) {
          h.diff = c(h.diff,abs(avg.h[i]-avg.h[j]))
        }
      }

      # sum up differences
      h.diff.sum = sum(h.diff)
      # write summed differences to container
      out = c(out,h.diff.sum)
    }

    # find minimum summed difference and generate matrix or respective items
    final.parcels = matrix(as.numeric(unlist(strsplit(parcels[which.min(out),],','))),ncol = 4)
    # obtain corresponding loadings per parcel
    final.h = matrix(loadings[final.parcels],ncol = 4)

    # return result as list
    return(list(items = final.parcels,loadings = final.h,avg.loadings = colMeans(final.h),summed.difference = min(out)))

  }

  ncs_parcels <- parcel.gen(loadings = ncs_load) # execute function

  remove(ncs_load,ncs_pca) # remove unnecessary objects

  # Add parcelling result to the key list

  keylist <- c(keylist, parcel1 = list(ncs_parcels$items[,1]), parcel2 = list(ncs_parcels$items[,2]),
               parcel3 = list(ncs_parcels$items[,3]), parcel4 = list(ncs_parcels$items[,4]))
```

```{r scores, echo=FALSE, message=FALSE, warning=FALSE}

# Create data frame to feed the values of every subject into

  score_data <- data.frame(id = c(1:180),
                           mbi = rep(0,180),
                           mbi_ee = rep(0,180), mbi_dp = rep(0,180), mbi_rpe = rep(0,180),
                           erq = rep(0,180),
                           erq_supp = rep(0,180), erq_reap = rep(0,180),
                           scs = rep(0,180),
                           ncs = rep(0,180),
                           nfc1 = rep(0,180), nfc2 = rep(0,180), nfc3 = rep(0,180), nfc4 = rep(0,180),
                           dth = rep(0,180),
                           dth1 = rep(0,180), dth2 = rep(0,180), dth3 = rep(0,180),
                           dtl = rep(0,180),
                           dtl1 = rep(0,180), dtl2 = rep(0,180), dtl3 = rep(0,180),
                           drf = rep(0,180),
                           drf1 = rep(0,180), drf2 = rep(0,180), drf3 = rep(0,180),
                           covb = rep(0,180))

  # Compute individual scores or (for the latent variable indicators) feed in raw values

  for (i in 1:nrow(data)) {
    score_data[i,c(2:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }
```

```{r descriptives, echo=FALSE, message=FALSE, warning=FALSE}

  # Tests for normal distribution

    # using Mardia's test for multivariate normal distribution
    # results will be fed into the desc_met data frame in the next step

    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","covb")],
                       mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")

  # Descriptive statistics

    # Categorical descriptives: data frame with percentages of responses per category

    desc_cat <- data.frame(answer = c(1,2,3,4,5),
                           age = c(nrow(data[data$age == 1,])/nrow(data), nrow(data[data$age == 2,])/nrow(data), nrow(data[data$age == 3,])/nrow(data),
                                   nrow(data[data$age == 4,])/nrow(data), nrow(data[data$age == 5,])/nrow(data)),
                           gender = c(nrow(data[data$gender == 1,])/nrow(data), nrow(data[data$gender == 2,])/nrow(data), nrow(data[data$gender == 3,])/nrow(data),0,0),
                           schooltype = c(nrow(data[data$schooltype == 1,])/nrow(data), nrow(data[data$schooltype == 2,])/nrow(data), nrow(data[data$schooltype == 3,])/nrow(data),
                                          nrow(data[data$schooltype == 4,])/nrow(data), nrow(data[data$schooltype == 5,])/nrow(data)))

    # Metric descriptives: data frame with descriptive values of questionnaires

    desc_met <- data.frame(value = c("mean","sd","skewness","kurtosis","normality"),
                           mbi = rep(0,5),
                           mbi_ee = rep(0,5), mbi_dp = rep(0,5), mbi_rpe = rep(0,5),
                           erq = rep(0,5),
                           erq_supp = rep(0,5), erq_reap = rep(0,5),
                           scs = rep(0,5),
                           ncs = rep(0,5),
                           covb = rep(0,5))

    desc_met[1,2:ncol(desc_met)] <- isnorm_test$Descriptives$Mean
    desc_met[2,2:ncol(desc_met)] <- isnorm_test$Descriptives$Std.Dev
    desc_met[3,2:ncol(desc_met)] <- isnorm_test$Descriptives$Skew
    desc_met[4,2:ncol(desc_met)] <- isnorm_test$Descriptives$Kurtosis
    desc_met[5,2:ncol(desc_met)] <- isnorm_test$univariateNormality$Normality

```

```{r consistency, echo=FALSE, message=FALSE, warning=FALSE}

  # Tests for internal consistency

    # Create data frame to feed values into

    consistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
                                          "lower CI omega","raw omega","upper CI omega"))

    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios

    set.seed(13) # seed for reproducing the bootstrapping

    # Maslach Burnout Inventory

    cronalph <- alpha(mbi, check.keys = TRUE)
    macomega <- ci.reliability(data=mbi, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI emotional exhaustion

    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI depersonalization

    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI reduced personal efficacy

    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ

    cronalph <- alpha(erq, check.keys = TRUE)
    macomega <- ci.reliability(data=erq, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ suppression

    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ reappraisal

    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Self Control Scale

    cronalph <- alpha(scs, check.keys = TRUE)
    macomega <- ci.reliability(data=scs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Need for Cognition Scale

    cronalph <- alpha(ncs, check.keys = TRUE)
    macomega <- ci.reliability(data=ncs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Covid burden

    cronalph <- alpha(covb, check.keys = TRUE)
    macomega <- ci.reliability(data=covb, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demands Too High

    cronalph <- alpha(dth, check.keys = FALSE)
    macomega <- ci.reliability(data=dth, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demands Too Low

    cronalph <- alpha(dtl, check.keys = FALSE)
    macomega <- ci.reliability(data=dtl, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demand Resource Fit

    cronalph <- alpha(drf, check.keys = FALSE)
    macomega <- ci.reliability(data=drf, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    remove(cronalph,macomega) # delete the temporary variable

    # create a vector of consistencies to be used as the diagonal in a table later
    consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                          format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
    # paste together to create the output "alpha(omega)"
    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

```

```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

    # The following function for nicely formatted correlation output was taken from
    # https://paulvanderlaken.com/2020/07/28/publication-ready-correlation-matrix-significance-r/
    # on the 5th of August 2021

    correlation_matrix <- function(df,
                                   type = "pearson",
                                   digits = 3,
                                   decimal.mark = ".",
                                   use = "all",
                                   show_significance = TRUE,
                                   replace_diagonal = FALSE,
                                   replacement = ""){
      # check arguments
      stopifnot({
        is.numeric(digits)
        digits >= 0
        use %in% c("all", "upper", "lower")
        is.logical(replace_diagonal)
        is.logical(show_significance)
        is.character(replacement)
      })
      # we need the Hmisc package for this
      require(Hmisc)

      # retain only numeric and boolean columns
      isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
      if (sum(!isNumericOrBoolean) > 0) {
        cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
      }
      df = df[isNumericOrBoolean]

      # transform input data frame to matrix
      x <- as.matrix(df)

      # run correlation analysis using Hmisc package
      correlation_matrix <- Hmisc::rcorr(x, type = type)
      R <- correlation_matrix$r # Matrix of correlation coeficients
      p <- correlation_matrix$P # Matrix of p-value

      # transform correlations to specific character format
      Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)

      # if there are any negative numbers, we want to put a space before the positives to align all
      if (sum(!is.na(R) & R < 0) > 0) {
        Rformatted = ifelse(!is.na(R) & R > 0, paste0(" ", Rformatted), Rformatted)
      }

      # add significance levels if desired
      if (show_significance) {
        # define notions for significance levels; spacing is important.
        stars <- ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", ""))))
        Rformatted = paste0(Rformatted, stars)
      }

      # make all character strings equally long
      max_length = max(nchar(Rformatted))
      Rformatted = vapply(Rformatted, function(x) {
        current_length = nchar(x)
        difference = max_length - current_length
        return(paste0(x, paste(rep(" ", difference), collapse = ''), sep = ''))
      }, FUN.VALUE = character(1))

      # build a new matrix that includes the formatted correlations and their significance stars
      Rnew <- matrix(Rformatted, ncol = ncol(x))
      rownames(Rnew) <- colnames(Rnew) <- colnames(x)

      # replace undesired values
      if (use == 'upper') {
        Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
      } else if (use == 'lower') {
        Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
      } else if (replace_diagonal) {
        diag(Rnew) <- replacement
      }

      return(Rnew)
    }

    # correlate variables, including the demand resource ratios
    corr_with_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","dth","dtl","drf","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # correlate variables without demand resource ratios (for table in manuscript)
    corr_no_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       show_significance = FALSE,
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # add previously assembled diagonal with alpha and omega values
    diag(corr_no_drr) <- consist_diag

    # set row and column names for better table printing
    row.names(corr_no_drr) <- c("MBI Score","MBI EE","MBI DP","MBI RPE","ERQ","ERQ Suppression","ERQ Reappraisal","Self Control","NFC","Covid-19 Burden")
    colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")

    # create array with p-values of correlation coefficients
    corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                        "scs","ncs","covb")]), type = "spearman")$P
    # replace upper triangle with NA
    corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA
    # replace p-values with asterisks depending on significance level
    corr_pvalues <- ifelse(is.na(corr_pvalues), "", ifelse(corr_pvalues < .001, "***", ifelse(corr_pvalues < .01, "**", ifelse(corr_pvalues < .05, "*", ""))))
    # create three arrays with logical indicators of the significance levels
    corr_threestars <- corr_pvalues %>%
      as_tibble() %>%
      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "***", TRUE, FALSE)))
    corr_twostars <- corr_pvalues %>%
      as_tibble() %>%
      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "**", TRUE, FALSE)))
    corr_onestar <- corr_pvalues %>%
      as_tibble() %>%
      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "*", TRUE, FALSE)))

```

# Results

```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

  desc_table <-
  kbl(corr_no_drr,
      booktabs = T,
      align = rep("r",11)) %>%
    kable_styling(latex_options = "striped", position = "center", full_width = T, font_size = 10) %>%
    column_spec(2, italic = corr_onestar$mbi|corr_twostars$mbi, bold = corr_threestars$mbi|corr_twostars$mbi) %>%
    column_spec(3, italic = corr_onestar$mbi_ee|corr_twostars$mbi_ee, bold = corr_threestars$mbi_ee|corr_twostars$mbi_ee) %>%
    column_spec(4, italic = corr_onestar$mbi_dp|corr_twostars$mbi_dp, bold = corr_threestars$mbi_dp|corr_twostars$mbi_dp) %>%
    column_spec(5, italic = corr_onestar$mbi_rpe|corr_twostars$mbi_rpe, bold = corr_threestars$mbi_rpe|corr_twostars$mbi_rpe) %>%
    column_spec(6, italic = corr_onestar$erq|corr_twostars$erq, bold = corr_threestars$erq|corr_twostars$erq) %>%
    column_spec(7, italic = corr_onestar$erq_supp|corr_twostars$erq_supp, bold = corr_threestars$erq_supp|corr_twostars$erq_supp) %>%
    column_spec(8, italic = corr_onestar$erq_reap|corr_twostars$erq_reap, bold = corr_threestars$erq_reap|corr_twostars$erq_reap) %>%
    column_spec(9, italic = corr_onestar$scs|corr_twostars$scs, bold = corr_threestars$scs|corr_twostars$scs) %>%
    column_spec(10, italic = corr_onestar$ncs|corr_twostars$ncs, bold = corr_threestars$ncs|corr_twostars$ncs) %>%
    column_spec(11, italic = corr_onestar$covb|corr_twostars$covb, bold = corr_threestars$covb|corr_twostars$covb) %>%
    column_spec(2:11, width = "1.5cm") %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 180. Italics indicate \\\\textit{p} < .05, italics and bold indicate \\\\textit{p} < .01, bold indicates \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.")

```

```{r objective1, echo=FALSE, message=FALSE, warning=FALSE}

  # Replication of Grass et al. (2018)

  repli_model <- '
  # direct paths
    scs ~ a1 * ncs
    erq_reap ~ a2 * ncs
    erq_supp ~ a3 * ncs
    mbi_rpe ~ b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

  # indirect effects
    Indirect1 := a1 * b1
    Indirect2 := a2 * b2
    Indirect3 := a3 * b3

  # contrast (if significant, the effects differ)
    Contrast := Indirect1 - Indirect2 - Indirect3

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)

  # Include covariance of mediators in the model
    scs ~~ erq_reap
    scs ~~ erq_supp
    erq_reap ~~ erq_supp'

  # Determine the model fit

  fit <- sem(
    model = repli_model,
    data  = score_data,
    se = "bootstrap",
    bootstrap = 2000
  )

  # Get summary

  fit_summ <- summary(fit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE}

  # SEM with demand-resource-ratios

  sem_model <- '
  # measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DTL =~ dtl1 + dtl2 + dtl3
    DRF =~ drf1 + drf2 + drf3
    MBI =~ mbi_ee + mbi_dp + mbi_rpe

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    MBI ~ NFC + DTH + DTL + DRF'

  # Determine the model fit

  fit2 <- sem(
    model = sem_model,
    data  = score_data,
    estimator = "MLR"
  )

  # Get summary

  fit2_summ <- summary(fit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)

```

```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE}

  # Exploratory analysis I: MBI subscale instead of sum score

  explor1_model <- '
  # measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DTL =~ dtl1 + dtl2 + dtl3
    DRF =~ drf1 + drf2 + drf3
    RPE =~ mbi_rpe

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    RPE ~ NFC + DTH + DTL + DRF'

  # Determine the model fit

  fit_explor1 <- sem(
    model = explor1_model,
    data  = score_data,
    estimator = "MLR"
  )

  # Get summary

  fit_explor1_summ <- summary(fit_explor1, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE}

  # Exploratory analysis II: Covid burden as a covariate

  # Correlations show that Covid burden is positively associated with MBI and
  # and MBI_EE, and negatively associated with DTH. We will therefore include
  # Covid burden as a mediator between DTH and MBI.

  explor2_model <- '
  measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DTL =~ dtl1 + dtl2 + dtl3
    DRF =~ drf1 + drf2 + drf3
    MBI =~ mbi_ee + mbi_dp + mbi_rpe
    COVB =~ covb

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    COVB ~ DTH
    MBI ~ NFC + DTH + DTL + DRF + COVB'

  # Determine the model fit

  fit_explor2 <- sem(
    model = explor2_model,
    data  = score_data,
    estimator = "MLR"
  )

  # Get summary

  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-08-10 Manuscript.Rmd
Suppressed computation of bootstrapping for future knits
Bootstrapped internal consistencies have been saved as "consistencies.rds" and can be imported to save time

@@
   # Set a number for the bootstrapping procedures
-  bootnum <- 300
+  bootnum <- 5000
 
@@
   load(here("data.Rda"))
+
+  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
+  load(here("consistencies.rds"))
+
 ```
@@
 We used `r cite_r("r_references.bib")` for all our analyses.
-### Multiple mediation model
+
+### *Multiple mediation model*
 Items were reverse coded according to the scale manuals.
@@
 Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
-### Structural equation model
+
+### *Structural equation model*
 Items were reverse coded according to the scale manuals.
@@
 The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.
-### Exploratory analysis
+
+### *Exploratory analysis*
 We preregistered two exploratory analyses.
@@
 
-```{r consistency, echo=FALSE, message=FALSE, warning=FALSE}
+```{r consistency, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
 

### 2021-08-11 Manuscript.Rmd
Added table to output and imports variable correctly
Won't knit to the end due to negative variances error in lavaan

@@
   # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
-  load(here("consistencies.rds"))
+  consistencies <- read_rds(here("consistencies.rds"))
+  # create a vector of consistencies to be used as the diagonal in a table later
+  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
+                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
+  # paste together to create the output "alpha(omega)"
+  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
 
@@
 
+`r desc_table`
+
 ```{r objective1, echo=FALSE, message=FALSE, warning=FALSE}

### 2021-08-16 Manuscript.Rmd
Updated reference to R and packages
Still won't compile due to negative variances though
Deleted automatic bib creation

@@
 library(bibtex)
-
-r_refs("r_references.bib") # creates bib to cite the used R packages
 
@@
 ## Data analysis
-We used `r cite_r("r_references.bib")` for all our analyses.
+We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *lavaan* [@Rosseel2012] and *psych* [@Revelle2021] for all our analyses.
 

### 2021-08-26 Manuscript/Manuscript.Rmd
changed structure of the repository

--- 2021-08-10 Manuscript.Rmd
@@
 
-r_refs("r_references.bib") # creates bib to cite the used R packages
-
 #install.packages("here")       # easy file referencing
@@
 ```{r import, echo=FALSE, message=FALSE, warning=FALSE}
-  # Please set your working directory using the drop down menu above
-  # Then put this file in this directory, as well as the data.Rda file
+  # Define the top level as the one where this file lies
+  # If the rest of the files follow the structure of the Github project, everything will work
 
-  here::i_am("Manuscript.Rmd")
+  here::i_am("flag_top_level_NFCBurnout.txt")
 
@@
 
-  load(here("data.Rda"))
+  load(here("Data", "data.Rda"))
 
   # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
-  load(here("consistencies.rds"))
+  consistencies <- read_rds(here("Data", "consistencies.rds"))
+  # create a vector of consistencies to be used as the diagonal in a table later
+  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
+                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
+  # paste together to create the output "alpha(omega)"
+  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
 

### 2021-08-26 Manuscript/Manuscript.tex
changed structure of the repository

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={NFC and burnout in teachers - A replication and extension study},
  pdfauthor={Josephine Zerna1, Nicole Engelmann2, Anja Strobel3, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={mediation, resources, demands, structural equation modelling, Covid-19},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NFC and burnout in teachers}
\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{NFC and burnout in teachers - A replication and extension study}
\author{Josephine Zerna\textsuperscript{1}, Nicole Engelmann\textsuperscript{2}, Anja Strobel\textsuperscript{3}, \& Alexander Strobel\textsuperscript{1}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Josephine Zerna: Conceptualization, Methodology, Formal analysis, Writing - original draft preparation, Writing - review \& editing; Nicole Engelmann: Conceptualization, Investigation, Writing - review \& editing; Anja Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing; Alexander Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing.

Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden\\\textsuperscript{2} Faculty of Education, Technische Universität Dresden\\\textsuperscript{3} Institute of Psychology, Chemnitz University of Technology}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo \& Petty, 1982).
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982).
While many studies have found positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Elias \& Loomis, 2002; Grass et al., 2017; Lavrijsen et al., 2021; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020).
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli \& Salanova, 2014).
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley \& Muramatsu, 2011; Lloyd et al., 2002).
Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced self-efficacy.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli \& Salanova, 2014).
NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021; \textbf{Brady?}) has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. (2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
The findings by Grass et al. (2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper is to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
We expect NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we would like to extend the analysis to other possible mediators.
These mediators are motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery (Salanova et al., 2006).
We would therefore like to investigate whether the association of NFC and burnout is mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (DTH), demands that are too low for one's personal resources (DTL), and a balanced fit of demands and resources (DRF).
Using the same data as for the replication, we compute a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expect NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
And since burnout results from constant unpleasant activation by high demands, we expect it to be positively associated with DTH and negatively associated with DRF.
However, we have no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).

\emph{The Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021).}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript are available at \url{https://osf.io/36ep9/}.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

Teachers were recruited via social media, emails to colleagues of N.E. and to Saxon schools with the request to pass on the information.
All teachers were eligible, no payment was issued.
Of the \(N=\) 278 participants, who started filling out the online survey, \(N=\) 180 (72.20\% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
Data was collected between the 12th of June and the 24th of July 2020.
At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.

\hypertarget{material}{%
\subsection{Material}\label{material}}

All questionnaires were used in their German form. Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) (Büssing \& Perrar, 1992), NFC was assessed using the 16-item Need for Cognition Scale (NCS) (Bless et al., 1994), self-control was assessed using the 13-item Self-Control Scale (SCS) (Bertrams \& Dickhäuser, 2009), reappraisal and suppression were assessed using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler \& Kessler, 2009), work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) (Fischer \& Lück, 2014).
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently have a higher workload.
The Covid-19 items can be found in the \textbf{Supplementary Material}.
The survey also included the Subjective Wellbeing Index of the World Health Organization (Brähler et al., 2007), which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar (Böhm-Kasper et al., 2001) cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

The questionnaires were provided online using SoSci Survey (Leiner, 2019).
Participants were informed about aims and duration of the study and data security, then they provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used \emph{R Studio} (R Core Team, 2020; RStudio Team, 2020) with the main packages \emph{lavaan} (Rosseel, 2012) and \emph{psych} (Revelle, 2021) for all our analyses.

\hypertarget{multiple-mediation-model}{%
\subsubsection{\texorpdfstring{\emph{Multiple mediation model}}{Multiple mediation model}}\label{multiple-mediation-model}}

Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.

\hypertarget{structural-equation-model}{%
\subsubsection{\texorpdfstring{\emph{Structural equation model}}{Structural equation model}}\label{structural-equation-model}}

Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. (2019), a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.

\hypertarget{exploratory-analysis}{%
\subsubsection{\texorpdfstring{\emph{Exploratory analysis}}{Exploratory analysis}}\label{exploratory-analysis}}

We preregistered two exploratory analyses.
Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales (Grass et al., 2018; Naderi et al., 2018).
And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.

\hypertarget{results}{%
\section{Results}\label{results}}

\begingroup\fontsize{10}{12}\selectfont

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}}
\toprule
  & MBI & MBI EE & MBI DP & MBI RPE & ERQ & ERQ S & ERQ R & SCS & NFC & COV\\
\midrule
\cellcolor{gray!6}{MBI Score} & \cellcolor{gray!6}{0.90(0.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
MBI EE & \textbf{0.925} & 0.91(0.92) &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{MBI DP} & \textbf{\cellcolor{gray!6}{0.748}} & \textbf{\cellcolor{gray!6}{0.535}} & \cellcolor{gray!6}{0.68(0.69)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
MBI RPE & \textbf{0.669} & \textbf{0.434} & \textbf{0.480} & 0.79(0.79) &  &  &  &  &  & \\
\cellcolor{gray!6}{ERQ} & \cellcolor{gray!6}{-0.058} & \cellcolor{gray!6}{-0.059} & \cellcolor{gray!6}{0.043} & \cellcolor{gray!6}{-0.099} & \cellcolor{gray!6}{0.73(0.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
\addlinespace
ERQ Suppression & 0.053 & -0.000 & \em{0.166} & 0.076 & \textbf{0.592} & 0.75(0.79) &  &  &  & \\
\cellcolor{gray!6}{ERQ Reappraisal} & \cellcolor{gray!6}{-0.101} & \cellcolor{gray!6}{-0.058} & \cellcolor{gray!6}{-0.061} & \em{\textbf{\cellcolor{gray!6}{-0.197}}} & \textbf{\cellcolor{gray!6}{0.715}} & \cellcolor{gray!6}{-0.075} & \cellcolor{gray!6}{0.84(0.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
Self Control & \textbf{-0.342} & \textbf{-0.283} & \textbf{-0.368} & \em{-0.185} & -0.034 & -0.121 & 0.050 & 0.85(0.86) &  & \\
\cellcolor{gray!6}{NFC} & \textbf{\cellcolor{gray!6}{-0.248}} & \em{\textbf{\cellcolor{gray!6}{-0.196}}} & \em{\textbf{\cellcolor{gray!6}{-0.219}}} & \em{\textbf{\cellcolor{gray!6}{-0.213}}} & \cellcolor{gray!6}{-0.008} & \em{\cellcolor{gray!6}{-0.176}} & \em{\cellcolor{gray!6}{0.158}} & \em{\textbf{\cellcolor{gray!6}{0.216}}} & \cellcolor{gray!6}{0.89(0.89)} & \cellcolor{gray!6}{}\\
Covid-19 Burden & \em{\textbf{0.241}} & \textbf{0.324} & 0.083 & 0.016 & -0.028 & 0.019 & -0.065 & -0.040 & 0.125 & 0.77(0.81)\\
\bottomrule
\multicolumn{11}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{11}{l}{\rule{0pt}{1em}MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \textbackslash{}\textbackslash{}textit\{N\} = 180. Italics indicate \textbackslash{}\textbackslash{}textit\{p\} < .05, italics and bold indicate \textbackslash{}\textbackslash{}textit\{p\} < .01, bold indicates \textbackslash{}\textbackslash{}textit\{p\} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.}\\
\end{tabu}
\endgroup{}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 60 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        14
##                                                       
##   Number of observations                           180
##                                                       
## Model Test User Model:
##                                                       
##   Test statistic                                 0.000
##   Degrees of freedom                                 0
## 
## Model Test Baseline Model:
## 
##   Test statistic                                49.640
##   Degrees of freedom                                10
##   P-value                                        0.000
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    1.000
##   Tucker-Lewis Index (TLI)                       1.000
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -2215.454
##   Loglikelihood unrestricted model (H1)      -2215.454
##                                                       
##   Akaike (AIC)                                4458.908
##   Bayesian (BIC)                              4503.609
##   Sample-size adjusted Bayesian (BIC)         4459.271
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.000
##   90 Percent confidence interval - lower         0.000
##   90 Percent confidence interval - upper         0.000
##   P-value RMSEA <= 0.05                             NA
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.000
## 
## Parameter Estimates:
## 
##   Standard errors                            Bootstrap
##   Number of requested bootstrap draws             2000
##   Number of successful bootstrap draws            2000
## 
## Regressions:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   scs ~                                                                 
##     ncs       (a1)    0.162    0.051    3.154    0.002    0.055    0.258
##   erq_reap ~                                                            
##     ncs       (a2)    0.055    0.034    1.619    0.105   -0.011    0.120
##   erq_supp ~                                                            
##     ncs       (a3)   -0.063    0.025   -2.524    0.012   -0.113   -0.017
##   mbi_rpe ~                                                             
##     scs       (b1)   -0.069    0.030   -2.318    0.020   -0.126   -0.009
##     erq_reap  (b2)   -0.094    0.036   -2.652    0.008   -0.159   -0.023
##     erq_supp  (b3)    0.002    0.051    0.043    0.966   -0.094    0.106
##     ncs        (c)   -0.051    0.021   -2.473    0.013   -0.089   -0.008
##    Std.lv  Std.all
##                   
##     0.162    0.271
##                   
##     0.055    0.123
##                   
##    -0.063   -0.182
##                   
##    -0.069   -0.169
##    -0.094   -0.173
##     0.002    0.003
##    -0.051   -0.208
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##  .scs ~~                                                                
##    .erq_reap          1.393    3.526    0.395    0.693   -5.236    8.427
##    .erq_supp         -3.166    2.802   -1.130    0.258   -8.806    2.383
##  .erq_reap ~~                                                           
##    .erq_supp         -0.257    2.351   -0.109    0.913   -4.838    4.416
##    Std.lv  Std.all
##                   
##     1.393    0.028
##    -3.166   -0.082
##                   
##    -0.257   -0.009
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##    .scs              65.382    6.206   10.536    0.000   52.369   76.607
##    .erq_reap         38.748    4.220    9.182    0.000   30.312   47.219
##    .erq_supp         22.604    1.897   11.914    0.000   18.685   26.236
##    .mbi_rpe          10.143    1.297    7.821    0.000    7.457   12.428
##    Std.lv  Std.all
##    65.382    0.927
##    38.748    0.985
##    22.604    0.967
##    10.143    0.866
## 
## R-Square:
##                    Estimate
##     scs               0.073
##     erq_reap          0.015
##     erq_supp          0.033
##     mbi_rpe           0.134
## 
## Defined Parameters:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##     Indirect1        -0.011    0.007   -1.695    0.090   -0.026   -0.001
##     Indirect2        -0.005    0.004   -1.429    0.153   -0.013    0.001
##     Indirect3        -0.000    0.004   -0.039    0.969   -0.008    0.006
##     Contrast         -0.006    0.009   -0.653    0.514   -0.024    0.011
##     Total            -0.067    0.023   -2.957    0.003   -0.111   -0.021
##    Std.lv  Std.all
##    -0.011   -0.046
##    -0.005   -0.021
##    -0.000   -0.001
##    -0.006   -0.024
##    -0.067   -0.276
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 100 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        39
##                                                       
##   Number of observations                           180
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                395.419     399.077
##   Degrees of freedom                                 97          97
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   0.991
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1504.484    1461.750
##   Degrees of freedom                               120         120
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.029
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.784       0.775
##   Tucker-Lewis Index (TLI)                       0.733       0.721
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.783
##   Robust Tucker-Lewis Index (TLI)                            0.732
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -5189.293   -5189.293
##   Scaling correction factor                                  1.231
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -4991.583   -4991.583
##   Scaling correction factor                                  1.060
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               10456.585   10456.585
##   Bayesian (BIC)                             10581.111   10581.111
##   Sample-size adjusted Bayesian (BIC)        10457.597   10457.597
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.131       0.132
##   90 Percent confidence interval - lower         0.117       0.118
##   90 Percent confidence interval - upper         0.144       0.145
##   P-value RMSEA <= 0.05                          0.000       0.000
##                                                                   
##   Robust RMSEA                                               0.131
##   90 Percent confidence interval - lower                     0.118
##   90 Percent confidence interval - upper                     0.144
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.173       0.173
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   NFC =~                                                                
##     nfc1              1.000                               1.000    1.000
##     nfc2              1.002    0.112    8.931    0.000    0.782    1.222
##     nfc3              1.059    0.087   12.235    0.000    0.889    1.228
##     nfc4              1.035    0.103   10.004    0.000    0.833    1.238
##   DTH =~                                                                
##     dth1              1.000                               1.000    1.000
##     dth2              0.916    0.119    7.672    0.000    0.682    1.150
##     dth3              1.668    0.280    5.967    0.000    1.120    2.216
##   DTL =~                                                                
##     dtl1              1.000                               1.000    1.000
##     dtl2              1.755    0.318    5.525    0.000    1.132    2.377
##     dtl3              1.987    0.425    4.672    0.000    1.154    2.821
##   DRF =~                                                                
##     drf1              1.000                               1.000    1.000
##     drf2              0.886    0.144    6.151    0.000    0.604    1.168
##     drf3              0.790    0.130    6.061    0.000    0.534    1.045
##   MBI =~                                                                
##     mbi_ee            1.000                               1.000    1.000
##     mbi_dp            0.231    0.042    5.516    0.000    0.149    0.314
##     mbi_rpe           0.249    0.049    5.047    0.000    0.152    0.345
##    Std.lv  Std.all
##                   
##     3.213    0.759
##     3.220    0.771
##     3.402    0.869
##     3.327    0.838
##                   
##     0.598    0.541
##     0.548    0.553
##     0.998    0.848
##                   
##     0.409    0.483
##     0.717    0.711
##     0.813    0.883
##                   
##     0.586    0.791
##     0.519    0.820
##     0.463    0.597
##                   
##     7.122    0.873
##     1.648    0.523
##     1.771    0.534
## 
## Regressions:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   DTH ~                                                                 
##     NFC               0.042    0.020    2.154    0.031    0.004    0.081
##   DTL ~                                                                 
##     NFC               0.023    0.015    1.522    0.128   -0.007    0.052
##   DRF ~                                                                 
##     NFC              -0.070    0.020   -3.488    0.000   -0.110   -0.031
##   MBI ~                                                                 
##     NFC               0.002    0.144    0.014    0.989   -0.281    0.285
##     DTH             -10.624    2.229   -4.767    0.000  -14.991   -6.256
##     DTL              -1.838    1.428   -1.287    0.198   -4.637    0.960
##     DRF               4.036    1.080    3.736    0.000    1.918    6.153
##    Std.lv  Std.all
##                   
##     0.228    0.228
##                   
##     0.180    0.180
##                   
##    -0.386   -0.386
##                   
##     0.001    0.001
##    -0.892   -0.892
##    -0.106   -0.106
##     0.332    0.332
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##    .nfc1              7.596    1.125    6.753    0.000    5.391    9.801
##    .nfc2              7.079    0.940    7.530    0.000    5.237    8.922
##    .nfc3              3.748    0.729    5.139    0.000    2.319    5.178
##    .nfc4              4.674    0.967    4.834    0.000    2.779    6.569
##    .dth1              0.866    0.107    8.079    0.000    0.656    1.077
##    .dth2              0.681    0.092    7.425    0.000    0.501    0.860
##    .dth3              0.390    0.089    4.365    0.000    0.215    0.565
##    .dtl1              0.549    0.093    5.884    0.000    0.366    0.732
##    .dtl2              0.504    0.087    5.820    0.000    0.334    0.674
##    .dtl3              0.186    0.097    1.911    0.056   -0.005    0.377
##    .drf1              0.206    0.048    4.276    0.000    0.112    0.300
##    .drf2              0.132    0.036    3.649    0.000    0.061    0.203
##    .drf3              0.387    0.057    6.835    0.000    0.276    0.498
##    .mbi_ee           15.839    5.619    2.819    0.005    4.826   26.852
##    .mbi_dp            7.207    0.920    7.835    0.000    5.404    9.010
##    .mbi_rpe           7.851    1.017    7.722    0.000    5.858    9.843
##     NFC              10.323    2.212    4.666    0.000    5.987   14.659
##    .DTH               0.339    0.100    3.397    0.001    0.143    0.535
##    .DTL               0.162    0.058    2.779    0.005    0.048    0.276
##    .DRF               0.293    0.083    3.522    0.000    0.130    0.455
##    .MBI               0.949    4.185    0.227    0.821   -7.253    9.152
##    Std.lv  Std.all
##     7.596    0.424
##     7.079    0.406
##     3.748    0.245
##     4.674    0.297
##     0.866    0.708
##     0.681    0.694
##     0.390    0.281
##     0.549    0.767
##     0.504    0.495
##     0.186    0.220
##     0.206    0.375
##     0.132    0.328
##     0.387    0.643
##    15.839    0.238
##     7.207    0.726
##     7.851    0.715
##     1.000    1.000
##     0.948    0.948
##     0.968    0.968
##     0.851    0.851
##     0.019    0.019
## 
## R-Square:
##                    Estimate
##     nfc1              0.576
##     nfc2              0.594
##     nfc3              0.755
##     nfc4              0.703
##     dth1              0.292
##     dth2              0.306
##     dth3              0.719
##     dtl1              0.233
##     dtl2              0.505
##     dtl3              0.780
##     drf1              0.625
##     drf2              0.672
##     drf3              0.357
##     mbi_ee            0.762
##     mbi_dp            0.274
##     mbi_rpe           0.285
##     DTH               0.052
##     DTL               0.032
##     DRF               0.149
##     MBI               0.981
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 125 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        34
##                                                       
##   Number of observations                           180
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                250.937     247.820
##   Degrees of freedom                                 71          71
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.013
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1161.800    1112.062
##   Degrees of freedom                                91          91
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.045
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.832       0.827
##   Tucker-Lewis Index (TLI)                       0.785       0.778
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.832
##   Robust Tucker-Lewis Index (TLI)                            0.785
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -4173.205   -4173.205
##   Scaling correction factor                                  1.224
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -4047.737   -4047.737
##   Scaling correction factor                                  1.081
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                                8414.410    8414.410
##   Bayesian (BIC)                              8522.971    8522.971
##   Sample-size adjusted Bayesian (BIC)         8415.293    8415.293
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.119       0.118
##   90 Percent confidence interval - lower         0.103       0.102
##   90 Percent confidence interval - upper         0.135       0.134
##   P-value RMSEA <= 0.05                          0.000       0.000
##                                                                   
##   Robust RMSEA                                               0.118
##   90 Percent confidence interval - lower                     0.103
##   90 Percent confidence interval - upper                     0.135
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.165       0.165
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   NFC =~                                                                
##     nfc1              1.000                               1.000    1.000
##     nfc2              1.013    0.112    9.043    0.000    0.793    1.232
##     nfc3              1.062    0.087   12.179    0.000    0.891    1.232
##     nfc4              1.045    0.104   10.045    0.000    0.841    1.249
##   DTH =~                                                                
##     dth1              1.000                               1.000    1.000
##     dth2              1.016    0.159    6.405    0.000    0.705    1.326
##     dth3              0.857    0.132    6.511    0.000    0.599    1.115
##   DTL =~                                                                
##     dtl1              1.000                               1.000    1.000
##     dtl2              1.759    0.327    5.377    0.000    1.118    2.401
##     dtl3              1.836    0.333    5.514    0.000    1.183    2.488
##   DRF =~                                                                
##     drf1              1.000                               1.000    1.000
##     drf2              0.878    0.126    6.987    0.000    0.632    1.124
##     drf3              0.776    0.124    6.243    0.000    0.532    1.020
##   RPE =~                                                                
##     mbi_rpe           1.000                               1.000    1.000
##    Std.lv  Std.all
##                   
##     3.195    0.755
##     3.236    0.775
##     3.392    0.867
##     3.338    0.841
##                   
##     0.785    0.709
##     0.797    0.805
##     0.672    0.571
##                   
##     0.424    0.500
##     0.745    0.738
##     0.778    0.845
##                   
##     0.590    0.796
##     0.518    0.817
##     0.458    0.591
##                   
##     3.297    1.000
## 
## Regressions:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   DTH ~                                                                 
##     NFC               0.054    0.024    2.245    0.025    0.007    0.101
##   DTL ~                                                                 
##     NFC               0.025    0.015    1.637    0.102   -0.005    0.055
##   DRF ~                                                                 
##     NFC              -0.071    0.020   -3.564    0.000   -0.110   -0.032
##   RPE ~                                                                 
##     NFC              -0.051    0.085   -0.597    0.551   -0.218    0.116
##     DTH              -0.497    0.366   -1.357    0.175   -1.214    0.221
##     DTL              -0.845    0.653   -1.293    0.196   -2.125    0.436
##     DRF               3.161    0.439    7.196    0.000    2.300    4.022
##    Std.lv  Std.all
##                   
##     0.220    0.220
##                   
##     0.189    0.189
##                   
##    -0.385   -0.385
##                   
##    -0.049   -0.049
##    -0.118   -0.118
##    -0.109   -0.109
##     0.566    0.566
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##    .nfc1              7.709    1.135    6.793    0.000    5.485    9.934
##    .nfc2              6.974    0.930    7.498    0.000    5.151    8.797
##    .nfc3              3.815    0.741    5.148    0.000    2.363    5.268
##    .nfc4              4.597    0.973    4.723    0.000    2.689    6.504
##    .dth1              0.608    0.113    5.374    0.000    0.386    0.830
##    .dth2              0.345    0.105    3.289    0.001    0.140    0.551
##    .dth3              0.933    0.123    7.613    0.000    0.693    1.174
##    .dtl1              0.537    0.092    5.845    0.000    0.357    0.717
##    .dtl2              0.464    0.077    5.990    0.000    0.312    0.615
##    .dtl3              0.242    0.075    3.241    0.001    0.096    0.388
##    .drf1              0.201    0.040    5.021    0.000    0.123    0.280
##    .drf2              0.133    0.032    4.209    0.000    0.071    0.195
##    .drf3              0.391    0.059    6.605    0.000    0.275    0.508
##    .mbi_rpe           0.000                               0.000    0.000
##     NFC              10.210    2.189    4.665    0.000    5.920   14.500
##    .DTH               0.586    0.128    4.583    0.000    0.336    0.837
##    .DTL               0.173    0.058    2.998    0.003    0.060    0.286
##    .DRF               0.297    0.077    3.868    0.000    0.146    0.447
##    .RPE               6.568    0.876    7.498    0.000    4.852    8.285
##    Std.lv  Std.all
##     7.709    0.430
##     6.974    0.400
##     3.815    0.249
##     4.597    0.292
##     0.608    0.497
##     0.345    0.352
##     0.933    0.674
##     0.537    0.750
##     0.464    0.455
##     0.242    0.286
##     0.201    0.366
##     0.133    0.332
##     0.391    0.651
##     0.000    0.000
##     1.000    1.000
##     0.952    0.952
##     0.964    0.964
##     0.852    0.852
##     0.604    0.604
## 
## R-Square:
##                    Estimate
##     nfc1              0.570
##     nfc2              0.600
##     nfc3              0.751
##     nfc4              0.708
##     dth1              0.503
##     dth2              0.648
##     dth3              0.326
##     dtl1              0.250
##     dtl2              0.545
##     dtl3              0.714
##     drf1              0.634
##     drf2              0.668
##     drf3              0.349
##     mbi_rpe           1.000
##     DTH               0.048
##     DTL               0.036
##     DRF               0.148
##     RPE               0.396
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 154 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        42
##                                                       
##   Number of observations                           180
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                430.369     430.449
##   Degrees of freedom                                111         111
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.000
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1568.311    1513.167
##   Degrees of freedom                               136         136
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.036
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.777       0.768
##   Tucker-Lewis Index (TLI)                       0.727       0.716
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.776
##   Robust Tucker-Lewis Index (TLI)                            0.726
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -5691.634   -5691.634
##   Scaling correction factor                                  1.220
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -5476.449   -5476.449
##   Scaling correction factor                                  1.060
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               11467.268   11467.268
##   Bayesian (BIC)                             11601.372   11601.372
##   Sample-size adjusted Bayesian (BIC)        11468.358   11468.358
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.126       0.126
##   90 Percent confidence interval - lower         0.114       0.114
##   90 Percent confidence interval - upper         0.139       0.139
##   P-value RMSEA <= 0.05                          0.000       0.000
##                                                                   
##   Robust RMSEA                                               0.126
##   90 Percent confidence interval - lower                     0.114
##   90 Percent confidence interval - upper                     0.139
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.170       0.170
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   NFC =~                                                                
##     nfc1              1.000                               1.000    1.000
##     nfc2              1.003    0.113    8.909    0.000    0.783    1.224
##     nfc3              1.060    0.087   12.195    0.000    0.889    1.230
##     nfc4              1.036    0.104    9.982    0.000    0.833    1.239
##   DTH =~                                                                
##     dth1              1.000                               1.000    1.000
##     dth2              0.886    0.108    8.217    0.000    0.675    1.097
##     dth3              1.500    0.254    5.909    0.000    1.003    1.998
##   DTL =~                                                                
##     dtl1              1.000                               1.000    1.000
##     dtl2              1.756    0.318    5.521    0.000    1.133    2.380
##     dtl3              1.980    0.421    4.700    0.000    1.154    2.806
##   DRF =~                                                                
##     drf1              1.000                               1.000    1.000
##     drf2              0.882    0.143    6.170    0.000    0.602    1.162
##     drf3              0.785    0.131    5.983    0.000    0.528    1.042
##   MBI =~                                                                
##     mbi_ee            1.000                               1.000    1.000
##     mbi_dp            0.237    0.046    5.115    0.000    0.146    0.328
##     mbi_rpe           0.255    0.054    4.728    0.000    0.149    0.361
##   COVB =~                                                               
##     covb              1.000                               1.000    1.000
##    Std.lv  Std.all
##                   
##     3.211    0.759
##     3.222    0.771
##     3.403    0.870
##     3.327    0.839
##                   
##     0.643    0.582
##     0.570    0.576
##     0.965    0.820
##                   
##     0.409    0.484
##     0.719    0.712
##     0.811    0.881
##                   
##     0.588    0.793
##     0.519    0.818
##     0.462    0.595
##                   
##     6.987    0.860
##     1.656    0.527
##     1.781    0.539
##                   
##     4.272    1.000
## 
## Regressions:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##   DTH ~                                                                 
##     NFC               0.037    0.022    1.729    0.084   -0.005    0.080
##   DTL ~                                                                 
##     NFC               0.023    0.015    1.515    0.130   -0.007    0.052
##   DRF ~                                                                 
##     NFC              -0.070    0.020   -3.479    0.001   -0.110   -0.031
##   COVB ~                                                                
##     DTH              -3.001    0.544   -5.518    0.000   -4.067   -1.935
##   MBI ~                                                                 
##     NFC              -0.009    0.149   -0.058    0.954   -0.301    0.284
##     DTH             -10.345    2.372   -4.362    0.000  -14.994   -5.696
##     DTL              -1.733    1.436   -1.206    0.228   -4.547    1.082
##     DRF               4.266    1.160    3.678    0.000    1.992    6.539
##     COVB             -0.224    0.130   -1.727    0.084   -0.478    0.030
##    Std.lv  Std.all
##                   
##     0.187    0.187
##                   
##     0.179    0.179
##                   
##    -0.384   -0.384
##                   
##    -0.452   -0.452
##                   
##    -0.004   -0.004
##    -0.953   -0.953
##    -0.102   -0.102
##     0.359    0.359
##    -0.137   -0.137
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
##    .nfc1              7.608    1.127    6.751    0.000    5.399    9.816
##    .nfc2              7.066    0.943    7.494    0.000    5.218    8.915
##    .nfc3              3.738    0.729    5.125    0.000    2.308    5.167
##    .nfc4              4.673    0.966    4.835    0.000    2.779    6.567
##    .dth1              0.810    0.103    7.839    0.000    0.608    1.013
##    .dth2              0.656    0.094    7.005    0.000    0.472    0.839
##    .dth3              0.454    0.103    4.421    0.000    0.252    0.655
##    .dtl1              0.549    0.093    5.892    0.000    0.366    0.731
##    .dtl2              0.502    0.086    5.825    0.000    0.333    0.671
##    .dtl3              0.189    0.096    1.961    0.050    0.000    0.378
##    .drf1              0.204    0.048    4.231    0.000    0.109    0.298
##    .drf2              0.133    0.036    3.686    0.000    0.062    0.204
##    .drf3              0.388    0.057    6.825    0.000    0.277    0.500
##    .mbi_ee           17.173    6.430    2.671    0.008    4.570   29.776
##    .mbi_dp            7.119    0.925    7.697    0.000    5.306    8.932
##    .mbi_rpe           7.740    1.033    7.494    0.000    5.716    9.764
##    .covb              0.000                               0.000    0.000
##     NFC              10.312    2.212    4.661    0.000    5.975   14.648
##    .DTH               0.400    0.111    3.584    0.000    0.181    0.618
##    .DTL               0.162    0.058    2.784    0.005    0.048    0.276
##    .DRF               0.295    0.084    3.508    0.000    0.130    0.460
##    .MBI              -0.334    4.157   -0.080    0.936   -8.481    7.813
##    .COVB             14.522    1.668    8.706    0.000   11.252   17.791
##    Std.lv  Std.all
##     7.608    0.425
##     7.066    0.405
##     3.738    0.244
##     4.673    0.297
##     0.810    0.662
##     0.656    0.669
##     0.454    0.327
##     0.549    0.766
##     0.502    0.493
##     0.189    0.224
##     0.204    0.371
##     0.133    0.331
##     0.388    0.645
##    17.173    0.260
##     7.119    0.722
##     7.740    0.709
##     0.000    0.000
##     1.000    1.000
##     0.965    0.965
##     0.968    0.968
##     0.853    0.853
##    -0.007   -0.007
##     0.796    0.796
## 
## R-Square:
##                    Estimate
##     nfc1              0.575
##     nfc2              0.595
##     nfc3              0.756
##     nfc4              0.703
##     dth1              0.338
##     dth2              0.331
##     dth3              0.673
##     dtl1              0.234
##     dtl2              0.507
##     dtl3              0.776
##     drf1              0.629
##     drf2              0.669
##     drf3              0.355
##     mbi_ee            0.740
##     mbi_dp            0.278
##     mbi_rpe           0.291
##     covb              1.000
##     DTH               0.035
##     DTL               0.032
##     DRF               0.147
##     MBI                  NA
##     COVB              0.204
\end{verbatim}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Abler2009}{}%
Abler, B., \& Kessler, H. (2009). Emotion {Regulation} {Questionnaire} -- {Eine} deutschsprachige {Fassung} des {ERQ} von {Gross} und {John}. \emph{Diagnostica}, \emph{55}(3), 144--152. \url{https://doi.org/10.1026/0012-1924.55.3.144}

\leavevmode\hypertarget{ref-Bertrams2009a}{}%
Bertrams, A., \& Dickhäuser, O. (2009). Messung dispositioneller {Selbstkontroll}-{Kapazität}. \emph{Diagnostica}, \emph{55}(1), 2--10. \url{https://doi.org/10.1026/0012-1924.55.1.2}

\leavevmode\hypertarget{ref-Bless1994}{}%
Bless, H., Wänke, M., Bohner, G., Fellhauer, R. F., \& Schwarz, N. (1994). Need for {Cognition}: {Eine} {Skala} zur {Erfassung} von {Engagement} und {Freude} bei {Denkaufgaben}. \emph{Zeitschrift für Sozialpsychologie}, \emph{25}. \url{https://doi.org/1779110}

\leavevmode\hypertarget{ref-BoehmKasper2001}{}%
Böhm-Kasper, O., Bos, O., Körner, S. C., \& Weishaupt, H. (2001). {EBI}. {Das} {Erfurter} {Belastungsinventar} zur {Erfassung} von {Belastung} und {Beanspruchung} von {Lehrern} und {Schülern} am {Gymnasium}. \emph{Schulforschung Und Schulentwicklung. Aktuelle Forschungsbeiträge}, \emph{14}, 35--66. \url{https://pub.uni-bielefeld.de/record/1858836}

\leavevmode\hypertarget{ref-Braehler2007}{}%
Brähler, E., Mühlan, H., Albani, C., \& Schmidt, S. (2007). Teststatistische {Prüfung} und {Normierung} der deutschen {Versionen} des {EUROHIS}-{QOL} {Lebensqualität}-{Index} und des {WHO}-5 {Wohlbefindens}-{Index}. \emph{Diagnostica}, \emph{53}(2), 83--96. \url{https://doi.org/10.1026/0012-1924.53.2.83}

\leavevmode\hypertarget{ref-Buessing1992}{}%
Büssing, A., \& Perrar, K.-M. (1992). Die {Messung} von {Burnout}. {Untersuchung} einer deutschen {Fassung} des {Maslach} {Burnout} {Inventory} ({MBI}-{D}). {[}{Measuring} burnout: {A} study of a {German} version of the {Maslach} {Burnout} {Inventory} ({MBI}-{D}).{]}. \emph{Diagnostica}, \emph{38}(4), 328--353.

\leavevmode\hypertarget{ref-Bye2009}{}%
Bye, D., \& Pushkar, D. (2009). How need for cognition and perceived control are differentially linked to emotional outcomes in the transition to retirement. \emph{Motivation and Emotion}, \emph{33}(3), 320--332. \url{https://doi.org/10.1007/s11031-009-9135-3}

\leavevmode\hypertarget{ref-Cacioppo1982}{}%
Cacioppo, J. T., \& Petty, R. E. (1982). The {Need} for {Cognition}. \emph{Journal of Personality and Social Psychology}, \emph{42}(1), 116--131. \url{https://doi.org/10.1037//0022-3514.42.1.116}

\leavevmode\hypertarget{ref-Cacioppo1996}{}%
Cacioppo, J. T., Petty, R. E., Feinstein, J. A., \& Jarvis, W. B. G. (1996). Dispositional differences in cognitive motivation: {The} life and times of individuals varying in need for cognition. \emph{Psychological Bulletin}, \emph{119}(2), 197--253. \url{https://doi.org/10.1037/0033-2909.119.2.197}

\leavevmode\hypertarget{ref-Cacioppo1984}{}%
Cacioppo, J. T., Petty, R. E., \& Kao, C. F. (1984). The {Efficient} {Assessment} of {Need} for {Cognition}. \emph{Journal of Personality Assessment}, \emph{48}(3), 306--307. \url{https://doi.org/10.1207/s15327752jpa4803_13}

\leavevmode\hypertarget{ref-Cazan2014}{}%
Cazan, A.-M., \& Indreica, S. E. (2014). Need for {Cognition} and {Approaches} to {Learning} among {University} {Students}. \emph{Procedia - Social and Behavioral Sciences}, \emph{127}, 134--138. \url{https://doi.org/10.1016/j.sbspro.2014.03.227}

\leavevmode\hypertarget{ref-Dodge2012}{}%
Dodge, R., Daly, A. P., Huyton, J., \& Sanders, L. D. (2012). The challenge of defining wellbeing. \emph{International Journal of Wellbeing}, \emph{2}(3). \url{https://www.internationaljournalofwellbeing.org/index.php/ijow/article/view/89}

\leavevmode\hypertarget{ref-Double2016}{}%
Double, K. S., \& Birney, D. P. (2016). The effects of personality and metacognitive beliefs on cognitive training adherence and performance. \emph{Personality and Individual Differences}, \emph{102}, 7--12. \url{https://doi.org/10.1016/j.paid.2016.04.101}

\leavevmode\hypertarget{ref-Dragano2017}{}%
Dragano, N., Siegrist, J., Nyberg, S. T., Lunau, T., Fransson, E. I., Alfredsson, L., Bjorner, J. B., Borritz, M., Burr, H., Erbel, R., Fahlén, G., Goldberg, M., Hamer, M., Heikkilä, K., Jöckel, K.-H., Knutsson, A., Madsen, I. E. H., Nielsen, M. L., Nordin, M., \ldots{} Kivimäki, M. (2017). Effort{{}}reward imbalance at work and incident coronary heart disease. \emph{Epidemiology}, \emph{28}(4), 619--626. \url{https://doi.org/10.1097/ede.0000000000000666}

\leavevmode\hypertarget{ref-Elias2002}{}%
Elias, S. M., \& Loomis, R. J. (2002). Utilizing {Need} for {Cognition} and {Perceived} {Self}-{Efficacy} to {Predict} {Academic} {Performance1}. \emph{Journal of Applied Social Psychology}, \emph{32}(8), 1687--1702. \url{https://doi.org/10.1111/j.1559-1816.2002.tb02770.x}

\leavevmode\hypertarget{ref-Fischer2014}{}%
Fischer, L., \& Lück, H. E. (2014). Allgemeine {Arbeitszufriedenheit}. \emph{Zusammenstellung Sozialwissenschaftlicher Items Und Skalen (ZIS)}. \url{https://doi.org/10.6102/ZIS1}

\leavevmode\hypertarget{ref-Fleischhauer2019}{}%
Fleischhauer, M., Miller, R., Wekenborg, M. K., Penz, M., Kirschbaum, C., \& Enge, S. (2019). Thinking against burnout? {An} individual's tendency to engage in and enjoy thinking as a potential resilience factor of burnout symptoms and burnout-related impairment in executive functioning. \emph{Frontiers in Psychology}, \emph{10}, 420. \url{https://doi.org/10.3389/fpsyg.2019.00420}

\leavevmode\hypertarget{ref-Froebe2021}{}%
Fröbe, A., \& Franco, P. (2021). Burnout among health care professionals in {COVID19} pandemic. \emph{Libri Oncologici}, 40--42. \url{https://pesquisa.bvsalud.org/global-literature-on-novel-coronavirus-2019-ncov/resource/pt/covidwho-1282947?lang=en}

\leavevmode\hypertarget{ref-Ghorbani2004}{}%
Ghorbani, N., Davison, H. K., Bing, M. N., Watson, P. J., \& Krauss, S. W. (2004). Private {Self}-{Consciousness} factors: {Relationships} {With} {Need} for {Cognition}, locus of control, and obsessive thinking in {Iran} and the {United} {States}. \emph{Journal of Social Psychology}, \emph{144}(4), 359--372. \url{http://search.ebscohost.com/login.aspx?direct=true\&db=a9h\&AN=14015824\&site=ehost-live}

\leavevmode\hypertarget{ref-Grass2018}{}%
Grass, J., John, N., \& Strobel, A. (2018). The joy of thinking as the key to success? {The} importance of {Need} for {Cognition} for subjective experience and achievement in academic studies. \emph{Zeitschrift Fur Padagogische Psychologie}, \emph{32}(3), 145--154. \url{https://doi.org/10.1024/1010-0652/a000222}

\leavevmode\hypertarget{ref-Grass2019}{}%
Grass, J., Krieger, F., Paulus, P., Greiff, S., Strobel, A., \& Strobel, A. (2019). Thinking in action: {Need} for {Cognition} predicts {Self}-{Control} together with {Action} {Orientation}. \emph{PLOS ONE}, \emph{14}(8), e0220282. \url{https://doi.org/10.1371/journal.pone.0220282}

\leavevmode\hypertarget{ref-Grass2017}{}%
Grass, J., Strobel, A., \& Strobel, A. (2017). Cognitive investments in academic success: {The} role of {Need} for {Cognition} at university. \emph{Frontiers in Psychology}, \emph{8}. \url{https://doi.org/10.3389/fpsyg.2017.00790}

\leavevmode\hypertarget{ref-GrayStanley2011}{}%
Gray-Stanley, J. A., \& Muramatsu, N. (2011). Work stress, burnout, and social and personal resources among direct care workers. \emph{Research in Developmental Disabilities}, \emph{32}(3), 1065--1074. \url{https://doi.org/10.1016/j.ridd.2011.01.025}

\leavevmode\hypertarget{ref-Gross1998a}{}%
Gross, J. J. (1998). Antecedent- and response-focused emotion regulation: {Divergent} consequences for experience, expression, and physiology. \emph{Journal of Personality and Social Psychology}, \emph{74}(1), 224--237. \url{https://doi.org/10.1037//0022-3514.74.1.224}

\leavevmode\hypertarget{ref-Heppner1983}{}%
Heppner, P. P., Reeder, B. L., \& Larson, L. M. (1983). Cognitive variables associated with personal problem-solving appraisal: {Implications} for counseling. \emph{Journal of Counseling Psychology}, \emph{30}(4), 537--545. \url{https://doi.org/10.1037/0022-0167.30.4.537}

\leavevmode\hypertarget{ref-Hobfoll1989}{}%
Hobfoll, S. E. (1989). Conservation of resources: {A} new attempt at conceptualizing stress. \emph{American Psychologist}, \emph{44}(3), 513--524. \url{https://doi.org/10.1037/0003-066X.44.3.513}

\leavevmode\hypertarget{ref-Kantas1997}{}%
Kantas, A., \& Vassilaki, E. (1997). Burnout in {Greek} teachers: {Main} findings and validity of the {Maslach} {Burnout} {Inventory}. \emph{Work \& Stress}, \emph{11}(1), 94--100. \url{https://doi.org/10.1080/02678379708256826}

\leavevmode\hypertarget{ref-Karagiannopoulou2020}{}%
Karagiannopoulou, E., Milienos, F. S., \& Rentzios, C. (2020). Grouping learning approaches and emotional factors to predict students' academic progress. \emph{International Journal of School \& Educational Psychology}, \emph{0}(0), 1--18. \url{https://doi.org/10.1080/21683603.2020.1832941}

\leavevmode\hypertarget{ref-Klaczynski1996}{}%
Klaczynski, P. A., \& Fauth, J. M. (1996). Intellectual ability, rationality, and intuitiveness as predictors of warranted and unwarranted optimism for future life events. \emph{Journal of Youth and Adolescence}, \emph{25}(6), 755--773. \url{https://doi.org/10.1007/BF01537452}

\leavevmode\hypertarget{ref-Lackritz2004}{}%
Lackritz, J. R. (2004). Exploring burnout among university faculty: Incidence, performance, and demographic issues. \emph{Teaching and Teacher Education}, \emph{20}(7), 713--729. \url{https://doi.org/10.1016/j.tate.2004.07.002}

\leavevmode\hypertarget{ref-Lavrijsen2021}{}%
Lavrijsen, J., Preckel, F., Verachtert, P., Vansteenkiste, M., \& Verschueren, K. (2021). Are motivational benefits of adequately challenging schoolwork related to students' need for cognition, cognitive ability, or both? \emph{Personality and Individual Differences}, \emph{171}, 110558. \url{https://doi.org/10.1016/j.paid.2020.110558}

\leavevmode\hypertarget{ref-Leiner2019}{}%
Leiner, D. J. (2019). \emph{{SoSci} {Survey}}. \url{https://www.soscisurvey.de}

\leavevmode\hypertarget{ref-Lloyd2002}{}%
Lloyd, C., King, R., \& Chenoweth, L. (2002). Social work, stress and burnout: A review. \emph{Journal of Mental Health}, \emph{11}(3), 255--265. \url{https://doi.org/10.1080/09638230020023642}

\leavevmode\hypertarget{ref-Madsen2017}{}%
Madsen, I. E. H., Nyberg, S. T., Hanson, L. L. M., Ferrie, J. E., Ahola, K., Alfredsson, L., Batty, G. D., Bjorner, J. B., Borritz, M., Burr, H., Chastang, J.-F., Graaf, R. de, Dragano, N., Hamer, M., Jokela, M., Knutsson, A., Koskenvuo, M., Koskinen, A., Leineweber, C., \ldots{} Kivimäki, M. (2017). Job strain as a risk factor for clinical depression: Systematic review and meta-analysis with additional individual participant data. \emph{Psychological Medicine}, \emph{47}(8), 1342--1356. \url{https://doi.org/10.1017/s003329171600355x}

\leavevmode\hypertarget{ref-Maslach1997}{}%
Maslach, C., Jackson, S. E., \& Leiter, M. P. (1997). Maslach {Burnout} {Inventory}: {Third} edition. In C. P. Zalaquett \& R. J. Wood (Eds.), \emph{Evaluating stress: A book of resources} (pp. 191--218). Scarecrow Education.

\leavevmode\hypertarget{ref-Maslach2016}{}%
Maslach, C., \& Leiter, M. (2016). Burnout. In \emph{Stress: Concepts, cognition, emotion, and behavior} (pp. 351--357). Elsevier. \url{https://doi.org/10.1016/b978-0-12-800951-2.00044-3}

\leavevmode\hypertarget{ref-Naderi2018}{}%
Naderi, Z., Bakhtiari, S., Momennasab, M., Abootalebi, M., \& Mirzaei, T. (2018). Prediction of academic burnout and academic performance based on the need for cognition and general self-efficacy: {A} cross-sectional analytical study. \emph{Latinoamericana de Hipertensión}, \emph{13}(6). \url{http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958}

\leavevmode\hypertarget{ref-Nowlin2017}{}%
Nowlin, E., Walker, D., Deeter-Schmelz, D. R., \& Haas, A. (2017). Emotion in sales performance: Affective orientation and {Need} for {Cognition} and the mediating role of motivation to work. \emph{Journal of Business \& Industrial Marketing}, \emph{33}(1), 107--116. \url{https://doi.org/10.1108/JBIM-06-2016-0136}

\leavevmode\hypertarget{ref-Osberg1987}{}%
Osberg, T. M. (1987). The convergent and discriminant validity of the {Need} for {Cognition} {Scale}. \emph{Journal of Personality Assessment}, \emph{51}(3), 441--450. \url{https://doi.org/10.1207/s15327752jpa5103_11}

\leavevmode\hypertarget{ref-RCT2020}{}%
R Core Team. (2020). \emph{R: {A} language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-Revelle2021}{}%
Revelle, W. (2021). \emph{Psych: {P}rocedures for psychological, psychometric, and personality research}. Northwestern University. \url{https://CRAN.R-project.org/package=psych}

\leavevmode\hypertarget{ref-Rosen2020}{}%
Rosen, C. C., Gabriel, A. S., Lee, H. W., Koopman, J., \& Johnson, R. E. (2020). When lending an ear turns into mistreatment: {An} episodic examination of leader mistreatment in response to venting at work. \emph{Personnel Psychology}, 1--21. \url{https://doi.org/10.1111/peps.12418}

\leavevmode\hypertarget{ref-Rosseel2012}{}%
Rosseel, Y. (2012). {lavaan}: {A}n {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. \url{https://www.jstatsoft.org/v48/i02/}

\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
RStudio Team. (2020). \emph{{RStudio}: {Integrated} development for {R}}. RStudio, PBC. \url{http://www.rstudio.com}

\leavevmode\hypertarget{ref-Salanova2006}{}%
Salanova, M., Bakker, A. B., \& Llorens, S. (2006). Flow at {Work}: {Evidence} for an {Upward} {Spiral} of {Personal} and {Organizational} {Resources}*. \emph{Journal of Happiness Studies}, \emph{7}(1), 1--22. \url{https://doi.org/10.1007/s10902-005-8854-8}

\leavevmode\hypertarget{ref-Schaufeli2001}{}%
Schaufeli, W., Bakker, A. B., Hoogduin, K., Schaap, C., \& Kladler, A. (2001). On the clinical validity of the {Maslach} {Burnout} {Inventory} and the burnout measure. \emph{Psychology \& Health}, \emph{16}(5), 565--582. \url{https://doi.org/10.1080/08870440108405527}

\leavevmode\hypertarget{ref-Schaufeli2014}{}%
Schaufeli, W., \& Salanova, M. (2014). Burnout, boredom and engagement at the workplace. In M. Peeters, J. de Jonge, \& T. Taris (Eds.), \emph{People at work: {An} {Introduction} to {Contemporary} {Work} {Psychology}} (pp. 293--320). Wiley Blackwell; Chichester. \url{https://lirias.kuleuven.be/retrieve/307889}

\leavevmode\hypertarget{ref-Simmons2012}{}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 word solution} (\{SSRN\} \{Scholarly\} \{Paper\} ID 2160588). Social Science Research Network. \url{https://doi.org/10.2139/ssrn.2160588}

\leavevmode\hypertarget{ref-Steptoe2013}{}%
Steptoe, A., \& Kivimäki, M. (2013). Stress and cardiovascular disease: An update on current knowledge. \emph{Annual Review of Public Health}, \emph{34}(1), 337--354. \url{https://doi.org/10.1146/annurev-publhealth-031912-114452}

\leavevmode\hypertarget{ref-Stumm2013}{}%
Stumm, S. von, \& Ackerman, P. L. (2013). Investment and intellect: A review and meta-analysis. \emph{Psychological Bulletin}, \emph{139}(4), 841--869. \url{https://doi.org/10.1037/a0030746}

\leavevmode\hypertarget{ref-Tolentino1990}{}%
Tolentino, E., Curry, L., \& Leak, G. (1990). Further validation of the short form of the {Need} for {Cognition} {Scale}. \emph{Psychological Reports}, \emph{66}(1), 321--322. \url{https://doi.org/10.2466/pr0.1990.66.1.321}

\leavevmode\hypertarget{ref-ValdiviaVazquez2021}{}%
Valdivia Vázquez, J. A., Hernández Castillo, G. D., \& Maiz García, S. I. (2021). Burnout in {Police} {Officers} from {Northern} {Mexico}: {A} validity study of the {Maslach} {Burnout} {Inventory}. \emph{Journal of Police and Criminal Psychology}. \url{https://doi.org/10.1007/s11896-021-09452-z}

\leavevmode\hypertarget{ref-Wiesner2005}{}%
Wiesner, M., Windle, M., \& Freeman, A. (2005). Work stress, substance use, and depression among young adult workers: An examination of main and moderator effect model. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 83--96. \url{https://doi.org/10.1037/1076-8998.10.2.83}

\leavevmode\hypertarget{ref-Zerna2021}{}%
Zerna, J., Strobel, A., \& Strobel, A. (2021). \emph{The role of {Need} for {Cognition} in wellbeing -- {A} review of associations and potential underlying mechanisms}. \url{https://doi.org/10.31234/osf.io/p6gwh}

\leavevmode\hypertarget{ref-Zheng2020}{}%
Zheng, A., Briley, D., Jacobucci, R., Harden, K. P., \& Tucker-Drob, E. (2020). \emph{Incremental {Validity} of {Character} {Measures} {Over} the {Big} {Five} and {Fluid} intelligence in {Predicting} {Academic} {Achievement}}. \url{https://doi.org/10.31234/osf.io/652qz}

\end{CSLReferences}

\endgroup

\end{document}

### 2021-08-30 Manuscript/Manuscript.Rmd
added multicorrelation plot

@@
 library(knitr)
+library(GGally)                 # from ggplot2, for multi-correlation plots
 
@@
 ```
+```{r objective2_troubleshooting, echo=FALSE, message=FALSE, warning=FALSE}
+
+# This function was taken from an answer on a Stackoverflow question on August 30th 2021
+# https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740
+
+  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
+    ggplot(data = data, mapping = mapping, ...) +
+      do.call(geom_point, pts) +
+      do.call(geom_smooth, smt)
+  }
+
+# Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
+  ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
+
+```
 

### 2021-08-30 Manuscript/Manuscript.Rmd
removed an outlier
Tried knitting fix but didn't work
LaTeX Error: File `tabu.sty' not found.

@@
 csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
+
+header-includes   : \usepackage{tabu}
 ---
@@
 
-```{r objective2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
 
@@
   # Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
-  ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
+  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
+
+  # Remove the outlier
+  score_data <- score_data[score_data$id != 161, ]
+
+            # SEM with demand-resource-ratios
+
+            sem_model <- '
+            # measurement model
+              NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+              DTH =~ dth1 + dth2 + dth3
+              DTL =~ dtl1 + dtl2 + dtl3
+              DRF =~ drf1 + drf2 + drf3
+              MBI =~ mbi_ee + mbi_dp + mbi_rpe
+
+            # structural model
+              DTH ~ NFC
+              DTL ~ NFC
+              DRF ~ NFC
+              MBI ~ NFC + DTH + DTL + DRF'
+
+            # Determine the model fit
+
+            fit2 <- sem(
+              model = sem_model,
+              data  = score_data,
+              estimator = "MLR"
+            )
+
+            # Get summary
+
+            fit2_summ <- summary(fit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+                    estimates = TRUE, ci = TRUE)
 
@@
 
-```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
 
@@
 
-```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
 

### 2021-08-31 Manuscript/Manuscript.Rmd
managed to get the knitting running

@@
 
-header-includes   : \usepackage{tabu}
+header-includes   :
+    - \usepackage{booktabs}
+    - \usepackage{longtable}
+    - \usepackage{array}
+    - \usepackage{multirow}
+    - \usepackage{wrapfig}
+    - \usepackage{float}
+    - \usepackage{colortbl}
+    - \usepackage{pdflscape}
+    - \usepackage{tabu}
+    - \usepackage{threeparttable}
+    - \usepackage{threeparttablex}
+    - \usepackage[normalem]{ulem}
+    - \usepackage{makecell}
+    - \usepackage{xcolor}
 ---

### 2021-08-31 Manuscript/Manuscript.Rmd
table knitting fully functional

@@
 #install.packages("Hmisc")      # for correlations with p-values
-#install.packages("kableExtra") # for great tables
+#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
 #install.packages("knitr")      # for knitting documents and tables
@@
   }
+
+  # This function was taken from an answer on a Stackoverflow question on August 30th 2021
+  # https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740
+
+  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
+    ggplot(data = data, mapping = mapping, ...) +
+      do.call(geom_point, pts) +
+      do.call(geom_smooth, smt)
+  }
+
+  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
+  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
+
+  # Remove the outlier
+  score_data <- score_data[score_data$mbi < 100, ]
+
 ```
@@
     # set row and column names for better table printing
-    row.names(corr_no_drr) <- c("MBI Score","MBI EE","MBI DP","MBI RPE","ERQ","ERQ Suppression","ERQ Reappraisal","Self Control","NFC","Covid-19 Burden")
+    row.names(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
     colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
@@
 
-```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
   kbl(corr_no_drr,
-      booktabs = T,
-      align = rep("r",11)) %>%
-    kable_styling(latex_options = "striped", position = "center", full_width = T, font_size = 10) %>%
+      booktabs = T, # no vertical lines
+      escape = F, # correctly print special characters
+      align = rep("r",11)) %>% # right aligns the text in every column except for the first
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
     column_spec(2, italic = corr_onestar$mbi|corr_twostars$mbi, bold = corr_threestars$mbi|corr_twostars$mbi) %>%
@@
     column_spec(11, italic = corr_onestar$covb|corr_twostars$covb, bold = corr_threestars$covb|corr_twostars$covb) %>%
-    column_spec(2:11, width = "1.5cm") %>%
     footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden.
-\\\\textit{N} = 180.
+\\\\textit{N} = 179.
 Italics indicate \\\\textit{p} < .05, italics and bold indicate \\\\textit{p} < .01, bold indicates \\\\textit{p} < .001.
-Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.")
+Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
+             escape = F, # correctly print special characters
+             threeparttable = T) # line breaks in the footnote
 
@@
 
-```{r objective1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
 
@@
 
-```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
-
-  # SEM with demand-resource-ratios
-
-  sem_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
-    DRF =~ drf1 + drf2 + drf3
-    MBI =~ mbi_ee + mbi_dp + mbi_rpe
-
-  # structural model
-    DTH ~ NFC
-    DTL ~ NFC
-    DRF ~ NFC
-    MBI ~ NFC + DTH + DTL + DRF'
-
-  # Determine the model fit
-
-  fit2 <- sem(
-    model = sem_model,
-    data  = score_data,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  fit2_summ <- summary(fit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-
-```
-```{r objective2_troubleshooting, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # This function was taken from an answer on a Stackoverflow question on August 30th 2021
-  # https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740
-
-  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
-    ggplot(data = data, mapping = mapping, ...) +
-      do.call(geom_point, pts) +
-      do.call(geom_smooth, smt)
-  }
-
-  # Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
-  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
-
-  # Remove the outlier
-  score_data <- score_data[score_data$id != 161, ]
+```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
 

### 2021-08-31 Manuscript/Manuscript.Rmd
basic plot for the mediation model

@@
 #install.packages("knitr")      # for knitting documents and tables
+#install.packages("semPlot")    # plotting path models
 
@@
 library(GGally)                 # from ggplot2, for multi-correlation plots
+library(semPlot)
 
@@
 
+```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Make a path diagram to visualize the results
+  # (This is just okay, it is not the final version, e.g. there is no path from NCS to MBI yet)
+
+  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
+                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
+                       sizeMan = 7, edge.label.cex = 0.8, # size specifications
+                       fade = FALSE, # do not make insignificant associations invisible
+                       theme = "colorblind" # select appropriate colour scheme
+                       )
+```
+
 ```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

### 2021-08-31 Manuscript/Manuscript.Rmd
plot looks better

@@
 library(semPlot)
+library(qgraph)
 
@@
   fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Burnout", "Need for Cognition"),
                        layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
-                       sizeMan = 7, edge.label.cex = 0.8, # size specifications
+                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
+                       edge.label.cex = 0.8, # size specifications
                        fade = FALSE, # do not make insignificant associations invisible

### 2021-09-01 Manuscript/Manuscript.Rmd
added plot for fit2
added labels to plot

@@
 
+  # Plot
+
+  fit2_plot <- semPaths(fit2, what = "par",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-1,-0.8,-0.6,-0.2,0,0.2,0.6,0.8,1,0.6,0.8,1,-0.8,-0.8,0,0.8,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 21, ncol = 2))
+
 ```

### 2021-09-02 Manuscript/Manuscript.Rmd
updated fit2 plot

--- 2021-08-31 Manuscript/Manuscript.Rmd
@@
 
+```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Visualize the results
+
+  fit2_plot <- semPaths(fit2, what = "par",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 21, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edge.label.cex = 0.81, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
+                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
+  )
+```
+
 ```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

### 2021-09-03 Manuscript/Manuscript.Rmd
updated plots

--- 2021-08-31 Manuscript/Manuscript.Rmd
@@
   fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
-                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Burnout", "Need for Cognition"),
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                        layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                        sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
-                       edge.label.cex = 0.8, # size specifications
+                       edge.label.cex = 1, # size specifications
                        fade = FALSE, # do not make insignificant associations invisible
-                       theme = "colorblind" # select appropriate colour scheme
+                       residuals = FALSE, # do not plot residuals
+                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
 )
@@
 
+```
+
+```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Visualize the results
+
+  fit2_plot <- semPaths(fit2, what = "par",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 21, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edge.label.cex = 1, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
+                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
+  )
 ```

### 2021-09-08 Manuscript/Manuscript.Rmd
changed recoding to correct version for Work Satisfaction Scale

@@
 
-  mbi <- data[,10:30]             # Maslach Burnout Inventory
+  mbi <- data[,10:30]             # Maslach Burnout Inventory grep(‚ncs‘, colnames(data))
   erq <- data[,31:40]             # Emotion Regulation Questionnaire
@@
   covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
+  dth <- 6 - dth
   dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
-  dtl <- 6 - dtl                                      # Recode from 1-5 to to 5-1
   dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
+  drf <- 6 - drf
   drf <- drf -3                                       # Recode all from 1-5 to to -2-+2
@@
     Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
-
-  # Include covariance of mediators in the model
-    scs ~~ erq_reap
-    scs ~~ erq_supp
-    erq_reap ~~ erq_supp'
+'
 
@@
   # structural model
-    DTH ~ NFC
-    DTL ~ NFC
-    DRF ~ NFC
-    MBI ~ NFC + DTH + DTL + DRF'
+    DTH ~ a1 * NFC
+    DTL ~ a2 * NFC
+    DRF ~ a3 * NFC
+    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
 
@@
 
-  fit2_plot <- semPaths(fit2, what = "par",
+  fit2_plot <- semPaths(fit2, what = "std",
                         nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),

### 2021-09-09 Manuscript/Manuscript.Rmd
added years spent teaching to data frame

@@
   score_data <- data.frame(id = c(1:180),
+                           years = data$yearsteaching,
                            mbi = rep(0,180),
@@
   for (i in 1:nrow(data)) {
-    score_data[i,c(2:ncol(score_data))] <- c(rowSums(mbi[i,]),
+    score_data[i,c(3:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                              rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
@@
   # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
-  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
+  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,6,10,11,16,20,24,28)], lower = list(continuous = my_fn))
+
+  # It looked like there was an outlier in the data, especially visible in the MBI data
+  # Check for the outlier in particular
 

### 2021-09-09 Manuscript/Manuscript.Rmd
updated mediation model and plot

@@
   # It looked like there was an outlier in the data, especially visible in the MBI data
-  # Check for the outlier in particular
+  # Check for the outlier in particular, using the data involved in the mediation
+  outlierplot <- outlier(score_data[ ,c(6,8:11)], plot = TRUE)
 
-  # Remove the outlier
+  # Remove participant 161
   score_data <- score_data[score_data$mbi < 100, ]
@@
   # direct paths
-    scs ~ a1 * ncs
+    scs       ~   a1 * ncs + years
     erq_reap  ~   a2 * ncs
@@
 
-  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
-                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
-                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
+  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
+                       layout = matrix(data = c(0,0,0,1,-1,-1,0.5,-0.1,-0.4,0.2,0.2,0.5), nrow = 6, ncol = 2), # manually set the node locations
                        sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
@@
                        residuals = FALSE, # do not plot residuals
+                       exoCov = FALSE, # do not plot covariance between exogenous variables
                        edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"

### 2021-09-09 Manuscript/Manuscript.Rmd
changed column reference

@@
 
-  mbi <- data[,10:30]             # Maslach Burnout Inventory grep(‚ncs‘, colnames(data))
-  erq <- data[,31:40]             # Emotion Regulation Questionnaire
-  scs <- data[,41:53]             # Self Control Scale
-  ws <- data[,54:90]              # Work Satisfaction
-  ncs <- data[,c(91:98,100:107)]  # Need for Cognition Scale (without the dummy item)
-  covb <- data[,108:118]          # Covid Burden Items
+  mbi <- data[,grep("MBI", colnames(data))]   # Maslach Burnout Inventory
+  erq <- data[,grep("ERQ", colnames(data))]   # Emotion Regulation Questionnaire
+  scs <- data[,grep("SCS", colnames(data))]   # Self Control Scale
+  ws <- data[,grep("WS", colnames(data))]     # Work Satisfaction
+  ncs <- data[,grep("NCS", colnames(data))]   # Need for Cognition Scale
+  ncs <- ncs[,-9]                             # remove the dummy item
+  covb <- data[,grep("COV", colnames(data))]  # Covid Burden Items
   dth <- ws[,c(4,8,9)]                        # the Work Satisfaction items for the latent variable Demands Too High
@@
     correlation_matrix <- function(df,
-                                   type = "pearson",
+                                   type = "spearman",
                                    digits = 3,
@@
   # direct paths
-    scs       ~   a1 * ncs + years
+    scs       ~   a1 * ncs
     erq_reap  ~   a2 * ncs
@@
   # Make a path diagram to visualize the results
-  # (This is just okay, it is not the final version, e.g. there is no path from NCS to MBI yet)
 
   fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
+                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
+                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
+                       edge.label.cex = 1, # size specifications
+                       fade = FALSE, # do not make insignificant associations invisible
+                       residuals = FALSE, # do not plot residuals
+                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
+)
+```
+
+```{r objective1years, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+  # Replication of Grass et al. (2018) using years spent teaching as a variable influencing self-control
+  # (as indicated by the correlation of it with SCS but not with the other variables)
+
+  repli_model_years <- '
+  # direct paths
+    scs       ~   a1 * ncs + y * years
+    erq_reap  ~   a2 * ncs
+    erq_supp  ~   a3 * ncs
+    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
+
+  # indirect effects
+    Indirect1 := (a1 * b1) + (y * b1)
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3) + (y * b1)
+'
+
+  # Determine the model fit
+
+  fityears <- sem(
+    model = repli_model_years,
+    data  = score_data,
+    se = "bootstrap",
+    bootstrap = 2000
+  )
+
+  # Get summary
+
+  fityears_summ <- summary(fityears, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+          estimates = TRUE, ci = TRUE)
+```
+
+```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Make a path diagram to visualize the results
+
+  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
                        nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
-                       layout = matrix(data = c(0,0,0,1,-1,-1,0.5,-0.1,-0.4,0.2,0.2,0.5), nrow = 6, ncol = 2), # manually set the node locations
+                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                        sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties

### 2021-09-10 Manuscript/Manuscript.Rmd
changed some details

@@
   # Define the top level as the one where this file lies
-  # If the rest of the files follow the structure of the Github project, everything will work
+  # If the rest of the files follow the structure of the Github repository, everything will work
+  # (Simply download the entire repository to any location on your computer)
 
@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC was assessed using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control was assessed using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression were assessed using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
-Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently have a higher workload.
+Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
+Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
 The Covid-19 items can be found in the **Supplementary Material**.
@@
 The latent factor MBI was computed using the three subscales as indicators.
-For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
-The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.
+For the demand-resource-ratios, we used three items from the work satisfaction scale each.
+The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
 
@@
   covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
-  dth <- 6 - dth
-  dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
-  dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
-  drf <- 6 - drf
-  drf <- drf -3                                       # Recode all from 1-5 to to -2-+2
+  # The following recoding is opposite to what is described in the methods section of the paper, which
+  # is due to the fact that the questionnaire is originally coded as 1 (false) to 5 (true), but it was
+  # coded as 1 (true) to 5 (false) in the SoSciSurvey of the present study.
+  dth <- 6 - dth                                      # Recode all from 1-5 to 5-1
+  dth <- dth - 3                                      # Recode all from 1-5 to -2-+2
+  dtl <- dtl - 3                                      # Recode all from 1-5 to -2-+2
+  drf <- 6 - drf                                      # Recode all from 1-5 to 5-1
+  drf <- drf -3                                       # Recode all from 1-5 to -2-+2
 
@@
 
-  # Remove participant 161
-  score_data <- score_data[score_data$mbi < 100, ]
+  # Remove participant 161 in a second version of the data frame (for the supplementary material analysis)
+  score_data_no_outlier <- score_data[score_data$mbi < 100, ]
 
@@
   # structural model
-    DTH ~ NFC
-    DTL ~ NFC
-    DRF ~ NFC
-    RPE ~ NFC + DTH + DTL + DRF'
+    DTH ~ a1 * NFC
+    DTL ~ a2 * NFC
+    DRF ~ a3 * NFC
+    RPE ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
 

### 2021-09-13 Manuscript/Manuscript.Rmd
changed layout of correlation table to asterisks

@@
     corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA
+
     # replace p-values with asterisks depending on significance level
     corr_pvalues <- ifelse(is.na(corr_pvalues), "", ifelse(corr_pvalues < .001, "***", ifelse(corr_pvalues < .01, "**", ifelse(corr_pvalues < .05, "*", ""))))
-    # create three arrays with logical indicators of the significance levels
-    corr_threestars <- corr_pvalues %>%
-      as_tibble() %>%
-      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "***", TRUE, FALSE)))
-    corr_twostars <- corr_pvalues %>%
-      as_tibble() %>%
-      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "**", TRUE, FALSE)))
-    corr_onestar <- corr_pvalues %>%
-      as_tibble() %>%
-      mutate(across(.cols = everything(),.fns = ~ ifelse(.x == "*", TRUE, FALSE)))
+
+    # convert to matrix for the paste()-function
+    corr_no_drr <- as.matrix(corr_no_drr)
+    corr_pvalues <- as.matrix(corr_pvalues)
+
+    # paste correlations and asterisks together
+    correlations <- matrix(paste(corr_no_drr, corr_pvalues, sep = ""),
+                           nrow = nrow(corr_no_drr), dimnames = dimnames(corr_no_drr))
 
@@
   desc_table <-
-  kbl(corr_no_drr,
+  kbl(correlations,
       booktabs = T, # no vertical lines
       escape = F, # correctly print special characters
-      align = rep("r",11)) %>% # right aligns the text in every column except for the first
+      align = rep("l",11)) %>% # right aligns the text in every column except for the first
     kable_styling(latex_options = c("striped", "scale_down")) %>%
-    column_spec(2, italic = corr_onestar$mbi|corr_twostars$mbi, bold = corr_threestars$mbi|corr_twostars$mbi) %>%
-    column_spec(3, italic = corr_onestar$mbi_ee|corr_twostars$mbi_ee, bold = corr_threestars$mbi_ee|corr_twostars$mbi_ee) %>%
-    column_spec(4, italic = corr_onestar$mbi_dp|corr_twostars$mbi_dp, bold = corr_threestars$mbi_dp|corr_twostars$mbi_dp) %>%
-    column_spec(5, italic = corr_onestar$mbi_rpe|corr_twostars$mbi_rpe, bold = corr_threestars$mbi_rpe|corr_twostars$mbi_rpe) %>%
-    column_spec(6, italic = corr_onestar$erq|corr_twostars$erq, bold = corr_threestars$erq|corr_twostars$erq) %>%
-    column_spec(7, italic = corr_onestar$erq_supp|corr_twostars$erq_supp, bold = corr_threestars$erq_supp|corr_twostars$erq_supp) %>%
-    column_spec(8, italic = corr_onestar$erq_reap|corr_twostars$erq_reap, bold = corr_threestars$erq_reap|corr_twostars$erq_reap) %>%
-    column_spec(9, italic = corr_onestar$scs|corr_twostars$scs, bold = corr_threestars$scs|corr_twostars$scs) %>%
-    column_spec(10, italic = corr_onestar$ncs|corr_twostars$ncs, bold = corr_threestars$ncs|corr_twostars$ncs) %>%
-    column_spec(11, italic = corr_onestar$covb|corr_twostars$covb, bold = corr_threestars$covb|corr_twostars$covb) %>%
     footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden.
 \\\\textit{N} = 179.
-Italics indicate \\\\textit{p} < .05, italics and bold indicate \\\\textit{p} < .01, bold indicates \\\\textit{p} < .001.
+* \\\\textit{p} < .05.
+** \\\\textit{p} < .01.
+*** \\\\textit{p} < .001.
 Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",

### 2021-09-13 Manuscript/Manuscript.Rmd
updated style of mediation plots

@@
                        layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
-                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
-                       edge.label.cex = 1, # size specifications
+                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edge.label.cex = 1, esize = 2, # size specifications
                        fade = FALSE, # do not make insignificant associations invisible
                        residuals = FALSE, # do not plot residuals
-                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
+                       edge.label.color = "black", posCol = "black", negCol = "black"
 )
@@
                        layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
-                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
-                       edge.label.cex = 1, # size specifications
+                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edge.label.cex = 1, esize = 2, # size specifications
                        fade = FALSE, # do not make insignificant associations invisible
@@
                        exoCov = FALSE, # do not plot covariance between exogenous variables
-                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
+                       edge.label.color = "black", posCol = "black", negCol = "black"
 )

### 2021-09-13 Manuscript/Manuscript.Rmd
updated demand-resource-model plot

@@
                         residuals = FALSE, fade = FALSE,
-                        edge.label.cex = 1, # size of the parameters
-                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
-                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
   )

### 2021-09-13 Manuscript/Manuscript.Rmd
updated all plots to have asterisks

--- 2021-09-13 Manuscript/Manuscript.Rmd
@@
 
+  # create an array of standardized parameters and an array of significances
+
+  fit_param <- fit_summ$PE$std.all[1:7]
+  fit_sign <- fit_summ$PE$pvalue[1:7]
+
+  # replace p-values with asterisks depending on significance level
+
+  fit_sign <- ifelse(fit_sign < .001, "***", ifelse(fit_sign < .01, "**", ifelse(fit_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit_param <- paste(format(round(fit_param, digits = 2), nsmall = 2), fit_sign, sep = "")
+
   # Make a path diagram to visualize the results
@@
                        layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
-                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
-                       edge.label.cex = 1, # size specifications
+                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
+                       edge.label.cex = 1, esize = 2, # size specifications
                        fade = FALSE, # do not make insignificant associations invisible
                        residuals = FALSE, # do not plot residuals
-                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
+                       edge.label.color = "black", posCol = "black", negCol = "black"
 )
@@
 
+  # create an array of standardized parameters and an array of significances
+
+  fityears_param <- fityears_summ$PE$std.all[1:8]
+  fityears_sign <- fityears_summ$PE$pvalue[1:8]
+
+  # replace p-values with asterisks depending on significance level
+
+  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")
+
   # Make a path diagram to visualize the results
@@
                        layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
-                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
-                       edge.label.cex = 1, # size specifications
+                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edge.label.cex = 1, esize = 2, # size specifications
+                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
                        fade = FALSE, # do not make insignificant associations invisible
@@
 
+  # create an array of standardized parameters and an array of significances
+
+  fit2_param <- fit2_summ$PE$std.all[1:23]
+  fit2_sign <- c(rep(1,16), fit2_summ$PE$pvalue[17:23])
+
+  # replace p-values with asterisks depending on significance level
+
+  fit2_sign <- ifelse(fit2_sign < .001, "***", ifelse(fit2_sign < .01, "**", ifelse(fit2_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit2_param <- paste(format(round(fit2_param, digits = 2), nsmall = 2), fit2_sign, sep = "")
+
   # Visualize the results
@@
                         residuals = FALSE, fade = FALSE,
-                        edge.label.cex = 1, # size of the parameters
-                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
-                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
+                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
   )

### 2021-09-13 Manuscript/Manuscript.Rmd
changed correlation table to also display DRRs

@@
 
-    # create a vector of consistencies to be used as the diagonal in a table later
-    consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
-                          format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
-    # paste together to create the output "alpha(omega)"
-    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
-
 ```
@@
 
-    # correlate variables, including the demand resource ratios
-    corr_with_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+    # correlate variables
+    correlations <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                     "scs","ncs","dth","dtl","drf","covb")],
-                                       type = "spearman",
-                                       use = "lower",
-                                       replace_diagonal = TRUE,
-                                       replacement = "")
-
-    # correlate variables without demand resource ratios (for table in manuscript)
-    corr_no_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                    "scs","ncs","covb")],
                                        type = "spearman",
@@
 
+    # reorder the columns of the consistencies data frame to match the correlation columns
+    consist_diag <- consistencies[c(colnames(correlations))]
+
+    # create a vector of consistencies to be used as the diagonal in a table later
+    consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+                          format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
+
+    # paste together to create the output "alpha(omega)"
+    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
+
     # add previously assembled diagonal with alpha and omega values
-    diag(corr_no_drr) <- consist_diag
+    diag(correlations) <- consist_diag
 
     # set row and column names for better table printing
-    row.names(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
-    colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
+    row.names(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")
+    colnames(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")
 
@@
     corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                        "scs","ncs","covb")]), type = "spearman")$P
+                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
     # replace upper triangle with NA
@@
     # convert to matrix for the paste()-function
-    corr_no_drr <- as.matrix(corr_no_drr)
+    correlations <- as.matrix(correlations)
     corr_pvalues <- as.matrix(corr_pvalues)
@@
     # paste correlations and asterisks together
-    correlations <- matrix(paste(corr_no_drr, corr_pvalues, sep = ""),
-                           nrow = nrow(corr_no_drr), dimnames = dimnames(corr_no_drr))
+    correlations <- matrix(paste(correlations, corr_pvalues, sep = ""),
+                           nrow = nrow(correlations), dimnames = dimnames(correlations))
 
@@
 # Results
+
+During visual inspection of correlation plots we noticed an unexpected outlier with very high MBI scores and very low NFC scores.
+A Q-Q-plot contrasting Mahalanobis *D^2^* against expected Chi Square values confirmed the outlier.
+To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the **Supplementary Material**.
 
@@
     footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden.
-\\\\textit{N} = 179.
+\\\\textit{N} = 180.
 * \\\\textit{p} < .05.

### 2021-09-13 Manuscript/Manuscript.Rmd
added table for metric descriptives

@@
 
-    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","covb")],
+    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")],
                        mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")
@@
 
-    desc_met <- data.frame(value = c("mean","sd","skewness","kurtosis","normality"),
-                           mbi = rep(0,5),
-                           mbi_ee = rep(0,5), mbi_dp = rep(0,5), mbi_rpe = rep(0,5),
-                           erq = rep(0,5),
-                           erq_supp = rep(0,5), erq_reap = rep(0,5),
-                           scs = rep(0,5),
-                           ncs = rep(0,5),
-                           covb = rep(0,5))
-
-    desc_met[1,2:ncol(desc_met)] <- isnorm_test$Descriptives$Mean
-    desc_met[2,2:ncol(desc_met)] <- isnorm_test$Descriptives$Std.Dev
-    desc_met[3,2:ncol(desc_met)] <- isnorm_test$Descriptives$Skew
-    desc_met[4,2:ncol(desc_met)] <- isnorm_test$Descriptives$Kurtosis
-    desc_met[5,2:ncol(desc_met)] <- isnorm_test$univariateNormality$Normality
+    desc_met <- data.frame(Variable = c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV"),
+                           Minimum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], min),
+                           Maximum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], max),
+                           Mean = isnorm_test$Descriptives$Mean,
+                           SD = isnorm_test$Descriptives$Std.Dev,
+                           Normality = isnorm_test$univariateNormality$Normality,
+                           Skewness = isnorm_test$Descriptives$Skew,
+                           Kurtosis = isnorm_test$Descriptives$Kurtosis)
+    # Drop the row names
+
+    rownames(desc_met) <- NULL
+
+    # Replace the capital YESes and NOs with small ones
+
+    desc_met$Normality[grep("NO", desc_met$Normality)] <- "No"
+    desc_met$Normality[grep("YES", desc_met$Normality)] <- "Yes"
+
+    # Round the values
+
+    desc_met[ ,c("Mean","SD","Skewness","Kurtosis")] <- round(desc_met[ ,c("Mean","SD","Skewness","Kurtosis")], digits = 2)
+
+    # Put the information in a table
+
+    met_table <-
+      kbl(desc_met,
+      booktabs = T, # no vertical lines
+      escape = F, # correctly print special characters
+      align = rep("r",8)) %>% # right aligns the text in every column except for the first
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation.
+\\\\textit{N} = 180.",
+             escape = F, # correctly print special characters
+             threeparttable = T) # line breaks in the footnote
 
@@
       escape = F, # correctly print special characters
-      align = rep("l",11)) %>% # right aligns the text in every column except for the first
+      align = rep("l",14)) %>% # right aligns the text in every column except for the first
     kable_styling(latex_options = c("striped", "scale_down")) %>%
-    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden.
+    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
 \\\\textit{N} = 180.
@@
              escape = F, # correctly print special characters
-             threeparttable = T) # line breaks in the footnote
-
-```
-
+             threeparttable = T) %>% # line breaks in the footnote
+  kableExtra::landscape() # make the table horizontal
+
+```
+
+Correlations and internal consistencies are displayed in **Table 1**.
 `r desc_table`

### 2021-09-13 Manuscript/Manuscript.Rmd
added results section text

@@
       escape = F, # correctly print special characters
-      align = rep("r",8)) %>% # right aligns the text in every column except for the first
+      align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
     kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
 To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the **Supplementary Material**.
+Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
+Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Roesseel2012].
 
@@
 
-Correlations and internal consistencies are displayed in **Table 1**.
+Correlations and internal consistencies are displayed in **Table 2**.
+Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha values of the three demand-resource-ratios can be considered *acceptable*.
+Even though these cut-offs have been criticized for being both arbitrary and insensitive to violations of internal consistency [@Dunn2014; @Taber2018], the more robust MacDonald's Omega [@Dunn2014] actually indicates *acceptable* to *good* internal consistency.
+
 `r desc_table`

### 2021-09-14 Manuscript/Manuscript.Rmd
changed typo
added text to methods and results

@@
 #install.packages("semPlot")    # plotting path models
+#install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))
 
@@
 library(qgraph)
+library(apa)                    # from the remotes package
 
@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *lavaan* [@Rosseel2012] and *psych* [@Revelle2021] for all our analyses.
+Data were checked for multivariate normality using Mardia's coefficient.
+To account for non-linear relationships, correlations were computed using Spearman's rank coefficient rather than Pearson's product moment correlation.
+Internal consistencies were assessed with Cronbach's Alpha and MacDonald's Omega.
+Since Cronbach's Alpha has been criticized for being insensitive to violations of internal consistency [@Dunn2014; @Taber2018], the additional computation of MacDonald's Omega has the purpose of ensuring a more reliable estimation.
 
@@
 Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
+NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
+Following Grass et al. [-@Grass2018], the results of the model were appraised by using $N$ = 2,000 bootstrap samples for confidence intervals.
+Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model, the Comparative Fit Index (CFI), which compares the fit to the baseline model, the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix, and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account.
 
@@
 
-  remove(ncs_load,ncs_pca) # remove unnecessary objects
-
   # Add parcelling result to the key list
@@
   # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
-  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,6,10,11,16,20,24,28)], lower = list(continuous = my_fn))
+  multicorrplot <- ggpairs(score_data[,c("years","mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+                                         "scs","ncs","dth","dtl","drf","covb")], lower = list(continuous = my_fn))
 
@@
     # set row and column names for better table printing
-    row.names(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")
-    colnames(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")
+    row.names(correlations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
+                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
+    colnames(correlations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
 
@@
 To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the **Supplementary Material**.
-Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
-Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Roesseel2012].
 
@@
 
+## Descriptive statistics
+
+Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
+Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Roesseel2012].
 Correlations and internal consistencies are displayed in **Table 2**.
-Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha values of the three demand-resource-ratios can be considered *acceptable*.
-Even though these cut-offs have been criticized for being both arbitrary and insensitive to violations of internal consistency [@Dunn2014; @Taber2018], the more robust MacDonald's Omega [@Dunn2014] actually indicates *acceptable* to *good* internal consistency.
+For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
+Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
+The more robust MacDonald's Omega [@Dunn2014] does not deviate much from Cronbach's Alpha and indicates *acceptable* to *good* internal consistency.
+As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
+Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman"), format = "rmarkdown")`).
+The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.
 
@@
 ```
+
+## Replication of Grass et al. (2018)
+
+[Describe mediation results here.]
 
@@
 
+[Describe mediation with years-teaching-variable here]
+
 ```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
@@
 
+## Demand-Resource Model
+
+Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout in a strictly confirmatory approach.
+The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
+The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
+Standardized path coefficients of the demand-resource model are illustrated in **Figure 3**.
+Even though all variables were correlated
+
 ```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

### 2021-09-16 Manuscript/Manuscript.Rmd
changed sentence in methods

@@
 ### *Structural equation model*
-Items were reverse coded according to the scale manuals.
+All items, apart for those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
 The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al.
@@
 The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
+Model parameters were estimated using the maximum likelihood method with robust standard errors.
+Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.
 

### 2021-09-20 Manuscript/Manuscript.Rmd
fixed typo
added results about model 2

@@
 ### *Structural equation model*
-All items, apart for those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
+All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
 The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al.
@@
 Standardized path coefficients of the demand-resource model are illustrated in **Figure 3**.
-Even though all variables were correlated
+The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) does not indicate good model fit.
+However, since it is in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might be due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which is violated here.
+This also holds true for the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% CI [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]
 

### 2021-09-23 Manuscript/Manuscript.Rmd
added exploratory analysis for Covid burden

@@
 #install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))
+#install.packages("ppcor")      # for partial correlations
 
@@
 library(apa)                    # from the remotes package
+library(ppcor)
 
@@
 
+```{r exploring_badfit, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Use function from http://www.sthda.com/english/wiki/correlation-matrix-a-
+  # quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-
+  # using-r-software#a-simple-function-to-format-the-correlation-matrix
+  # accessed on September 23rd 2021
+
+  flattenCorrMatrix <- function(cormat, pmat) {
+    ut <- upper.tri(cormat)
+    data.frame(
+      row = rownames(cormat)[row(cormat)[ut]],
+      column = rownames(cormat)[col(cormat)[ut]],
+      cor  =(cormat)[ut],
+      p = pmat[ut]
+      )
+  }
+
+  # Compute data frame of partial correlations
+
+  partialcorr <- flattenCorrMatrix(pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
+                                                     "erq","erq_supp","erq_reap","scs","ncs",
+                                                     "dth","dtl","drf","covb")], method = "spearman")$estimate,
+                                  pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
+                                                    "erq","erq_supp","erq_reap","scs","ncs",
+                                                    "dth","dtl","drf","covb")], method = "spearman")$p.value)
+  # Add easy-to-read significance column
+
+  partialcorr$sign <- ifelse(partialcorr$p < 0.05, "sign", "ns")
+
+```
+
 ```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
@@
     DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
     DRF =~ drf1 + drf2 + drf3
-    MBI =~ mbi_ee + mbi_dp + mbi_rpe
+    MBI_EE =~ mbi_ee
+    MBI_RPE =~ mbi_rpe
+    SCS =~ scs
     COVB =~ covb
+    YEARS =~ years
 
   # structural model
-    DTH ~ NFC
-    DTL ~ NFC
-    DRF ~ NFC
-    COVB ~ DTH
-    MBI ~ NFC + DTH + DTL + DRF + COVB'
+    COVB ~ YEARS
+    SCS ~ YEARS
+    NFC ~ SCS
+    DTH ~ COVB + DRF
+    DRF ~ SCS + NFC
+    MBI_EE ~ DTH
+    MBI_RPE ~ DRF'
 

### 2021-09-24 Manuscript/Manuscript.Rmd
added plot for explor2, but it is a mess

@@
 
-  # Correlations show that Covid burden is positively associated with MBI and
-  # and MBI_EE, and negatively associated with DTH. We will therefore include
-  # Covid burden as a mediator between DTH and MBI.
-
   explor2_model <- '
@@
     SCS ~ YEARS
-    NFC ~ SCS
-    DTH ~ COVB + DRF
+    NFC ~~ SCS
+    NFC ~~ COVB
+    DTH ~ COVB + SCS + NFC
     DRF ~ SCS + NFC
-    MBI_EE ~ DTH
-    MBI_RPE ~ DRF'
+    DTH ~~ DRF
+    MBI_EE ~ DTH + COVB
+    MBI_RPE ~ DRF
+
+    dth1 ~~ dth2
+    dth1 ~~ dth3
+    dth2 ~~ dth3
+
+    drf1 ~~ drf2
+    drf1 ~~ drf3
+    drf2 ~~ drf3
+'
 
@@
 ```
+```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # create an array of standardized parameters and an array of significances
+
+  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:10,16:32)]
+  fit_explor2_sign <- c(rep(1,10), fit_explor2_summ$PE$pvalue[16:32])
+
+  # replace p-values with asterisks depending on significance level
+
+  fit_explor2_sign <- ifelse(fit_explor2_sign < .001, "***", ifelse(fit_explor2_sign < .01, "**", ifelse(fit_explor2_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit_explor2_param <- paste(format(round(fit_explor2_param, digits = 2), nsmall = 2), fit_explor2_sign, sep = "")
+
+  # Visualize the results
+
+  fit_explor2_plot <- semPaths(fit_explor2, what = "std",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
+                                       "dth1","dth2","dth3","drf1","drf2","drf3",
+                                       "YEARS",
+                                       "SCS",
+                                       "COVB",
+                                       "NFC",
+                                       "DRF","DTH",
+                                       "MBI_EE","MBI_RPE"),
+                        layout = matrix(data = c(-0.7,-0.56,-0.44,-0.3,
+                                                 0.3,0.5,0.7,0.3,0.5,0.7,
+                                                 -1,
+                                                 -0.4,
+                                                 -0.4,
+                                                 -0.4,
+                                                 0.4,0.4,
+                                                 1,1,
+                                                 1,1,1,1,
+                                                 1,1,1,-1,-1,-1,
+                                                 -0.3,
+                                                 -1,
+                                                 -0.3,
+                                                 0.5,
+                                                 0.5,-0.5,
+                                                 0.5,-0.5),
+                                        nrow = 18, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edgeLabels = fit_explor2_param, # specify the edge labels with the asterisks as previously created
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
+  )
+```
 

### 2021-10-25 Manuscript/Manuscript.Rmd
created table for mediation results

@@
 
-```{r consistency, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
+```{r consistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
       escape = F, # correctly print special characters
-      align = rep("l",14)) %>% # right aligns the text in every column except for the first
+      align = rep("l",14)) %>% # left aligns the text in every column
     kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
 
+```{r objective1_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
+                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
+                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
+                                   "Total Effect"),
+                          "Effect" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "z-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "p-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  fit_table[2:ncol(fit_table)] <- format(round(fit_table[2:ncol(fit_table)], digits = 3), nsmall = 2)
+
+  replication_table <-
+    kbl(fit_table,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",6))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "RPE = Reduced personal efficacy subscale of the Maslach Burnout Inventory.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+
+```
+
 ```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-[Describe mediation results here.]
+In order to replicate findings by Grass et al.
+[-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
 

### 2021-10-25 Manuscript/Manuscript.Rmd
added results description for mediation

@@
 All teachers were eligible, no payment was issued.
-Of the $N=$ 278 participants, who started filling out the online survey, $N=$ `r nrow(data)` (`r round((table(data$gender)[1]/nrow(data))*100, digits = 1)`% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
+Of the $N=$ 278 participants, who started filling out the online survey, $N =$ `r nrow(data)` (`r round((table(data$gender)[1]/nrow(data))*100, digits = 1)`% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
 All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "RPE = Reduced personal efficacy subscale of the Maslach Burnout Inventory.",
+    footnote(general = "CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
              escape = F, # correctly print special characters
@@
 [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
+The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
+Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fit_summ$FIT[["rmsea.pvalue"]], digits = 2)`,), suggests good fit of the proposed model throughout all indices.
+standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
 

### 2021-10-25 Manuscript/Manuscript.Rmd
added more mediation results description

@@
 standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
+We could replicate a positive association of NFC and self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
+Instead, we found a significant indirect effect of NFC on reduced personal efficacy via self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
+[-@Grass2018].
 

### 2021-10-26 Manuscript/Manuscript.Rmd
added column to table

@@
                                    "Total Effect"),
-                          "Effect" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "B" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                           "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
@@
                           "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "\beta" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                           check.names = FALSE)
@@
         escape = F, # correctly print special characters)
-        align = c("l",rep("r",6))) %>% # right aligns the text in every numerical column
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
     kable_styling(latex_options = c("striped")) %>%
@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
+    footnote(general = "B = unstandardized regression coefficient, \beta = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
              escape = F, # correctly print special characters

### 2021-10-26 Manuscript/Manuscript.Rmd
corrected cursive characters in table

--- 2021-10-25 Manuscript/Manuscript.Rmd
@@
   kbl(correlations,
-      booktabs = T, # no vertical lines
-      escape = F, # correctly print special characters
+      booktabs = TRUE, # no vertical lines
+      escape = FALSE, # correctly print special characters
       align = rep("l",14)) %>% # left aligns the text in every column
@@
 Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
-             escape = F, # correctly print special characters
-             threeparttable = T) %>% # line breaks in the footnote
+             escape = FALSE, # correctly print special characters
+             threeparttable = TRUE) %>% # line breaks in the footnote
   kableExtra::landscape() # make the table horizontal
@@
                                    "Total Effect"),
-                          "Effect" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "z-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "p-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                           "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                           "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                           check.names = FALSE)
@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
           estimates = TRUE, ci = TRUE)
+```
+
+```{r objective1years_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  fityears_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
+                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
+                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
+                                   "Total Effect"),
+                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  fityears_table[2:ncol(fityears_table)] <- format(round(fityears_table[2:ncol(fityears_table)], digits = 3), nsmall = 2)
+
+  replicationyears_table <-
+    kbl(fityears_table,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 9, 11) %>%
+    pack_rows("Total Effect", 12, 12) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
 ```

### 2021-10-26 Manuscript/Manuscript.Rmd
added results description of Years Spent Teaching model

@@
 
-### *Exploratory analysis*
+### *Exploratory analyses*
 We preregistered two exploratory analyses.
@@
 Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fit_summ$FIT[["rmsea.pvalue"]], digits = 2)`,), suggests good fit of the proposed model throughout all indices.
-standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
-We could replicate a positive association of NFC and self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
-However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Instead, we found a significant indirect effect of NFC on reduced personal efficacy via self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
-Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
+Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
+We could replicate a positive association of NFC and self control ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
+Instead, we found a significant indirect effect of NFC on reduced personal efficacy via self control ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
 [-@Grass2018].
@@
                                    "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
-                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
+                                   "NFC and years spent teaching $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                    "Total Effect"),
@@
 
-[Describe mediation with years-teaching-variable here]
+Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
+Since grade was not assessed in this sample, and age was assessed as a categorical variable, we will instead incorporate how many years each participant had spent teaching at the point of assessment.
+As it was not preregistered, this is an exploratory analysis.
+Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fityears_summ$FIT[["rmsea.pvalue"]], digits = 2)`,) suggest good fit of the proposed model throughout all indices.
+Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
+The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
+However, because of the positive association of years spent teaching and self control ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
+Therefore, the total effect also increased slightly, compared to the first model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
 

### 2021-10-26 Manuscript/Manuscript.Rmd
indentation

@@
 ```
+
 ```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}

### 2021-10-27 Manuscript/Manuscript.Rmd
created plot for exploratory analysis

@@
 
+    MBI_EE ~~ MBI_RPE
+    NFC ~~ YEARS
+
     dth1 ~~ dth2
@@
 
-  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:10,16:32)]
-  fit_explor2_sign <- c(rep(1,10), fit_explor2_summ$PE$pvalue[16:32])
+  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:30)]
+  fit_explor2_sign <- c(rep(1,15), fit_explor2_summ$PE$pvalue[16:30])
 
@@
                                        "dth1","dth2","dth3","drf1","drf2","drf3",
-                                       "YEARS",
+                                       "mbi_ee", "mbi_rpe",
+                                       "scs", "covb", "years",
+                                       "NFC",
+                                       "DTH","DRF",
+                                       "MBI_EE","MBI_RPE",
                                        "SCS",
                                        "COVB",
-                                       "NFC",
-                                       "DRF","DTH",
-                                       "MBI_EE","MBI_RPE"),
-                        layout = matrix(data = c(-0.7,-0.56,-0.44,-0.3,
+                                       "YEARS"),
+                        layout = matrix(data = c(-0.6,-0.4,-0.2,0,
                                                  0.3,0.5,0.7,0.3,0.5,0.7,
+                                                 1,1,
+                                                 -0.5,-0.2,-1,
+                                                 -0.2,
+                                                 0.5,0.5,
+                                                 1,1,
+                                                 -0.5,
+                                                 -0.2,
                                                  -1,
+                                                 1,1,1,1,
+                                                 -1,-1,-1,1,1,1,
+                                                 -1,1,
+                                                 -1,-1,-1,
+                                                 0.5,
+                                                 -0.5,0.5,
+                                                 0,0.5,
+                                                 0.1,
                                                  -0.4,
-                                                 -0.4,
-                                                 -0.4,
-                                                 0.4,0.4,
-                                                 1,1,
-                                                 1,1,1,1,
-                                                 1,1,1,-1,-1,-1,
-                                                 -0.3,
-                                                 -1,
-                                                 -0.3,
-                                                 0.5,
-                                                 0.5,-0.5,
-                                                 0.5,-0.5),
-                                        nrow = 18, ncol = 2),
+                                                 0.1),
+                                        nrow = 23, ncol = 2),
                         residuals = FALSE, fade = FALSE,

### 2021-10-27 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
+## Exploratory analyses
+
+The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
+
 ```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
@@
                                        "DTH","DRF",
-                                       "MBI_EE","MBI_RPE",
+                                       "MBI EE","MBI RPE",
                                        "SCS",

### 2021-10-28 Manuscript/Manuscript.Rmd
updated CI results reporting

@@
 The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
-Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fit_summ$FIT[["rmsea.pvalue"]], digits = 2)`,), suggests good fit of the proposed model throughout all indices.
+Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggests good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
@@
 As it was not preregistered, this is an exploratory analysis.
-Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fityears_summ$FIT[["rmsea.pvalue"]], digits = 2)`,) suggest good fit of the proposed model throughout all indices.
+Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggest good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
@@
 
-Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout in a strictly confirmatory approach.
+Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
 The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
 The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
-Standardized path coefficients of the demand-resource model are illustrated in **Figure 3**.
+Standardized path coefficients of the demand-resource model are illustrated in **Figure**.
 The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) does not indicate good model fit.
 However, since it is in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might be due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which is violated here.
-This also holds true for the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% CI [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]
+This also holds true for the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]
 

### 2021-10-28 Manuscript/Manuscript.Rmd
updated tense

@@
 Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
-The more robust MacDonald's Omega [@Dunn2014] does not deviate much from Cronbach's Alpha and indicates *acceptable* to *good* internal consistency.
+The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
 As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
@@
 The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
-Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggests good fit of the proposed model throughout all indices.
+Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
@@
 Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
-Since grade was not assessed in this sample, and age was assessed as a categorical variable, we will instead incorporate how many years each participant had spent teaching at the point of assessment.
-As it was not preregistered, this is an exploratory analysis.
-Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggest good fit of the proposed model throughout all indices.
+Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
+As it was not preregistered, this was an exploratory analysis.
+Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
@@
 Standardized path coefficients of the demand-resource model are illustrated in **Figure**.
-The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) does not indicate good model fit.
-However, since it is in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might be due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which is violated here.
-This also holds true for the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]
+The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
+However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
+This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
+Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
+NFC showed no direct association with the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
 

### 2021-10-28 Manuscript/Manuscript.Rmd
completed description of DRR results

@@
 Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
+The latent variable DTL was neither related to NFC ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
 

### 2021-10-28 Manuscript/Manuscript.Rmd
added table for DRR model

@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
     pack_rows("Total Effect", 12, 12) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
   )
+```
+```{r fit2_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  fit2_table <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
+                                      "DTH $\\rightarrow$ MBI", "DTL $\\rightarrow$ MBI", "DRF $\\rightarrow$ MBI",
+                                      "NFC $\\rightarrow$ MBI via DTH", "NFC $\\rightarrow$ MBI via DTL", "NFC $\\rightarrow$ MBI via DRF",
+                                      "Total Effect"),
+                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  fit2_table[2:ncol(fit2_table)] <- format(round(fit2_table[2:ncol(fit2_table)], digits = 3), nsmall = 2)
+
+  drrmodel_table <-
+    kbl(fit2_table,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
 ```

### 2021-10-28 Manuscript/Manuscript.Rmd
began writing DRR2 model results

@@
 The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
-Standardized path coefficients of the demand-resource model are illustrated in **Figure**.
+Standardized path coefficients of the demand-resource model are illustrated in **Figure**, total, direct, and indirect effects are listed in **Table**.
 The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
@@
 The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
+The total, direct, and indirect effects are listed in **Supplementary Table**.
+Similar to the previous model, this model's indices did not indicate good fit with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
+NFC showed no direct association with reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
+And again, NFC was associated with lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
+The latent variable DTL was neither related to NFC ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
 

### 2021-10-29 Manuscript/Manuscript.Rmd
finished results of exploratory1

@@
 The total, direct, and indirect effects are listed in **Supplementary Table**.
-Similar to the previous model, this model's indices did not indicate good fit with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
+Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
 NFC showed no direct association with reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
 And again, NFC was associated with lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
-Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
 The latent variable DTL was neither related to NFC ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).

### 2021-10-29 Manuscript/Manuscript.Rmd
updated explor2 model and wrote results

@@
   # structural model
-    COVB ~ YEARS
-    SCS ~ YEARS
+    COVB ~ yc * YEARS
+    SCS ~ ys * YEARS
     NFC ~~ SCS
     NFC ~~ COVB
-    DTH ~ COVB + SCS + NFC
-    DRF ~ SCS + NFC
+    DTH ~ cdth * COVB + sdth * SCS + ndth* NFC
+    DRF ~ sdrf * SCS + ndrf * NFC
     DTH ~~ DRF
-    MBI_EE ~ DTH + COVB
-    MBI_RPE ~ DRF
+    MBI_EE ~ dthe * DTH + ce * COVB
+    MBI_RPE ~ drfr * DRF
 
@@
     drf2 ~~ drf3
+
+  # Indirect effects
+    Indirect1 := (ndrf * drfr) + (ys * sdrf * drfr)
+    Indirect2 := (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2
+
+  # total effect
+    Total := (ndrf * drfr) + (ys * sdrf * drfr) + (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)
 '
@@
 
+The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
+We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
+Then we modified the structure of the model in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
+The final model is illustrated in **Figure**, the total, direct, and indirect effects are listed in **Supplementary Table**.
+All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$`r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$`r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$`r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$`r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
+Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
+Years spent teaching was associated with higher self control ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
+NFC covaried with self control ($\sigma_{NFC,SCS}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 3)`) and Covid burden ($\sigma_{NFC,COVB}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 3)`), but not with years spent teaching ($p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "YEARS"], digits = 3)`).
+In turn, NFC was associated with higher DRF scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
+DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Covid burden was not associated with DRF or reduced personal efficacy.
+
 # Discussion

### 2021-11-01 Manuscript/Manuscript.Rmd
added figure for explor1

@@
           estimates = TRUE, ci = TRUE)
+```
+```{r exploratory1_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # create an array of standardized parameters and an array of significances
+
+  fit_explor1_param <- fit_explor1_summ$PE$std.all[1:21]
+  fit_explor1_sign <- c(rep(1,14), fit_explor1_summ$PE$pvalue[17:21])
+
+  # replace p-values with asterisks depending on significance level
+
+  fit_explor1_sign <- ifelse(fit_explor1_sign < .001, "***", ifelse(fit_explor1_sign < .01, "**", ifelse(fit_explor1_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit_explor1_param <- paste(format(round(fit_explor1_param, digits = 2), nsmall = 2), fit_explor1_sign, sep = "")
+
+  # Visualize the results
+
+  fit_explor1_plot <- semPaths(fit_explor1, what = "std",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","MBI"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 19, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
+  )
 ```

### 2021-11-01 Manuscript/Manuscript.Rmd
changed results description of replication

@@
 However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Instead, we found a significant indirect effect of NFC on reduced personal efficacy via self control ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
 Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.

### 2021-11-01 Manuscript/Manuscript.Rmd
added description of years spent teaching
added item translation of DRR items

@@
 The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
+The items can be translated as follows: 4) "There is too much pressure on me.", 8) "There is often too much being demanded of us at work.", 9) "I often feel tired and weary because of my work.", 12) "I can realize my ideas here.", 17) "I take pleasure in my work.", 22) "Does your place of work give you the opportunity to do what you do best?", 24) "Does your place of work give you enough opportunities to use your skills?", 26) "Are you happy with your promotion prospects?", and 27) "Are you happy with your position when comparing it to your skills?".
 Model parameters were estimated using the maximum likelihood method with robust standard errors.
@@
 Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
+We placed this variable as an independent variable influencing self control, as the latter was the only variable in the model that showed a partial correlation with years spent teaching.
 As it was not preregistered, this was an exploratory analysis.
@@
   fit_explor1_plot <- semPaths(fit_explor1, what = "std",
-                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","MBI"),
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
                         layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,

### 2021-11-01 Manuscript/Manuscript.Rmd
changed figure for explor2

@@
     DRF =~ drf1 + drf2 + drf3
-    MBI_EE =~ mbi_ee
-    MBI_RPE =~ mbi_rpe
-    SCS =~ scs
-    COVB =~ covb
-    YEARS =~ years
 
   # structural model
-    COVB ~ yc * YEARS
-    SCS ~ ys * YEARS
-    NFC ~~ SCS
-    NFC ~~ COVB
-    DTH ~ cdth * COVB + sdth * SCS + ndth* NFC
-    DRF ~ sdrf * SCS + ndrf * NFC
+    covb ~ yc * years
+    scs ~ ys * years
+    NFC ~~ scs
+    NFC ~~ covb
+    DTH ~ cdth * covb + sdth * scs + ndth* NFC
+    DRF ~ sdrf * scs + ndrf * NFC
     DTH ~~ DRF
-    MBI_EE ~ dthe * DTH + ce * COVB
-    MBI_RPE ~ drfr * DRF
-
-    MBI_EE ~~ MBI_RPE
-    NFC ~~ YEARS
+    mbi_ee ~ dthe * DTH + ce * covb
+    mbi_rpe ~ drfr * DRF
+
+    mbi_ee ~~ mbi_rpe
+    NFC ~~ years
 
@@
 
-  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:30)]
-  fit_explor2_sign <- c(rep(1,15), fit_explor2_summ$PE$pvalue[16:30])
+  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:25)]
+  fit_explor2_sign <- c(rep(1,10), fit_explor2_summ$PE$pvalue[11:25])
 
@@
                                nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
-                                       "dth1","dth2","dth3","drf1","drf2","drf3",
-                                       "mbi_ee", "mbi_rpe",
-                                       "scs", "covb", "years",
+                                              "COVB", "SCS",
+                                              "dth1","dth2","dth3",
+                                              "EE",
+                                              "drf1","drf2","drf3",
+                                              "RPE",
+                                              "YEARS",
                                               "NFC",
-                                       "DTH","DRF",
-                                       "MBI EE","MBI RPE",
-                                       "SCS",
-                                       "COVB",
-                                       "YEARS"),
+                                              "DTH","DRF"),
                         layout = matrix(data = c(-0.6,-0.4,-0.2,0,
-                                                 0.3,0.5,0.7,0.3,0.5,0.7,
-                                                 1,1,
-                                                 -0.5,-0.2,-1,
+                                                 -0.2,-0.5,
+                                                 0.3,0.5,0.7,
+                                                 1,
+                                                 0.3,0.5,0.7,
+                                                 1,
+                                                 -1,
                                                  -0.2,
                                                  0.5,0.5,
-                                                 1,1,
-                                                 -0.5,
-                                                 -0.2,
-                                                 -1,
                                                  1,1,1,1,
-                                                 -1,-1,-1,1,1,1,
-                                                 -1,1,
+                                                 -0.4,0.1,
                                                  -1,-1,-1,
+                                                 0,
+                                                 1,1,1,
                                                  0.5,
-                                                 -0.5,0.5,
-                                                 0,0.5,
                                                  0.1,
-                                                 -0.4,
-                                                 0.1),
-                                        nrow = 23, ncol = 2),
+                                                 0.5,
+                                                 -0.5,0.5),
+                                        nrow = 18, ncol = 2),
                         residuals = FALSE, fade = FALSE,

### 2021-11-01 Manuscript/Manuscript.Rmd
changed tense in introduction

@@
 Lackritz [-@Lackritz2004] found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
-Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced self-efficacy.
+Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced personal efficacy.
 
@@
 [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
-One goal of this paper is to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
-We expect NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.
-
-Furthermore, we would like to extend the analysis to other possible mediators.
-These mediators are motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
+One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
+We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.
+
+Furthermore, we extended the analysis to other possible mediators.
+These mediators were motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
 Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
@@
 These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery [@Salanova2006].
-We would therefore like to investigate whether the association of NFC and burnout is mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
-Using the same data as for the replication, we compute a structural equation model (SEM) to assess the influence of these mediators.
-Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expect NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
-And since burnout results from constant unpleasant activation by high demands, we expect it to be positively associated with DTH and negatively associated with DRF.
-However, we have no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
+We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
+Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
+Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
+And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with DTH and negatively associated with DRF.
+However, we had no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
 

### 2021-11-02 Manuscript/Manuscript.Rmd
added discussion text

@@
 However, we had no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
-
-*The Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021].*
+It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
 
@@
 
+The present study aimed to replicate findings of mediators between Need for Cognition and burnout in teachers, as well as to extend the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
+The questionnaire data had been acquired in the scope of a thesis on burnout in teachers.
+We could replicate a negative association of NFC and the burnout subscale reduced personal efficacy, but this relationship was mediated by self control, not by habitual reappraisal.
+Furthermore, the negative relationship between NFC and burnout was fully mediated by less excessive demands and a better fit of demands and resources, but this model did not have good fit.
+The exploratory model showed the same relationship, but *...*
+
 \newpage

### 2021-11-25 Manuscript/Manuscript.Rmd
tried knitting but there is a bug in line 892
fixed knitting bugs

@@
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
 abstract: |
@@
 [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
-The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
-Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
+The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
+Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
-We could replicate a positive association of NFC and self control ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
-However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
-Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
+We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
+Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
 [-@Grass2018].
@@
 As it was not preregistered, this was an exploratory analysis.
-Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
+Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI=$ `r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
 Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
 The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
-However, because of the positive association of years spent teaching and self control ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
-Therefore, the total effect also increased slightly, compared to the first model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
+However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
+Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
 
@@
 Standardized path coefficients of the demand-resource model are illustrated in **Figure**, total, direct, and indirect effects are listed in **Table**.
-The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
-However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
+The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
+However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
 This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
 Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
-NFC showed no direct association with the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
-Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
-The latent variable DTL was neither related to NFC ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
+NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
+The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
 
@@
 
-```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
+```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 The total, direct, and indirect effects are listed in **Supplementary Table**.
-Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
-NFC showed no direct association with reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
-And again, NFC was associated with lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
-The latent variable DTL was neither related to NFC ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
-
-```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
+Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
+NFC showed no direct association with reduced personal efficacy ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
+And again, NFC was associated with lower scores in the latent variable DTH ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
+The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
+
+```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 The final model is illustrated in **Figure**, the total, direct, and indirect effects are listed in **Supplementary Table**.
-All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$`r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$`r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$`r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$`r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
+All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
 Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
-Years spent teaching was associated with higher self control ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
-NFC covaried with self control ($\sigma_{NFC,SCS}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 3)`) and Covid burden ($\sigma_{NFC,COVB}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 3)`), but not with years spent teaching ($p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "YEARS"], digits = 3)`).
-In turn, NFC was associated with higher DRF scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
-DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
+NFC covaried with self control ($\sigma_{NFC,SCS}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 3)`) and Covid burden ($\sigma_{NFC,COVB}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "YEARS"], digits = 3)`).
+In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
+DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
 Covid burden was not associated with DRF or reduced personal efficacy.

### 2021-11-29 Manuscript/Manuscript.Rmd
fixed knitting bugs and renamed tables and plots

@@
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
-This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady 2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
+This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
 What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
@@
 
-```{r scores, echo=FALSE, message=FALSE, warning=FALSE}
+```{r scores, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-    met_table <-
+    Table1 <-
       kbl(desc_met,
@@
 
-```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  desc_table <-
+```{r correlations_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  Table2 <-
   kbl(correlations,
@@
 Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
-Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Roesseel2012].
+Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
+
+`r Table1`
+
 Correlations and internal consistencies are displayed in **Table 2**.
@@
 
-`r desc_table`
+`r Table2`
 
@@
 
-  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
+  Table3 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                    "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
@@
 
-  fit_table[2:ncol(fit_table)] <- format(round(fit_table[2:ncol(fit_table)], digits = 3), nsmall = 2)
+  Table3[2:ncol(Table3)] <- format(round(Table3[2:ncol(Table3)], digits = 3), nsmall = 2)
 
   replication_table <-
-    kbl(fit_table,
+    kbl(Table3,
         booktabs = T, # no vertical lines
@@
 
-  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
+  Figure1 <- semPaths(fit, what="std", # display the parameters on the arrows
                        nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
@@
 Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
-Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al.
+Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al.
 [-@Grass2018].
@@
 
-  fityears_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
+  Table4 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                    "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
@@
 
-  fityears_table[2:ncol(fityears_table)] <- format(round(fityears_table[2:ncol(fityears_table)], digits = 3), nsmall = 2)
+  Table4[2:ncol(Table4)] <- format(round(Table4[2:ncol(Table4)], digits = 3), nsmall = 2)
 
   replicationyears_table <-
-    kbl(fityears_table,
+    kbl(Table4,
         booktabs = T, # no vertical lines
@@
 
-  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
+  Figure2 <- semPaths(fityears, what="std", # display the parameters on the arrows
                        nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
@@
 
-  fit2_plot <- semPaths(fit2, what = "std",
+  Figure3 <- semPaths(fit2, what = "std",
                         nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
@@
                         edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
                         edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
@@
 ```
-```{r fit2_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+```{r objective2_table, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-  fit2_table <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
+  Table5 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
                                       "DTH $\\rightarrow$ MBI", "DTL $\\rightarrow$ MBI", "DRF $\\rightarrow$ MBI",
@@
 
-  fit2_table[2:ncol(fit2_table)] <- format(round(fit2_table[2:ncol(fit2_table)], digits = 3), nsmall = 2)
+  Table5[2:ncol(Table5)] <- format(round(Table5[2:ncol(Table5)], digits = 3), nsmall = 2)
 
   drrmodel_table <-
-    kbl(fit2_table,
+    kbl(Table5,
         booktabs = T, # no vertical lines
@@
 The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
-However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
+However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2012], which was violated here.
 This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
@@
 
-  fit_explor1_plot <- semPaths(fit_explor1, what = "std",
+  Figure4 <- semPaths(fit_explor1, what = "std",
                         nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
@@
                         edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
                         edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
@@
 
-  fit_explor2_plot <- semPaths(fit_explor2, what = "std",
+  Figure5 <- semPaths(fit_explor2, what = "std",
                                nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
@@
                         edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,rep(0.5,32)),
                         edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
@@
 Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
-NFC covaried with self control ($\sigma_{NFC,SCS}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 3)`) and Covid burden ($\sigma_{NFC,COVB}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "YEARS"], digits = 3)`).
+NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 3)`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"], digits = 3)`).
 In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.

### 2021-11-29 Manuscript/Manuscript.Rmd
added tables for explor1 and explor2

@@
 
-Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
+Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
 Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
@@
 
-Correlations and internal consistencies are displayed in **Table 2**.
+Correlations and internal consistencies are displayed in Table 2.
 For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
@@
 Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
-Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
+Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
 We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
@@
 [-@Grass2018].
+
+`r Table3`
 
@@
 Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI=$ `r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
-Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
+Standardized estimates are displayed in Figure 2, total, direct, and indirect effects are listed in Table 4.
 The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
@@
 Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
+
+`r Table4`
 
@@
 The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
-Standardized path coefficients of the demand-resource model are illustrated in **Figure**, total, direct, and indirect effects are listed in **Table**.
+Standardized path coefficients of the demand-resource model are illustrated in Figure 3, total, direct, and indirect effects are listed in Table 5.
 The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
@@
 The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
+
+`r Table5`
 
@@
 ```
-```{r exploratory1_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+```{r exploratory1_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-  Figure4 <- semPaths(fit_explor1, what = "std",
+  FigureS1 <- semPaths(fit_explor1, what = "std",
                         nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
@@
 
+```{r exploratory1_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  TableS1 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ RPE",
+                                      "DTH $\\rightarrow$ RPE", "DTL $\\rightarrow$ RPE", "DRF $\\rightarrow$ RPE",
+                                      "NFC $\\rightarrow$ RPE via DTH", "NFC $\\rightarrow$ RPE via DTL", "NFC $\\rightarrow$ RPE via DRF",
+                                      "Total Effect"),
+                          "$B$" = c(fit_explor1_summ$PE$est[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fit_explor1_summ$PE$se[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fit_explor1_summ$PE$z[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fit_explor1_summ$PE$ci.lower[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fit_explor1_summ$PE$ci.upper[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  TableS1[2:ncol(TableS1)] <- format(round(TableS1[2:ncol(TableS1)], digits = 3), nsmall = 2)
+
+  TableS1 <-
+    kbl(TableS1,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, RPE = Reduced Personal Efficacy subscale of the Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
 ## Exploratory analyses
@@
 The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
-The total, direct, and indirect effects are listed in **Supplementary Table**.
+The path coefficients are illustrated in Supplementary Figure S1, total, direct, and indirect effects are listed in **Supplementary Table**.
 Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
@@
 
-  Figure5 <- semPaths(fit_explor2, what = "std",
+  FigureS2 <- semPaths(fit_explor2, what = "std",
                                nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
@@
 
+```{r explor2_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  TableS2 <- data.frame("Path" = c("Years $\\rightarrow$ COVB", "Years $\\rightarrow$ SCS",
+                                   "COVB $\\rightarrow$ DTH", "SCS $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTH",
+                                   "SCS $\\rightarrow$ DRF", "NFC $\\rightarrow$ DRF",
+                                   "DTH $\\rightarrow$ EE", "COVB $\\rightarrow$ EE", "DRF $\\rightarrow$ RPE",
+                                   "NFC and Years $\\rightarrow$ RPE via SCS and DRF",
+                                   "NFC and Years $\\rightarrow$ EE via SCS, COVB, and DTH",
+                                   "Total Effect"),
+                          "$B$" = c(fit_explor2_summ$PE$est[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fit_explor2_summ$PE$se[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fit_explor2_summ$PE$z[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fit_explor2_summ$PE$ci.lower[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fit_explor2_summ$PE$ci.upper[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  TableS2[2:ncol(TableS2)] <- format(round(TableS2[2:ncol(TableS2)], digits = 3), nsmall = 2)
+
+  TableS2 <-
+    kbl(TableS2,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 10) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 11, 12) %>%
+    pack_rows("Total Effect", 13, 13) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
+
 The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
@@
 Then we modified the structure of the model in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
-The final model is illustrated in **Figure**, the total, direct, and indirect effects are listed in **Supplementary Table**.
+The final model is illustrated in Supplementary Figure S2, the total, direct, and indirect effects are listed in **Supplementary Table**.
 All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).

### 2021-11-29 Manuscript/Manuscript.Rmd
set figure width

@@
 
-```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
 
@@
 
-```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
 
@@
 
-```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
 

### 2021-12-03 Manuscript/Manuscript.Rmd
started abstract

@@
 abstract: |
+  The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
+  While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
+  One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
+  In the present study, we analyzed questionnaire data of teachers that had been collected in spring of 2020.
+  Firstly, we aimed to replicate results by Grass et al.
+(2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
+  With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
+  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources.
+
   One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

### 2022-01-26 Manuscript/Manuscript.Rmd
wrote some discussion

@@
   Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources.
-
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  The hypothesized model did not have good fit, but indicated that individuals high in NFC have lower burnout scores due to demands that either fit their resources or do not exceed them.
 
@@
 
-  replication_table <-
+  Table3 <-
     kbl(Table3,
@@
 The questionnaire data had been acquired in the scope of a thesis on burnout in teachers.
-We could replicate a negative association of NFC and the burnout subscale reduced personal efficacy, but this relationship was mediated by self control, not by habitual reappraisal.
-Furthermore, the negative relationship between NFC and burnout was fully mediated by less excessive demands and a better fit of demands and resources, but this model did not have good fit.
-The exploratory model showed the same relationship, but *...*
+
+While the mediation model, which replicated the findings of Grass et al. [-@Grass2018], had good fit, not all patterns were similar to the original study.
+NFC was negatively associated with the burnout subscale reduced personal efficacy, but this relationship was not mediated by any other variable.
+Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.
+The higher self-control that comes with more teaching experience is not in line with findings of stable self-control over time [@Hay2006], but in line with other findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Olivia2019].
+The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
+Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
 

### 2022-02-04 Manuscript/Manuscript.Rmd
changed heading formatting

@@
 
-### *Multiple mediation model*
+### Replication of Grass et al. (2018)
 Items were reverse coded according to the scale manuals.
@@
 
-### *Structural equation model*
+### Demand-resource-ratio model
 All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
@@
 
-### *Exploratory analyses*
+### Exploratory analyses
 We preregistered two exploratory analyses.
@@
 
+## Replication of Grass et al. (2018)
+
 While the mediation model, which replicated the findings of Grass et al. [-@Grass2018], had good fit, not all patterns were similar to the original study.
-NFC was negatively associated with the burnout subscale reduced personal efficacy, but this relationship was not mediated by any other variable.
+NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
+There was, however, a positive association between self-control and reduced personal efficacy, and a negative one between NFC and suppression.
+
+NFC had a direct and negative effect on reduced personal efficacy, but this relationship was not mediated by any other variable.
 Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.

### 2022-02-10 Manuscript/Manuscript.Rmd
current version but with knitting error

@@
 
-bibliography      : references.bib
+bibliography      : NFC_Burnout.bib
 
@@
 In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
-The questionnaire data had been acquired in the scope of a thesis on burnout in teachers.
+Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.
 
@@
 
-While the mediation model, which replicated the findings of Grass et al. [-@Grass2018], had good fit, not all patterns were similar to the original study.
-NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
+While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
 There was, however, a positive association between self-control and reduced personal efficacy, and a negative one between NFC and suppression.
@@
 Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.
-The higher self-control that comes with more teaching experience is not in line with findings of stable self-control over time [@Hay2006], but in line with other findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Olivia2019].
+The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
 The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
 Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
+However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.
+
+We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with reduced personal efficacy, but not their association with NFC.
+There is ample evidence that reappraisal is associated with positive outcomes for students [@Levine2012;@Schmidt2010;@Haga2007] and teachers alike [@Moe2020;@Tsouloupas2010;@Jiang2016], so it is suprising that reappraisal did not mediate between NFC and reduced personal efficacy.
+Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
+One possible explanation could be that the ways by which reappraisal can be achieved, such as taking the role of an uninvolved observer, are less feasible for teachers in retaining their sense of efficacy in the classroom than the self-control needed to structurally manage students and situations.
+Hence, the mediation of NFC and reduced personal efficacy by self-control when taking the years spent teaching into account.
+
+## Demand-resource-ratio model
+
+Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via DTH and DRF but not DTL.
+Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
+Interestingly, the correlation between NFC and burnout, which can be classified as medium according to Gignac and Szodorai [-@Gignac2016], disappeared in the context of the demand-resource-ratios as mediators.
+The mediator that did not reach significance was the perception of own resources exceeding the job demands.
+As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. [-@Reijseger2013.].
+The fact that the items that make up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.
+This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands [@Lepine2005;@Podsakoff2007;@Lazarus1984].
+Challenge demands such as time pressure, responsibility, and workload [@Podsakoff2007] are being positively valued due to their potential to increase personal growth, positive affect, and problem-focused coping [@Lepine2005].
+In contrast, hindrance demands such as inadequate resources, role conflict, and organisational politics [@Podsakoff2007] are perceived as negative because they harm personal growth, trigger negative emotions, and increase passive coping [@Lepine2005].
+Ventura et al.
+[-@Ventura2015] found that hindrance but not challenge demands were positively related to burnout in teachers, and teachers who reported high challenge and low hindrance demands also reported higher engagement.
+Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy [@Bandura1997], so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom [@Cherniss1993;@Vera2012].
+Self-efficacy and self-control are closely entwined [@Przepiorka2019;@Vera2004;@Yang2019] and both are positively associated with NFC [@Xu2021;@Bertrams2012;@Naderi2018;@Holch2020].
+Cacioppo et al.
+[@Cacioppo1996] even proposed that higher levels of NFC might develop as a result of a high need for structure or control in those who have the skill, ability, and inclination to do so.
+These associations would imply that teachers with high levels of NFC report lower levels of burnout because their higher (desire for) self-control motivates them to appraise demands as a chance for personal growth, thereby meeting their passion for thinking and problem-solving.
+Nevertheless, appraisal is no universal remedy for circumstances that threaten well-being, as there certainly are circumstances that one cannot get any benefit out of.
+It remains an open question whether a high desire for control and high NFC might cloud one's judgement in this case, by encouraging to invest one's own insufficient resources in order to meet these high external demands.
+Such behavioural tendencies would threaten personal well-being in the long term, as the demands cannot be met, self-efficacy declines, and stress increases.
+
+## Exploratory analyses
+### Demand-resource-ratio model with subscale
+
+The demand-resource-ratio model with the subscale reduced personal efficacy in place of the MBI score did not have good fit indices.
+Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and reduced personal efficacy via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
+Overall, this pattern does not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI [@Grass2018;@Naderi2018].
+Teachers with high NFC appear to retain their sense of personal efficacy to a higher degree, because they experience a fit of demands and resources, which allows them to complete tasks and reinforce their self-efficacy in return.
+However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via DTH was not significant with this subscale, suggesting that the large association of DTH and MBI in the confirmatory model was driven by a different subscale.
+To explore this, we built a second exploratory model, based on partial correlations and suggestions to improve fit indices by the *lavaan* package.
+
+### Structural equation model with Covid burden
+
+Due to the complete freedom in setting up the structure of this model, it had good fit indices.
+Interestingly, the third MBI subscale depersonalisation and the latent variable DTL did not explain any variance in the model, so they were removed.
+Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
+One possible explanation is that teachers with higher NFC show higher consideration of the consequences and progression of the pandemic, thereby anticipating that it will take a long time until normal teaching can resume, which heightens their feeling of being burdened.
+Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively [@Vannucci2018;@Nishiguchi2018], a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
+Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology [@Hauk2018] and therefore stressed by the prospect of online teaching.
+Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in reduced personal efficacy.
+Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower DTH score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
+The degree of association between DTH and emotional exhaustion indeed suggested a congruence between the two, indicating that emotional exhaustion in burnout is caused by excessive demands that cannot be met with one's resources, while reduced personal efficacy in burnout is caused by a lack of opportunities to utilize one's resources at work.
+Curiously, higher Covid burden also showed a small negative association with emotional exhaustion.
+It could be that for some teachers, remote teaching was experienced as a relief from the strain of dealing with a group of over twenty students each day, who are more likely to misbehave in a classroom setting than when they are home alone.
+So while those teachers did feel the pandemic burden, they also felt less emotionally exhausted.
+
+## Limitations and future implications
+
+The data used in this study had been collected for another purpose, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
+Firstly, collecting coping style data would have enabled a full replication of the mediation model of Grass et al. [-@Grass2018].
+Secondly, longitudinal data would have facilitated more definitive conclusions about causal relations, as well as about inter-individual differences in the perception of demands and resources as the pandemic progresses.
+Furthermore, the latent variables for the demand-resource-ratios were item groups chosen from the work satisfaction questionnaire and had not been validated for this use before.
+However, as two of them showed meaningful relations with self-control, NFC, and two of the three MBI subscales, pursuing this concept further seems promising.
+Especially because we worked with pre-existing data, we preregistered all analyses and clearly differentiated between confirmatory and exploratory models in order to make the results as reliable as possible.
+Applied to real-life teaching practise, our results suggest that a healthy work environment should offer ample opportunities to make use of one's abilities, without creating demands that are too high.
+As a consequence, experiences and sense of self-efficacy will increase, which in turn heightens confidence in one's skills to deal with future demands that are higher, preventing loss of personal efficacy and burnout in the long term.
 

### 2022-02-11 Manuscript/Manuscript.Rmd
knits properly

@@
 shorttitle        : "NFC and burnout in teachers"
-
 author: 
@@
     affiliation   : "1"
+    orcid         : "0000-0003-2892-884X"
     corresponding : yes    # Define only one corresponding author
@@
     affiliation   : "3"
+    orcid         : "0000-0002-0313-0615"
     role:
@@
     affiliation   : "1"
+    orcid         : "0000-0002-9426-5397"
     role:
@@
   One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
-  In the present study, we analyzed questionnaire data of teachers that had been collected in spring of 2020.
+  In the present study, we analyzed questionnaire data of N\ =\ 180 teachers that had been collected in spring of 2020.
   Firstly, we aimed to replicate results by Grass et al.
@@
   With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
-  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources.
-  The hypothesized model did not have good fit, but indicated that individuals high in NFC have lower burnout scores due to demands that either fit their resources or do not exceed them.
+  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
+  The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to the demands.
 
@@
 wordcount         : "X"
-
 bibliography      : NFC_Burnout.bib
-
-floatsintext      : no
+floatsintext      : yes
+figsintext        : yes
 figurelist        : no
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
-
-csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
-
+csl               : apa.csl
 header-includes   :
@@
     - \usepackage{xcolor}
+    - \usepackage{setspace}\doublespacing
+    - \usepackage{chngcntr}
 ---
+\renewcommand\thesection{\Alph{section}}
+\counterwithout{figure}{section}
+\setcounter{figure}{0}
 
 ```{r setup, include = FALSE}
-library(papaja)
-library(bibtex)
-
-#install.packages("here")       # easy file referencing
-#install.packages("tidyverse")  # plotting and managing data
-#install.packages("lavaan")     # for structural equation modelling
-#install.packages("psych")      # Cronbach's Alpha and such
-#install.packages("MVN")        # Mardia's test and such
-#install.packages("MBESS")      # MacDonald's Omega
-#install.packages("Hmisc")      # for correlations with p-values
-#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
-#install.packages("knitr")      # for knitting documents and tables
-#install.packages("semPlot")    # plotting path models
-#install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))
-#install.packages("ppcor")      # for partial correlations
-
-library(here)
-library(tidyverse)
-library(ggplot2)
-library(lavaan)
-library(psych)
-library(MVN)
-library(MBESS)
-library(Hmisc)
-library(kableExtra)
-library(knitr)
+
+  # set the output for figures and tables to the width of the text throughout the entire script
+
+  knitr::opts_chunk$set(out.width = "\\textwidth")
+
+  # define required packages
+
+  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
+               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor")
+
+  # check whether each package is installed and install and/or load library
+
+  installed_packages <- packages %in% rownames(installed.packages())
+  if (any(installed_packages == FALSE)) {
+    install.packages(packages[!installed_packages])
+  }
+  invisible(lapply(packages, library, character.only = TRUE))
+
+  # those two libraries come from packages with different names, so we load them individually
+
   library(GGally)                 # from ggplot2, for multi-correlation plots
-library(semPlot)
-library(qgraph)
   library(apa)                    # from the remotes package
-library(ppcor)
-
-```
-
-```{r analysis-preferences, echo=FALSE, message=FALSE, warning=FALSE}
+
+```
+
+```{r analysispreferences, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r correlations_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r correlationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}
 
@@
 
-```{r objective1_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
 
@@
 
-  Table3 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
-                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
-                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
+  Table3 <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
+                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
+                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                    "Total Effect"),
@@
 
-```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
+```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018)"}
 
@@
 
-```{r objective1years_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-  Table4 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
-                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
-                                   "NFC and years spent teaching $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
+  Table4 <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
+                                  "NFC on Reappraisal", "NFC on Suppression",
+                                  "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
+                                  "NFC and years spent teaching on RPE via Self Control",
+                                  "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                   "Total Effect"),
@@
 
-```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
+```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
+```{r objective2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Mediation of NFC and burnout by demand-resource-ratios"}
 
@@
 
-```{r objective2_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-  Table5 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
-                                      "DTH $\\rightarrow$ MBI", "DTL $\\rightarrow$ MBI", "DRF $\\rightarrow$ MBI",
-                                      "NFC $\\rightarrow$ MBI via DTH", "NFC $\\rightarrow$ MBI via DTL", "NFC $\\rightarrow$ MBI via DRF",
+  Table5 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
+                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
+                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
                                       "Total Effect"),
@@
 
-```{r exploring_badfit, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploringbadfit, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r exploratory1_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-```{r exploratory1_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploratory1table, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-  TableS1 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ RPE",
-                                      "DTH $\\rightarrow$ RPE", "DTL $\\rightarrow$ RPE", "DRF $\\rightarrow$ RPE",
-                                      "NFC $\\rightarrow$ RPE via DTH", "NFC $\\rightarrow$ RPE via DTL", "NFC $\\rightarrow$ RPE via DRF",
+  TableS1 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on RPE",
+                                      "DTH on RPE", "DTL on RPE", "DRF on RPE",
+                                      "NFC on RPE via DTH", "NFC on RPE via DTL", "NFC on RPE via DRF",
                                       "Total Effect"),
@@
   explor2_model <- '
-  measurement model
+  # measurement model
     NFC =~ nfc1 + nfc2 + nfc3 + nfc4
@@
 
-```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r explor2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Exploratory analysis of variable relations"}
 
@@
 
-```{r explor2_table, echo=FALSE, message=FALSE, warning=FALSE}
+```{r explor2table, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-  TableS2 <- data.frame("Path" = c("Years $\\rightarrow$ COVB", "Years $\\rightarrow$ SCS",
-                                   "COVB $\\rightarrow$ DTH", "SCS $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTH",
-                                   "SCS $\\rightarrow$ DRF", "NFC $\\rightarrow$ DRF",
-                                   "DTH $\\rightarrow$ EE", "COVB $\\rightarrow$ EE", "DRF $\\rightarrow$ RPE",
-                                   "NFC and Years $\\rightarrow$ RPE via SCS and DRF",
-                                   "NFC and Years $\\rightarrow$ EE via SCS, COVB, and DTH",
+  TableS2 <- data.frame("Path" = c("Years on COVB", "Years on SCS",
+                                   "COVB on DTH", "SCS on DTH", "NFC on DTH",
+                                   "SCS on DRF", "NFC on DRF",
+                                   "DTH on EE", "COVB on EE", "DRF on RPE",
+                                   "NFC and Years on RPE via SCS and DRF",
+                                   "NFC and Years on EE via SCS, COVB, and DTH",
                                    "Total Effect"),

### 2022-02-11 Manuscript/Manuscript.Rmd
knitting works

@@
   One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
-  In the present study, we analyzed questionnaire data of N\ =\ 180 teachers that had been collected in spring of 2020.
+  In the present study, we analyzed questionnaire data of N = 180 teachers that had been collected in spring of 2020.
   Firstly, we aimed to replicate results by Grass et al.
@@
   consistencies <- read_rds(here("Data", "consistencies.rds"))
+  outlierconsistencies <- read_rds(here("Data", "outlierconsistencies.rds"))
+
   # create a vector of consistencies to be used as the diagonal in a table later
@@
 ## Participants
-Teachers were recruited via social media, emails to colleagues of N.E. and to Saxon schools with the request to pass on the information.
+Teachers were recruited via social media, emails to colleagues of N.E., and to Saxon schools with the request to pass on the information.
 All teachers were eligible, no payment was issued.
@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) [@Fischer2014].
+Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
 Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
-The Covid-19 items can be found in the **Supplementary Material**.
+The Covid-19 items can be found in the *Supplementary Material S1*.
 The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
@@
 
-    Table1 <-
+    desc_table <-
       kbl(desc_met,
@@
 A Q-Q-plot contrasting Mahalanobis *D^2^* against expected Chi Square values confirmed the outlier.
-To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the **Supplementary Material**.
+To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the *Supplementary Material S2*.
 
@@
 
-  Table2 <-
+  corr_table <-
   kbl(correlations,
@@
 
-`r Table1`
+`r desc_table`
 
@@
 
-`r Table2`
+`r corr_table`
 
@@
 
-  Table3 <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
+  replic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
                                    "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
@@
 
-  Table3[2:ncol(Table3)] <- format(round(Table3[2:ncol(Table3)], digits = 3), nsmall = 2)
-
-  Table3 <-
-    kbl(Table3,
+  replic_table[2:ncol(replic_table)] <- format(round(replic_table[2:ncol(replic_table)], digits = 3), nsmall = 2)
+
+  replic_table <-
+    kbl(replic_table,
         booktabs = T, # no vertical lines
@@
 
-  Figure1 <- semPaths(fit, what="std", # display the parameters on the arrows
+  replic_figure <- semPaths(fit, what="std", # display the parameters on the arrows
                        nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
@@
 
-`r Table3`
+`r replic_table`
 
@@
 
-  Table4 <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
+  replic_years_table <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
                                   "NFC on Reappraisal", "NFC on Suppression",
@@
 
-  Table4[2:ncol(Table4)] <- format(round(Table4[2:ncol(Table4)], digits = 3), nsmall = 2)
-
-  replicationyears_table <-
-    kbl(Table4,
+  replic_years_table[2:ncol(replic_years_table)] <- format(round(replic_years_table[2:ncol(replic_years_table)], digits = 3), nsmall = 2)
+
+  replic_years_table <-
+    kbl(replic_years_table,
         booktabs = T, # no vertical lines
@@
 
-```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # create an array of standardized parameters and an array of significances
-
-  fityears_param <- fityears_summ$PE$std.all[1:8]
-  fityears_sign <- fityears_summ$PE$pvalue[1:8]
-
-  # replace p-values with asterisks depending on significance level
-
-  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))
-
-  # paste correlations and asterisks together
-
-  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")
-
-  # Make a path diagram to visualize the results
-
-  Figure2 <- semPaths(fityears, what="std", # display the parameters on the arrows
-                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
-                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
-                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
-                       edge.label.cex = 1, esize = 2, # size specifications
-                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
-                       fade = FALSE, # do not make insignificant associations invisible
-                       residuals = FALSE, # do not plot residuals
-                       exoCov = FALSE, # do not plot covariance between exogenous variables
-                       edge.label.color = "black", posCol = "black", negCol = "black"
-)
-```
-
 Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
@@
 Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI=$ `r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
-Standardized estimates are displayed in Figure 2, total, direct, and indirect effects are listed in Table 4.
+Standardized estimates, total, direct, and indirect effects are displayed and listed in *Supplementary Material S3*.
 The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
@@
 Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
-
-`r Table4`
 
@@
 
-  Figure3 <- semPaths(fit2, what = "std",
+  drr_figure <- semPaths(fit2, what = "std",
                         nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
@@
 
-  Table5 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
+  drr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
                                       "DTH on MBI", "DTL on MBI", "DRF on MBI",
@@
 
-  Table5[2:ncol(Table5)] <- format(round(Table5[2:ncol(Table5)], digits = 3), nsmall = 2)
+  drr_table[2:ncol(drr_table)] <- format(round(drr_table[2:ncol(drr_table)], digits = 3), nsmall = 2)
 
   drrmodel_table <-
-    kbl(Table5,
+    kbl(drr_table,
         booktabs = T, # no vertical lines
@@
 The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
-Standardized path coefficients of the demand-resource model are illustrated in Figure 3, total, direct, and indirect effects are listed in Table 5.
+Standardized path coefficients of the demand-resource model are illustrated in Figure 2, total, direct, and indirect effects are listed in Table 4.
 The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
@@
 
-`r Table5`
+`r drr_table`
 
@@
 
-```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
 
@@
 
-```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # create an array of standardized parameters and an array of significances
-
-  fit_explor1_param <- fit_explor1_summ$PE$std.all[1:21]
-  fit_explor1_sign <- c(rep(1,14), fit_explor1_summ$PE$pvalue[17:21])
-
-  # replace p-values with asterisks depending on significance level
-
-  fit_explor1_sign <- ifelse(fit_explor1_sign < .001, "***", ifelse(fit_explor1_sign < .01, "**", ifelse(fit_explor1_sign < .05, "*", "")))
-
-  # paste correlations and asterisks together
-
-  fit_explor1_param <- paste(format(round(fit_explor1_param, digits = 2), nsmall = 2), fit_explor1_sign, sep = "")
-
-  # Visualize the results
-
-  FigureS1 <- semPaths(fit_explor1, what = "std",
-                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
-                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
-                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
-                                        nrow = 19, ncol = 2),
-                        residuals = FALSE, fade = FALSE,
-                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
-                        edge.label.cex = 1, esize = 2, # size of the parameters
-                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
-                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
-                        posCol = "black", negCol = "black" # color of arrows
-  )
-```
-
 ```{r exploratory1table, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-  TableS1 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on RPE",
+  drr_rpe_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on RPE",
                                       "DTH on RPE", "DTL on RPE", "DRF on RPE",
@@
 
-  TableS1[2:ncol(TableS1)] <- format(round(TableS1[2:ncol(TableS1)], digits = 3), nsmall = 2)
-
-  TableS1 <-
-    kbl(TableS1,
+  drr_rpe_table[2:ncol(drr_rpe_table)] <- format(round(drr_rpe_table[2:ncol(drr_rpe_table)], digits = 3), nsmall = 2)
+
+  drr_rpe_table <-
+    kbl(drr_rpe_table,
         booktabs = T, # no vertical lines
@@
 ```
+
 ## Exploratory analyses
@@
 The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
-The path coefficients are illustrated in Supplementary Figure S1, total, direct, and indirect effects are listed in **Supplementary Table**.
+Path coefficients, total, direct, and indirect effects are displayed and listed in *Supplementary Material S4*.
 Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
@@
 
-```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
 
@@
 
-  FigureS2 <- semPaths(fit_explor2, what = "std",
+  explor2_fig <- semPaths(fit_explor2, what = "std",
                                nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
@@
 
-  TableS2 <- data.frame("Path" = c("Years on COVB", "Years on SCS",
+  explor2_table <- data.frame("Path" = c("Years on COVB", "Years on SCS",
                                    "COVB on DTH", "SCS on DTH", "NFC on DTH",
@@
 
-  TableS2[2:ncol(TableS2)] <- format(round(TableS2[2:ncol(TableS2)], digits = 3), nsmall = 2)
-
-  TableS2 <-
-    kbl(TableS2,
+  explor2_table[2:ncol(explor2_table)] <- format(round(explor2_table[2:ncol(explor2_table)], digits = 3), nsmall = 2)
+
+  explor2_table <-
+    kbl(explor2_table,
         booktabs = T, # no vertical lines
@@
 Then we modified the structure of the model in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
-The final model is illustrated in Supplementary Figure S2, the total, direct, and indirect effects are listed in **Supplementary Table**.
+The final model is illustrated in Figure 3, the total, direct, and indirect effects are listed in *Supplementary Material S5*.
 All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
@@
 \endgroup
+
+\newpage
+
+# Supplementary Material
+
+## S1: Items used to assess Covid burden
+
+1. How burdened do you currently feel by the measures associated with Covid-19?
+
+2. Are you in a Covid-19 risk group?
+
+3. Do you have or have you had a Covid-19 infection?
+
+4. Are or were family members or other people close to you infected with Covid-19?
+
+5. Do you feel more burdened at work?
+
+6. Are your worried more?
+
+7. Do you feel restricted in your current day-to-day life?
+
+8. Do you currently have additional responsibilities?
+
+9. How much time do you currently spend on leisure activities?
+
+10. Do you currently spend more/less time on work-related activities (e.g. preparing lessons, reading literature, attending trainings for digital teaching)?
+
+11. Did the current demands within your job change?
+
+For each response scale, please refer to Excel file with the full list of items and response types on OSF [https://osf.io/36ep9/](https://osf.io/36ep9/).
+
+\newpage
+
+## S2: Results when excluding the outlier with very high MBI scores and very low NFC scores
+
+```{r outlierconsistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Tests for internal consistency
+
+    # Create data frame to feed values into
+
+    outlierconsistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
+                                          "lower CI omega","raw omega","upper CI omega"))
+
+    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios
+
+    set.seed(13) # seed for reproducing the bootstrapping
+
+    # Maslach Burnout Inventory
+
+    cronalph <- alpha(mbi, check.keys = TRUE)
+    macomega <- ci.reliability(data=mbi[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI emotional exhaustion
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI depersonalization
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI reduced personal efficacy
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ
+
+    cronalph <- alpha(erq, check.keys = TRUE)
+    macomega <- ci.reliability(data=erq[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ suppression
+
+    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ reappraisal
+
+    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Self Control Scale
+
+    cronalph <- alpha(scs, check.keys = TRUE)
+    macomega <- ci.reliability(data=scs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Need for Cognition Scale
+
+    cronalph <- alpha(ncs, check.keys = TRUE)
+    macomega <- ci.reliability(data=ncs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Covid burden
+
+    cronalph <- alpha(covb, check.keys = TRUE)
+    macomega <- ci.reliability(data=covb[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demands Too High
+
+    cronalph <- alpha(dth, check.keys = FALSE)
+    macomega <- ci.reliability(data=dth[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demands Too Low
+
+    cronalph <- alpha(dtl, check.keys = FALSE)
+    macomega <- ci.reliability(data=dtl[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demand Resource Fit
+
+    cronalph <- alpha(drf, check.keys = FALSE)
+    macomega <- ci.reliability(data=drf[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    remove(cronalph,macomega) # delete the temporary variable
+
+```
+
+```{r outliercorrelations, echo=FALSE, message=FALSE, warning=FALSE}
+
+    # correlate variables
+    outliercorrelations <- correlation_matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+                                                    "scs","ncs","dth","dtl","drf","covb")],
+                                       type = "spearman",
+                                       use = "lower",
+                                       show_significance = FALSE,
+                                       replace_diagonal = TRUE,
+                                       replacement = "")
+
+    # reorder the columns of the consistencies data frame to match the correlation columns
+    outlierconsist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
+
+    # create a vector of consistencies to be used as the diagonal in a table later
+    outlierconsist_diag <- cbind(format(round(t(outlierconsist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+                          format(round(t(outlierconsist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
+
+    # paste together to create the output "alpha(omega)"
+    outlierconsist_diag <- apply(outlierconsist_diag[,c(1:4)], 1 ,paste, collapse = "")
+
+    # add previously assembled diagonal with alpha and omega values
+    diag(outliercorrelations) <- outlierconsist_diag
+
+    # set row and column names for better table printing
+    row.names(outliercorrelations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
+                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
+    colnames(outliercorrelations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
+
+    # create array with p-values of correlation coefficients
+    outliercorr_pvalues <- rcorr(as.matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
+    # replace upper triangle with NA
+    outliercorr_pvalues[upper.tri(outliercorr_pvalues, diag = TRUE)] <- NA
+
+    # replace p-values with asterisks depending on significance level
+    outliercorr_pvalues <- ifelse(is.na(outliercorr_pvalues), "",
+                                  ifelse(outliercorr_pvalues < .001, "***", ifelse(outliercorr_pvalues < .01, "**", ifelse(outliercorr_pvalues < .05, "*", ""))))
+
+    # convert to matrix for the paste()-function
+    outliercorrelations <- as.matrix(outliercorrelations)
+    outliercorr_pvalues <- as.matrix(outliercorr_pvalues)
+
+    # paste correlations and asterisks together
+    outliercorrelations <- matrix(paste(outliercorrelations, outliercorr_pvalues, sep = ""),
+                           nrow = nrow(outliercorrelations), dimnames = dimnames(outliercorrelations))
+
+```
+
+```{r outliercorrelationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}
+
+  outliercorr_table <-
+  kbl(outliercorrelations,
+      booktabs = TRUE, # no vertical lines
+      escape = FALSE, # correctly print special characters
+      align = rep("l",14)) %>% # left aligns the text in every column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+\\\\textit{N} = 179.
+* \\\\textit{p} < .05.
+** \\\\textit{p} < .01.
+*** \\\\textit{p} < .001.
+Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
+             escape = FALSE, # correctly print special characters
+             threeparttable = TRUE) %>% # line breaks in the footnote
+  kableExtra::landscape() # make the table horizontal
+
+```
+
+```{r outlierobjective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+  # Replication of Grass et al. (2018)
+
+  outlierrepli_model <- '
+  # direct paths
+    scs       ~   a1 * ncs
+    erq_reap  ~   a2 * ncs
+    erq_supp  ~   a3 * ncs
+    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
+'
+
+  # Determine the model fit
+
+  outlierfit <- sem(
+    model = outlierrepli_model,
+    data  = score_data_no_outlier,
+    se = "bootstrap",
+    bootstrap = 2000
+  )
+
+  # Get summary
+
+  outlierfit_summ <- summary(outlierfit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+          estimates = TRUE, ci = TRUE)
+```
+
+```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  outlierreplic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
+                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
+                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
+                                   "Total Effect"),
+                          "$B$" = c(outlierfit_summ$PE$est[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(outlierfit_summ$PE$se[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(outlierfit_summ$PE$z[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(outlierfit_summ$PE$pvalue[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(outlierfit_summ$PE$ci.lower[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(outlierfit_summ$PE$ci.upper[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(outlierfit_summ$PE$std.all[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  outlierreplic_table[2:ncol(outlierreplic_table)] <- format(round(outlierreplic_table[2:ncol(outlierreplic_table)], digits = 3), nsmall = 2)
+
+  outlierreplic_table <-
+    kbl(outlierreplic_table,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+
+```
+
+```{r outlierobjective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+  # SEM with demand-resource-ratios
+
+  outliersem_model <- '
+  # measurement model
+    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+    DTH =~ dth1 + dth2 + dth3
+    DTL =~ dtl1 + dtl2 + dtl3
+    DRF =~ drf1 + drf2 + drf3
+    MBI =~ mbi_ee + mbi_dp + mbi_rpe
+
+  # structural model
+    DTH ~ a1 * NFC
+    DTL ~ a2 * NFC
+    DRF ~ a3 * NFC
+    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
+
+  # Determine the model fit
+
+  outlierfit2 <- sem(
+    model = outliersem_model,
+    data  = score_data_no_outlier,
+    estimator = "MLR"
+  )
+
+  # Get summary
+
+  outlierfit2_summ <- summary(outlierfit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+          estimates = TRUE, ci = TRUE)
+
+```
+
+```{r outlierobjective2table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  outlierdrr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
+                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
+                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
+                                      "Total Effect"),
+                          "$B$" = c(outlierfit2_summ$PE$est[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(outlierfit2_summ$PE$se[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(outlierfit2_summ$PE$z[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(outlierfit2_summ$PE$pvalue[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(outlierfit2_summ$PE$ci.lower[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(outlierfit2_summ$PE$ci.upper[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(outlierfit2_summ$PE$std.all[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  outlierdrr_table[2:ncol(outlierdrr_table)] <- format(round(outlierdrr_table[2:ncol(outlierdrr_table)], digits = 3), nsmall = 2)
+
+  outlierdrrmodel_table <-
+    kbl(outlierdrr_table,
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
+
+## S3: Replication of Grass et al. (2018) when including years spent teaching
+
+```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018) when including years spent teaching"}
+
+  # create an array of standardized parameters and an array of significances
+
+  fityears_param <- fityears_summ$PE$std.all[1:8]
+  fityears_sign <- fityears_summ$PE$pvalue[1:8]
+
+  # replace p-values with asterisks depending on significance level
+
+  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")
+
+  # Make a path diagram to visualize the results
+
+  replic_years_figure <- semPaths(fityears, what="std", # display the parameters on the arrows
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
+                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
+                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edge.label.cex = 1, esize = 2, # size specifications
+                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
+                       fade = FALSE, # do not make insignificant associations invisible
+                       residuals = FALSE, # do not plot residuals
+                       exoCov = FALSE, # do not plot covariance between exogenous variables
+                       edge.label.color = "black", posCol = "black", negCol = "black"
+)
+```
+
+`r replic_years_table`
+
+## S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy
+
+```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Demand-resource-ratio model with the MBI subscale reduced personal efficacy"}
+
+  # create an array of standardized parameters and an array of significances
+
+  fit_explor1_param <- fit_explor1_summ$PE$std.all[1:21]
+  fit_explor1_sign <- c(rep(1,14), fit_explor1_summ$PE$pvalue[17:21])
+
+  # replace p-values with asterisks depending on significance level
+
+  fit_explor1_sign <- ifelse(fit_explor1_sign < .001, "***", ifelse(fit_explor1_sign < .01, "**", ifelse(fit_explor1_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit_explor1_param <- paste(format(round(fit_explor1_param, digits = 2), nsmall = 2), fit_explor1_sign, sep = "")
+
+  # Visualize the results
+
+  drr_rpe_plot <- semPaths(fit_explor1, what = "std",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 19, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
+  )
+```
+
+## S5: Exploratory model with all relevant variables
+
+`r explor2_fig`

### 2022-02-14 Manuscript/Manuscript.Rmd
fixed knitting

@@
 keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
-wordcount         : "X"
+wordcount         : "~ 5600"
 bibliography      : NFC_Burnout.bib
@@
 \counterwithout{figure}{section}
+\counterwithout{table}{section}
 \setcounter{figure}{0}
+\setcounter{table}{0}
 
@@
   packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
-               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor")
+               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor", "stats", "apa", "GGally")
 
@@
   invisible(lapply(packages, library, character.only = TRUE))
-
-  # those two libraries come from packages with different names, so we load them individually
-
-  library(GGally)                 # from ggplot2, for multi-correlation plots
-  library(apa)                    # from the remotes package
 
@@
 NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
-This is supported by the findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
+This is supported by findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
@@
 Grass et al.
-[-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
+[-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active coping, and passive coping, but not by suppression or self-control.
 Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
@@
 Furthermore, we extended the analysis to other possible mediators.
-These mediators were motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
-Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
+These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
+Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
 Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
@@
 Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
-The Covid-19 items can be found in the *Supplementary Material S1*.
+The translated Covid-19 items can be found in the *Supplementary Material S1*.
 The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
-Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.
+Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.
 
@@
 The questionnaires were provided online using SoSci Survey [@Leiner2019].
-Participants were informed about aims and duration of the study and data security, then they provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.
+Participants were informed about aims and duration of the study and data security, provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.
 
@@
       kbl(desc_met,
+          caption = "Descriptive statistics of the questionnaire scores.",
           booktabs = T, # no vertical lines
@@
   kbl(correlations,
+      caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
       booktabs = TRUE, # no vertical lines
@@
 Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
-Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
+Only the ERQ sum score and its reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
 
@@
 The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
-As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
-Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman"), format = "rmarkdown")`).
+As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
+Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown")`).
 The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.
@@
     kbl(replic_table,
+        caption = "Results of the replication of Grass et al. (2018).",
         booktabs = T, # no vertical lines
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
     pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
 
-```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018)"}
+## Replication of Grass et al. (2018)
+
+In order to replicate findings by Grass et al.
+[-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
+The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
+Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
+Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
+We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
+Furthermore, even though NFC and reduced personal efficacy were both associated with self-control, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al.
+[-@Grass2018].
+
+```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al. (2018). * $p<.05$, ** $p<.01$."}
 
@@
                        layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
-                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       sizeMan = 26, sizeMan2 = 8, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                        edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
@@
 
-## Replication of Grass et al. (2018)
-
-In order to replicate findings by Grass et al.
-[-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
-The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
-Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
-Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
-We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
-However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
-Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al.
-[-@Grass2018].
-
 `r replic_table`
@@
 
-```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  replic_years_table <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
-                                  "NFC on Reappraisal", "NFC on Suppression",
-                                  "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
-                                  "NFC and years spent teaching on RPE via Self Control",
-                                  "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
-                                  "Total Effect"),
-                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  replic_years_table[2:ncol(replic_years_table)] <- format(round(replic_years_table[2:ncol(replic_years_table)], digits = 3), nsmall = 2)
-
-  replic_years_table <-
-    kbl(replic_years_table,
-        booktabs = T, # no vertical lines
-        escape = F, # correctly print special characters)
-        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 9, 11) %>%
-    pack_rows("Total Effect", 12, 12) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
-             escape = F, # correctly print special characters
-             threeparttable = T)# line breaks in the footnote
-```
-
 Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
@@
 Standardized estimates, total, direct, and indirect effects are displayed and listed in *Supplementary Material S3*.
-The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
+The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the first model.
 However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
@@
 
-```{r objective2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Mediation of NFC and burnout by demand-resource-ratios"}
+```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  drr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
+                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
+                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
+                                      "Total Effect"),
+                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  drr_table[2:ncol(drr_table)] <- format(round(drr_table[2:ncol(drr_table)], digits = 3), nsmall = 2)
+
+  drrmodel_table <-
+    kbl(drr_table,
+        caption = "Results of the demand-resource-ratio model.",
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
+
+## Demand-Resource Model
+
+Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
+The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
+The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
+Standardized path coefficients of the demand-resource model are illustrated in Figure 2, total, direct, and indirect effects are listed in Table 4.
+The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
+However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2012], which was violated here.
+This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
+Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
+NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
+The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
+
+```{r objective2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized path coefficients in the mediation of NFC and burnout by demand-resource-ratios.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, MBI = Maslach Burnout Inventory, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, ee = emotional exhaustion, dp = depersonalisation, rpe = reduced personal efficacy."}
 
@@
 
-```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  drr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
-                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
-                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
-                                      "Total Effect"),
-                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  drr_table[2:ncol(drr_table)] <- format(round(drr_table[2:ncol(drr_table)], digits = 3), nsmall = 2)
-
-  drrmodel_table <-
-    kbl(drr_table,
-        booktabs = T, # no vertical lines
-        escape = F, # correctly print special characters)
-        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
-             escape = F, # correctly print special characters
-             threeparttable = T)# line breaks in the footnote
-```
-
-## Demand-Resource Model
-
-Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
-The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
-The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
-Standardized path coefficients of the demand-resource model are illustrated in Figure 2, total, direct, and indirect effects are listed in Table 4.
-The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
-However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2012], which was violated here.
-This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
-Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
-NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
-Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
-The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
-
-`r drr_table`
+`r drrmodel_table`
 
@@
 
-```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
 
@@
     kbl(drr_rpe_table,
+        caption = "Results of the demand-resource-ratio model with reduced personal efficacy in place of the MBI score.",
         booktabs = T, # no vertical lines
@@
 
-```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
 
@@
 
-```{r explor2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Exploratory analysis of variable relations"}
+The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
+We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
+Then we modified the structure of the model using the *modincides()*-function in *lavaan* in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
+The final model is illustrated in Figure 3, the total, direct, and indirect effects are listed in *Supplementary Material S5*.
+All fit indices suggested that the proposed model had good fit while the baseline model did not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
+Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
+Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
+NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 3)`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"], digits = 3)`).
+In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
+DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Covid burden was not associated with DRF or reduced personal efficacy.
+
+```{r explor2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized path coefficients in the exploratory analysis of variable relations.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+Years = years spent teaching, SCS = Self-Control Scale, COVB = Covid burden, NFC = Need for Cognition, DTH = demands too high, DRF = demand resource fit, nfc1-4 = item parcels, dth/drf1-3 = item indicators, EE = emotional exhaustion, RPE = reduced personal efficacy."}
 
@@
 
+# Discussion
+
+The present study aimed to replicate findings of mediators between Need for Cognition and burnout in teachers, as well as to extend the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
+Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.
+
+## Replication of Grass et al. (2018)
+
+While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
+There was, however, a positive association between self-control and reduced personal efficacy, and a negative one between NFC and suppression.
+
+NFC had a direct and negative effect on reduced personal efficacy, but this relationship was not mediated by any other variable.
+Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.
+The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
+The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
+Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
+However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.
+
+We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with reduced personal efficacy, but not their association with NFC.
+There is ample evidence that reappraisal is associated with positive outcomes for students [@Levine2012;@Schmidt2010;@Haga2007] and teachers alike [@Moe2020;@Tsouloupas2010;@Jiang2016], so it is suprising that reappraisal did not mediate between NFC and reduced personal efficacy.
+Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
+One possible explanation could be that the ways by which reappraisal can be achieved, such as taking the role of an uninvolved observer, are less feasible for teachers in retaining their sense of efficacy in the classroom than the self-control needed to structurally manage students and situations.
+Hence, the mediation of NFC and reduced personal efficacy by self-control when taking the years spent teaching into account.
+
+## Demand-resource-ratio model
+
+Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via DTH and DRF but not DTL.
+Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
+Interestingly, the correlation between NFC and burnout, which can be classified as medium according to Gignac and Szodorai [-@Gignac2016], disappeared in the context of the demand-resource-ratios as mediators.
+The mediator that did not reach significance was the perception of own resources exceeding the job demands.
+As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. [-@Reijseger2013.].
+The fact that the items that made up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.
+This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands [@Lepine2005;@Podsakoff2007;@Lazarus1984].
+Challenge demands such as time pressure, responsibility, and workload [@Podsakoff2007] are being positively valued due to their potential to increase personal growth, positive affect, and problem-focused coping [@Lepine2005].
+In contrast, hindrance demands such as inadequate resources, role conflict, and organisational politics [@Podsakoff2007] are perceived as negative because they harm personal growth, trigger negative emotions, and increase passive coping [@Lepine2005].
+Ventura et al.
+[-@Ventura2015] found that hindrance but not challenge demands were positively related to burnout in teachers, and teachers who reported high challenge and low hindrance demands also reported higher engagement.
+Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy [@Bandura1997], so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom [@Cherniss1993;@Vera2012].
+Self-efficacy and self-control are closely entwined [@Przepiorka2019;@Vera2004;@Yang2019] and both are positively associated with NFC [@Xu2021;@Bertrams2012;@Naderi2018;@Holch2020].
+Cacioppo et al.
+[-@Cacioppo1996] even proposed that higher levels of NFC might develop as a result of a high need for structure or control in those who have the skill, ability, and inclination to do so.
+These associations would imply that teachers with high levels of NFC report lower levels of burnout because their higher (desire for) self-control motivates them to appraise demands as a chance for personal growth, thereby meeting their passion for thinking and problem-solving.
+Nevertheless, appraisal is no universal remedy for circumstances that threaten well-being, as there certainly are circumstances that one cannot get any benefit out of.
+It remains an open question whether a high desire for control and high NFC might cloud one's judgement in this case, by encouraging to invest one's own insufficient resources in order to meet these high external demands.
+Such behavioural tendencies would threaten personal well-being in the long term, as the demands cannot be met, self-efficacy declines, and stress increases.
+
+## Exploratory analyses
+### Demand-resource-ratio model with subscale
+
+The demand-resource-ratio model with the subscale reduced personal efficacy in place of the MBI score did not have good fit indices.
+Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and reduced personal efficacy via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
+Overall, this pattern did not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI [@Grass2018;@Naderi2018].
+Teachers with high NFC appear to retain their sense of personal efficacy to a higher degree, because they experience a fit of demands and resources, which allows them to complete tasks and reinforce their self-efficacy in return.
+However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via DTH was not significant with this subscale, suggesting that the large association of DTH and MBI in the confirmatory model was driven by a different subscale.
+To explore this, we built a second exploratory model.
+
+### Exploratory model with Covid burden
+
+Due to the complete freedom in setting up the structure of this model, it had good fit indices.
+Interestingly, the third MBI subscale depersonalisation and the latent variable DTL did not explain any variance in the model, so they were removed.
+Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
+One possible explanation is that teachers with higher NFC show higher consideration of the consequences and progression of the pandemic, thereby anticipating that it will take a long time until normal teaching can resume, which heightens their feeling of being burdened.
+Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively [@Vannucci2018;@Nishiguchi2018], a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
+Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology [@Hauk2018] and therefore stressed by the prospect of online teaching.
+Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in reduced personal efficacy.
+Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower DTH score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
+The degree of association between DTH and emotional exhaustion indeed suggested a congruence between the two, indicating that emotional exhaustion in burnout is caused by excessive demands that cannot be met with one's resources, while reduced personal efficacy in burnout is caused by a lack of opportunities to utilize one's resources at work.
+Curiously, higher Covid burden also showed a small negative association with emotional exhaustion.
+It could be that for some teachers, remote teaching was experienced as a relief from the strain of dealing with a group of over twenty students each day, who are more likely to misbehave in a classroom setting than when they are studying at home.
+So while those teachers did feel the pandemic burden, they also felt less emotionally exhausted.
+
+## Limitations and future implications
+
+The data used in this study had been collected for another purpose, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
+Firstly, collecting coping style data would have enabled a full replication of the mediation model of Grass et al. [-@Grass2018].
+Secondly, longitudinal data would have facilitated more definitive conclusions about causal relations, as well as about inter-individual differences in the perception of demands and resources as the pandemic progresses.
+Furthermore, the latent variables for the demand-resource-ratios were item groups chosen from the work satisfaction questionnaire and had not been validated for this use before.
+However, as two of them showed meaningful relations with self-control, NFC, and two of the three MBI subscales, pursuing this concept further seems promising.
+Especially because we worked with pre-existing data, we preregistered all analyses and clearly differentiated between confirmatory and exploratory models in order to make the results as reliable as possible.
+Applied to real-life teaching practise, our results suggest that a healthy work environment should offer ample opportunities to make use of one's abilities, without creating demands that are too high.
+As a consequence, experiences and sense of self-efficacy will increase, which in turn heightens confidence in one's skills to deal with future demands that are higher, preventing loss of personal efficacy and burnout in the long term.
+
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
+
+\newpage
+
+# Supplementary Material
+
+## S1: Items used to assess Covid burden
+
+1. How burdened do you currently feel by the measures associated with Covid-19?
+
+2. Are you in a Covid-19 risk group?
+
+3. Do you have or have you had a Covid-19 infection?
+
+4. Are or were family members or other people close to you infected with Covid-19?
+
+5. Do you feel more burdened at work?
+
+6. Are your worried more?
+
+7. Do you feel restricted in your current day-to-day life?
+
+8. Do you currently have additional responsibilities?
+
+9. How much time do you currently spend on leisure activities?
+
+10. Do you currently spend more/less time on work-related activities (e.g. preparing lessons, reading literature, attending trainings for digital teaching)?
+
+11. Did the current demands within your job change?
+
+For each response scale, please refer to Excel file with the full list of items and response types on OSF [https://osf.io/36ep9/](https://osf.io/36ep9/).
+
+\newpage
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+## S2: Results when excluding the outlier with very high MBI scores and very low NFC scores
+
+```{r outlierconsistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # Tests for internal consistency
+
+    # Create data frame to feed values into
+
+    outlierconsistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
+                                          "lower CI omega","raw omega","upper CI omega"))
+
+    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios
+
+    set.seed(13) # seed for reproducing the bootstrapping
+
+    # Maslach Burnout Inventory
+
+    cronalph <- alpha(mbi, check.keys = TRUE)
+    macomega <- ci.reliability(data=mbi[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI emotional exhaustion
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI depersonalization
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # MBI reduced personal efficacy
+
+    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ
+
+    cronalph <- alpha(erq, check.keys = TRUE)
+    macomega <- ci.reliability(data=erq[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ suppression
+
+    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # ERQ reappraisal
+
+    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
+    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Self Control Scale
+
+    cronalph <- alpha(scs, check.keys = TRUE)
+    macomega <- ci.reliability(data=scs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Need for Cognition Scale
+
+    cronalph <- alpha(ncs, check.keys = TRUE)
+    macomega <- ci.reliability(data=ncs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Covid burden
+
+    cronalph <- alpha(covb, check.keys = TRUE)
+    macomega <- ci.reliability(data=covb[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demands Too High
+
+    cronalph <- alpha(dth, check.keys = FALSE)
+    macomega <- ci.reliability(data=dth[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demands Too Low
+
+    cronalph <- alpha(dtl, check.keys = FALSE)
+    macomega <- ci.reliability(data=dtl[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    # Demand Resource Fit
+
+    cronalph <- alpha(drf, check.keys = FALSE)
+    macomega <- ci.reliability(data=drf[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
+    outlierconsistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
+                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
+                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
+
+    remove(cronalph,macomega) # delete the temporary variable
+
+```
+
+```{r outliercorrelations, echo=FALSE, message=FALSE, warning=FALSE}
+
+    # correlate variables
+    outliercorrelations <- correlation_matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+                                                    "scs","ncs","dth","dtl","drf","covb")],
+                                       type = "spearman",
+                                       use = "lower",
+                                       show_significance = FALSE,
+                                       replace_diagonal = TRUE,
+                                       replacement = "")
+
+    # reorder the columns of the consistencies data frame to match the correlation columns
+    outlierconsist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
+
+    # create a vector of consistencies to be used as the diagonal in a table later
+    outlierconsist_diag <- cbind(format(round(t(outlierconsist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+                          format(round(t(outlierconsist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
+
+    # paste together to create the output "alpha(omega)"
+    outlierconsist_diag <- apply(outlierconsist_diag[,c(1:4)], 1 ,paste, collapse = "")
+
+    # add previously assembled diagonal with alpha and omega values
+    diag(outliercorrelations) <- outlierconsist_diag
+
+    # set row and column names for better table printing
+    row.names(outliercorrelations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
+                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
+    colnames(outliercorrelations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
+
+    # create array with p-values of correlation coefficients
+    outliercorr_pvalues <- rcorr(as.matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
+    # replace upper triangle with NA
+    outliercorr_pvalues[upper.tri(outliercorr_pvalues, diag = TRUE)] <- NA
+
+    # replace p-values with asterisks depending on significance level
+    outliercorr_pvalues <- ifelse(is.na(outliercorr_pvalues), "",
+                                  ifelse(outliercorr_pvalues < .001, "***", ifelse(outliercorr_pvalues < .01, "**", ifelse(outliercorr_pvalues < .05, "*", ""))))
+
+    # convert to matrix for the paste()-function
+    outliercorrelations <- as.matrix(outliercorrelations)
+    outliercorr_pvalues <- as.matrix(outliercorr_pvalues)
+
+    # paste correlations and asterisks together
+    outliercorrelations <- matrix(paste(outliercorrelations, outliercorr_pvalues, sep = ""),
+                           nrow = nrow(outliercorrelations), dimnames = dimnames(outliercorrelations))
+
+```
+
+```{r outliercorrelationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}
+
+  outliercorr_table <-
+  kbl(outliercorrelations,
+      caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
+      booktabs = TRUE, # no vertical lines
+      escape = FALSE, # correctly print special characters
+      align = rep("l",14)) %>% # left aligns the text in every column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+\\\\textit{N} = 179.
+* \\\\textit{p} < .05.
+** \\\\textit{p} < .01.
+*** \\\\textit{p} < .001.
+Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
+             escape = FALSE, # correctly print special characters
+             threeparttable = TRUE) %>% # line breaks in the footnote
+  kableExtra::landscape() # make the table horizontal
+
+```
+
+`r outliercorr_table`
+
+```{r outlierobjective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+  # Replication of Grass et al. (2018)
+
+  outlierrepli_model <- '
+  # direct paths
+    scs       ~   a1 * ncs
+    erq_reap  ~   a2 * ncs
+    erq_supp  ~   a3 * ncs
+    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
+'
+
+  # Determine the model fit
+
+  outlierfit <- sem(
+    model = outlierrepli_model,
+    data  = score_data_no_outlier,
+    se = "bootstrap",
+    bootstrap = 2000
+  )
+
+  # Get summary
+
+  outlierfit_summ <- summary(outlierfit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+          estimates = TRUE, ci = TRUE)
+```
+
+```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  outlierreplic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
+                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
+                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
+                                   "Total Effect"),
+                          "$B$" = c(outlierfit_summ$PE$est[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(outlierfit_summ$PE$se[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(outlierfit_summ$PE$z[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(outlierfit_summ$PE$pvalue[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(outlierfit_summ$PE$ci.lower[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(outlierfit_summ$PE$ci.upper[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(outlierfit_summ$PE$std.all[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  outlierreplic_table[2:ncol(outlierreplic_table)] <- format(round(outlierreplic_table[2:ncol(outlierreplic_table)], digits = 3), nsmall = 2)
+
+  outlierreplic_table <-
+    kbl(outlierreplic_table,
+        caption = "Results of the replication of Grass et al. (2018).",
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+
+```
+
+`r outlierreplic_table`
+
+```{r outlierobjective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+  # SEM with demand-resource-ratios
+
+  outliersem_model <- '
+  # measurement model
+    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+    DTH =~ dth1 + dth2 + dth3
+    DTL =~ dtl1 + dtl2 + dtl3
+    DRF =~ drf1 + drf2 + drf3
+    MBI =~ mbi_ee + mbi_dp + mbi_rpe
+
+  # structural model
+    DTH ~ a1 * NFC
+    DTL ~ a2 * NFC
+    DRF ~ a3 * NFC
+    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
+
+  # Determine the model fit
+
+  outlierfit2 <- sem(
+    model = outliersem_model,
+    data  = score_data_no_outlier,
+    estimator = "MLR"
+  )
+
+  # Get summary
+
+  outlierfit2_summ <- summary(outlierfit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+          estimates = TRUE, ci = TRUE)
+
+```
+
+```{r outlierobjective2table, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  outlierdrr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
+                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
+                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
+                                      "Total Effect"),
+                          "$B$" = c(outlierfit2_summ$PE$est[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(outlierfit2_summ$PE$se[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(outlierfit2_summ$PE$z[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(outlierfit2_summ$PE$pvalue[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(outlierfit2_summ$PE$ci.lower[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(outlierfit2_summ$PE$ci.upper[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(outlierfit2_summ$PE$std.all[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  outlierdrr_table[2:ncol(outlierdrr_table)] <- format(round(outlierdrr_table[2:ncol(outlierdrr_table)], digits = 3), nsmall = 2)
+
+  outlierdrrmodel_table <-
+    kbl(outlierdrr_table,
+        caption = "Results of the demand-resource-ratio model.",
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters)
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 8, 10) %>%
+    pack_rows("Total Effect", 11, 11) %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
+
+`r outlierdrrmodel_table`
+
+\newpage
+
+## S3: Replication of Grass et al. (2018) when including years spent teaching
+
+```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al.
+(2018) when including years spent teaching.
+* $p<.05$, ** $p<.01$."}
+
+  # create an array of standardized parameters and an array of significances
+
+  fityears_param <- fityears_summ$PE$std.all[1:8]
+  fityears_sign <- fityears_summ$PE$pvalue[1:8]
+
+  # replace p-values with asterisks depending on significance level
+
+  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")
+
+  # Make a path diagram to visualize the results
+
+  replic_years_figure <- semPaths(fityears, what="std", # display the parameters on the arrows
+                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
+                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
+                       sizeMan = 26, sizeMan2 = 8, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
+                       edge.label.cex = 1, esize = 2, # size specifications
+                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
+                       fade = FALSE, # do not make insignificant associations invisible
+                       residuals = FALSE, # do not plot residuals
+                       exoCov = FALSE, # do not plot covariance between exogenous variables
+                       edge.label.color = "black", posCol = "black", negCol = "black"
+)
+```
+
+```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # put relevant data from the mediation into a table for reporting
+
+  # put data into data frame
+
+  replic_years_table <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
+                                  "NFC on Reappraisal", "NFC on Suppression",
+                                  "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
+                                  "NFC and years spent teaching on RPE via Self Control",
+                                  "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
+                                  "Total Effect"),
+                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
+                          check.names = FALSE)
+
+  # format the numbers to three digits after the decimal point
+
+  replic_years_table[2:ncol(replic_years_table)] <- format(round(replic_years_table[2:ncol(replic_years_table)], digits = 3), nsmall = 2)
+
+  replic_years_table <-
+    kbl(replic_years_table,
+        caption = "Results of the replication of Grass et al. (2018) when including years spent teaching.",
+        booktabs = T, # no vertical lines
+        escape = F, # correctly print special characters
+        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped", "scale_down")) %>%
+    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
+    pack_rows("Indirect Effects", 9, 11) %>%
+    pack_rows("Total Effect", 12, 12) %>%
+    column_spec(1, width = "5cm") %>%
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+             escape = F, # correctly print special characters
+             threeparttable = T)# line breaks in the footnote
+```
+
+`r replic_years_table`
+
+\newpage
+
+## S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy
+
+```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized path coefficients of the demand-resource-ratio model with the MBI subscale reduced personal efficacy.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, RPE = reduced personal efficacy."}
+
+  # create an array of standardized parameters and an array of significances
+
+  fit_explor1_param <- fit_explor1_summ$PE$std.all[1:21]
+  fit_explor1_sign <- c(rep(1,14), fit_explor1_summ$PE$pvalue[17:21])
+
+  # replace p-values with asterisks depending on significance level
+
+  fit_explor1_sign <- ifelse(fit_explor1_sign < .001, "***", ifelse(fit_explor1_sign < .01, "**", ifelse(fit_explor1_sign < .05, "*", "")))
+
+  # paste correlations and asterisks together
+
+  fit_explor1_param <- paste(format(round(fit_explor1_param, digits = 2), nsmall = 2), fit_explor1_sign, sep = "")
+
+  # Visualize the results
+
+  drr_rpe_plot <- semPaths(fit_explor1, what = "std",
+                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
+                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
+                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
+                                        nrow = 19, ncol = 2),
+                        residuals = FALSE, fade = FALSE,
+                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
+                        edge.label.cex = 1, esize = 2, # size of the parameters
+                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
+                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
+                        posCol = "black", negCol = "black" # color of arrows
+  )
+```
+
+\newpage
+
+## S5: Exploratory model with all relevant variables
+
 ```{r explor2table, echo=FALSE, message=FALSE, warning=FALSE}
@@
     kbl(explor2_table,
+        caption = "Results of the exploratory model with Covid burden.",
         booktabs = T, # no vertical lines
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
+    kable_styling(latex_options = c("striped", "scale_down"), font_size = 11) %>%
     pack_rows("Direct Effects", 1, 10) %>% # group the rows and add a header in between
@@
     pack_rows("Total Effect", 13, 13) %>%
+    column_spec(1, width = "5cm") %>%
     footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching.",
@@
 
-The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
-We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
-Then we modified the structure of the model in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
-The final model is illustrated in Figure 3, the total, direct, and indirect effects are listed in *Supplementary Material S5*.
-All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
-Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
-Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
-NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 3)`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"], digits = 3)`).
-In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
-DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
-Covid burden was not associated with DRF or reduced personal efficacy.
-
-# Discussion
-
-The present study aimed to replicate findings of mediators between Need for Cognition and burnout in teachers, as well as to extend the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
-In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
-Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.
-
-## Replication of Grass et al. (2018)
-
-While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
-There was, however, a positive association between self-control and reduced personal efficacy, and a negative one between NFC and suppression.
-
-NFC had a direct and negative effect on reduced personal efficacy, but this relationship was not mediated by any other variable.
-Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.
-The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
-The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
-Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
-However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.
-
-We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with reduced personal efficacy, but not their association with NFC.
-There is ample evidence that reappraisal is associated with positive outcomes for students [@Levine2012;@Schmidt2010;@Haga2007] and teachers alike [@Moe2020;@Tsouloupas2010;@Jiang2016], so it is suprising that reappraisal did not mediate between NFC and reduced personal efficacy.
-Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
-One possible explanation could be that the ways by which reappraisal can be achieved, such as taking the role of an uninvolved observer, are less feasible for teachers in retaining their sense of efficacy in the classroom than the self-control needed to structurally manage students and situations.
-Hence, the mediation of NFC and reduced personal efficacy by self-control when taking the years spent teaching into account.
-
-## Demand-resource-ratio model
-
-Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via DTH and DRF but not DTL.
-Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
-Interestingly, the correlation between NFC and burnout, which can be classified as medium according to Gignac and Szodorai [-@Gignac2016], disappeared in the context of the demand-resource-ratios as mediators.
-The mediator that did not reach significance was the perception of own resources exceeding the job demands.
-As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. [-@Reijseger2013.].
-The fact that the items that make up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.
-This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands [@Lepine2005;@Podsakoff2007;@Lazarus1984].
-Challenge demands such as time pressure, responsibility, and workload [@Podsakoff2007] are being positively valued due to their potential to increase personal growth, positive affect, and problem-focused coping [@Lepine2005].
-In contrast, hindrance demands such as inadequate resources, role conflict, and organisational politics [@Podsakoff2007] are perceived as negative because they harm personal growth, trigger negative emotions, and increase passive coping [@Lepine2005].
-Ventura et al.
-[-@Ventura2015] found that hindrance but not challenge demands were positively related to burnout in teachers, and teachers who reported high challenge and low hindrance demands also reported higher engagement.
-Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy [@Bandura1997], so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom [@Cherniss1993;@Vera2012].
-Self-efficacy and self-control are closely entwined [@Przepiorka2019;@Vera2004;@Yang2019] and both are positively associated with NFC [@Xu2021;@Bertrams2012;@Naderi2018;@Holch2020].
-Cacioppo et al.
-[@Cacioppo1996] even proposed that higher levels of NFC might develop as a result of a high need for structure or control in those who have the skill, ability, and inclination to do so.
-These associations would imply that teachers with high levels of NFC report lower levels of burnout because their higher (desire for) self-control motivates them to appraise demands as a chance for personal growth, thereby meeting their passion for thinking and problem-solving.
-Nevertheless, appraisal is no universal remedy for circumstances that threaten well-being, as there certainly are circumstances that one cannot get any benefit out of.
-It remains an open question whether a high desire for control and high NFC might cloud one's judgement in this case, by encouraging to invest one's own insufficient resources in order to meet these high external demands.
-Such behavioural tendencies would threaten personal well-being in the long term, as the demands cannot be met, self-efficacy declines, and stress increases.
-
-## Exploratory analyses
-### Demand-resource-ratio model with subscale
-
-The demand-resource-ratio model with the subscale reduced personal efficacy in place of the MBI score did not have good fit indices.
-Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and reduced personal efficacy via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
-Overall, this pattern does not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI [@Grass2018;@Naderi2018].
-Teachers with high NFC appear to retain their sense of personal efficacy to a higher degree, because they experience a fit of demands and resources, which allows them to complete tasks and reinforce their self-efficacy in return.
-However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via DTH was not significant with this subscale, suggesting that the large association of DTH and MBI in the confirmatory model was driven by a different subscale.
-To explore this, we built a second exploratory model, based on partial correlations and suggestions to improve fit indices by the *lavaan* package.
-
-### Structural equation model with Covid burden
-
-Due to the complete freedom in setting up the structure of this model, it had good fit indices.
-Interestingly, the third MBI subscale depersonalisation and the latent variable DTL did not explain any variance in the model, so they were removed.
-Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
-One possible explanation is that teachers with higher NFC show higher consideration of the consequences and progression of the pandemic, thereby anticipating that it will take a long time until normal teaching can resume, which heightens their feeling of being burdened.
-Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively [@Vannucci2018;@Nishiguchi2018], a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
-Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology [@Hauk2018] and therefore stressed by the prospect of online teaching.
-Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in reduced personal efficacy.
-Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower DTH score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
-The degree of association between DTH and emotional exhaustion indeed suggested a congruence between the two, indicating that emotional exhaustion in burnout is caused by excessive demands that cannot be met with one's resources, while reduced personal efficacy in burnout is caused by a lack of opportunities to utilize one's resources at work.
-Curiously, higher Covid burden also showed a small negative association with emotional exhaustion.
-It could be that for some teachers, remote teaching was experienced as a relief from the strain of dealing with a group of over twenty students each day, who are more likely to misbehave in a classroom setting than when they are home alone.
-So while those teachers did feel the pandemic burden, they also felt less emotionally exhausted.
-
-## Limitations and future implications
-
-The data used in this study had been collected for another purpose, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
-Firstly, collecting coping style data would have enabled a full replication of the mediation model of Grass et al. [-@Grass2018].
-Secondly, longitudinal data would have facilitated more definitive conclusions about causal relations, as well as about inter-individual differences in the perception of demands and resources as the pandemic progresses.
-Furthermore, the latent variables for the demand-resource-ratios were item groups chosen from the work satisfaction questionnaire and had not been validated for this use before.
-However, as two of them showed meaningful relations with self-control, NFC, and two of the three MBI subscales, pursuing this concept further seems promising.
-Especially because we worked with pre-existing data, we preregistered all analyses and clearly differentiated between confirmatory and exploratory models in order to make the results as reliable as possible.
-Applied to real-life teaching practise, our results suggest that a healthy work environment should offer ample opportunities to make use of one's abilities, without creating demands that are too high.
-As a consequence, experiences and sense of self-efficacy will increase, which in turn heightens confidence in one's skills to deal with future demands that are higher, preventing loss of personal efficacy and burnout in the long term.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-
-# Supplementary Material
-
-## S1: Items used to assess Covid burden
-
-1. How burdened do you currently feel by the measures associated with Covid-19?
-
-2. Are you in a Covid-19 risk group?
-
-3. Do you have or have you had a Covid-19 infection?
-
-4. Are or were family members or other people close to you infected with Covid-19?
-
-5. Do you feel more burdened at work?
-
-6. Are your worried more?
-
-7. Do you feel restricted in your current day-to-day life?
-
-8. Do you currently have additional responsibilities?
-
-9. How much time do you currently spend on leisure activities?
-
-10. Do you currently spend more/less time on work-related activities (e.g. preparing lessons, reading literature, attending trainings for digital teaching)?
-
-11. Did the current demands within your job change?
-
-For each response scale, please refer to Excel file with the full list of items and response types on OSF [https://osf.io/36ep9/](https://osf.io/36ep9/).
-
-\newpage
-
-## S2: Results when excluding the outlier with very high MBI scores and very low NFC scores
-
-```{r outlierconsistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Tests for internal consistency
-
-    # Create data frame to feed values into
-
-    outlierconsistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
-                                          "lower CI omega","raw omega","upper CI omega"))
-
-    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios
-
-    set.seed(13) # seed for reproducing the bootstrapping
-
-    # Maslach Burnout Inventory
-
-    cronalph <- alpha(mbi, check.keys = TRUE)
-    macomega <- ci.reliability(data=mbi[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI emotional exhaustion
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI depersonalization
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI reduced personal efficacy
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ
-
-    cronalph <- alpha(erq, check.keys = TRUE)
-    macomega <- ci.reliability(data=erq[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ suppression
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ reappraisal
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Self Control Scale
-
-    cronalph <- alpha(scs, check.keys = TRUE)
-    macomega <- ci.reliability(data=scs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Need for Cognition Scale
-
-    cronalph <- alpha(ncs, check.keys = TRUE)
-    macomega <- ci.reliability(data=ncs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Covid burden
-
-    cronalph <- alpha(covb, check.keys = TRUE)
-    macomega <- ci.reliability(data=covb[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too High
-
-    cronalph <- alpha(dth, check.keys = FALSE)
-    macomega <- ci.reliability(data=dth[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too Low
-
-    cronalph <- alpha(dtl, check.keys = FALSE)
-    macomega <- ci.reliability(data=dtl[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demand Resource Fit
-
-    cronalph <- alpha(drf, check.keys = FALSE)
-    macomega <- ci.reliability(data=drf[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    remove(cronalph,macomega) # delete the temporary variable
-
-```
-
-```{r outliercorrelations, echo=FALSE, message=FALSE, warning=FALSE}
-
-    # correlate variables
-    outliercorrelations <- correlation_matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                    "scs","ncs","dth","dtl","drf","covb")],
-                                       type = "spearman",
-                                       use = "lower",
-                                       show_significance = FALSE,
-                                       replace_diagonal = TRUE,
-                                       replacement = "")
-
-    # reorder the columns of the consistencies data frame to match the correlation columns
-    outlierconsist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
-
-    # create a vector of consistencies to be used as the diagonal in a table later
-    outlierconsist_diag <- cbind(format(round(t(outlierconsist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
-                          format(round(t(outlierconsist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
-
-    # paste together to create the output "alpha(omega)"
-    outlierconsist_diag <- apply(outlierconsist_diag[,c(1:4)], 1 ,paste, collapse = "")
-
-    # add previously assembled diagonal with alpha and omega values
-    diag(outliercorrelations) <- outlierconsist_diag
-
-    # set row and column names for better table printing
-    row.names(outliercorrelations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
-                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
-    colnames(outliercorrelations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
-
-    # create array with p-values of correlation coefficients
-    outliercorr_pvalues <- rcorr(as.matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
-    # replace upper triangle with NA
-    outliercorr_pvalues[upper.tri(outliercorr_pvalues, diag = TRUE)] <- NA
-
-    # replace p-values with asterisks depending on significance level
-    outliercorr_pvalues <- ifelse(is.na(outliercorr_pvalues), "",
-                                  ifelse(outliercorr_pvalues < .001, "***", ifelse(outliercorr_pvalues < .01, "**", ifelse(outliercorr_pvalues < .05, "*", ""))))
-
-    # convert to matrix for the paste()-function
-    outliercorrelations <- as.matrix(outliercorrelations)
-    outliercorr_pvalues <- as.matrix(outliercorr_pvalues)
-
-    # paste correlations and asterisks together
-    outliercorrelations <- matrix(paste(outliercorrelations, outliercorr_pvalues, sep = ""),
-                           nrow = nrow(outliercorrelations), dimnames = dimnames(outliercorrelations))
-
-```
-
-```{r outliercorrelationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}
-
-  outliercorr_table <-
-  kbl(outliercorrelations,
-      booktabs = TRUE, # no vertical lines
-      escape = FALSE, # correctly print special characters
-      align = rep("l",14)) %>% # left aligns the text in every column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
-\\\\textit{N} = 179.
-* \\\\textit{p} < .05.
-** \\\\textit{p} < .01.
-*** \\\\textit{p} < .001.
-Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
-             escape = FALSE, # correctly print special characters
-             threeparttable = TRUE) %>% # line breaks in the footnote
-  kableExtra::landscape() # make the table horizontal
-
-```
-
-```{r outlierobjective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # Replication of Grass et al. (2018)
-
-  outlierrepli_model <- '
-  # direct paths
-    scs       ~   a1 * ncs
-    erq_reap  ~   a2 * ncs
-    erq_supp  ~   a3 * ncs
-    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
-'
-
-  # Determine the model fit
-
-  outlierfit <- sem(
-    model = outlierrepli_model,
-    data  = score_data_no_outlier,
-    se = "bootstrap",
-    bootstrap = 2000
-  )
-
-  # Get summary
-
-  outlierfit_summ <- summary(outlierfit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
-
-```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  outlierreplic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
-                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
-                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
-                                   "Total Effect"),
-                          "$B$" = c(outlierfit_summ$PE$est[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(outlierfit_summ$PE$se[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(outlierfit_summ$PE$z[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(outlierfit_summ$PE$pvalue[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(outlierfit_summ$PE$ci.lower[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(outlierfit_summ$PE$ci.upper[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(outlierfit_summ$PE$std.all[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  outlierreplic_table[2:ncol(outlierreplic_table)] <- format(round(outlierreplic_table[2:ncol(outlierreplic_table)], digits = 3), nsmall = 2)
-
-  outlierreplic_table <-
-    kbl(outlierreplic_table,
-        booktabs = T, # no vertical lines
-        escape = F, # correctly print special characters)
-        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
-             escape = F, # correctly print special characters
-             threeparttable = T)# line breaks in the footnote
-
-```
-
-```{r outlierobjective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # SEM with demand-resource-ratios
-
-  outliersem_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
-    DRF =~ drf1 + drf2 + drf3
-    MBI =~ mbi_ee + mbi_dp + mbi_rpe
-
-  # structural model
-    DTH ~ a1 * NFC
-    DTL ~ a2 * NFC
-    DRF ~ a3 * NFC
-    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
-
-  # Determine the model fit
-
-  outlierfit2 <- sem(
-    model = outliersem_model,
-    data  = score_data_no_outlier,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  outlierfit2_summ <- summary(outlierfit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-
-```
-
-```{r outlierobjective2table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  outlierdrr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
-                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
-                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
-                                      "Total Effect"),
-                          "$B$" = c(outlierfit2_summ$PE$est[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(outlierfit2_summ$PE$se[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(outlierfit2_summ$PE$z[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(outlierfit2_summ$PE$pvalue[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(outlierfit2_summ$PE$ci.lower[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(outlierfit2_summ$PE$ci.upper[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(outlierfit2_summ$PE$std.all[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  outlierdrr_table[2:ncol(outlierdrr_table)] <- format(round(outlierdrr_table[2:ncol(outlierdrr_table)], digits = 3), nsmall = 2)
-
-  outlierdrrmodel_table <-
-    kbl(outlierdrr_table,
-        booktabs = T, # no vertical lines
-        escape = F, # correctly print special characters)
-        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.",
-             escape = F, # correctly print special characters
-             threeparttable = T)# line breaks in the footnote
-```
-
-## S3: Replication of Grass et al. (2018) when including years spent teaching
-
-```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018) when including years spent teaching"}
-
-  # create an array of standardized parameters and an array of significances
-
-  fityears_param <- fityears_summ$PE$std.all[1:8]
-  fityears_sign <- fityears_summ$PE$pvalue[1:8]
-
-  # replace p-values with asterisks depending on significance level
-
-  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))
-
-  # paste correlations and asterisks together
-
-  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")
-
-  # Make a path diagram to visualize the results
-
-  replic_years_figure <- semPaths(fityears, what="std", # display the parameters on the arrows
-                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
-                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
-                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
-                       edge.label.cex = 1, esize = 2, # size specifications
-                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
-                       fade = FALSE, # do not make insignificant associations invisible
-                       residuals = FALSE, # do not plot residuals
-                       exoCov = FALSE, # do not plot covariance between exogenous variables
-                       edge.label.color = "black", posCol = "black", negCol = "black"
-)
-```
-
-`r replic_years_table`
-
-## S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy
-
-```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Demand-resource-ratio model with the MBI subscale reduced personal efficacy"}
-
-  # create an array of standardized parameters and an array of significances
-
-  fit_explor1_param <- fit_explor1_summ$PE$std.all[1:21]
-  fit_explor1_sign <- c(rep(1,14), fit_explor1_summ$PE$pvalue[17:21])
-
-  # replace p-values with asterisks depending on significance level
-
-  fit_explor1_sign <- ifelse(fit_explor1_sign < .001, "***", ifelse(fit_explor1_sign < .01, "**", ifelse(fit_explor1_sign < .05, "*", "")))
-
-  # paste correlations and asterisks together
-
-  fit_explor1_param <- paste(format(round(fit_explor1_param, digits = 2), nsmall = 2), fit_explor1_sign, sep = "")
-
-  # Visualize the results
-
-  drr_rpe_plot <- semPaths(fit_explor1, what = "std",
-                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
-                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
-                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
-                                        nrow = 19, ncol = 2),
-                        residuals = FALSE, fade = FALSE,
-                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
-                        edge.label.cex = 1, esize = 2, # size of the parameters
-                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
-                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
-                        posCol = "black", negCol = "black" # color of arrows
-  )
-```
-
-## S5: Exploratory model with all relevant variables
-
-`r explor2_fig`
+`r explor2_table`

### 2022-02-14 Manuscript/Manuscript.Rmd
final fix

@@
 The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
-As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
-Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown")`).
+As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
+Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`).
 The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

### 2022-02-17 Manuscript/Manuscript.Rmd

@@
 NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984].
-While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020], recent investigations have also looked at NFC as a personal resource in academic and work contexts.
+<!-- den Satz würde ich entweder weglassen oder noch die deutsche NFC Skala mit referenzieren -->
+While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020]<!-- von Stumm & Ackerman, 2013 als Metaanalyse mit aufnehmen, dafür 1-2 Einzelstudien raus -->, recent investigations have also looked at NFC as a personal resource in academic and work contexts.
 Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020].
-These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005].
+These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005] consequences.
 

### 2022-02-18 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
+Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], NFC using the 16-item Need for Cognition Scale [NCS, @Bless1994], self-control using the 13-item Self-Control Scale [SCS, @Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire [ERQ, @Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
 Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
 The translated Covid-19 items can be found in the *Supplementary Material S1*.
-The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
+The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.<!-- warum eigentlich nicht? -->
 Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.

### 2022-02-18 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 The robust Chi-square statistic of $\chi^2=$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
-However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $*df<\chi^2<$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2012], which was violated here.
+However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)` $df<\chi^2>$ `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1` $df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2012], which was violated here.
 This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].

### 2022-02-21 Manuscript/Manuscript.Rmd
split Rmd into Analysis and Manuscript

@@
 
-  # define required packages
-
-  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
-               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor", "stats", "apa", "GGally")
-
-  # check whether each package is installed and install and/or load library
-
-  installed_packages <- packages %in% rownames(installed.packages())
-  if (any(installed_packages == FALSE)) {
-    install.packages(packages[!installed_packages])
-  }
-  invisible(lapply(packages, library, character.only = TRUE))
-
-```
-
-```{r analysispreferences, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Seed for random number generation
-  set.seed(13)
-  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-
-  # Set a number for the bootstrapping procedures
-  bootnum <- 5000
+  # load libraries
+
+  library(bibtex)       # for referencing, "bibtex" package
+  library(here)         # for path independent file referencing, "here" package
+  library(papaja)       # APA conform output, "papaja" package
+  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
+  library(ggplot2)      # for plotting, "ggplot2" package
+  library(GGally)       # for plotting, "GGally" package
+  library(semPlot)      # for plotting, "semPlot" package
+  library(knitr)        # for including plots and such, "knitr" package
+  library(apa)          # APA conform output, "apa" package
+  library(effectsize)   # for effect sizes and CIs, "effectsize" package
+
+  # set top level directory to source file
+
+  here::i_am("flag_top_level_NFCBurnout.txt")
+
+  # load the workspace variables that have been computed with the Analysis.R script
+
+  load(here("Data","Workspace.RData"))
 
@@
 
-```{r import, echo=FALSE, message=FALSE, warning=FALSE}
-  # Define the top level as the one where this file lies
-  # If the rest of the files follow the structure of the Github repository, everything will work
-  # (Simply download the entire repository to any location on your computer)
-
-  here::i_am("flag_top_level_NFCBurnout.txt")
-
-  # Load the data file
-
-  load(here("Data", "data.Rda"))
-
-  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
-  consistencies <- read_rds(here("Data", "consistencies.rds"))
-  outlierconsistencies <- read_rds(here("Data", "outlierconsistencies.rds"))
-
-  # create a vector of consistencies to be used as the diagonal in a table later
-  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
-                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
-  # paste together to create the output "alpha(omega)"
-  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
-
-```
-
 ## Participants
@@
 
-```{r splitandrecode, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Put questionnaire data into different data frames for easy access
-
-  mbi <- data[,grep("MBI", colnames(data))]   # Maslach Burnout Inventory
-  erq <- data[,grep("ERQ", colnames(data))]   # Emotion Regulation Questionnaire
-  scs <- data[,grep("SCS", colnames(data))]   # Self Control Scale
-  ws <- data[,grep("WS", colnames(data))]     # Work Satisfaction
-  ncs <- data[,grep("NCS", colnames(data))]   # Need for Cognition Scale
-  ncs <- ncs[,-9]                             # remove the dummy item
-  covb <- data[,grep("COV", colnames(data))]  # Covid Burden Items
-  dth <- ws[,c(4,8,9)]                        # the Work Satisfaction items for the latent variable Demands Too High
-  dtl <- ws[,c(12,26,27)]                     # the Work Satisfaction items for the latent variable Demands Too Low
-  drf <- ws[,c(17,21,24)]                     # the Work Satisfaction items for the latent variable Demand-Resource-Fit
-
-  # Create a list with keys for the questionnaire subscales/latent variables/item parcels
-
-  keylist <- list(mbi_ee = c(5,7,10,11,14,18,19,20,21), mbi_dp = c(1,6,9,15,17), mbi_rpe = c(2,3,4,8,12,13,16),
-                  erq_supp = c(2,4,6,9), erq_reap = c(1,3,5,7,8,10),
-                  scs = c(2,3,4,5,6,7,8,10,11),
-                  ncs = c(4,6,7,8,9,10,11,12,15,16),
-                  ws = c(4,5,6,8,9,10,11,13,16,19,20,33))
-
-  # Recode all the reverse coded items
-
-  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
-  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
-  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
-  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
-  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
-  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
-  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
-  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
-  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
-  # The following recoding is opposite to what is described in the methods section of the paper, which
-  # is due to the fact that the questionnaire is originally coded as 1 (false) to 5 (true), but it was
-  # coded as 1 (true) to 5 (false) in the SoSciSurvey of the present study.
-  dth <- 6 - dth                                      # Recode all from 1-5 to 5-1
-  dth <- dth - 3                                      # Recode all from 1-5 to -2-+2
-  dtl <- dtl - 3                                      # Recode all from 1-5 to -2-+2
-  drf <- 6 - drf                                      # Recode all from 1-5 to 5-1
-  drf <- drf -3                                       # Recode all from 1-5 to -2-+2
-
-```
-
-```{r parcelling, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Parcelling preparation: Compute factor loadings on the first PCA component
-
-  ncs_pca <- princomp(ncs, cor = FALSE, scores = TRUE)
-  ncs_load <- ncs_pca$loadings[,1]
-
-  # Parcelling function
-
-  parcel.gen <- function(loadings, parcels = 4,seed = 242,iterations = 10000) {
-
-    p = parcels                   # number of parcels
-    l = length(loadings)          # number of items
-    set.seed(seed)              # seed for reproducibility
-
-    out = parcels = NULL            # set up containers
-    for (k in 1:iterations) {
-
-      s = sample(1:l,l,replace = F) # random item order
-      m = matrix(s,ncol = 4)        # separate into parcels
-
-      # temporarily convert item numbers per parcel to concatenated strings
-      parcels.i = NULL
-      for (i in 1:p) {
-        parcels.i = c(parcels.i,paste0(sort(m[,i]),collapse = ","))
-      }
-      # write to container
-      parcels = rbind(parcels,parcels.i)
-
-      # compute average item loadings per parcel
-      avg.h = colMeans(matrix(loadings[m],ncol = 4))
-
-      # compute differences between all average item loadings
-      h.diff = NULL
-      for (i in 1:(p-1)) {
-        for (j in (i+1):p) {
-          h.diff = c(h.diff,abs(avg.h[i]-avg.h[j]))
-        }
-      }
-
-      # sum up differences
-      h.diff.sum = sum(h.diff)
-      # write summed differences to container
-      out = c(out,h.diff.sum)
-    }
-
-    # find minimum summed difference and generate matrix or respective items
-    final.parcels = matrix(as.numeric(unlist(strsplit(parcels[which.min(out),],','))),ncol = 4)
-    # obtain corresponding loadings per parcel
-    final.h = matrix(loadings[final.parcels],ncol = 4)
-
-    # return result as list
-    return(list(items = final.parcels,loadings = final.h,avg.loadings = colMeans(final.h),summed.difference = min(out)))
-
-  }
-
-  ncs_parcels <- parcel.gen(loadings = ncs_load) # execute function
-
-  # Add parcelling result to the key list
-
-  keylist <- c(keylist, parcel1 = list(ncs_parcels$items[,1]), parcel2 = list(ncs_parcels$items[,2]),
-               parcel3 = list(ncs_parcels$items[,3]), parcel4 = list(ncs_parcels$items[,4]))
-```
-
-```{r scores, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-# Create data frame to feed the values of every subject into
-
-  score_data <- data.frame(id = c(1:180),
-                           years = data$yearsteaching,
-                           mbi = rep(0,180),
-                           mbi_ee = rep(0,180), mbi_dp = rep(0,180), mbi_rpe = rep(0,180),
-                           erq = rep(0,180),
-                           erq_supp = rep(0,180), erq_reap = rep(0,180),
-                           scs = rep(0,180),
-                           ncs = rep(0,180),
-                           nfc1 = rep(0,180), nfc2 = rep(0,180), nfc3 = rep(0,180), nfc4 = rep(0,180),
-                           dth = rep(0,180),
-                           dth1 = rep(0,180), dth2 = rep(0,180), dth3 = rep(0,180),
-                           dtl = rep(0,180),
-                           dtl1 = rep(0,180), dtl2 = rep(0,180), dtl3 = rep(0,180),
-                           drf = rep(0,180),
-                           drf1 = rep(0,180), drf2 = rep(0,180), drf3 = rep(0,180),
-                           covb = rep(0,180))
-
-  # Compute individual scores or (for the latent variable indicators) feed in raw values
-
-  for (i in 1:nrow(data)) {
-    score_data[i,c(3:ncol(score_data))] <- c(rowSums(mbi[i,]),
-                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
-                                             rowSums(erq[i,]),
-                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
-                                             rowSums(scs[i,]),
-                                             rowSums(ncs[i,]),
-                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
-                                             rowSums(dth[i,]),
-                                             dth[i,1], dth[i,2], dth[i,3],
-                                             rowSums(dtl[i,]),
-                                             dtl[i,1], dtl[i,2], dtl[i,3],
-                                             rowSums(drf[i,]),
-                                             drf[i,1], drf[i,2], drf[i,3],
-                                             rowSums(covb[i,]))
-  }
-
-  # This function was taken from an answer on a Stackoverflow question on August 30th 2021
-  # https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740
-
-  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
-    ggplot(data = data, mapping = mapping, ...) +
-      do.call(geom_point, pts) +
-      do.call(geom_smooth, smt)
-  }
-
-  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
-  multicorrplot <- ggpairs(score_data[,c("years","mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                         "scs","ncs","dth","dtl","drf","covb")], lower = list(continuous = my_fn))
-
-  # It looked like there was an outlier in the data, especially visible in the MBI data
-  # Check for the outlier in particular, using the data involved in the mediation
-  outlierplot <- outlier(score_data[ ,c(6,8:11)], plot = TRUE)
-
-  # Remove participant 161 in a second version of the data frame (for the supplementary material analysis)
-  score_data_no_outlier <- score_data[score_data$mbi < 100, ]
-
-```
-
-```{r descriptives, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Tests for normal distribution
-
-    # using Mardia's test for multivariate normal distribution
-    # results will be fed into the desc_met data frame in the next step
-
-    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")],
-                       mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")
-
-  # Descriptive statistics
-
-    # Categorical descriptives: data frame with percentages of responses per category
-
-    desc_cat <- data.frame(answer = c(1,2,3,4,5),
-                           age = c(nrow(data[data$age == 1,])/nrow(data), nrow(data[data$age == 2,])/nrow(data), nrow(data[data$age == 3,])/nrow(data),
-                                   nrow(data[data$age == 4,])/nrow(data), nrow(data[data$age == 5,])/nrow(data)),
-                           gender = c(nrow(data[data$gender == 1,])/nrow(data), nrow(data[data$gender == 2,])/nrow(data), nrow(data[data$gender == 3,])/nrow(data),0,0),
-                           schooltype = c(nrow(data[data$schooltype == 1,])/nrow(data), nrow(data[data$schooltype == 2,])/nrow(data), nrow(data[data$schooltype == 3,])/nrow(data),
-                                          nrow(data[data$schooltype == 4,])/nrow(data), nrow(data[data$schooltype == 5,])/nrow(data)))
-
-    # Metric descriptives: data frame with descriptive values of questionnaires
-
-    desc_met <- data.frame(Variable = c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV"),
-                           Minimum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], min),
-                           Maximum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], max),
-                           Mean = isnorm_test$Descriptives$Mean,
-                           SD = isnorm_test$Descriptives$Std.Dev,
-                           Normality = isnorm_test$univariateNormality$Normality,
-                           Skewness = isnorm_test$Descriptives$Skew,
-                           Kurtosis = isnorm_test$Descriptives$Kurtosis)
-    # Drop the row names
-
-    rownames(desc_met) <- NULL
-
-    # Replace the capital YESes and NOs with small ones
-
-    desc_met$Normality[grep("NO", desc_met$Normality)] <- "No"
-    desc_met$Normality[grep("YES", desc_met$Normality)] <- "Yes"
-
-    # Round the values
-
-    desc_met[ ,c("Mean","SD","Skewness","Kurtosis")] <- round(desc_met[ ,c("Mean","SD","Skewness","Kurtosis")], digits = 2)
-
-    # Put the information in a table
-
+# Results
+
+During visual inspection of correlation plots we noticed an unexpected outlier with very high MBI scores and very low NFC scores.
+A Q-Q-plot contrasting Mahalanobis *D^2^* against expected Chi Square values confirmed the outlier.
+To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the *Supplementary Material S2*.
+
+```{r cdescriptivestable, echo=FALSE, message=FALSE, warning=FALSE, caption="Descriptive statistics of the questionnaire scores."}
   desc_table <-
@@
                threeparttable = T) # line breaks in the footnote
-
-```
-
-```{r consistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Tests for internal consistency
-
-    # Create data frame to feed values into
-
-    consistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
-                                          "lower CI omega","raw omega","upper CI omega"))
-
-    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios
-
-    set.seed(13) # seed for reproducing the bootstrapping
-
-    # Maslach Burnout Inventory
-
-    cronalph <- alpha(mbi, check.keys = TRUE)
-    macomega <- ci.reliability(data=mbi, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI emotional exhaustion
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI depersonalization
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI reduced personal efficacy
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ
-
-    cronalph <- alpha(erq, check.keys = TRUE)
-    macomega <- ci.reliability(data=erq, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ suppression
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ reappraisal
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Self Control Scale
-
-    cronalph <- alpha(scs, check.keys = TRUE)
-    macomega <- ci.reliability(data=scs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Need for Cognition Scale
-
-    cronalph <- alpha(ncs, check.keys = TRUE)
-    macomega <- ci.reliability(data=ncs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Covid burden
-
-    cronalph <- alpha(covb, check.keys = TRUE)
-    macomega <- ci.reliability(data=covb, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too High
-
-    cronalph <- alpha(dth, check.keys = FALSE)
-    macomega <- ci.reliability(data=dth, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too Low
-
-    cronalph <- alpha(dtl, check.keys = FALSE)
-    macomega <- ci.reliability(data=dtl, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demand Resource Fit
-
-    cronalph <- alpha(drf, check.keys = FALSE)
-    macomega <- ci.reliability(data=drf, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    consistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    remove(cronalph,macomega) # delete the temporary variable
-
-```
-
-```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
-
-    # The following function for nicely formatted correlation output was taken from
-    # https://paulvanderlaken.com/2020/07/28/publication-ready-correlation-matrix-significance-r/
-    # on the 5th of August 2021
-
-    correlation_matrix <- function(df,
-                                   type = "spearman",
-                                   digits = 3,
-                                   decimal.mark = ".",
-                                   use = "all",
-                                   show_significance = TRUE,
-                                   replace_diagonal = FALSE,
-                                   replacement = ""){
-      # check arguments
-      stopifnot({
-        is.numeric(digits)
-        digits >= 0
-        use %in% c("all", "upper", "lower")
-        is.logical(replace_diagonal)
-        is.logical(show_significance)
-        is.character(replacement)
-      })
-      # we need the Hmisc package for this
-      require(Hmisc)
-
-      # retain only numeric and boolean columns
-      isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
-      if (sum(!isNumericOrBoolean) > 0) {
-        cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
-      }
-      df = df[isNumericOrBoolean]
-
-      # transform input data frame to matrix
-      x <- as.matrix(df)
-
-      # run correlation analysis using Hmisc package
-      correlation_matrix <- Hmisc::rcorr(x, type = type)
-      R <- correlation_matrix$r # Matrix of correlation coeficients
-      p <- correlation_matrix$P # Matrix of p-value
-
-      # transform correlations to specific character format
-      Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)
-
-      # if there are any negative numbers, we want to put a space before the positives to align all
-      if (sum(!is.na(R) & R < 0) > 0) {
-        Rformatted = ifelse(!is.na(R) & R > 0, paste0(" ", Rformatted), Rformatted)
-      }
-
-      # add significance levels if desired
-      if (show_significance) {
-        # define notions for significance levels; spacing is important.
-        stars <- ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", ""))))
-        Rformatted = paste0(Rformatted, stars)
-      }
-
-      # make all character strings equally long
-      max_length = max(nchar(Rformatted))
-      Rformatted = vapply(Rformatted, function(x) {
-        current_length = nchar(x)
-        difference = max_length - current_length
-        return(paste0(x, paste(rep(" ", difference), collapse = ''), sep = ''))
-      }, FUN.VALUE = character(1))
-
-      # build a new matrix that includes the formatted correlations and their significance stars
-      Rnew <- matrix(Rformatted, ncol = ncol(x))
-      rownames(Rnew) <- colnames(Rnew) <- colnames(x)
-
-      # replace undesired values
-      if (use == 'upper') {
-        Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
-      } else if (use == 'lower') {
-        Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
-      } else if (replace_diagonal) {
-        diag(Rnew) <- replacement
-      }
-
-      return(Rnew)
-    }
-
-    # correlate variables
-    correlations <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                    "scs","ncs","dth","dtl","drf","covb")],
-                                       type = "spearman",
-                                       use = "lower",
-                                       show_significance = FALSE,
-                                       replace_diagonal = TRUE,
-                                       replacement = "")
-
-    # reorder the columns of the consistencies data frame to match the correlation columns
-    consist_diag <- consistencies[c(colnames(correlations))]
-
-    # create a vector of consistencies to be used as the diagonal in a table later
-    consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
-                          format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
-
-    # paste together to create the output "alpha(omega)"
-    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
-
-    # add previously assembled diagonal with alpha and omega values
-    diag(correlations) <- consist_diag
-
-    # set row and column names for better table printing
-    row.names(correlations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
-                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
-    colnames(correlations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
-
-    # create array with p-values of correlation coefficients
-    corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
-    # replace upper triangle with NA
-    corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA
-
-    # replace p-values with asterisks depending on significance level
-    corr_pvalues <- ifelse(is.na(corr_pvalues), "", ifelse(corr_pvalues < .001, "***", ifelse(corr_pvalues < .01, "**", ifelse(corr_pvalues < .05, "*", ""))))
-
-    # convert to matrix for the paste()-function
-    correlations <- as.matrix(correlations)
-    corr_pvalues <- as.matrix(corr_pvalues)
-
-    # paste correlations and asterisks together
-    correlations <- matrix(paste(correlations, corr_pvalues, sep = ""),
-                           nrow = nrow(correlations), dimnames = dimnames(correlations))
-
-```
-
-# Results
-
-During visual inspection of correlation plots we noticed an unexpected outlier with very high MBI scores and very low NFC scores.
-A Q-Q-plot contrasting Mahalanobis *D^2^* against expected Chi Square values confirmed the outlier.
-To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the *Supplementary Material S2*.
+```
 
@@
   corr_table <-
-  kbl(correlations,
+  kable(correlations,
       caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
@@
 
-```{r objective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # Replication of Grass et al. (2018)
-
-  repli_model <- '
-  # direct paths
-    scs       ~   a1 * ncs
-    erq_reap  ~   a2 * ncs
-    erq_supp  ~   a3 * ncs
-    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
-'
-
-  # Determine the model fit
-
-  fit <- sem(
-    model = repli_model,
-    data  = score_data,
-    se = "bootstrap",
-    bootstrap = 2000
-  )
-
-  # Get summary
-
-  fit_summ <- summary(fit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
-
 ```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  replic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
-                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
-                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
-                                   "Total Effect"),
-                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  replic_table[2:ncol(replic_table)] <- format(round(replic_table[2:ncol(replic_table)], digits = 3), nsmall = 2)
 
@@
 
-```{r objective1years, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # Replication of Grass et al. (2018) using years spent teaching as a variable influencing self-control
-  # (as indicated by the correlation of it with SCS but not with the other variables)
-
-  repli_model_years <- '
-  # direct paths
-    scs       ~   a1 * ncs + y * years
-    erq_reap  ~   a2 * ncs
-    erq_supp  ~   a3 * ncs
-    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
-
-  # indirect effects
-    Indirect1 := (a1 * b1) + (y * b1)
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3) + (y * b1)
-'
-
-  # Determine the model fit
-
-  fityears <- sem(
-    model = repli_model_years,
-    data  = score_data,
-    se = "bootstrap",
-    bootstrap = 2000
-  )
-
-  # Get summary
-
-  fityears_summ <- summary(fityears, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
-
 Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
@@
 
-```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # SEM with demand-resource-ratios
-
-  sem_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
-    DRF =~ drf1 + drf2 + drf3
-    MBI =~ mbi_ee + mbi_dp + mbi_rpe
-
-  # structural model
-    DTH ~ a1 * NFC
-    DTL ~ a2 * NFC
-    DRF ~ a3 * NFC
-    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
-
-  # Determine the model fit
-
-  fit2 <- sem(
-    model = sem_model,
-    data  = score_data,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  fit2_summ <- summary(fit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-
-```
-
-```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  drr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
-                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
-                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
-                                      "Total Effect"),
-                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  drr_table[2:ncol(drr_table)] <- format(round(drr_table[2:ncol(drr_table)], digits = 3), nsmall = 2)
+```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the demand-resource-ratio model."}
 
@@
 
-```{r exploringbadfit, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Use function from http://www.sthda.com/english/wiki/correlation-matrix-a-
-  # quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-
-  # using-r-software#a-simple-function-to-format-the-correlation-matrix
-  # accessed on September 23rd 2021
-
-  flattenCorrMatrix <- function(cormat, pmat) {
-    ut <- upper.tri(cormat)
-    data.frame(
-      row = rownames(cormat)[row(cormat)[ut]],
-      column = rownames(cormat)[col(cormat)[ut]],
-      cor  =(cormat)[ut],
-      p = pmat[ut]
-      )
-  }
-
-  # Compute data frame of partial correlations
-
-  partialcorr <- flattenCorrMatrix(pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
-                                                     "erq","erq_supp","erq_reap","scs","ncs",
-                                                     "dth","dtl","drf","covb")], method = "spearman")$estimate,
-                                  pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
-                                                    "erq","erq_supp","erq_reap","scs","ncs",
-                                                    "dth","dtl","drf","covb")], method = "spearman")$p.value)
-  # Add easy-to-read significance column
-
-  partialcorr$sign <- ifelse(partialcorr$p < 0.05, "sign", "ns")
-
-```
-
-```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
-
-  # Exploratory analysis I: MBI subscale instead of sum score
-
-  explor1_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
-    DRF =~ drf1 + drf2 + drf3
-    RPE =~ mbi_rpe
-
-  # structural model
-    DTH ~ a1 * NFC
-    DTL ~ a2 * NFC
-    DRF ~ a3 * NFC
-    RPE ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
-
-  # Determine the model fit
-
-  fit_explor1 <- sem(
-    model = explor1_model,
-    data  = score_data,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  fit_explor1_summ <- summary(fit_explor1, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
-
-```{r exploratory1table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  drr_rpe_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on RPE",
-                                      "DTH on RPE", "DTL on RPE", "DRF on RPE",
-                                      "NFC on RPE via DTH", "NFC on RPE via DTL", "NFC on RPE via DRF",
-                                      "Total Effect"),
-                          "$B$" = c(fit_explor1_summ$PE$est[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fit_explor1_summ$PE$se[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fit_explor1_summ$PE$z[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fit_explor1_summ$PE$ci.lower[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fit_explor1_summ$PE$ci.upper[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  drr_rpe_table[2:ncol(drr_rpe_table)] <- format(round(drr_rpe_table[2:ncol(drr_rpe_table)], digits = 3), nsmall = 2)
+```{r exploratory1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the demand-resource-ratio model with reduced personal efficacy in place of the MBI score."}
 
@@
 The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
-
-```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
-
-  # Exploratory analysis II: Covid burden as a covariate
-
-  explor2_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DRF =~ drf1 + drf2 + drf3
-
-  # structural model
-    covb ~ yc * years
-    scs ~ ys * years
-    NFC ~~ scs
-    NFC ~~ covb
-    DTH ~ cdth * covb + sdth * scs + ndth* NFC
-    DRF ~ sdrf * scs + ndrf * NFC
-    DTH ~~ DRF
-    mbi_ee ~ dthe * DTH + ce * covb
-    mbi_rpe ~ drfr * DRF
-
-    mbi_ee ~~ mbi_rpe
-    NFC ~~ years
-
-    dth1 ~~ dth2
-    dth1 ~~ dth3
-    dth2 ~~ dth3
-
-    drf1 ~~ drf2
-    drf1 ~~ drf3
-    drf2 ~~ drf3
-
-  # Indirect effects
-    Indirect1 := (ndrf * drfr) + (ys * sdrf * drfr)
-    Indirect2 := (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2
-
-  # total effect
-    Total := (ndrf * drfr) + (ys * sdrf * drfr) + (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)
-'
-
-  # Determine the model fit
-
-  fit_explor2 <- sem(
-    model = explor2_model,
-    data  = score_data,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
 
@@
 
-```{r outlierconsistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # Tests for internal consistency
-
-    # Create data frame to feed values into
-
-    outlierconsistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
-                                          "lower CI omega","raw omega","upper CI omega"))
-
-    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios
-
-    set.seed(13) # seed for reproducing the bootstrapping
-
-    # Maslach Burnout Inventory
-
-    cronalph <- alpha(mbi, check.keys = TRUE)
-    macomega <- ci.reliability(data=mbi[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI emotional exhaustion
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI depersonalization
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # MBI reduced personal efficacy
-
-    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(mbi[-161,], select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ
-
-    cronalph <- alpha(erq, check.keys = TRUE)
-    macomega <- ci.reliability(data=erq[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ suppression
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # ERQ reappraisal
-
-    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
-    macomega <- ci.reliability(data=subset(erq[-161,], select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Self Control Scale
-
-    cronalph <- alpha(scs, check.keys = TRUE)
-    macomega <- ci.reliability(data=scs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Need for Cognition Scale
-
-    cronalph <- alpha(ncs, check.keys = TRUE)
-    macomega <- ci.reliability(data=ncs[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Covid burden
-
-    cronalph <- alpha(covb, check.keys = TRUE)
-    macomega <- ci.reliability(data=covb[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too High
-
-    cronalph <- alpha(dth, check.keys = FALSE)
-    macomega <- ci.reliability(data=dth[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demands Too Low
-
-    cronalph <- alpha(dtl, check.keys = FALSE)
-    macomega <- ci.reliability(data=dtl[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    # Demand Resource Fit
-
-    cronalph <- alpha(drf, check.keys = FALSE)
-    macomega <- ci.reliability(data=drf[-161,], type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
-    outlierconsistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
-                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
-                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)
-
-    remove(cronalph,macomega) # delete the temporary variable
-
-```
-
-```{r outliercorrelations, echo=FALSE, message=FALSE, warning=FALSE}
-
-    # correlate variables
-    outliercorrelations <- correlation_matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                    "scs","ncs","dth","dtl","drf","covb")],
-                                       type = "spearman",
-                                       use = "lower",
-                                       show_significance = FALSE,
-                                       replace_diagonal = TRUE,
-                                       replacement = "")
-
-    # reorder the columns of the consistencies data frame to match the correlation columns
-    outlierconsist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
-
-    # create a vector of consistencies to be used as the diagonal in a table later
-    outlierconsist_diag <- cbind(format(round(t(outlierconsist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
-                          format(round(t(outlierconsist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
-
-    # paste together to create the output "alpha(omega)"
-    outlierconsist_diag <- apply(outlierconsist_diag[,c(1:4)], 1 ,paste, collapse = "")
-
-    # add previously assembled diagonal with alpha and omega values
-    diag(outliercorrelations) <- outlierconsist_diag
-
-    # set row and column names for better table printing
-    row.names(outliercorrelations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
-                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
-    colnames(outliercorrelations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")
-
-    # create array with p-values of correlation coefficients
-    outliercorr_pvalues <- rcorr(as.matrix(score_data_no_outlier[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
-                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
-    # replace upper triangle with NA
-    outliercorr_pvalues[upper.tri(outliercorr_pvalues, diag = TRUE)] <- NA
-
-    # replace p-values with asterisks depending on significance level
-    outliercorr_pvalues <- ifelse(is.na(outliercorr_pvalues), "",
-                                  ifelse(outliercorr_pvalues < .001, "***", ifelse(outliercorr_pvalues < .01, "**", ifelse(outliercorr_pvalues < .05, "*", ""))))
-
-    # convert to matrix for the paste()-function
-    outliercorrelations <- as.matrix(outliercorrelations)
-    outliercorr_pvalues <- as.matrix(outliercorr_pvalues)
-
-    # paste correlations and asterisks together
-    outliercorrelations <- matrix(paste(outliercorrelations, outliercorr_pvalues, sep = ""),
-                           nrow = nrow(outliercorrelations), dimnames = dimnames(outliercorrelations))
-
-```
-
 ```{r outliercorrelationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}
@@
 
-```{r outlierobjective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # Replication of Grass et al. (2018)
-
-  outlierrepli_model <- '
-  # direct paths
-    scs       ~   a1 * ncs
-    erq_reap  ~   a2 * ncs
-    erq_supp  ~   a3 * ncs
-    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
-'
-
-  # Determine the model fit
-
-  outlierfit <- sem(
-    model = outlierrepli_model,
-    data  = score_data_no_outlier,
-    se = "bootstrap",
-    bootstrap = 2000
-  )
-
-  # Get summary
-
-  outlierfit_summ <- summary(outlierfit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-```
-
 ```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  outlierreplic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
-                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
-                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
-                                   "Total Effect"),
-                          "$B$" = c(outlierfit_summ$PE$est[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(outlierfit_summ$PE$se[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(outlierfit_summ$PE$z[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(outlierfit_summ$PE$pvalue[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(outlierfit_summ$PE$ci.lower[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(outlierfit_summ$PE$ci.upper[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(outlierfit_summ$PE$std.all[outlierfit_summ$PE$label != "" & outlierfit_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  outlierreplic_table[2:ncol(outlierreplic_table)] <- format(round(outlierreplic_table[2:ncol(outlierreplic_table)], digits = 3), nsmall = 2)
 
@@
 
-```{r outlierobjective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-  # SEM with demand-resource-ratios
-
-  outliersem_model <- '
-  # measurement model
-    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
-    DTH =~ dth1 + dth2 + dth3
-    DTL =~ dtl1 + dtl2 + dtl3
-    DRF =~ drf1 + drf2 + drf3
-    MBI =~ mbi_ee + mbi_dp + mbi_rpe
-
-  # structural model
-    DTH ~ a1 * NFC
-    DTL ~ a2 * NFC
-    DRF ~ a3 * NFC
-    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
-
-  # indirect effects
-    Indirect1 := a1 * b1
-    Indirect2 := a2 * b2
-    Indirect3 := a3 * b3
-
-  # contrast (if significant, the effects differ)
-    Contrast := Indirect1 - Indirect2 - Indirect3
-
-  # total effect
-    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
-
-  # Determine the model fit
-
-  outlierfit2 <- sem(
-    model = outliersem_model,
-    data  = score_data_no_outlier,
-    estimator = "MLR"
-  )
-
-  # Get summary
-
-  outlierfit2_summ <- summary(outlierfit2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
-          estimates = TRUE, ci = TRUE)
-
-```
-
-```{r outlierobjective2table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  outlierdrr_table <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
-                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
-                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
-                                      "Total Effect"),
-                          "$B$" = c(outlierfit2_summ$PE$est[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(outlierfit2_summ$PE$se[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(outlierfit2_summ$PE$z[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(outlierfit2_summ$PE$pvalue[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(outlierfit2_summ$PE$ci.lower[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(outlierfit2_summ$PE$ci.upper[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(outlierfit2_summ$PE$std.all[outlierfit2_summ$PE$label != "" & outlierfit2_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  outlierdrr_table[2:ncol(outlierdrr_table)] <- format(round(outlierdrr_table[2:ncol(outlierdrr_table)], digits = 3), nsmall = 2)
+```{r outlierobjective2table, echo=FALSE, message=FALSE, warning=FALSE, caption = "Results of the demand-resource-ratio model."}
 
@@
 
-```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  replic_years_table <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
-                                  "NFC on Reappraisal", "NFC on Suppression",
-                                  "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
-                                  "NFC and years spent teaching on RPE via Self Control",
-                                  "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
-                                  "Total Effect"),
-                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  replic_years_table[2:ncol(replic_years_table)] <- format(round(replic_years_table[2:ncol(replic_years_table)], digits = 3), nsmall = 2)
+```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE, caption = "Results of the replication of Grass et al. (2018) when including years spent teaching."}
 
@@
 
-```{r explor2table, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # put relevant data from the mediation into a table for reporting
-
-  # put data into data frame
-
-  explor2_table <- data.frame("Path" = c("Years on COVB", "Years on SCS",
-                                   "COVB on DTH", "SCS on DTH", "NFC on DTH",
-                                   "SCS on DRF", "NFC on DRF",
-                                   "DTH on EE", "COVB on EE", "DRF on RPE",
-                                   "NFC and Years on RPE via SCS and DRF",
-                                   "NFC and Years on EE via SCS, COVB, and DTH",
-                                   "Total Effect"),
-                          "$B$" = c(fit_explor2_summ$PE$est[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "$SE$" = c(fit_explor2_summ$PE$se[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "$z$-value" = c(fit_explor2_summ$PE$z[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "$p$-value" = c(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "CI Lower" = c(fit_explor2_summ$PE$ci.lower[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "CI Upper" = c(fit_explor2_summ$PE$ci.upper[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          "$\\beta$" = c(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
-                          check.names = FALSE)
-
-  # format the numbers to three digits after the decimal point
-
-  explor2_table[2:ncol(explor2_table)] <- format(round(explor2_table[2:ncol(explor2_table)], digits = 3), nsmall = 2)
+```{r explor2table, echo=FALSE, message=FALSE, warning=FALSE, caption = "Results of the exploratory model with Covid burden."}
 

### 2022-02-21 Manuscript/Analysis.R

@@ -1,0 +1,1174 @@
+################################################################################
+#
+# Analysis script for the manuscript
+# "NFC and burnout in teachers - A replication and extension study"
+# by Zerna, J., Engelmann, N., Strobel, A., & Strobel., A. (2022)
+#
+# Corresponding author: Josephine Zerna (josephine.zerna@tu-dresden.de)
+#
+# Please download the repsitory from github.com/JZerna/NFC-Burnout
+#
+#
+################################################################################
+
+##### Setup ####################################################################
+
+  # load here-library for path-independent project structure (install here by calling install.packages("here") if necessary)
+  # set top level directory to source file
+  
+  library(here)
+  
+  here::i_am("flag_top_level_NFCBurnout.txt")
+  
+  # load reproducible environment library to get all packages with correct versions form the renv.lock file
+  # install renv by calling install.packages("renv") if necessary
+  
+  library(renv)
+  renv::activate(here("Manuscript"))
+  renv::restore(here("Manuscript"))
+  
+  # the required packages are:
+  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
+  # "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "ppcor", "stats", "apa", "GGally"
+  
+  # Seed for random number generation
+  set.seed(13)
+  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+  
+  # Set a number for the bootstrapping procedures
+  bootnum <- 5000
+  
+##### Data import ##############################################################
+  
+  # Load the data file
+  
+  load(here("Data", "data.Rda"))
+  
+  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
+  consistencies <- read_rds(here("Data", "consistencies.rds"))
+  outlierconsistencies <- read_rds(here("Data", "outlierconsistencies.rds"))
+  
+  # create a vector of consistencies to be used as the diagonal in a table later
+  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
+                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
+  # paste together to create the output "alpha(omega)"
[…]

### 2022-02-21 Manuscript/Analysis.R
changed how correlation table is created

@@ -42,7 +42,7 @@
   
   # Load the data file
   
-  load(here("Data", "data.Rda"))
+  base::load(here("Data", "data.Rda"))
   
   # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
   consistencies <- read_rds(here("Data", "consistencies.rds"))
@@ -264,18 +264,6 @@
   
   desc_met[ ,c("Mean","SD","Skewness","Kurtosis")] <- round(desc_met[ ,c("Mean","SD","Skewness","Kurtosis")], digits = 2)
   
-  # Put the information in a table
-  
-  desc_table <-
-    kbl(desc_met,
-        caption = "Descriptive statistics of the questionnaire scores.",
-        booktabs = T, # no vertical lines
-        escape = F, # correctly print special characters
-        align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
-             escape = F, # correctly print special characters
-             threeparttable = T) # line breaks in the footnote
   
 ##### Tests for internal consistency ###########################################
   
@@ -433,7 +421,7 @@
     
     # run correlation analysis using Hmisc package
     correlation_matrix <- Hmisc::rcorr(x, type = type)
-    R <- correlation_matrix$r # Matrix of correlation coeficients
+    R <- correlation_matrix$r # Matrix of correlation coefficients
     p <- correlation_matrix$P # Matrix of p-value 
     
     # transform correlations to specific character format
@@ -481,7 +469,8 @@
                                                   "scs","ncs","dth","dtl","drf","covb")],
                                      type = "spearman",
                                      use = "lower",
-                                     show_significance = FALSE,
+                                     digits = 2,
+                                     show_significance = TRUE,
[…]

### 2022-02-21 Manuscript/Manuscript.Rmd
changed YAML decimal alignment + first comments

@@
   Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
-  The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to the demands.
+  The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to their demands.
 
@@
     - \usepackage{chngcntr}
+    - \usepackage{siunitx}
+    - \newcolumntype{d}{S[table-format=3.2]}
 ---
@@
 As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait [@Stumm2013], and has come to the fore of psychological research in the last years.
-NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984].
-<!-- den Satz würde ich entweder weglassen oder noch die deutsche NFC Skala mit referenzieren -->
-While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020]<!-- von Stumm & Ackerman, 2013 als Metaanalyse mit aufnehmen, dafür 1-2 Einzelstudien raus -->, recent investigations have also looked at NFC as a personal resource in academic and work contexts.
-Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020].
-These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005] consequences.
+NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984; German form: @Bless1994].
+While many studies have found medium sized positive associations of NFC with academic performance [@Cazan2014; @Stumm2013; @Grass2017; @Lavrijsen2021; @Zheng2020], recent investigations have also looked at NFC as a personal resource in academic and work contexts.
+Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020], with these associations being small to medium sized by and large.
+These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological consequences [@Madsen2017; @Maslach2016; @Wiesner2005].
 
@@
 Lackritz [-@Lackritz2004] found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
-Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced personal efficacy.
+Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: *Emotional exhaustion*, *depersonalisation*, and *reduced personal efficacy*.
 
@@
 NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
-This is supported by findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
+This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
@@
 NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
-Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
+*Reduced personal efficacy* was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
 NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
@@
 We preregistered two exploratory analyses.
-Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales [@Grass2018; @Naderi2018].
+Firstly, we repeated the SEM with the subscale *reduced personal efficacy* in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales [@Grass2018; @Naderi2018].
 And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.
@@
 ```{r cdescriptivestable, echo=FALSE, message=FALSE, warning=FALSE, caption="Descriptive statistics of the questionnaire scores."}
+
   desc_table <-
@@
       escape = FALSE, # correctly print special characters
-      align = rep("l",14)) %>% # left aligns the text in every column
+      align = c("l",rep("d",13))) %>% # left aligns the text in every column
     kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
 In order to replicate findings by Grass et al.
-[-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
+[-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and *reduced personal efficacy* was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
 The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
@@
 Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
-We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
-However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Furthermore, even though NFC and reduced personal efficacy were both associated with self-control, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
+We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and *reduced personal efficacy* ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"], digits = 3)`), nor the indirect effect of NFC on *reduced personal efficacy* via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
+Furthermore, even though NFC and *reduced personal efficacy* were both associated with self-control, the indirect effect of NFC on *reduced personal efficacy* via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
 Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al.
@@
 Standardized estimates, total, direct, and indirect effects are displayed and listed in *Supplementary Material S3*.
-The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the first model.
-However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
+The associations between NFC, self control, reappraisal, suppression, and *reduced personal efficacy* were almost identical to the first model.
+However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to *reduced personal efficacy* reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
 Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
@@
 
-The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
+The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale *reduced personal efficacy* would be used in place of the MBI sum score.
 Path coefficients, total, direct, and indirect effects are displayed and listed in *Supplementary Material S4*.
 Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
-NFC showed no direct association with reduced personal efficacy ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
-And again, NFC was associated with lower scores in the latent variable DTH ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
+NFC showed no direct association with *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
+And again, NFC was associated with lower scores in the latent variable DTH ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
 The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
@@
 All fit indices suggested that the proposed model had good fit while the baseline model did not ($\chi^2=$ `r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$ `r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$ `r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$ `r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
-Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
+Neither the ERQ sum score, nor its subscales, nor the *depersonalisation* subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
 Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
@@
 In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
-DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
-Covid burden was not associated with DRF or reduced personal efficacy.
+DRF scores fully mediated the negative association of NFC and self control with *reduced personal efficacy* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and *emotional exhaustion*, but DTH also partially mediated between Covid burden and *emotional exhaustion* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Covid burden was not associated with DRF or *reduced personal efficacy*.
 
@@
 
-While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and reduced personal efficacy were negatively related, but there was no association between NFC and reappraisal.
-There was, however, a positive association between self-control and reduced personal efficacy, and a negative one between NFC and suppression.
+While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and *reduced personal efficacy* were negatively related, but there was no association between NFC and reappraisal.
+There was, however, a positive association between self-control and *reduced personal efficacy*, and a negative one between NFC and suppression.
 
-NFC had a direct and negative effect on reduced personal efficacy, but this relationship was not mediated by any other variable.
-Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower reduced personal efficacy.
+NFC had a direct and negative effect on *reduced personal efficacy*, but this relationship was not mediated by any other variable.
+Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower *reduced personal efficacy*.
 The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
@@
 
-We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with reduced personal efficacy, but not their association with NFC.
-There is ample evidence that reappraisal is associated with positive outcomes for students [@Levine2012;@Schmidt2010;@Haga2007] and teachers alike [@Moe2020;@Tsouloupas2010;@Jiang2016], so it is suprising that reappraisal did not mediate between NFC and reduced personal efficacy.
+We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with *reduced personal efficacy*, but not their association with NFC.
+There is ample evidence that reappraisal is associated with positive outcomes for students [@Levine2012;@Schmidt2010;@Haga2007] and teachers alike [@Moe2020;@Tsouloupas2010;@Jiang2016], so it is suprising that reappraisal did not mediate between NFC and *reduced personal efficacy*.
 Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
 One possible explanation could be that the ways by which reappraisal can be achieved, such as taking the role of an uninvolved observer, are less feasible for teachers in retaining their sense of efficacy in the classroom than the self-control needed to structurally manage students and situations.
-Hence, the mediation of NFC and reduced personal efficacy by self-control when taking the years spent teaching into account.
+Hence, the mediation of NFC and *reduced personal efficacy* by self-control when taking the years spent teaching into account.
 
@@
 
-The demand-resource-ratio model with the subscale reduced personal efficacy in place of the MBI score did not have good fit indices.
-Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and reduced personal efficacy via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
+The demand-resource-ratio model with the subscale *reduced personal efficacy* in place of the MBI score did not have good fit indices.
+Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and *reduced personal efficacy* via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
 Overall, this pattern did not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI [@Grass2018;@Naderi2018].
@@
 Due to the complete freedom in setting up the structure of this model, it had good fit indices.
-Interestingly, the third MBI subscale depersonalisation and the latent variable DTL did not explain any variance in the model, so they were removed.
+Interestingly, the third MBI subscale *depersonalisation* and the latent variable DTL did not explain any variance in the model, so they were removed.
 Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
@@
 Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology [@Hauk2018] and therefore stressed by the prospect of online teaching.
-Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in reduced personal efficacy.
+Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in *reduced personal efficacy*.
 Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower DTH score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
-The degree of association between DTH and emotional exhaustion indeed suggested a congruence between the two, indicating that emotional exhaustion in burnout is caused by excessive demands that cannot be met with one's resources, while reduced personal efficacy in burnout is caused by a lack of opportunities to utilize one's resources at work.
-Curiously, higher Covid burden also showed a small negative association with emotional exhaustion.
+The degree of association between DTH and *emotional exhaustion* indeed suggested a congruence between the two, indicating that *emotional exhaustion* in burnout is caused by excessive demands that cannot be met with one's resources, while *reduced personal efficacy* in burnout is caused by a lack of opportunities to utilize one's resources at work.
+Curiously, higher Covid burden also showed a small negative association with *emotional exhaustion*.
 It could be that for some teachers, remote teaching was experienced as a relief from the strain of dealing with a group of over twenty students each day, who are more likely to misbehave in a classroom setting than when they are studying at home.
@@
       escape = FALSE, # correctly print special characters
-      align = rep("l",14)) %>% # left aligns the text in every column
+      align = c("l",rep("d",14))) %>% # left aligns the text in every column
     kable_styling(latex_options = c("striped", "scale_down")) %>%

### 2022-02-22 Manuscript/Manuscript.Rmd
added MBI subscale explanation

@@
 Lackritz [-@Lackritz2004] found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
-Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: *Emotional exhaustion*, *depersonalisation*, and *reduced personal efficacy*.
+Burnout is most often assessed using the Maslach Burnout Inventory (MBI) [@Maslach1997], a self-report questionnaire with three subscales: *Emotional exhaustion*, a sense of fatigue and depletion, *depersonalisation*, a negative attitude towards clients, along with a loss of idealism, and *reduced personal efficacy*, a decline of capability and coping skills.
 
@@
 Grass et al.
-[-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active coping, and passive coping, but not by suppression or self-control.
+[-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
 Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
 The findings by Grass et al.
-[-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
+[-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
 One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.

### 2022-02-22 Manuscript/Manuscript.Rmd
replaced abbreviations with latent factor names

@@
 These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
+This can take the form of patients with higher NFC having lower intentions to consult their physician [@Latimer2007] or adults with higher NFC having higher intentions to consume high calorie beverages [@Gallivan2020] after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
 Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
@@
 In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
-These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery [@Salanova2006].
-We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
+These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery [@Salanova2006].
+We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (*demands too high*), demands that are too low for one’s personal resources (*demands too low*), and a balanced fit of demands and resources (*demand-resource-fit*).
 Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
-Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
-And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with DTH and negatively associated with DRF.
-However, we had no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
+Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, positively associated with *demands too low*, and positively associated with *demand-resource-fit*.
+And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
+However, we had no hypothesis regarding the association of *demands too low* and burnout, because even though *demands too low* is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
 It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
@@
 For the demand-resource-ratios, we used three items from the work satisfaction scale each.
-The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
+The latent factor *demands too high* was indicated by items 4, 8, and 9, *demands too low* by the recoded items 12, 26, and 27, and *demand-resource-fit* by items 17, 22, and 24.
 The items can be translated as follows: 4) "There is too much pressure on me.", 8) "There is often too much being demanded of us at work.", 9) "I often feel tired and weary because of my work.", 12) "I can realize my ideas here.", 17) "I take pleasure in my work.", 22) "Does your place of work give you the opportunity to do what you do best?", 24) "Does your place of work give you enough opportunities to use your skills?", 26) "Are you happy with your promotion prospects?", and 27) "Are you happy with your position when comparing it to your skills?".
@@
 Correlations and internal consistencies are displayed in Table 2.
-For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
+For this descriptive analysis, the variables *demands too high*, *demands too low*, and *demand-resource-fit* were computed as a sum of their item scores, not weighted as in the structural equation model.
 Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
 The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
-As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
-Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`).
+As expected, the MBI score was positively correlated with *demands too high* (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`) and negatively with *demand-resource-fit* (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
+Surprisingly, the correlation between the MBI score and *demands too low* was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`).
 The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.
@@
 NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
-Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
-The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
+The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
 
@@
     pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, RPE = Reduced Personal Efficacy subscale of the Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, *demand-resource-fit* = Demand Resource Fit, RPE = Reduced Personal Efficacy subscale of the Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
 Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
-NFC showed no direct association with *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
-And again, NFC was associated with lower scores in the latent variable DTH ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
-The latent variable DTL was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
+NFC showed no direct association with *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
+And again, NFC was associated with lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
+The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
 
@@
 NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 3)`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"], digits = 3)`).
-In turn, NFC was associated with higher DRF scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
-DRF scores fully mediated the negative association of NFC and self control with *reduced personal efficacy* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and *emotional exhaustion*, but DTH also partially mediated between Covid burden and *emotional exhaustion* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
-Covid burden was not associated with DRF or *reduced personal efficacy*.
+In turn, NFC was associated with higher *demand-resource-fit* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower *demands too high* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
+*Demand-resource-fit* scores fully mediated the negative association of NFC and self control with *reduced personal efficacy* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for *demands too high* scores and *emotional exhaustion*, but *demands too high* also partially mediated between Covid burden and *emotional exhaustion* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Covid burden was not associated with *demand-resource-fit* or *reduced personal efficacy*.
 
@@
 
-Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via DTH and DRF but not DTL.
+Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via *demands too high* and *demand-resource-fit* but not *demands too low*.
 Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
@@
 The demand-resource-ratio model with the subscale *reduced personal efficacy* in place of the MBI score did not have good fit indices.
-Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and *reduced personal efficacy* via DTH did not reach significance, but both the mediation via DRF and the total effect remained significant.
+Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and *reduced personal efficacy* via *demands too high* did not reach significance, but both the mediation via *demand-resource-fit* and the total effect remained significant.
 Overall, this pattern did not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI [@Grass2018;@Naderi2018].
 Teachers with high NFC appear to retain their sense of personal efficacy to a higher degree, because they experience a fit of demands and resources, which allows them to complete tasks and reinforce their self-efficacy in return.
-However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via DTH was not significant with this subscale, suggesting that the large association of DTH and MBI in the confirmatory model was driven by a different subscale.
+However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via *demands too high* was not significant with this subscale, suggesting that the large association of *demands too high* and MBI in the confirmatory model was driven by a different subscale.
 To explore this, we built a second exploratory model.
@@
 Due to the complete freedom in setting up the structure of this model, it had good fit indices.
-Interestingly, the third MBI subscale *depersonalisation* and the latent variable DTL did not explain any variance in the model, so they were removed.
+Interestingly, the third MBI subscale *depersonalisation* and the latent variable *demands too low* did not explain any variance in the model, so they were removed.
 Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
@@
 Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in *reduced personal efficacy*.
-Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower DTH score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
-The degree of association between DTH and *emotional exhaustion* indeed suggested a congruence between the two, indicating that *emotional exhaustion* in burnout is caused by excessive demands that cannot be met with one's resources, while *reduced personal efficacy* in burnout is caused by a lack of opportunities to utilize one's resources at work.
+Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower *demands too high* score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
+The degree of association between *demands too high* and *emotional exhaustion* indeed suggested a congruence between the two, indicating that *emotional exhaustion* in burnout is caused by excessive demands that cannot be met with one's resources, while *reduced personal efficacy* in burnout is caused by a lack of opportunities to utilize one's resources at work.
 Curiously, higher Covid burden also showed a small negative association with *emotional exhaustion*.

### 2022-02-22 Manuscript/Manuscript.Rmd
added ethics

@@
 Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
-Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, positively associated with *demands too low*, and positively associated with *demand-resource-fit*.
+Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, and positively associated with *demands too low* and *demand-resource-fit*.
 And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
@@
 It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
+To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.
 
@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
-Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript are available at [https://osf.io/36ep9/](https://osf.io/36ep9/).
+Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the *R* package *papaja* [@Aust2020], are available at [https://osf.io/36ep9/](https://osf.io/36ep9/).
+The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
+It was not considered to require further ethical approvals and hence, as uncritical concerning ethical aspects according to the criteria used by the Ethics Committee, which includes aspects of the sample of healthy adults, voluntary attendance, noninvasive measures, no deception, and appropriate physical and mental demands on the subject.
 

### 2022-02-22 Manuscript/Manuscript.Rmd
added power calculation

@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
-Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the *R* package *papaja* [@Aust2020], are available at [https://osf.io/36ep9/](https://osf.io/36ep9/).
+Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package *papaja* [@Aust2020], are available at [https://osf.io/36ep9/](https://osf.io/36ep9/).
 The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
@@
 ## Participants
-Teachers were recruited via social media, emails to colleagues of N.E., and to Saxon schools with the request to pass on the information.
+We set out to recruit a sample of $N\ge287$ teachers as determined using the R package *pwr* [@Champely2020], assuming a small to medium correlation of $r=.20$ between the measures of interest and targeting at a power of $1-\beta=.80$ at  $\alpha=.01$.
+Teachers were recruited via social media, personal contacts to teachers, and to Saxon schools with the request to pass on the information.
 All teachers were eligible, no payment was issued.
@@
 At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.
+This may have also be one reason why we did not reach our estimated sample size.
+Using the smallest standardized indirect effect from the mediation in Grass et al.
+[-@Grass2018] in a post hoc power analysis with *G\*Power* [@Faul2007;@Faul2009] yielded a power of $1-\beta=.85$ for linear multiple regression, given $\alpha=.05$, $N=180$, and $f^2=.05$.
 

### 2022-02-22 Manuscript/Manuscript.Rmd
replaced p value formatting function

@@
 
+  # function for reporting p-values in main text (wrapper for papaja::printp)
+
+  rp <- function(p, bound = "max") {
+    if (length(p) == 1) {
+      # single p-value is passed
+      if (p >= .001) {
+        # returns "p = ..."
+        p_out = paste0("$p=", papaja::printp(p), "$")
+    } else {
+        # returns "p < .001"
+        p_out = paste0("$p", papaja::printp(p), "$")
+    } 
+  } else if (length(p) > 1) {
+      # vector of p-values is passed
+      if (bound == "max") {
+        # returns "p <= ..."
+        p_out = paste0("$p", "\\le", papaja::printp(max(p)), "$")
+    } else if (bound == "min") {
+        # returns "p >= ..."
+        p_out = paste0("$p", "\\ge", papaja::printp(min(p)), "$")
+    }
+
+  }
+    return(p_out)
+  }
+
 ```
@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], NFC using the 16-item Need for Cognition Scale [NCS, @Bless1994], self-control using the 13-item Self-Control Scale [SCS, @Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire [ERQ, @Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
+Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], with items such as "I don't really care what happens to some recipients" and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
+Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and low retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
+NFC was assessed with the 16-item short version of the German NFC scale [NCS; @Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
+Self-control was measured using the short form of the German Self-Control Scale [SCS-K-D; @Bertrams2009a] that comprises 13 items (e.g., “I am able to work effectively toward long-term goals”) with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability [Cronbach’s $\alpha$  ~ .80, 7-week retest reliability $r_{tt}$  = .82; @Bertrams2009a].
+Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire [ERQ, @Abler2009].
+The scale has items such as "When I’m faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (reappraisal) and "I keep my emotions to myself" (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2019].
+Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014] with items such as "Sometimes I feel like my work doesn't really matter in my firm", which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
+The scale has a split-half reliability of $r_{tt}=.95$ [@Fischer2014].
 Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
 The translated Covid-19 items can be found in the *Supplementary Material S1*.
-The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.<!-- warum eigentlich nicht? -->
 Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.
@@
 The questionnaires were provided online using SoSci Survey [@Leiner2019].
-Participants were informed about aims and duration of the study and data security, provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.
+Participants were informed about aims and duration of the study and data security, then they provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.
 
@@
 Since Cronbach's Alpha has been criticized for being insensitive to violations of internal consistency [@Dunn2014; @Taber2018], the additional computation of MacDonald's Omega has the purpose of ensuring a more reliable estimation.
+Correlations between variables were classified according the scheme by Gignac and Szodorai [-@Gignac2016], which recommends .10, .20, and .30 to be considered small, typical, and relatively large, respectively.
 
@@
 NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
-Following Grass et al. [-@Grass2018], the results of the model were appraised by using $N$ = 2,000 bootstrap samples for confidence intervals.
-Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model, the Comparative Fit Index (CFI), which compares the fit to the baseline model, the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix, and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account.
+Following Grass et al. [-@Grass2018], bootstrapped confidence with $N=2,000$ replicates were computed to account for deviations from normality.
+Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).
 
@@
 All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
-The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al.
-[-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
+The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure [@Little2002], a method that is used in SEM when only relations between but not within constructs are of interest.
 Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
@@
 Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
-Only the ERQ sum score and its reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
+Only the ERQ sum score and its reappraisal subscale followed a normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].
 
@@
 The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
-As expected, the MBI score was positively correlated with *demands too high* (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`) and negatively with *demand-resource-fit* (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
+As expected, the MBI score showed a large positive correlation with *demands too high* (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`) and a large negatve one with *demand-resource-fit* (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`).
 Surprisingly, the correlation between the MBI score and *demands too low* was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown", print = FALSE)`).
@@
 Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
-We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and *reduced personal efficacy* ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
-However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"], digits = 3)`), nor the indirect effect of NFC on *reduced personal efficacy* via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
-Furthermore, even though NFC and *reduced personal efficacy* were both associated with self-control, the indirect effect of NFC on *reduced personal efficacy* via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
-Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al.
+We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"])`), and a negative association of habitual reappraisal and *reduced personal efficacy* ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"])`).
+However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"])`), nor the indirect effect of NFC on *reduced personal efficacy* via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"])`).
+Furthermore, even though NFC and *reduced personal efficacy* were both associated with self-control, the indirect effect of NFC on *reduced personal efficacy* via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"])`).
+Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, `r rp(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"])`), which was not the case in the study by Grass et al.
 [-@Grass2018].
@@
 The associations between NFC, self control, reappraisal, suppression, and *reduced personal efficacy* were almost identical to the first model.
-However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to *reduced personal efficacy* reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
-Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).
+However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, `r rp(fityears_summ$PE$pvalue[fityears_summ$PE$label == "y"])`), the indirect path leading from NFC and years spent teaching via self control to *reduced personal efficacy* reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, `r rp(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"])`).
+Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, `r rp(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"])`).
 
@@
 Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
-NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
-Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
-The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
+NFC showed no direct association with the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, `r rp(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"])`), even though it was negatively correlated with the sum score and all subscales.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, `r rp(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"])`) and via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, `r rp(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"])`).
+The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, `r rp(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"])`) nor to the MBI score ($\beta=$ `r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, `r rp(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"])`).
 
@@
 Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2=$ `r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
-NFC showed no direct association with *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
-And again, NFC was associated with lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
-The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
+NFC showed no direct association with *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"])`), but an indirect one via higher scores in the latent variable *demand-resource-fit* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"])`).
+And again, NFC was associated with lower scores in the latent variable *demands too high* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"])`), but the latter did not mediate the relationship between NFC and *reduced personal efficacy* ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"])`) as it did with the MBI score in the previous model.
+The latent variable *demands too low* was neither related to NFC ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"])`) nor to the MBI score ($\beta=$ `r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, `r rp(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"])`).
 
@@
 Neither the ERQ sum score, nor its subscales, nor the *depersonalisation* subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
-Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
-NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 3)`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 3)`), but not with years spent teaching ($p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"], digits = 3)`).
-In turn, NFC was associated with higher *demand-resource-fit* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower *demands too high* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
-*Demand-resource-fit* scores fully mediated the negative association of NFC and self control with *reduced personal efficacy* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for *demands too high* scores and *emotional exhaustion*, but *demands too high* also partially mediated between Covid burden and *emotional exhaustion* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
+Years spent teaching was associated with higher self control ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"])`) and higher Covid burden ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"])`) but not with NFC.
+NFC covaried with self control ($\sigma_{NFC,scs}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "scs"])`) and Covid burden ($\sigma_{NFC,covb}=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "covb"])`), but not with years spent teaching (`r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "years"])`).
+In turn, NFC was associated with higher *demand-resource-fit* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"])`) and lower *demands too high* scores ($\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"])`) but not directly with any of the two MBI subscales.
+*Demand-resource-fit* scores fully mediated the negative association of NFC and self control with *reduced personal efficacy* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"])`), which was also true for *demands too high* scores and *emotional exhaustion*, but *demands too high* also partially mediated between Covid burden and *emotional exhaustion* (indirect effect $\beta=$ `r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, `r rp(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"])`).
 Covid burden was not associated with *demand-resource-fit* or *reduced personal efficacy*.

### 2022-02-22 Manuscript/Manuscript.Rmd
added sentence to discussion intro

@@
 
-The present study aimed to replicate findings of mediators between Need for Cognition and burnout in teachers, as well as to extend the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
+To achieve this, we replicated findings of mediators between Need for Cognition and burnout, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
 In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.

### 2022-02-23 Manuscript/Manuscript.Rmd
added sample size to appendix tables

@@
 
-While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control were positively associated, and reappraisal and *reduced personal efficacy* were negatively related, but there was no association between NFC and reappraisal.
-There was, however, a positive association between self-control and *reduced personal efficacy*, and a negative one between NFC and suppression.
+While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control had a medium positive association, and reappraisal and *reduced personal efficacy* had a small negative association, but NFC and reappraisal were not associated.
+There was, however, a small negative association between self-control and *reduced personal efficacy*, and between NFC and suppression.
 
-NFC had a direct and negative effect on *reduced personal efficacy*, but this relationship was not mediated by any other variable.
-Only when the amount of teaching experience was included as a predictor of self-control next to NFC, an indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower *reduced personal efficacy*.
+NFC had a direct, medium negative effect on *reduced personal efficacy*, but this relationship was not mediated by any other variable.
+Only when the amount of teaching experience was included as a predictor of self-control next to NFC, a very small indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower *reduced personal efficacy*.
 The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
@@
 (2018) when including years spent teaching.
-* $p<.05$, ** $p<.01$."}
+* $p<.05$, ** $p<.01$, $N=180$."}
 
@@
     column_spec(1, width = "5cm") %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=180$.",
              escape = F, # correctly print special characters
@@
 * $p<.05$, ** $p<.01$, *** $p<.001$.
-NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, RPE = reduced personal efficacy."}
+NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, RPE = reduced personal efficacy, $N=180$."}
 
@@
     column_spec(1, width = "5cm") %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching.",
+    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching, $N=180$.",
              escape = F, # correctly print special characters

### 2022-02-23 Manuscript/Manuscript.Rmd
added conclusions paragraph

@@
 Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
-Interestingly, the correlation between NFC and burnout, which can be classified as medium according to Gignac and Szodorai [-@Gignac2016], disappeared in the context of the demand-resource-ratios as mediators.
+Interestingly, the medium correlation between NFC and burnout disappeared in the context of the demand-resource-ratios as mediators.
 The mediator that did not reach significance was the perception of own resources exceeding the job demands.
@@
 ## Exploratory analyses
-### Demand-resource-ratio model with subscale
+### Demand-resource-ratio model with subscale reduced personal efficacy
 
@@
 So while those teachers did feel the pandemic burden, they also felt less emotionally exhausted.
+However, as this part of the study was exploratory, the results should be interpreted with some caution and examined with new data in a confirmatory approach.
 
@@
 
-The data used in this study had been collected for another purpose, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
+The data used in this study had been collected with a focus on emotion regulation and burnout, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
 Firstly, collecting coping style data would have enabled a full replication of the mediation model of Grass et al. [-@Grass2018].
@@
 Especially because we worked with pre-existing data, we preregistered all analyses and clearly differentiated between confirmatory and exploratory models in order to make the results as reliable as possible.
+
+## Conclusions
+
+Our study showed that self-control mediated between NFC and burnout when teaching experience was being taken into account.
+Contrary to prior studies, neither habitual use of reappraisal nor use of suppression mediated between NFC and burnout.
+However, a crucial role in the relation of NFC and burnout seemed to be the perceived ratio of personal resources and demands, specifically, a resource-demand-fit was associated with lower and excessive demands were associated with higher burnout scores.
 Applied to real-life teaching practise, our results suggest that a healthy work environment should offer ample opportunities to make use of one's abilities, without creating demands that are too high.

### 2022-02-23 Manuscript/Analysis.R
finally functional

@@ -24,8 +24,9 @@
   # install renv by calling install.packages("renv") if necessary
   
   library(renv)
-  renv::activate(here("Manuscript"))
-  renv::restore(here("Manuscript"))
+  source(here("Manuscript", "renv", "activate.R"))
+  #renv::activate(here("Manuscript"))
+  #renv::restore(here("Manuscript"))
   
   # the required packages are:
   # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
@@ -45,8 +46,8 @@
   base::load(here("Data", "data.Rda"))
   
   # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
-  consistencies <- read_rds(here("Data", "consistencies.rds"))
-  outlierconsistencies <- read_rds(here("Data", "outlierconsistencies.rds"))
+  consistencies <- readRDS(here("Data", "consistencies.rds"))
+  outlierconsistencies <- readRDS(here("Data", "outlierconsistencies.rds"))
   
   # create a vector of consistencies to be used as the diagonal in a table later
   consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
@@ -210,12 +211,12 @@
   }
   
   # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
-  multicorrplot <- ggpairs(score_data[,c("years","mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
+  multicorrplot <- GGally::ggpairs(score_data[,c("years","mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                          "scs","ncs","dth","dtl","drf","covb")], lower = list(continuous = my_fn))
   
   # It looked like there was an outlier in the data, especially visible in the MBI data
   # Check for the outlier in particular, using the data involved in the mediation
-  outlierplot <- outlier(score_data[ ,c(6,8:11)], plot = TRUE)
+  outlierplot <- psych::outlier(score_data[ ,c(6,8:11)], plot = TRUE)
   
   # Remove participant 161 in a second version of the data frame (for the supplementary material analysis)
   score_data_no_outlier <- score_data[score_data$mbi < 100, ]
@@ -227,7 +228,7 @@
[…]

### 2022-02-23 Manuscript/Manuscript.Rmd
corrected brackets in materials section

@@
 Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and low retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
-NFC was assessed with the 16-item short version of the German NFC scale [NCS; @Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
-The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
-Self-control was measured using the short form of the German Self-Control Scale [SCS-K-D; @Bertrams2009a] that comprises 13 items (e.g., “I am able to work effectively toward long-term goals”) with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability [Cronbach’s $\alpha$  ~ .80, 7-week retest reliability $r_{tt}$  = .82; @Bertrams2009a].
-Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire [ERQ, @Abler2009].
+NFC was assessed with the 16-item short version of the German NFC scale (NCS) [@Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+The scale shows comparably high internal consistency (Cronbach’s $\alpha>.80$) [@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
+Self-control was measured using the short form of the German Self-Control Scale [SCS-K-D; @Bertrams2009a] that comprises 13 items (e.g., “I am able to work effectively toward long-term goals”) with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach’s $\alpha>.80$, 7-week retest reliability $r_{tt}=.82$) [@Bertrams2009a].
+Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009].
 The scale has items such as "When I’m faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (reappraisal) and "I keep my emotions to myself" (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2019].

### 2022-02-23 Manuscript/Manuscript.Rmd
tried double backslash for &nbsp; but doesnt work

@@
     - \usepackage{chngcntr}
-    - \usepackage{siunitx}
-    - \newcolumntype{d}{S[table-format=3.2]}
 ---
@@
   desc_table <-
-      kbl(desc_met,
+      knitr::kable(desc_met,
           caption = "Descriptive statistics of the questionnaire scores.",
@@
           align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
-      kable_styling(latex_options = c("striped", "scale_down")) %>%
-      footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation.
+      kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+      kableExtra::footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation.
 \\\\textit{N} = 180.",
@@
   corr_table <-
-  kable(correlations,
+  knitr::kable(correlations,
       caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
@@
       escape = FALSE, # correctly print special characters
-      align = c("l",rep("d",13))) %>% # left aligns the text in every column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+      align = rep("l",14)) %>% # left aligns the text in every column
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
 \\\\textit{N} = 180.
@@
              escape = FALSE, # correctly print special characters
-             threeparttable = TRUE) %>% # line breaks in the footnote
+             threeparttable = T) %>% # line breaks in the footnote
   kableExtra::landscape() # make the table horizontal
@@
   replic_table <-
-    kbl(replic_table,
+    knitr::kable(replic_table,
         caption = "Results of the replication of Grass et al. (2018).",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
+    kableExtra::pack_rows("Total Effect", 11, 11) %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
   drrmodel_table <-
-    kbl(drr_table,
+    knitr::kable(drr_table,
         caption = "Results of the demand-resource-ratio model.",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
+    kableExtra::pack_rows("Total Effect", 11, 11) %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
   drr_rpe_table <-
-    kbl(drr_rpe_table,
+    knitr::kable(drr_rpe_table,
         caption = "Results of the demand-resource-ratio model with reduced personal efficacy in place of the MBI score.",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, *demand-resource-fit* = Demand Resource Fit, RPE = Reduced Personal Efficacy subscale of the Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
+    kableExtra::pack_rows("Total Effect", 11, 11) %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, *demand-resource-fit* = Demand Resource Fit, RPE = Reduced Personal Efficacy subscale of the Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
              escape = F, # correctly print special characters
@@
   outliercorr_table <-
-  kbl(outliercorrelations,
+  knitr::kable(outliercorrelations,
       caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
@@
       escape = FALSE, # correctly print special characters
-      align = c("l",rep("d",14))) %>% # left aligns the text in every column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+      align = rep("l",14)) %>% # left aligns the text in every column
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
 \\\\textit{N} = 179.
@@
   outlierreplic_table <-
-    kbl(outlierreplic_table,
+    knitr::kable(outlierreplic_table,
         caption = "Results of the replication of Grass et al. (2018).",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
+    kableExtra::pack_rows("Total Effect", 11, 11) %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
              escape = F, # correctly print special characters
@@
   outlierdrrmodel_table <-
-    kbl(outlierdrr_table,
+    knitr::kable(outlierdrr_table,
         caption = "Results of the demand-resource-ratio model.",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 8, 10) %>%
-    pack_rows("Total Effect", 11, 11) %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
+    kableExtra::pack_rows("Total Effect", 11, 11) %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.",
              escape = F, # correctly print special characters
@@
   replic_years_table <-
-    kbl(replic_years_table,
+    knitr::kable(replic_years_table,
         caption = "Results of the replication of Grass et al. (2018) when including years spent teaching.",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down")) %>%
-    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 9, 11) %>%
-    pack_rows("Total Effect", 12, 12) %>%
-    column_spec(1, width = "5cm") %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=180$.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 9, 11) %>%
+    kableExtra::pack_rows("Total Effect", 12, 12) %>%
+    kableExtra::column_spec(1, width = "5cm") %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=180$.",
              escape = F, # correctly print special characters
@@
   explor2_table <-
-    kbl(explor2_table,
+    knitr::kable(explor2_table,
         caption = "Results of the exploratory model with Covid burden.",
@@
         align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped", "scale_down"), font_size = 11) %>%
-    pack_rows("Direct Effects", 1, 10) %>% # group the rows and add a header in between
-    pack_rows("Indirect Effects", 11, 12) %>%
-    pack_rows("Total Effect", 13, 13) %>%
-    column_spec(1, width = "5cm") %>%
-    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching, $N=180$.",
+    kableExtra::kable_styling(latex_options = c("striped", "scale_down"), font_size = 11) %>%
+    kableExtra::pack_rows("Direct Effects", 1, 10) %>% # group the rows and add a header in between
+    kableExtra::pack_rows("Indirect Effects", 11, 12) %>%
+    kableExtra::pack_rows("Total Effect", 13, 13) %>%
+    kableExtra::column_spec(1, width = "5cm") %>%
+    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching, $N=180$.",
              escape = F, # correctly print special characters

### 2022-02-23 Manuscript/Manuscript.tex
tried double backslash for &nbsp; but doesnt work

@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
 
@@
 \shorttitle{NFC and burnout in teachers}
-\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
+\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: ~ 5600}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{setspace}\doublespacing
+\usepackage{chngcntr}
 \ifxetex
@@
 
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-The authors made the following contributions.
-Josephine Zerna: Conceptualization, Methodology, Formal analysis, Writing - original draft preparation, Writing - review \& editing; Nicole Engelmann: Conceptualization, Investigation, Writing - review \& editing; Anja Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing; Alexander Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing.
-
-Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany.
-E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}
-
-}
-
 \affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden\\\textsuperscript{2} Faculty of Education, Technische Universität Dresden\\\textsuperscript{3} Institute of Psychology, Chemnitz University of Technology}
@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
+While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
+One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
+In the present study, we analyzed questionnaire data of N = 180 teachers that had been collected in spring of 2020.
+Firstly, we aimed to replicate results by Grass et al.~(2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
+With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
+Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
+The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to their demands.
 }
@@
 
+\renewcommand\thesection{\Alph{section}}
+\counterwithout{figure}{section}
+\counterwithout{table}{section}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
 \hypertarget{introduction}{%
@@
 As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
-NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982).
-While many studies have found positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Elias \& Loomis, 2002; Grass et al., 2017; Lavrijsen et al., 2021; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
-Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020).
-These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).
+NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982; German form: Bless et al., 1994).
+While many studies have found medium sized positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm \& Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
+Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
+These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).
 
@@
 Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
-Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced self-efficacy.
+Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: \emph{Emotional exhaustion}, a sense of fatigue and depletion, \emph{depersonalisation}, a negative attitude towards clients, along with a loss of idealism, and \emph{reduced personal efficacy}, a decline of capability and coping skills.
 
@@
 NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
-This is supported by the findings that NFC is negatively associated with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
+This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
-This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021; \textbf{Brady?}) has been demonstrated in multiple studies.
+This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
 What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
 Grass et al.
-(2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
+(2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
 Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
 The findings by Grass et al.
-(2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
-One goal of this paper is to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
-We expect NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.
-
-Furthermore, we would like to extend the analysis to other possible mediators.
-These mediators are motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
-Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
+(2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor (Strobel et al., 2017).
+One goal of this paper was to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
+We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.
+
+Furthermore, we extended the analysis to other possible mediators.
+These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
+This can take the form of patients with higher NFC having lower intentions to consult their physician (Latimer et al., 2007) or adults with higher NFC having higher intentions to consume high calorie beverages (Gallivan, 2020) after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
+Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
 Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
 In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
-These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery (Salanova et al., 2006).
-We would therefore like to investigate whether the association of NFC and burnout is mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (DTH), demands that are too low for one's personal resources (DTL), and a balanced fit of demands and resources (DRF).
-Using the same data as for the replication, we compute a structural equation model (SEM) to assess the influence of these mediators.
-Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expect NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
-And since burnout results from constant unpleasant activation by high demands, we expect it to be positively associated with DTH and negatively associated with DRF.
-However, we have no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).
-
-\emph{The Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021).}
+These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery (Salanova et al., 2006).
+We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (\emph{demands too high}), demands that are too low for one's personal resources (\emph{demands too low}), and a balanced fit of demands and resources (\emph{demand-resource-fit}).
+Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
+Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
+And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with \emph{demands too high} and negatively associated with \emph{demand-resource-fit}.
+However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).
+It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
+To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.
 
@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
-Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript are available at \url{https://osf.io/36ep9/}.
+Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust \& Barth, 2020), are available at \url{https://osf.io/36ep9/}.
+The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
+It was not considered to require further ethical approvals and hence, as uncritical concerning ethical aspects according to the criteria used by the Ethics Committee, which includes aspects of the sample of healthy adults, voluntary attendance, noninvasive measures, no deception, and appropriate physical and mental demands on the subject.
 
@@
 
-Teachers were recruited via social media, emails to colleagues of N.E. and to Saxon schools with the request to pass on the information.
+We set out to recruit a sample of \(N\ge287\) teachers as determined using the R package \emph{pwr} (Champely, 2020), assuming a small to medium correlation of \(r=.20\) between the measures of interest and targeting at a power of \(1-\beta=.80\) at \(\alpha=.01\).
+Teachers were recruited via social media, personal contacts to teachers, and to Saxon schools with the request to pass on the information.
 All teachers were eligible, no payment was issued.
-Of the \(N=\) 278 participants, who started filling out the online survey, \(N=\) 180 (72.20\% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
+Of the \(N=\) 278 participants, who started filling out the online survey, \(N =\) 180 (72.20\% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
 All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
@@
 At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.
+This may have also be one reason why we did not reach our estimated sample size.
+Using the smallest standardized indirect effect from the mediation in Grass et al.
+(2018) in a post hoc power analysis with \emph{G*Power} (Faul et al., 2007, 2009) yielded a power of \(1-\beta=.85\) for linear multiple regression, given \(\alpha=.05\), \(N=180\), and \(f^2=.05\).
 
@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) (Büssing \& Perrar, 1992), NFC was assessed using the 16-item Need for Cognition Scale (NCS) (Bless et al., 1994), self-control was assessed using the 13-item Self-Control Scale (SCS) (Bertrams \& Dickhäuser, 2009), reappraisal and suppression were assessed using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler \& Kessler, 2009), work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (AAZ) (Fischer \& Lück, 2014).
-Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently have a higher workload.
-The Covid-19 items can be found in the \textbf{Supplementary Material}.
-The survey also included the Subjective Wellbeing Index of the World Health Organization (Brähler et al., 2007), which we will not analyze.
-Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar (Böhm-Kasper et al., 2001) cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.
+Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI, Büssing \& Perrar, 1992), with items such as ``I don't really care what happens to some recipients'' and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
+Its subscales \emph{emotional exhaustion}, \emph{depersonalization}, and \emph{reduced personal efficacy} showed acceptable internal consistency (Cronbach's \(\alpha>.70\)) and low retest reliabilities of \(r_{tt}=.60\), \(r_{tt}=.54\), and \(r_{tt}=.57\), respectively, over the span of one year in teachers (Maslach et al., 1997).
+NFC was assessed with the 16-item short version of the German NFC scale (NCS) (Bless et al., 1994), consisting of items (e.g., ``Thinking is not my idea of fun,'' recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\)) (Bless et al., 1994; Fleischhauer et al., 2010) and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks (Fleischhauer et al., 2015).
+Self-control was measured using the short form of the German Self-Control Scale {[}SCS-K-D; Bertrams and Dickhäuser (2009){]} that comprises 13 items (e.g., ``I am able to work effectively toward long-term goals'') with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach's \(\alpha>.80\), 7-week retest reliability \(r_{tt}=.82\)) (Bertrams \& Dickhäuser, 2009).
+Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler \& Kessler, 2009).
+The scale has items such as ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (reappraisal) and ``I keep my emotions to myself'' (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)) (Preece et al., 2019).
+Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (Fischer \& Lück, 2014) with items such as ``Sometimes I feel like my work doesn't really matter in my firm,'' which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
+The scale has a split-half reliability of \(r_{tt}=.95\) (Fischer \& Lück, 2014).
+Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
+The translated Covid-19 items can be found in the \emph{Supplementary Material S1}.
+Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar (Böhm-Kasper et al., 2001) could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.
 
@@
 We used \emph{R Studio} (R Core Team, 2020; RStudio Team, 2020) with the main packages \emph{lavaan} (Rosseel, 2012) and \emph{psych} (Revelle, 2021) for all our analyses.
-
-\hypertarget{multiple-mediation-model}{%
-\subsubsection{\texorpdfstring{\emph{Multiple mediation model}}{Multiple mediation model}}\label{multiple-mediation-model}}
+Data were checked for multivariate normality using Mardia's coefficient.
+To account for non-linear relationships, correlations were computed using Spearman's rank coefficient rather than Pearson's product moment correlation.
+Internal consistencies were assessed with Cronbach's Alpha and MacDonald's Omega.
+Since Cronbach's Alpha has been criticized for being insensitive to violations of internal consistency (Dunn et al., 2014; Taber, 2018), the additional computation of MacDonald's Omega has the purpose of ensuring a more reliable estimation.
+Correlations between variables were classified according the scheme by Gignac and Szodorai (2016), which recommends .10, .20, and .30 to be considered small, typical, and relatively large, respectively.
+
+\hypertarget{replication-of-grass-et-al.-2018}{%
+\subsubsection{Replication of Grass et al.~(2018)}\label{replication-of-grass-et-al.-2018}}
 
@@
 NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
-Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
-
-\hypertarget{structural-equation-model}{%
-\subsubsection{\texorpdfstring{\emph{Structural equation model}}{Structural equation model}}\label{structural-equation-model}}
-
-Items were reverse coded according to the scale manuals.
-The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al.
-(2019), a method that is used in SEM when only relations between but not within constructs are of interest.
+\emph{Reduced personal efficacy} was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
+NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
+Following Grass et al. (2018), bootstrapped confidence with \(N=2,000\) replicates were computed to account for deviations from normality.
+Multiple indices were used to evaluate model fit as recommended by Hu and Bentler (1999): the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model (\(CFI>.95\) indicates good fit, but \(CFI>.90\) is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix (\(SRMR<.08\) indicates fair fit, \(SRMR<.05\) good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account (\(RMSEA<.08\) indicates acceptable fit, \(RMSEA<.05\) good fit, \(RMSEA<.01\) excellent fit).
+
+\hypertarget{demand-resource-ratio-model}{%
+\subsubsection{Demand-resource-ratio model}\label{demand-resource-ratio-model}}
+
+All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
+The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure (Little et al., 2002), a method that is used in SEM when only relations between but not within constructs are of interest.
 Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
@@
 The latent factor MBI was computed using the three subscales as indicators.
-For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
-The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.
-
-\hypertarget{exploratory-analysis}{%
-\subsubsection{\texorpdfstring{\emph{Exploratory analysis}}{Exploratory analysis}}\label{exploratory-analysis}}
+For the demand-resource-ratios, we used three items from the work satisfaction scale each.
+The latent factor \emph{demands too high} was indicated by items 4, 8, and 9, \emph{demands too low} by the recoded items 12, 26, and 27, and \emph{demand-resource-fit} by items 17, 22, and 24.
+The items can be translated as follows: 4) ``There is too much pressure on me.'' 8) ``There is often too much being demanded of us at work.'' 9) ``I often feel tired and weary because of my work.'' 12) ``I can realize my ideas here.'' 17) ``I take pleasure in my work.'' 22) ``Does your place of work give you the opportunity to do what you do best?'' 24) ``Does your place of work give you enough opportunities to use your skills?'' 26) ``Are you happy with your promotion prospects?'' and 27) ``Are you happy with your position when comparing it to your skills?''
+Model parameters were estimated using the maximum likelihood method with robust standard errors.
+Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.
+
+\hypertarget{exploratory-analyses}{%
+\subsubsection{Exploratory analyses}\label{exploratory-analyses}}
 
 We preregistered two exploratory analyses.
-Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales (Grass et al., 2018; Naderi et al., 2018).
+Firstly, we repeated the SEM with the subscale \emph{reduced personal efficacy} in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales (Grass et al., 2018; Naderi et al., 2018).
 And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.
@@
 
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}>{\raggedleft\arraybackslash}p{1.5cm}}
+During visual inspection of correlation plots we noticed an unexpected outlier with very high MBI scores and very low NFC scores.
+A Q-Q-plot contrasting Mahalanobis \emph{D\textsuperscript{2}} against expected Chi Square values confirmed the outlier.
+To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the \emph{Supplementary Material S2}.
+
+\hypertarget{descriptive-statistics}{%
+\subsection{Descriptive statistics}\label{descriptive-statistics}}
+
+Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
+Only the ERQ sum score and its reappraisal subscale followed a normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics (Rosseel, 2012).
+
+\begin{table}
+
+\caption{\label{tab:cdescriptivestable}Descriptive statistics of the questionnaire scores.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrrrrr}
 \toprule
-  & MBI & MBI EE & MBI DP & MBI RPE & ERQ & ERQ S & ERQ R & SCS & NFC & COV\\
+Variable & Minimum & Maximum & Mean & SD & Normality & Skewness & Kurtosis\\
 \midrule
-\cellcolor{gray!6}{MBI Score} & \cellcolor{gray!6}{0.90(0.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-MBI EE & \textbf{0.925} & 0.91(0.92) &  &  &  &  &  &  &  & \\
-\cellcolor{gray!6}{MBI DP} & \textbf{\cellcolor{gray!6}{0.748}} & \textbf{\cellcolor{gray!6}{0.535}} & \cellcolor{gray!6}{0.68(0.69)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-MBI RPE & \textbf{0.669} & \textbf{0.434} & \textbf{0.480} & 0.79(0.79) &  &  &  &  &  & \\
-\cellcolor{gray!6}{ERQ} & \cellcolor{gray!6}{-0.058} & \cellcolor{gray!6}{-0.059} & \cellcolor{gray!6}{0.043} & \cellcolor{gray!6}{-0.099} & \cellcolor{gray!6}{0.73(0.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+\cellcolor{gray!6}{MBI} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{52.93} & \cellcolor{gray!6}{13.06} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{0.02}\\
+MBI EE & 12 & 52 & 27.99 & 8.87 & No & 0.19 & -0.59\\
+\cellcolor{gray!6}{MBI DP} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{9.72} & \cellcolor{gray!6}{3.26} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{0.82} & \cellcolor{gray!6}{0.86}\\
+MBI RPE & 7 & 28 & 15.22 & 3.43 & No & 0.42 & 1.11\\
+\cellcolor{gray!6}{ERQ} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{63} & \cellcolor{gray!6}{39.18} & \cellcolor{gray!6}{7.82} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{-0.16} & \cellcolor{gray!6}{0.45}\\
 \addlinespace
-ERQ Suppression & 0.053 & -0.000 & \em{0.166} & 0.076 & \textbf{0.592} & 0.75(0.79) &  &  &  & \\
-\cellcolor{gray!6}{ERQ Reappraisal} & \cellcolor{gray!6}{-0.101} & \cellcolor{gray!6}{-0.058} & \cellcolor{gray!6}{-0.061} & \em{\textbf{\cellcolor{gray!6}{-0.197}}} & \textbf{\cellcolor{gray!6}{0.715}} & \cellcolor{gray!6}{-0.075} & \cellcolor{gray!6}{0.84(0.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-Self Control & \textbf{-0.342} & \textbf{-0.283} & \textbf{-0.368} & \em{-0.185} & -0.034 & -0.121 & 0.050 & 0.85(0.86) &  & \\
-\cellcolor{gray!6}{NFC} & \textbf{\cellcolor{gray!6}{-0.248}} & \em{\textbf{\cellcolor{gray!6}{-0.196}}} & \em{\textbf{\cellcolor{gray!6}{-0.219}}} & \em{\textbf{\cellcolor{gray!6}{-0.213}}} & \cellcolor{gray!6}{-0.008} & \em{\cellcolor{gray!6}{-0.176}} & \em{\cellcolor{gray!6}{0.158}} & \em{\textbf{\cellcolor{gray!6}{0.216}}} & \cellcolor{gray!6}{0.89(0.89)} & \cellcolor{gray!6}{}\\
-Covid-19 Burden & \em{\textbf{0.241}} & \textbf{0.324} & 0.083 & 0.016 & -0.028 & 0.019 & -0.065 & -0.040 & 0.125 & 0.77(0.81)\\
+ERQ S & 4 & 26 & 12.59 & 4.85 & No & 0.14 & -0.73\\
+\cellcolor{gray!6}{ERQ R} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{42} & \cellcolor{gray!6}{26.59} & \cellcolor{gray!6}{6.29} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{-0.05} & \cellcolor{gray!6}{0.01}\\
+SCS & -19 & 23 & 7.79 & 8.42 & No & -0.39 & -0.22\\
+\cellcolor{gray!6}{NFC} & \cellcolor{gray!6}{-34} & \cellcolor{gray!6}{48} & \cellcolor{gray!6}{20.37} & \cellcolor{gray!6}{14.04} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{-0.59} & \cellcolor{gray!6}{0.56}\\
+DTH & -6 & 6 & 0.49 & 2.65 & No & -0.15 & -0.56\\
+\addlinespace
+\cellcolor{gray!6}{DTL} & \cellcolor{gray!6}{-6} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-2.22} & \cellcolor{gray!6}{2.24} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{0.28}\\
+DRF & -4 & 6 & 3.63 & 1.79 & No & -0.91 & 1.75\\
+\cellcolor{gray!6}{COV} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{33} & \cellcolor{gray!6}{24.53} & \cellcolor{gray!6}{4.28} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{-0.14} & \cellcolor{gray!6}{-0.70}\\
 \bottomrule
-\multicolumn{11}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{11}{l}{\rule{0pt}{1em}MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden.
-\textbackslash{}\textbackslash{}textit\{N\} = 180.
-Italics indicate \textbackslash{}\textbackslash{}textit\{p\} < .05, italics and bold indicate \textbackslash{}\textbackslash{}textit\{p\} < .01, bold indicates \textbackslash{}\textbackslash{}textit\{p\} < .001.
-Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.}\\
-\end{tabu}
-\endgroup{}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 60 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        14
-##                                                       
-##   Number of observations                           180
-##                                                       
-## Model Test User Model:
-##                                                       
-##   Test statistic                                 0.000
-##   Degrees of freedom                                 0
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                                49.640
-##   Degrees of freedom                                10
-##   P-value                                        0.000
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    1.000
-##   Tucker-Lewis Index (TLI)                       1.000
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -2215.454
-##   Loglikelihood unrestricted model (H1)      -2215.454
-##                                                       
-##   Akaike (AIC)                                4458.908
-##   Bayesian (BIC)                              4503.609
-##   Sample-size adjusted Bayesian (BIC)         4459.271
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.000
-##   90 Percent confidence interval - lower         0.000
-##   90 Percent confidence interval - upper         0.000
-##   P-value RMSEA <= 0.05                             NA
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.000
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                            Bootstrap
-##   Number of requested bootstrap draws             2000
-##   Number of successful bootstrap draws            2000
-## 
-## Regressions:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   scs ~                                                                 
-##     ncs       (a1)    0.162    0.051    3.154    0.002    0.055    0.258
-##   erq_reap ~                                                            
-##     ncs       (a2)    0.055    0.034    1.619    0.105   -0.011    0.120
-##   erq_supp ~                                                            
-##     ncs       (a3)   -0.063    0.025   -2.524    0.012   -0.113   -0.017
-##   mbi_rpe ~                                                             
-##     scs       (b1)   -0.069    0.030   -2.318    0.020   -0.126   -0.009
-##     erq_reap  (b2)   -0.094    0.036   -2.652    0.008   -0.159   -0.023
-##     erq_supp  (b3)    0.002    0.051    0.043    0.966   -0.094    0.106
-##     ncs        (c)   -0.051    0.021   -2.473    0.013   -0.089   -0.008
-##    Std.lv  Std.all
-##                   
-##     0.162    0.271
-##                   
-##     0.055    0.123
-##                   
-##    -0.063   -0.182
-##                   
-##    -0.069   -0.169
-##    -0.094   -0.173
-##     0.002    0.003
-##    -0.051   -0.208
-## 
-## Covariances:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##  .scs ~~                                                                
-##    .erq_reap          1.393    3.526    0.395    0.693   -5.236    8.427
-##    .erq_supp         -3.166    2.802   -1.130    0.258   -8.806    2.383
-##  .erq_reap ~~                                                           
-##    .erq_supp         -0.257    2.351   -0.109    0.913   -4.838    4.416
-##    Std.lv  Std.all
-##                   
-##     1.393    0.028
-##    -3.166   -0.082
-##                   
-##    -0.257   -0.009
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##    .scs              65.382    6.206   10.536    0.000   52.369   76.607
-##    .erq_reap         38.748    4.220    9.182    0.000   30.312   47.219
-##    .erq_supp         22.604    1.897   11.914    0.000   18.685   26.236
-##    .mbi_rpe          10.143    1.297    7.821    0.000    7.457   12.428
-##    Std.lv  Std.all
-##    65.382    0.927
-##    38.748    0.985
-##    22.604    0.967
-##    10.143    0.866
-## 
-## R-Square:
-##                    Estimate
-##     scs               0.073
-##     erq_reap          0.015
-##     erq_supp          0.033
-##     mbi_rpe           0.134
-## 
-## Defined Parameters:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##     Indirect1        -0.011    0.007   -1.695    0.090   -0.026   -0.001
-##     Indirect2        -0.005    0.004   -1.429    0.153   -0.013    0.001
-##     Indirect3        -0.000    0.004   -0.039    0.969   -0.008    0.006
-##     Contrast         -0.006    0.009   -0.653    0.514   -0.024    0.011
-##     Total            -0.067    0.023   -2.957    0.003   -0.111   -0.021
-##    Std.lv  Std.all
-##    -0.011   -0.046
-##    -0.005   -0.021
-##    -0.000   -0.001
-##    -0.006   -0.024
-##    -0.067   -0.276
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 100 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        39
-##                                                       
-##   Number of observations                           180
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                395.419     399.077
-##   Degrees of freedom                                 97          97
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   0.991
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1504.484    1461.750
-##   Degrees of freedom                               120         120
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.029
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.784       0.775
-##   Tucker-Lewis Index (TLI)                       0.733       0.721
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.783
-##   Robust Tucker-Lewis Index (TLI)                            0.732
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -5189.293   -5189.293
-##   Scaling correction factor                                  1.231
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -4991.583   -4991.583
-##   Scaling correction factor                                  1.060
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               10456.585   10456.585
-##   Bayesian (BIC)                             10581.111   10581.111
-##   Sample-size adjusted Bayesian (BIC)        10457.597   10457.597
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.131       0.132
-##   90 Percent confidence interval - lower         0.117       0.118
-##   90 Percent confidence interval - upper         0.144       0.145
-##   P-value RMSEA <= 0.05                          0.000       0.000
-##                                                                   
-##   Robust RMSEA                                               0.131
-##   90 Percent confidence interval - lower                     0.118
-##   90 Percent confidence interval - upper                     0.144
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.173       0.173
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   NFC =~                                                                
-##     nfc1              1.000                               1.000    1.000
-##     nfc2              1.002    0.112    8.931    0.000    0.782    1.222
-##     nfc3              1.059    0.087   12.235    0.000    0.889    1.228
-##     nfc4              1.035    0.103   10.004    0.000    0.833    1.238
-##   DTH =~                                                                
-##     dth1              1.000                               1.000    1.000
-##     dth2              0.916    0.119    7.672    0.000    0.682    1.150
-##     dth3              1.668    0.280    5.967    0.000    1.120    2.216
-##   DTL =~                                                                
-##     dtl1              1.000                               1.000    1.000
-##     dtl2              1.755    0.318    5.525    0.000    1.132    2.377
-##     dtl3              1.987    0.425    4.672    0.000    1.154    2.821
-##   DRF =~                                                                
-##     drf1              1.000                               1.000    1.000
-##     drf2              0.886    0.144    6.151    0.000    0.604    1.168
-##     drf3              0.790    0.130    6.061    0.000    0.534    1.045
-##   MBI =~                                                                
-##     mbi_ee            1.000                               1.000    1.000
-##     mbi_dp            0.231    0.042    5.516    0.000    0.149    0.314
-##     mbi_rpe           0.249    0.049    5.047    0.000    0.152    0.345
-##    Std.lv  Std.all
-##                   
-##     3.213    0.759
-##     3.220    0.771
-##     3.402    0.869
-##     3.327    0.838
-##                   
-##     0.598    0.541
-##     0.548    0.553
-##     0.998    0.848
-##                   
-##     0.409    0.483
-##     0.717    0.711
-##     0.813    0.883
-##                   
-##     0.586    0.791
-##     0.519    0.820
-##     0.463    0.597
-##                   
-##     7.122    0.873
-##     1.648    0.523
-##     1.771    0.534
-## 
-## Regressions:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   DTH ~                                                                 
-##     NFC               0.042    0.020    2.154    0.031    0.004    0.081
-##   DTL ~                                                                 
-##     NFC               0.023    0.015    1.522    0.128   -0.007    0.052
-##   DRF ~                                                                 
-##     NFC              -0.070    0.020   -3.488    0.000   -0.110   -0.031
-##   MBI ~                                                                 
-##     NFC               0.002    0.144    0.014    0.989   -0.281    0.285
-##     DTH             -10.624    2.229   -4.767    0.000  -14.991   -6.256
-##     DTL              -1.838    1.428   -1.287    0.198   -4.637    0.960
-##     DRF               4.036    1.080    3.736    0.000    1.918    6.153
-##    Std.lv  Std.all
-##                   
-##     0.228    0.228
-##                   
-##     0.180    0.180
-##                   
-##    -0.386   -0.386
-##                   
-##     0.001    0.001
-##    -0.892   -0.892
-##    -0.106   -0.106
-##     0.332    0.332
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##    .nfc1              7.596    1.125    6.753    0.000    5.391    9.801
-##    .nfc2              7.079    0.940    7.530    0.000    5.237    8.922
-##    .nfc3              3.748    0.729    5.139    0.000    2.319    5.178
-##    .nfc4              4.674    0.967    4.834    0.000    2.779    6.569
-##    .dth1              0.866    0.107    8.079    0.000    0.656    1.077
-##    .dth2              0.681    0.092    7.425    0.000    0.501    0.860
-##    .dth3              0.390    0.089    4.365    0.000    0.215    0.565
-##    .dtl1              0.549    0.093    5.884    0.000    0.366    0.732
-##    .dtl2              0.504    0.087    5.820    0.000    0.334    0.674
-##    .dtl3              0.186    0.097    1.911    0.056   -0.005    0.377
-##    .drf1              0.206    0.048    4.276    0.000    0.112    0.300
-##    .drf2              0.132    0.036    3.649    0.000    0.061    0.203
-##    .drf3              0.387    0.057    6.835    0.000    0.276    0.498
-##    .mbi_ee           15.839    5.619    2.819    0.005    4.826   26.852
-##    .mbi_dp            7.207    0.920    7.835    0.000    5.404    9.010
-##    .mbi_rpe           7.851    1.017    7.722    0.000    5.858    9.843
-##     NFC              10.323    2.212    4.666    0.000    5.987   14.659
-##    .DTH               0.339    0.100    3.397    0.001    0.143    0.535
-##    .DTL               0.162    0.058    2.779    0.005    0.048    0.276
-##    .DRF               0.293    0.083    3.522    0.000    0.130    0.455
-##    .MBI               0.949    4.185    0.227    0.821   -7.253    9.152
-##    Std.lv  Std.all
-##     7.596    0.424
-##     7.079    0.406
-##     3.748    0.245
-##     4.674    0.297
-##     0.866    0.708
-##     0.681    0.694
-##     0.390    0.281
-##     0.549    0.767
-##     0.504    0.495
-##     0.186    0.220
-##     0.206    0.375
-##     0.132    0.328
-##     0.387    0.643
-##    15.839    0.238
-##     7.207    0.726
-##     7.851    0.715
-##     1.000    1.000
-##     0.948    0.948
-##     0.968    0.968
-##     0.851    0.851
-##     0.019    0.019
-## 
-## R-Square:
-##                    Estimate
-##     nfc1              0.576
-##     nfc2              0.594
-##     nfc3              0.755
-##     nfc4              0.703
-##     dth1              0.292
-##     dth2              0.306
-##     dth3              0.719
-##     dtl1              0.233
-##     dtl2              0.505
-##     dtl3              0.780
-##     drf1              0.625
-##     drf2              0.672
-##     drf3              0.357
-##     mbi_ee            0.762
-##     mbi_dp            0.274
-##     mbi_rpe           0.285
-##     DTH               0.052
-##     DTL               0.032
-##     DRF               0.149
-##     MBI               0.981
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 125 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        34
-##                                                       
-##   Number of observations                           180
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                250.937     247.820
-##   Degrees of freedom                                 71          71
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   1.013
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1161.800    1112.062
-##   Degrees of freedom                                91          91
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.045
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.832       0.827
-##   Tucker-Lewis Index (TLI)                       0.785       0.778
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.832
-##   Robust Tucker-Lewis Index (TLI)                            0.785
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -4173.205   -4173.205
-##   Scaling correction factor                                  1.224
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -4047.737   -4047.737
-##   Scaling correction factor                                  1.081
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                                8414.410    8414.410
-##   Bayesian (BIC)                              8522.971    8522.971
-##   Sample-size adjusted Bayesian (BIC)         8415.293    8415.293
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.119       0.118
-##   90 Percent confidence interval - lower         0.103       0.102
-##   90 Percent confidence interval - upper         0.135       0.134
-##   P-value RMSEA <= 0.05                          0.000       0.000
-##                                                                   
-##   Robust RMSEA                                               0.118
-##   90 Percent confidence interval - lower                     0.103
-##   90 Percent confidence interval - upper                     0.135
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.165       0.165
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   NFC =~                                                                
-##     nfc1              1.000                               1.000    1.000
-##     nfc2              1.013    0.112    9.043    0.000    0.793    1.232
-##     nfc3              1.062    0.087   12.179    0.000    0.891    1.232
-##     nfc4              1.045    0.104   10.045    0.000    0.841    1.249
-##   DTH =~                                                                
-##     dth1              1.000                               1.000    1.000
-##     dth2              1.016    0.159    6.405    0.000    0.705    1.326
-##     dth3              0.857    0.132    6.511    0.000    0.599    1.115
-##   DTL =~                                                                
-##     dtl1              1.000                               1.000    1.000
-##     dtl2              1.759    0.327    5.377    0.000    1.118    2.401
-##     dtl3              1.836    0.333    5.514    0.000    1.183    2.488
-##   DRF =~                                                                
-##     drf1              1.000                               1.000    1.000
-##     drf2              0.878    0.126    6.987    0.000    0.632    1.124
-##     drf3              0.776    0.124    6.243    0.000    0.532    1.020
-##   RPE =~                                                                
-##     mbi_rpe           1.000                               1.000    1.000
-##    Std.lv  Std.all
-##                   
-##     3.195    0.755
-##     3.236    0.775
-##     3.392    0.867
-##     3.338    0.841
-##                   
-##     0.785    0.709
-##     0.797    0.805
-##     0.672    0.571
-##                   
-##     0.424    0.500
-##     0.745    0.738
-##     0.778    0.845
-##                   
-##     0.590    0.796
-##     0.518    0.817
-##     0.458    0.591
-##                   
-##     3.297    1.000
-## 
-## Regressions:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   DTH ~                                                                 
-##     NFC               0.054    0.024    2.245    0.025    0.007    0.101
-##   DTL ~                                                                 
-##     NFC               0.025    0.015    1.637    0.102   -0.005    0.055
-##   DRF ~                                                                 
-##     NFC              -0.071    0.020   -3.564    0.000   -0.110   -0.032
-##   RPE ~                                                                 
-##     NFC              -0.051    0.085   -0.597    0.551   -0.218    0.116
-##     DTH              -0.497    0.366   -1.357    0.175   -1.214    0.221
-##     DTL              -0.845    0.653   -1.293    0.196   -2.125    0.436
-##     DRF               3.161    0.439    7.196    0.000    2.300    4.022
-##    Std.lv  Std.all
-##                   
-##     0.220    0.220
-##                   
-##     0.189    0.189
-##                   
-##    -0.385   -0.385
-##                   
-##    -0.049   -0.049
-##    -0.118   -0.118
-##    -0.109   -0.109
-##     0.566    0.566
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##    .nfc1              7.709    1.135    6.793    0.000    5.485    9.934
-##    .nfc2              6.974    0.930    7.498    0.000    5.151    8.797
-##    .nfc3              3.815    0.741    5.148    0.000    2.363    5.268
-##    .nfc4              4.597    0.973    4.723    0.000    2.689    6.504
-##    .dth1              0.608    0.113    5.374    0.000    0.386    0.830
-##    .dth2              0.345    0.105    3.289    0.001    0.140    0.551
-##    .dth3              0.933    0.123    7.613    0.000    0.693    1.174
-##    .dtl1              0.537    0.092    5.845    0.000    0.357    0.717
-##    .dtl2              0.464    0.077    5.990    0.000    0.312    0.615
-##    .dtl3              0.242    0.075    3.241    0.001    0.096    0.388
-##    .drf1              0.201    0.040    5.021    0.000    0.123    0.280
-##    .drf2              0.133    0.032    4.209    0.000    0.071    0.195
-##    .drf3              0.391    0.059    6.605    0.000    0.275    0.508
-##    .mbi_rpe           0.000                               0.000    0.000
-##     NFC              10.210    2.189    4.665    0.000    5.920   14.500
-##    .DTH               0.586    0.128    4.583    0.000    0.336    0.837
-##    .DTL               0.173    0.058    2.998    0.003    0.060    0.286
-##    .DRF               0.297    0.077    3.868    0.000    0.146    0.447
-##    .RPE               6.568    0.876    7.498    0.000    4.852    8.285
-##    Std.lv  Std.all
-##     7.709    0.430
-##     6.974    0.400
-##     3.815    0.249
-##     4.597    0.292
-##     0.608    0.497
-##     0.345    0.352
-##     0.933    0.674
-##     0.537    0.750
-##     0.464    0.455
-##     0.242    0.286
-##     0.201    0.366
-##     0.133    0.332
-##     0.391    0.651
-##     0.000    0.000
-##     1.000    1.000
-##     0.952    0.952
-##     0.964    0.964
-##     0.852    0.852
-##     0.604    0.604
-## 
-## R-Square:
-##                    Estimate
-##     nfc1              0.570
-##     nfc2              0.600
-##     nfc3              0.751
-##     nfc4              0.708
-##     dth1              0.503
-##     dth2              0.648
-##     dth3              0.326
-##     dtl1              0.250
-##     dtl2              0.545
-##     dtl3              0.714
-##     drf1              0.634
-##     drf2              0.668
-##     drf3              0.349
-##     mbi_rpe           1.000
-##     DTH               0.048
-##     DTL               0.036
-##     DRF               0.148
-##     RPE               0.396
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 154 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        42
-##                                                       
-##   Number of observations                           180
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                430.369     430.449
-##   Degrees of freedom                                111         111
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   1.000
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1568.311    1513.167
-##   Degrees of freedom                               136         136
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.036
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.777       0.768
-##   Tucker-Lewis Index (TLI)                       0.727       0.716
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.776
-##   Robust Tucker-Lewis Index (TLI)                            0.726
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -5691.634   -5691.634
-##   Scaling correction factor                                  1.220
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -5476.449   -5476.449
-##   Scaling correction factor                                  1.060
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               11467.268   11467.268
-##   Bayesian (BIC)                             11601.372   11601.372
-##   Sample-size adjusted Bayesian (BIC)        11468.358   11468.358
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.126       0.126
-##   90 Percent confidence interval - lower         0.114       0.114
-##   90 Percent confidence interval - upper         0.139       0.139
-##   P-value RMSEA <= 0.05                          0.000       0.000
-##                                                                   
-##   Robust RMSEA                                               0.126
-##   90 Percent confidence interval - lower                     0.114
-##   90 Percent confidence interval - upper                     0.139
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.170       0.170
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   NFC =~                                                                
-##     nfc1              1.000                               1.000    1.000
-##     nfc2              1.003    0.113    8.909    0.000    0.783    1.224
-##     nfc3              1.060    0.087   12.195    0.000    0.889    1.230
-##     nfc4              1.036    0.104    9.982    0.000    0.833    1.239
-##   DTH =~                                                                
-##     dth1              1.000                               1.000    1.000
-##     dth2              0.886    0.108    8.217    0.000    0.675    1.097
-##     dth3              1.500    0.254    5.909    0.000    1.003    1.998
-##   DTL =~                                                                
-##     dtl1              1.000                               1.000    1.000
-##     dtl2              1.756    0.318    5.521    0.000    1.133    2.380
-##     dtl3              1.980    0.421    4.700    0.000    1.154    2.806
-##   DRF =~                                                                
-##     drf1              1.000                               1.000    1.000
-##     drf2              0.882    0.143    6.170    0.000    0.602    1.162
-##     drf3              0.785    0.131    5.983    0.000    0.528    1.042
-##   MBI =~                                                                
-##     mbi_ee            1.000                               1.000    1.000
-##     mbi_dp            0.237    0.046    5.115    0.000    0.146    0.328
-##     mbi_rpe           0.255    0.054    4.728    0.000    0.149    0.361
-##   COVB =~                                                               
-##     covb              1.000                               1.000    1.000
-##    Std.lv  Std.all
-##                   
-##     3.211    0.759
-##     3.222    0.771
-##     3.403    0.870
-##     3.327    0.839
-##                   
-##     0.643    0.582
-##     0.570    0.576
-##     0.965    0.820
-##                   
-##     0.409    0.484
-##     0.719    0.712
-##     0.811    0.881
-##                   
-##     0.588    0.793
-##     0.519    0.818
-##     0.462    0.595
-##                   
-##     6.987    0.860
-##     1.656    0.527
-##     1.781    0.539
-##                   
-##     4.272    1.000
-## 
-## Regressions:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##   DTH ~                                                                 
-##     NFC               0.037    0.022    1.729    0.084   -0.005    0.080
-##   DTL ~                                                                 
-##     NFC               0.023    0.015    1.515    0.130   -0.007    0.052
-##   DRF ~                                                                 
-##     NFC              -0.070    0.020   -3.479    0.001   -0.110   -0.031
-##   COVB ~                                                                
-##     DTH              -3.001    0.544   -5.518    0.000   -4.067   -1.935
-##   MBI ~                                                                 
-##     NFC              -0.009    0.149   -0.058    0.954   -0.301    0.284
-##     DTH             -10.345    2.372   -4.362    0.000  -14.994   -5.696
-##     DTL              -1.733    1.436   -1.206    0.228   -4.547    1.082
-##     DRF               4.266    1.160    3.678    0.000    1.992    6.539
-##     COVB             -0.224    0.130   -1.727    0.084   -0.478    0.030
-##    Std.lv  Std.all
-##                   
-##     0.187    0.187
-##                   
-##     0.179    0.179
-##                   
-##    -0.384   -0.384
-##                   
-##    -0.452   -0.452
-##                   
-##    -0.004   -0.004
-##    -0.953   -0.953
-##    -0.102   -0.102
-##     0.359    0.359
-##    -0.137   -0.137
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|) ci.lower ci.upper
-##    .nfc1              7.608    1.127    6.751    0.000    5.399    9.816
-##    .nfc2              7.066    0.943    7.494    0.000    5.218    8.915
-##    .nfc3              3.738    0.729    5.125    0.000    2.308    5.167
-##    .nfc4              4.673    0.966    4.835    0.000    2.779    6.567
-##    .dth1              0.810    0.103    7.839    0.000    0.608    1.013
-##    .dth2              0.656    0.094    7.005    0.000    0.472    0.839
-##    .dth3              0.454    0.103    4.421    0.000    0.252    0.655
-##    .dtl1              0.549    0.093    5.892    0.000    0.366    0.731
-##    .dtl2              0.502    0.086    5.825    0.000    0.333    0.671
-##    .dtl3              0.189    0.096    1.961    0.050    0.000    0.378
-##    .drf1              0.204    0.048    4.231    0.000    0.109    0.298
-##    .drf2              0.133    0.036    3.686    0.000    0.062    0.204
-##    .drf3              0.388    0.057    6.825    0.000    0.277    0.500
-##    .mbi_ee           17.173    6.430    2.671    0.008    4.570   29.776
-##    .mbi_dp            7.119    0.925    7.697    0.000    5.306    8.932
-##    .mbi_rpe           7.740    1.033    7.494    0.000    5.716    9.764
-##    .covb              0.000                               0.000    0.000
-##     NFC              10.312    2.212    4.661    0.000    5.975   14.648
-##    .DTH               0.400    0.111    3.584    0.000    0.181    0.618
-##    .DTL               0.162    0.058    2.784    0.005    0.048    0.276
-##    .DRF               0.295    0.084    3.508    0.000    0.130    0.460
-##    .MBI              -0.334    4.157   -0.080    0.936   -8.481    7.813
-##    .COVB             14.522    1.668    8.706    0.000   11.252   17.791
-##    Std.lv  Std.all
-##     7.608    0.425
-##     7.066    0.405
-##     3.738    0.244
-##     4.673    0.297
-##     0.810    0.662
-##     0.656    0.669
-##     0.454    0.327
-##     0.549    0.766
-##     0.502    0.493
-##     0.189    0.224
-##     0.204    0.371
-##     0.133    0.331
-##     0.388    0.645
-##    17.173    0.260
-##     7.119    0.722
-##     7.740    0.709
-##     0.000    0.000
-##     1.000    1.000
-##     0.965    0.965
-##     0.968    0.968
-##     0.853    0.853
-##    -0.007   -0.007
-##     0.796    0.796
-## 
-## R-Square:
-##                    Estimate
-##     nfc1              0.575
-##     nfc2              0.595
-##     nfc3              0.756
-##     nfc4              0.703
-##     dth1              0.338
-##     dth2              0.331
-##     dth3              0.673
-##     dtl1              0.234
-##     dtl2              0.507
-##     dtl3              0.776
-##     drf1              0.629
-##     drf2              0.669
-##     drf3              0.355
-##     mbi_ee            0.740
-##     mbi_dp            0.278
-##     mbi_rpe           0.291
-##     covb              1.000
-##     DTH               0.035
-##     DTL               0.032
-##     DRF               0.147
-##     MBI                  NA
-##     COVB              0.204
-\end{verbatim}
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation.
+\textit{N} = 180.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Correlations and internal consistencies are displayed in Table 2.
+For this descriptive analysis, the variables \emph{demands too high}, \emph{demands too low}, and \emph{demand-resource-fit} were computed as a sum of their item scores, not weighted as in the structural equation model.
+Using traditional cut-off values (Nunnally \& Bernstein, 1994), the Cronbach's Alpha of the three demand-resource-ratios can be considered \emph{acceptable}.
+The more robust MacDonald's Omega (Dunn et al., 2014) did not deviate much from Cronbach's Alpha and indicated \emph{acceptable} to \emph{good} internal consistency.
+As expected, the MBI score showed a large positive correlation with \emph{demands too high} (\(r_s\) = .67, \emph{p} \textless{} .001) and a large negatve one with \emph{demand-resource-fit} (\(r_s\) = -.55, \emph{p} \textless{} .001).
+Surprisingly, the correlation between the MBI score and \emph{demands too low} was positive and also large (\(r_s\) = .44, \emph{p} \textless{} .001).
+The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.
+
+\begin{landscape}\begin{table}
+
+\caption{\label{tab:correlationstable}Spearman correlations and internal consistencies of the questionnaire scores.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{llllllllllllll}
+\toprule
+  & { 1 } & { 2 } & { 3 } & { 4 } & { 5 } & { 6 } & { 7 } & { 8 } & { 9 } & { 10 } & { 11 } & { 12 } & { 13 }\\
+\midrule
+\cellcolor{gray!6}{1.
+MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.92) &  &  &  &  &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{3.
+MBI DP} & \cellcolor{gray!6}{\&nbsp; .75***} & \cellcolor{gray!6}{\&nbsp; .54***} & \cellcolor{gray!6}{\&nbsp; .68(.69)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+4. MBI RPE & \&nbsp; .67*** & \&nbsp; .43*** & \&nbsp; .48*** & \&nbsp; .79(.79) &  &  &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{5.
+ERQ} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{\&nbsp; .04} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+\addlinespace
+6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{7.
+ERQ R} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+8. SCS & -.34*** & -.28*** & -.37*** & -.19* & -.03 & -.12 & \&nbsp; .05 & \&nbsp; .85(.86) &  &  &  &  & \\
+\cellcolor{gray!6}{9.
+NFC} & \cellcolor{gray!6}{-.25***} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.22**} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.01} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{\&nbsp; .22**} & \cellcolor{gray!6}{\&nbsp; .89(.89)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+10. DTH & \&nbsp; .67*** & \&nbsp; .72*** & \&nbsp; .35*** & \&nbsp; .36*** & \&nbsp; .03 & \&nbsp; .05 & -.01 & -.21** & -.15* & \&nbsp; .73(.73) &  &  & \\
+\addlinespace
+\cellcolor{gray!6}{11.
+DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .36***} & \cellcolor{gray!6}{\&nbsp; .38***} & \cellcolor{gray!6}{\&nbsp; .43***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.14} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{-.16*} & \cellcolor{gray!6}{\&nbsp; .41***} & \cellcolor{gray!6}{\&nbsp; .73(.75)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+12. DRF & -.55*** & -.46*** & -.41*** & -.53*** & -.00 & -.10 & \&nbsp; .10 & \&nbsp; .18* & \&nbsp; .24** & -.42*** & -.56*** & \&nbsp; .77(.77) & \\
+\cellcolor{gray!6}{13.
+COV} & \cellcolor{gray!6}{\&nbsp; .24**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{-.04} & \cellcolor{gray!6}{\&nbsp; .13} & \cellcolor{gray!6}{\&nbsp; .45***} & \cellcolor{gray!6}{\&nbsp; .10} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+\textit{N} = 180.
+* \textit{p} < .05.
+** \textit{p} < .01.
+*** \textit{p} < .001.
+Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+\end{landscape}
+
+\hypertarget{replication-of-grass-et-al.-2018-1}{%
+\subsection{Replication of Grass et al.~(2018)}\label{replication-of-grass-et-al.-2018-1}}
+
+In order to replicate findings by Grass et al.
+(2018) we computed a multiple mediation model to investigate whether the association of NFC and \emph{reduced personal efficacy} was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
+The baseline model did not fit the data (\(\chi\)\textsuperscript{2}(10, \(N=\) 180) = 49.64, \(p < .001\)).
+Applying the cutoffs by Hu and Bentler (1999) to the fit indices of \(CFI=\) 1, \(TLI=\) 1.14, \(SRMR=\) 0.02, and \(RMSEA=\) 0.00, 95\% \(CI\) {[}0,0.09{]}, suggested good fit of the proposed model throughout all indices.
+Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
+We could replicate a positive association of NFC and self control (\(\beta=\) 0.27, \(p=.002\)), and a negative association of habitual reappraisal and \emph{reduced personal efficacy} (\(\beta=\) -0.17, \(p=.008\)).
+However, we could neither replicate the effect of NFC on reappraisal (\(\beta=\) 0.12, \(p=.105\)), nor the indirect effect of NFC on \emph{reduced personal efficacy} via reappraisal (\(\beta=\) -0.02, \(p=.153\)).
+Furthermore, even though NFC and \emph{reduced personal efficacy} were both associated with self-control, the indirect effect of NFC on \emph{reduced personal efficacy} via self control did not reach significance (\(\beta=\) -0.05, \(p=.090\)).
+Additionally, NFC was negatively associated with habitual use of suppression (\(\beta=\) -0.18, \(p=.012\)), which was not the case in the study by Grass et al. (2018).
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Manuscript_files/figure-latex/objective1plot-1} \caption{Standardized regression coefficients in the replication of Grass et al.
+(2018).
+* $p<.05$, ** $p<.01$.}\label{fig:objective1plot}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:objective1table}Results of the replication of Grass et al. (2018).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Self Control} & \cellcolor{gray!6}{0.162} & \cellcolor{gray!6}{0.051} & \cellcolor{gray!6}{3.154} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{0.258} & \cellcolor{gray!6}{0.271}\\
+\hspace{1em}NFC on Reappraisal & 0.055 & 0.034 & 1.619 & 0.105 & -0.011 & 0.120 & 0.123\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Suppression} & \cellcolor{gray!6}{-0.063} & \cellcolor{gray!6}{0.025} & \cellcolor{gray!6}{-2.524} & \cellcolor{gray!6}{0.012} & \cellcolor{gray!6}{-0.113} & \cellcolor{gray!6}{-0.017} & \cellcolor{gray!6}{-0.182}\\
+\hspace{1em}Self Control on RPE & -0.069 & 0.030 & -2.318 & 0.020 & -0.126 & -0.009 & -0.169\\
+\hspace{1em}\cellcolor{gray!6}{Reappraisal on RPE} & \cellcolor{gray!6}{-0.094} & \cellcolor{gray!6}{0.036} & \cellcolor{gray!6}{-2.652} & \cellcolor{gray!6}{0.008} & \cellcolor{gray!6}{-0.159} & \cellcolor{gray!6}{-0.023} & \cellcolor{gray!6}{-0.173}\\
+\hspace{1em}Suppression on RPE & 0.002 & 0.051 & 0.043 & 0.966 & -0.094 & 0.106 & 0.003\\
+\hspace{1em}\cellcolor{gray!6}{NFC on RPE} & \cellcolor{gray!6}{-0.051} & \cellcolor{gray!6}{0.021} & \cellcolor{gray!6}{-2.473} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{-0.089} & \cellcolor{gray!6}{-0.008} & \cellcolor{gray!6}{-0.208}\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}NFC on RPE via Self Control & -0.011 & 0.007 & -1.695 & 0.090 & -0.026 & -0.001 & -0.046\\
+\hspace{1em}\cellcolor{gray!6}{NFC on RPE via Reappraisal} & \cellcolor{gray!6}{-0.005} & \cellcolor{gray!6}{0.004} & \cellcolor{gray!6}{-1.429} & \cellcolor{gray!6}{0.153} & \cellcolor{gray!6}{-0.013} & \cellcolor{gray!6}{0.001} & \cellcolor{gray!6}{-0.021}\\
+\hspace{1em}NFC on RPE via Suppression & 0.000 & 0.004 & -0.039 & 0.969 & -0.008 & 0.006 & -0.001\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}\cellcolor{gray!6}{Total Effect} & \cellcolor{gray!6}{-0.067} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-2.957} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{-0.111} & \cellcolor{gray!6}{-0.021} & \cellcolor{gray!6}{-0.276}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Grass et al. (2018) controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
+Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
+We placed this variable as an independent variable influencing self control, as the latter was the only variable in the model that showed a partial correlation with years spent teaching.
+As it was not preregistered, this was an exploratory analysis.
+Again, the baseline model did not fit the data (\(\chi\)\textsuperscript{2}(14, \(N=\) 180) = 60.41, \(p < .001\)), and the fit indices of \(CFI=\) 1, \(TLI=\) 1.19, \(SRMR=\) 0.02, and \(RMSEA=\) 0.00, 95\% \(CI\) {[}0,0.04{]}, suggested good fit of the proposed model throughout all indices.
+Standardized estimates, total, direct, and indirect effects are displayed and listed in \emph{Supplementary Material S3}.
+The associations between NFC, self control, reappraisal, suppression, and \emph{reduced personal efficacy} were almost identical to the first model.
+However, because of the positive association of years spent teaching and self control (\(\beta=\) 0.22, \(p.001\)), the indirect path leading from NFC and years spent teaching via self control to \emph{reduced personal efficacy} reached significance in this model (\(\beta=\) -0.09, \(p=.049\)).
+Therefore, the total effect also increased slightly, compared to the first model (\(\beta=\) -0.32, \(p=.002\)).
+
+\hypertarget{demand-resource-model}{%
+\subsection{Demand-Resource Model}\label{demand-resource-model}}
+
+Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
+The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of 0.00.
+The first parcel contained item 4, 6, 8, and 9, the second parcel item 2, 14, 15, and 16, the third parcel item 7, 11, 12, and 13, and the fourth parcel item 1, 3, 5, and 10.
+Standardized path coefficients of the demand-resource model are illustrated in Figure 2, total, direct, and indirect effects are listed in Table 4.
+The robust Chi-square statistic of \(\chi^2=\) 399.08 (\(p < .001\)) did not indicate good model fit.
+However, since it was in the range of 4 \(df<\chi^2>\) 5 \(df\) the lack of good fit might have been due to the underlying assumption of multivariate normality (Hu \& Bentler, 1999; Schumacker \& Lomax, 2012), which was violated here.
+This also held true for the CFI of 0.78, the SRMR of 0.17, and the RMSEA of 0.13, 95\% \(CI\) {[}0.12,0.14{]}.
+Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
+NFC showed no direct association with the MBI score (\(\beta=\) 0, \(p=.989\)), even though it was negatively correlated with the sum score and all subscales.
+Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable \emph{demands too high} (\(\beta=\) -0.20, \(p=.026\)) and via higher scores in the latent variable \emph{demand-resource-fit} (\(\beta=\) -0.13, \(p=.025\)).
+The latent variable \emph{demands too low} was neither related to NFC (\(\beta=\) -0.18, \(p=.128\)) nor to the MBI score (\(\beta=\) 0.11, \(p=.198\)).
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Manuscript_files/figure-latex/objective2plot-1} \caption{Standardized path coefficients in the mediation of NFC and burnout by demand-resource-ratios.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, MBI = Maslach Burnout Inventory, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, ee = emotional exhaustion, dp = depersonalisation, rpe = reduced personal efficacy.}\label{fig:objective2plot}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:objective2table}Results of the demand-resource-ratio model.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DTH} & \cellcolor{gray!6}{-0.042} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{-2.154} & \cellcolor{gray!6}{0.031} & \cellcolor{gray!6}{-0.081} & \cellcolor{gray!6}{-0.004} & \cellcolor{gray!6}{-0.228}\\
+\hspace{1em}NFC on DTL & -0.023 & 0.015 & -1.522 & 0.128 & -0.052 & 0.007 & -0.180\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DRF} & \cellcolor{gray!6}{0.070} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{3.488} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{0.031} & \cellcolor{gray!6}{0.110} & \cellcolor{gray!6}{0.386}\\
+\hspace{1em}NFC on MBI & 0.002 & 0.144 & 0.014 & 0.989 & -0.281 & 0.285 & 0.001\\
+\hspace{1em}\cellcolor{gray!6}{DTH on MBI} & \cellcolor{gray!6}{10.624} & \cellcolor{gray!6}{2.229} & \cellcolor{gray!6}{4.767} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{6.256} & \cellcolor{gray!6}{14.991} & \cellcolor{gray!6}{0.892}\\
+\hspace{1em}DTL on MBI & 1.838 & 1.428 & 1.287 & 0.198 & -0.960 & 4.637 & 0.106\\
+\hspace{1em}\cellcolor{gray!6}{DRF on MBI} & \cellcolor{gray!6}{-4.036} & \cellcolor{gray!6}{1.080} & \cellcolor{gray!6}{-3.736} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{-6.153} & \cellcolor{gray!6}{-1.918} & \cellcolor{gray!6}{-0.332}\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}NFC on MBI via DTH & -0.451 & 0.203 & -2.221 & 0.026 & -0.848 & -0.053 & -0.203\\
+\hspace{1em}\cellcolor{gray!6}{NFC on MBI via DTL} & \cellcolor{gray!6}{-0.042} & \cellcolor{gray!6}{0.033} & \cellcolor{gray!6}{-1.270} & \cellcolor{gray!6}{0.204} & \cellcolor{gray!6}{-0.107} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.019}\\
+\hspace{1em}NFC on MBI via DRF & -0.284 & 0.127 & -2.236 & 0.025 & -0.533 & -0.035 & -0.128\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}\cellcolor{gray!6}{Total Effect} & \cellcolor{gray!6}{-0.775} & \cellcolor{gray!6}{0.258} & \cellcolor{gray!6}{-3.003} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{-1.280} & \cellcolor{gray!6}{-0.269} & \cellcolor{gray!6}{-0.349}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, $beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\hypertarget{exploratory-analyses-1}{%
+\subsection{Exploratory analyses}\label{exploratory-analyses-1}}
+
+The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale \emph{reduced personal efficacy} would be used in place of the MBI sum score.
+Path coefficients, total, direct, and indirect effects are displayed and listed in \emph{Supplementary Material S4}.
+Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of \(\chi^2=\) 247.82 (\(p < .001\)), a CFI of 0.83, a SRMR of 0.17, and a RMSEA of 0.12, 95\% \(CI\) {[}0.10,0.13{]}.
+NFC showed no direct association with \emph{reduced personal efficacy} (\(\beta=\) -0.05, \(p=.551\)), but an indirect one via higher scores in the latent variable \emph{demand-resource-fit} (\(\beta=\) -0.22, \(p=.002\)).
+And again, NFC was associated with lower scores in the latent variable \emph{demands too high} (\(\beta=\) -0.22, \(p=.025\)), but the latter did not mediate the relationship between NFC and \emph{reduced personal efficacy} (\(\beta=\) -0.03, \(p=.243\)) as it did with the MBI score in the previous model.
+The latent variable \emph{demands too low} was neither related to NFC (\(\beta=\) -0.19, \(p=.102\)) nor to the MBI score (\(\beta=\) 0.11, \(p=.196\)).
+
+The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
+We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
+Then we modified the structure of the model using the \emph{modincides()}-function in \emph{lavaan} in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
+The final model is illustrated in Figure 3, the total, direct, and indirect effects are listed in \emph{Supplementary Material S5}.
+All fit indices suggested that the proposed model had good fit while the baseline model did not (\(\chi^2=\) 130.13 (\(p < .001\)), \(CFI=\) 0.95, \(RMSEA=\) 0.07 (95\% \(CI\) {[}0.05,0.08{]}), \(SRMR=\) 0.06).
+Neither the ERQ sum score, nor its subscales, nor the \emph{depersonalisation} subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
+Years spent teaching was associated with higher self control (\(\beta=\) 0.21, \(p=.002\)) and higher Covid burden (\(\beta=\) 0.17, \(p=.020\)) but not with NFC.
+NFC covaried with self control (\(\sigma_{NFC,scs}=\) 0.31, \(p=.008\)) and Covid burden (\(\sigma_{NFC,covb}=\) 0.19, \(p=.018\)), but not with years spent teaching (\(p=.722\)).
+In turn, NFC was associated with higher \emph{demand-resource-fit} scores (\(\beta=\) 0.34, \(p=.002\)) and lower \emph{demands too high} scores (\(\beta=\) -0.21, \(p=.008\)) but not directly with any of the two MBI subscales.
+\emph{Demand-resource-fit} scores fully mediated the negative association of NFC and self control with \emph{reduced personal efficacy} (indirect effect \(\beta=\) -0.29, \(p.001\)), which was also true for \emph{demands too high} scores and \emph{emotional exhaustion}, but \emph{demands too high} also partially mediated between Covid burden and \emph{emotional exhaustion} (indirect effect \(\beta=\) -0.18, \(p=.008\)).
+Covid burden was not associated with \emph{demand-resource-fit} or \emph{reduced personal efficacy}.
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Manuscript_files/figure-latex/explor2plot-1} \caption{Standardized path coefficients in the exploratory analysis of variable relations.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+Years = years spent teaching, SCS = Self-Control Scale, COVB = Covid burden, NFC = Need for Cognition, DTH = demands too high, DRF = demand resource fit, nfc1-4 = item parcels, dth/drf1-3 = item indicators, EE = emotional exhaustion, RPE = reduced personal efficacy.}\label{fig:explor2plot}
+\end{figure}
 
@@
 \section{Discussion}\label{discussion}}
+
+The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
+To achieve this, we replicated findings of mediators between Need for Cognition and burnout, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
+Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.
+
+\hypertarget{replication-of-grass-et-al.-2018-2}{%
+\subsection{Replication of Grass et al.~(2018)}\label{replication-of-grass-et-al.-2018-2}}
+
+While the mediation model had good fit, not all patterns were similar to the original study: NFC and self-control had a medium positive association, and reappraisal and \emph{reduced personal efficacy} had a small negative association, but NFC and reappraisal were not associated.
+There was, however, a small negative association between self-control and \emph{reduced personal efficacy}, and between NFC and suppression.
+
+NFC had a direct, medium negative effect on \emph{reduced personal efficacy}, but this relationship was not mediated by any other variable.
+Only when the amount of teaching experience was included as a predictor of self-control next to NFC, a very small indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower \emph{reduced personal efficacy}.
+The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 (Oliva et al., 2019).
+The participants in the study by Grass et al. (2018) were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
+Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
+However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.
+
+We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with \emph{reduced personal efficacy}, but not their association with NFC.
+There is ample evidence that reappraisal is associated with positive outcomes for students (Haga et al., 2007; Levine et al., 2012; Schmidt et al., 2010) and teachers alike (Jiang et al., 2016; Moè \& Katz, 2020; Tsouloupas et al., 2010), so it is suprising that reappraisal did not mediate between NFC and \emph{reduced personal efficacy}.
+Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
+One possible explanation could be that the ways by which reappraisal can be achieved, such as taking the role of an uninvolved observer, are less feasible for teachers in retaining their sense of efficacy in the classroom than the self-control needed to structurally manage students and situations.
+Hence, the mediation of NFC and \emph{reduced personal efficacy} by self-control when taking the years spent teaching into account.
+
+\hypertarget{demand-resource-ratio-model-1}{%
+\subsection{Demand-resource-ratio model}\label{demand-resource-ratio-model-1}}
+
+Despite not having good fit indices, the model suggested a complete mediation of NFC and burnout via \emph{demands too high} and \emph{demand-resource-fit} but not \emph{demands too low}.
+Specifically, individuals with higher NFC had lower burnout scores through perceiving demands as fitting to and not exceeding their own resources.
+Interestingly, the medium correlation between NFC and burnout disappeared in the context of the demand-resource-ratios as mediators.
+The mediator that did not reach significance was the perception of own resources exceeding the job demands.
+As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. (2013.).
+The fact that the items that made up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.
+This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands (Lazarus \& Folkman, 1984; Lepine et al., 2005; Podsakoff et al., 2007).
+Challenge demands such as time pressure, responsibility, and workload (Podsakoff et al., 2007) are being positively valued due to their potential to increase personal growth, positive affect, and problem-focused coping (Lepine et al., 2005).
+In contrast, hindrance demands such as inadequate resources, role conflict, and organisational politics (Podsakoff et al., 2007) are perceived as negative because they harm personal growth, trigger negative emotions, and increase passive coping (Lepine et al., 2005).
+Ventura et al.
+(2015) found that hindrance but not challenge demands were positively related to burnout in teachers, and teachers who reported high challenge and low hindrance demands also reported higher engagement.
+Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy (Bandura, 1997), so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom (Cherniss, 1993; M.
+Vera et al., 2012).
+Self-efficacy and self-control are closely entwined (Przepiórka et al., 2019; E.
+M.
+Vera et al., 2004; Yang et al., 2019) and both are positively associated with NFC (Bertrams \& Dickhäuser, 2012; Holch \& Marwood, 2020; Naderi et al., 2018; Xu \& Cheng, 2021).
+Cacioppo et al. (1996) even proposed that higher levels of NFC might develop as a result of a high need for structure or control in those who have the skill, ability, and inclination to do so.
+These associations would imply that teachers with high levels of NFC report lower levels of burnout because their higher (desire for) self-control motivates them to appraise demands as a chance for personal growth, thereby meeting their passion for thinking and problem-solving.
+Nevertheless, appraisal is no universal remedy for circumstances that threaten well-being, as there certainly are circumstances that one cannot get any benefit out of.
+It remains an open question whether a high desire for control and high NFC might cloud one's judgement in this case, by encouraging to invest one's own insufficient resources in order to meet these high external demands.
+Such behavioural tendencies would threaten personal well-being in the long term, as the demands cannot be met, self-efficacy declines, and stress increases.
+
+\hypertarget{exploratory-analyses-2}{%
+\subsection{Exploratory analyses}\label{exploratory-analyses-2}}
+
+\hypertarget{demand-resource-ratio-model-with-subscale-reduced-personal-efficacy}{%
+\subsubsection{Demand-resource-ratio model with subscale reduced personal efficacy}\label{demand-resource-ratio-model-with-subscale-reduced-personal-efficacy}}
+
+The demand-resource-ratio model with the subscale \emph{reduced personal efficacy} in place of the MBI score did not have good fit indices.
+Compared to the confirmatory demand-resource-ratio model, the mediation of NFC and \emph{reduced personal efficacy} via \emph{demands too high} did not reach significance, but both the mediation via \emph{demand-resource-fit} and the total effect remained significant.
+Overall, this pattern did not resemble those from previous studies in which NFC had the strongest relation with this subscale of the MBI (Grass et al., 2018; Naderi et al., 2018).
+Teachers with high NFC appear to retain their sense of personal efficacy to a higher degree, because they experience a fit of demands and resources, which allows them to complete tasks and reinforce their self-efficacy in return.
+However, while this association was similar in the confirmatory and the exploratory demand-resource-ratio model, the mediation via \emph{demands too high} was not significant with this subscale, suggesting that the large association of \emph{demands too high} and MBI in the confirmatory model was driven by a different subscale.
+To explore this, we built a second exploratory model.
+
+\hypertarget{exploratory-model-with-covid-burden}{%
+\subsubsection{Exploratory model with Covid burden}\label{exploratory-model-with-covid-burden}}
+
+Due to the complete freedom in setting up the structure of this model, it had good fit indices.
+Interestingly, the third MBI subscale \emph{depersonalisation} and the latent variable \emph{demands too low} did not explain any variance in the model, so they were removed.
+Once again, NFC and self-control were positively related, but NFC was also positively related to Covid burden.
+One possible explanation is that teachers with higher NFC show higher consideration of the consequences and progression of the pandemic, thereby anticipating that it will take a long time until normal teaching can resume, which heightens their feeling of being burdened.
+Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively (Nishiguchi et al., 2018; Vannucci \& Chiorri, 2018), a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
+Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology (Hauk et al., 2018) and therefore stressed by the prospect of online teaching.
+Teachers with higher self-control and higher NFC reported a stronger fit of demands and resources, which was associated with a strong decrease in \emph{reduced personal efficacy}.
+Higher self-control, higher NFC, and lower Covid burden was in turn associated with a lower \emph{demands too high} score, so teachers with those characteristics felt less overwhelmed and consequently less emotionally exhausted.
+The degree of association between \emph{demands too high} and \emph{emotional exhaustion} indeed suggested a congruence between the two, indicating that \emph{emotional exhaustion} in burnout is caused by excessive demands that cannot be met with one's resources, while \emph{reduced personal efficacy} in burnout is caused by a lack of opportunities to utilize one's resources at work.
+Curiously, higher Covid burden also showed a small negative association with \emph{emotional exhaustion}.
+It could be that for some teachers, remote teaching was experienced as a relief from the strain of dealing with a group of over twenty students each day, who are more likely to misbehave in a classroom setting than when they are studying at home.
+So while those teachers did feel the pandemic burden, they also felt less emotionally exhausted.
+However, as this part of the study was exploratory, the results should be interpreted with some caution and examined with new data in a confirmatory approach.
+
+\hypertarget{limitations-and-future-implications}{%
+\subsection{Limitations and future implications}\label{limitations-and-future-implications}}
+
+The data used in this study had been collected with a focus on emotion regulation and burnout, so there were several aspects that would have improved the investigation of our research questions but were not feasible.
+Firstly, collecting coping style data would have enabled a full replication of the mediation model of Grass et al. (2018).
+Secondly, longitudinal data would have facilitated more definitive conclusions about causal relations, as well as about inter-individual differences in the perception of demands and resources as the pandemic progresses.
+Furthermore, the latent variables for the demand-resource-ratios were item groups chosen from the work satisfaction questionnaire and had not been validated for this use before.
+However, as two of them showed meaningful relations with self-control, NFC, and two of the three MBI subscales, pursuing this concept further seems promising.
+Especially because we worked with pre-existing data, we preregistered all analyses and clearly differentiated between confirmatory and exploratory models in order to make the results as reliable as possible.
+
+\hypertarget{conclusions}{%
+\subsection{Conclusions}\label{conclusions}}
+
+Our study showed that self-control mediated between NFC and burnout when teaching experience was being taken into account.
+Contrary to prior studies, neither habitual use of reappraisal nor use of suppression mediated between NFC and burnout.
+However, a crucial role in the relation of NFC and burnout seemed to be the perceived ratio of personal resources and demands, specifically, a resource-demand-fit was associated with lower and excessive demands were associated with higher burnout scores.
+Applied to real-life teaching practise, our results suggest that a healthy work environment should offer ample opportunities to make use of one's abilities, without creating demands that are too high.
+As a consequence, experiences and sense of self-efficacy will increase, which in turn heightens confidence in one's skills to deal with future demands that are higher, preventing loss of personal efficacy and burnout in the long term.
 
@@
 
+\leavevmode\hypertarget{ref-Aust2020}{}%
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Bandura1997}{}%
+Bandura, A. (1997). \emph{Self-{Efficacy}: {The} exercise of control}. Worth Publishers.
+
 \leavevmode\hypertarget{ref-Bertrams2009a}{}%
 Bertrams, A., \& Dickhäuser, O. (2009). Messung dispositioneller {Selbstkontroll}-{Kapazität}. \emph{Diagnostica}, \emph{55}(1), 2--10. \url{https://doi.org/10.1026/0012-1924.55.1.2}
+
+\leavevmode\hypertarget{ref-Bertrams2012}{}%
+Bertrams, A., \& Dickhäuser, O. (2012). Passionate thinkers feel better. \emph{Journal of Individual Differences}, \emph{33}(2), 69--75. \url{https://doi.org/10.1027/1614-0001/a000081}
 
@@
 
-\leavevmode\hypertarget{ref-Braehler2007}{}%
-Brähler, E., Mühlan, H., Albani, C., \& Schmidt, S.
-(2007).
-Teststatistische {Prüfung} und {Normierung} der deutschen {Versionen} des {EUROHIS}-{QOL} {Lebensqualität}-{Index} und des {WHO}-5 {Wohlbefindens}-{Index}.
-\emph{Diagnostica}, \emph{53}(2), 83--96.
-\url{https://doi.org/10.1026/0012-1924.53.2.83}
+\leavevmode\hypertarget{ref-Brady2021}{}%
+Brady, K.
+J.
+S., Sheldrick, R.
+C., Ni, P., Trockel, M.
+T., Shanafelt, T.
+D., Rowe, S.
+G., \& Kazis, L.
+E.
+(2021).
+Examining the measurement equivalence of the {Maslach} {Burnout} {Inventory} across age, gender, and specialty groups in {US} physicians.
+\emph{Journal of Patient-Reported Outcomes}, \emph{5}(1), 43.
+\url{https://doi.org/10.1186/s41687-021-00312-2}
 
@@
 \url{https://doi.org/10.1016/j.sbspro.2014.03.227}
+
+\leavevmode\hypertarget{ref-Champely2020}{}%
+Champely, S. (2020). \emph{Pwr: Basic functions for power analysis}. \url{https://CRAN.R-project.org/package=pwr}
+
+\leavevmode\hypertarget{ref-Cherniss1993}{}%
+Cherniss, C. (1993). \emph{Professional burnout: Recent developments in theory and research} (W. B. Schaufeli, C. Maslach, \& T. Marek, Eds.; pp. 135--149). Taylor \& Francis.
 
@@
 
-\leavevmode\hypertarget{ref-Elias2002}{}%
-Elias, S.
-M., \& Loomis, R.
-J.
-(2002).
-Utilizing {Need} for {Cognition} and {Perceived} {Self}-{Efficacy} to {Predict} {Academic} {Performance1}.
-\emph{Journal of Applied Social Psychology}, \emph{32}(8), 1687--1702.
-\url{https://doi.org/10.1111/j.1559-1816.2002.tb02770.x}
+\leavevmode\hypertarget{ref-Dunn2014}{}%
+Dunn, T.
+J., Baguley, T., \& Brunsden, V.
+(2014).
+From alpha to omega: {A} practical solution to the pervasive problem of internal consistency estimation.
+\emph{British Journal of Psychology}, \emph{105}(3), 399--412.
+\url{https://doi.org/10.1111/bjop.12046}
+
+\leavevmode\hypertarget{ref-Faul2009}{}%
+Faul, F., Erdfelder, E., Buchner, A., \& Lang, A.-G.
+(2009).
+Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses.
+\emph{Behavior Research Methods}, \emph{41}(4), 1149--1160.
+\url{https://doi.org/10.3758/BRM.41.4.1149}
+
+\leavevmode\hypertarget{ref-Faul2007}{}%
+Faul, F., Erdfelder, E., Lang, A.-G., \& Buchner, A.
+(2007).
+G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences.
+\emph{Behavior Research Methods}, \emph{39}(2), 175--191.
+\url{https://doi.org/10.3758/BF03193146}
 
@@
 Fischer, L., \& Lück, H. E. (2014). Allgemeine {Arbeitszufriedenheit}. \emph{Zusammenstellung Sozialwissenschaftlicher Items Und Skalen (ZIS)}. \url{https://doi.org/10.6102/ZIS1}
+
+\leavevmode\hypertarget{ref-Fleischhauer2010}{}%
+Fleischhauer, M., Enge, S., Brocke, B., Ullrich, J., Strobel, A., \& Strobel, A.
+(2010).
+Same or different?
+{Clarifying} the relationship of need for cognition to personality and intelligence.
+\emph{Personality \& Social Psychology Bulletin}, \emph{36}(1), 82--96.
+\url{https://doi.org/10.1177/0146167209351886}
 
@@
 
+\leavevmode\hypertarget{ref-Fleischhauer2015}{}%
+Fleischhauer, M., Strobel, A., \& Strobel, A.
+(2015).
+Directly and indirectly assessed {Need for Cognition} differentially predict spontaneous and reflective information processing behavior.
+\emph{Journal of Individual Differences}, \emph{36}(2), 101--109.
+\url{https://doi.org/10.1027/1614-0001/a000161}
+
 \leavevmode\hypertarget{ref-Froebe2021}{}%
@@
 \url{https://pesquisa.bvsalud.org/global-literature-on-novel-coronavirus-2019-ncov/resource/pt/covidwho-1282947?lang=en}
+
+\leavevmode\hypertarget{ref-Gallivan2020}{}%
+Gallivan, N. (2020). \emph{Behavior feedback and {Need} for {Cognition}: {Factors} affecting coffee beverage consumption} {[}Thesis{]}. \url{https://krex.k-state.edu/dspace/handle/2097/40878}
 
@@
 
+\leavevmode\hypertarget{ref-Gignac2016}{}%
+Gignac, G.
+E., \& Szodorai, E.
+T.
+(2016).
+Effect size guidelines for individual differences researchers.
+\emph{Personality and Individual Differences}, \emph{102}, 74--78.
+\url{https://doi.org/10.1016/j.paid.2016.06.069}
+
 \leavevmode\hypertarget{ref-Grass2018}{}%
@@
 {The} importance of {Need} for {Cognition} for subjective experience and achievement in academic studies.
-\emph{Zeitschrift Fur Padagogische Psychologie}, \emph{32}(3), 145--154.
+\emph{Zeitschrift für Padagogische Psychologie}, \emph{32}(3), 145--154.
 \url{https://doi.org/10.1024/1010-0652/a000222}
-
-\leavevmode\hypertarget{ref-Grass2019}{}%
-Grass, J., Krieger, F., Paulus, P., Greiff, S., Strobel, A., \& Strobel, A.
-(2019).
-Thinking in action: {Need} for {Cognition} predicts {Self}-{Control} together with {Action} {Orientation}.
-\emph{PLOS ONE}, \emph{14}(8), e0220282.
-\url{https://doi.org/10.1371/journal.pone.0220282}
 
@@
 \url{https://doi.org/10.1037//0022-3514.74.1.224}
+
+\leavevmode\hypertarget{ref-Haga2007}{}%
+Haga, S.
+M., Kraft, P., \& Corby, E.-K.
+(2007).
+Emotion regulation: Antecedents and well-being outcomes of cognitive reappraisal and expressive suppression in cross-cultural samples.
+\emph{Journal of Happiness Studies}, \emph{10}(3), 271--291.
+\url{https://doi.org/10.1007/s10902-007-9080-3}
+
+\leavevmode\hypertarget{ref-Hauk2018}{}%
+Hauk, N., Hüffmeier, J., \& Krumm, S.
+(2018).
+Ready to be a {Silver Surfer}?
+{A} meta-analysis on the relationship between chronological age and technology acceptance.
+\emph{Computers in Human Behavior}, \emph{84}, 304--319.
+\url{https://doi.org/10.1016/j.chb.2018.01.020}
 
@@
 
+\leavevmode\hypertarget{ref-Holch2020}{}%
+Holch, P., \& Marwood, J.
+R.
+(2020).
+{EHealth} literacy in {UK} teenagers and young adults: {Exploration} of predictors and factor structure of the {eHealth} {Literacy} {Scale} ({eHEALS}).
+\emph{JMIR Formative Research}, \emph{4}(9), e14450.
+\url{https://doi.org/10.2196/14450}
+
+\leavevmode\hypertarget{ref-Hu1999}{}%
+Hu, L., \& Bentler, P.
+M.
+(1999).
+Cutoff criteria for fit indexes in covariance structure analysis: {Conventional} criteria versus new alternatives.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{6}(1), 1--55.
+\url{https://doi.org/10.1080/10705519909540118}
+
+\leavevmode\hypertarget{ref-Jiang2016}{}%
+Jiang, J., Vauras, M., Volet, S., \& Wang, Y.
+(2016).
+Teachers{{}} emotions and emotion regulation strategies: Self- and students{{}} perceptions.
+\emph{Teaching and Teacher Education}, \emph{54}, 22--31.
+\url{https://doi.org/10.1016/j.tate.2015.11.008}
+
 \leavevmode\hypertarget{ref-Kantas1997}{}%
@@
 
+\leavevmode\hypertarget{ref-Latimer2007}{}%
+Latimer, A.
+E., Williams‐Piehota, P., Cox, A., Katulak, N.
+A., Salovey, P., \& Mowad, L.
+(2007).
+Encouraging {Cancer} {Patients} to {Talk} to {Their} {Physicians} {About} {Clinical} {Trials}: {Considering} {Patients}' {Information} {Needs1}.
+\emph{Journal of Applied Biobehavioral Research}, \emph{12}(3-4), 178--195.
+\url{https://doi.org/10.1111/j.1751-9861.2008.00020.x}
+
 \leavevmode\hypertarget{ref-Lavrijsen2021}{}%
@@
 
+\leavevmode\hypertarget{ref-Lazarus1984}{}%
+Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, {Appraisal}, and {Coping}}. Springer Publsihing Company.
+
 \leavevmode\hypertarget{ref-Leiner2019}{}%
 Leiner, D. J. (2019). \emph{{SoSci} {Survey}}. \url{https://www.soscisurvey.de}
+
+\leavevmode\hypertarget{ref-Lepine2005}{}%
+Lepine, J.
+A., Podsakoff, N.
+P., \& Lepine, M.
+A.
+(2005).
+A meta-analytic test of the {C}hallenge {S}tressor{{}}{H}indrance {S}tressor {F}ramework: {A}n explanation for inconsistent relationships among stressors and performance.
+\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
+\url{https://doi.org/10.5465/amj.2005.18803921}
+
+\leavevmode\hypertarget{ref-Levine2012}{}%
+Levine, L.
+J., Schmidt, S., Kang, H.
+S., \& Tinti, C.
+(2012).
+Remembering the silver lining: Reappraisal and positive bias in memory for emotion.
+\emph{Cognition {\&} Emotion}, \emph{26}(5), 871--884.
+\url{https://doi.org/10.1080/02699931.2011.625403}
+
+\leavevmode\hypertarget{ref-Little2002}{}%
+Little, T.
+D., Cunningham, W.
+A., Shahar, G., \& Widaman, K.
+F.
+(2002).
+To {Parcel} or {Not} to {Parcel}: {Exploring} the {Question}, {Weighing} the {Merits}.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 151--173.
+\url{https://doi.org/10.1207/S15328007SEM0902_1}
 
@@
 
+\leavevmode\hypertarget{ref-Moe2020}{}%
+Moè, A., \& Katz, I.
+(2020).
+Emotion regulation and need satisfaction shape a motivating teaching style.
+\emph{Teachers and Teaching}, \emph{27}(5), 370--387.
+\url{https://doi.org/10.1080/13540602.2020.1777960}
+
 \leavevmode\hypertarget{ref-Naderi2018}{}%
@@
 \url{http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958}
+
+\leavevmode\hypertarget{ref-Nishiguchi2018}{}%
+Nishiguchi, Y., Mori, M., \& Tanno, Y.
+(2018).
+Need for {Cognition} promotes adaptive style of self-focusing with the mediation of {Effortful} {Control}.
+\emph{Japanese Psychological Research}, \emph{60}(1), 54--61.
+\url{https://doi.org/10.1111/jpr.12167}
 
@@
 
+\leavevmode\hypertarget{ref-Nunnally1994}{}%
+Nunnally, J., \& Bernstein, I. (1994). \emph{Psychometric {Theory}}. McGraw-Hill Companies,Incorporated.
+
+\leavevmode\hypertarget{ref-Oliva2019}{}%
+Oliva, A., Antolín-Suárez, L., \& Rodríguez-Meirinhos, A.
+(2019).
+Uncovering the link between self-control, age, and psychological maladjustment among {Spanish} adolescents and young adults.
+\emph{Psychosocial Intervention}, \emph{28}(1), 49--55.
+\url{https://doi.org/10.5093/pi2019a1}
+
 \leavevmode\hypertarget{ref-Osberg1987}{}%
@@
 
+\leavevmode\hypertarget{ref-Podsakoff2007}{}%
+Podsakoff, N.
+P., LePine, J.
+A., \& LePine, M.
+A.
+(2007).
+Differential {Challenge Stressor-Hindrance Stressor} relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology}, \emph{92}(2), 438--454.
+\url{https://doi.org/10.1037/0021-9010.92.2.438}
+
+\leavevmode\hypertarget{ref-Preece2019}{}%
+Preece, D.
+A., Becerra, R., Robinson, K., \& Gross, J.
+J.
+(2019).
+{The Emotion Regulation Questionnaire: Psychometric} properties in general community samples.
+\emph{Journal of Personality Assessment}, \emph{102}(3), 348--356.
+\url{https://doi.org/10.1080/00223891.2018.1564319}
+
+\leavevmode\hypertarget{ref-Przepiorka2019}{}%
+Przepiórka, A., Błachnio, A., \& Siu, N.
+Y.-F.
+(2019).
+The relationships between self-efficacy, self-control, chronotype, procrastination and sleep problems in young adults.
+\emph{Chronobiology International}, \emph{36}(8), 1025--1035.
+\url{https://doi.org/10.1080/07420528.2019.1607370}
+
 \leavevmode\hypertarget{ref-RCT2020}{}%
 R Core Team. (2020). \emph{R: {A} language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-Reijseger2013}{}%
+Reijseger, G., Schaufeli, W.
+B., Peeters, M.
+C.
+W., Taris, T.
+W., Beek, I.
+van, \& Ouweneel, E.
+(2013).
+Watching the paint dry at work: Psychometric examination of the {Dutch} {Boredom} {Scale}.
+\emph{Anxiety, Stress, \& Coping}, \emph{26}(5), 508--525.
+\url{https://doi.org/10.1080/10615806.2012.720676}
 
@@
 
+\leavevmode\hypertarget{ref-Schmidt2010}{}%
+Schmidt, S., Tinti, C., Levine, L.
+J., \& Testa, S.
+(2010).
+Appraisals, emotions and emotion regulation: An integrative approach.
+\emph{Motivation and Emotion}, \emph{34}(1), 63--72.
+\url{https://doi.org/10.1007/s11031-010-9155-z}
+
+\leavevmode\hypertarget{ref-Schumacker2012}{}%
+Schumacker, R. E., \& Lomax, R. G. (2012). \emph{A {Beginner}'s {Guide} to {Structural} {Equation} {Modeling}: {Third} {Edition}}. Routledge.
+
 \leavevmode\hypertarget{ref-Simmons2012}{}%
@@
 
+\leavevmode\hypertarget{ref-Strobel2017}{}%
+Strobel, A., Anacker, K., \& Strobel, A.
+(2017).
+Cognitive engagement mediates the relationship between positive life events and positive emotionality.
+\emph{Frontiers in Psychology}, \emph{8}.
+\url{https://doi.org/10.3389/fpsyg.2017.01861}
+
 \leavevmode\hypertarget{ref-Stumm2013}{}%
 Stumm, S. von, \& Ackerman, P. L. (2013). Investment and intellect: A review and meta-analysis. \emph{Psychological Bulletin}, \emph{139}(4), 841--869. \url{https://doi.org/10.1037/a0030746}
+
+\leavevmode\hypertarget{ref-Taber2018}{}%
+Taber, K.
+S.
+(2018).
+The use of {Cronbach}'s {Alpha} when developing and reporting research instruments in science education.
+\emph{Research in Science Education}, \emph{48}(6), 1273--1296.
+\url{https://doi.org/10.1007/s11165-016-9602-2}
 
@@
 \url{https://doi.org/10.2466/pr0.1990.66.1.321}
+
+\leavevmode\hypertarget{ref-Tsouloupas2010}{}%
+Tsouloupas, C.
+N., Carson, R.
+L., Matthews, R., Grawitch, M.
+J., \& Barber, L.
+K.
+(2010).
+Exploring the association between teachers' perceived student misbehaviour and emotional exhaustion: The importance of teacher efficacy beliefs and emotion regulation.
+\emph{Educational Psychology}, \emph{30}(2), 173--189.
+\url{https://doi.org/10.1080/01443410903494460}
 
@@
 
+\leavevmode\hypertarget{ref-Vannucci2018}{}%
+Vannucci, M., \& Chiorri, C.
+(2018).
+Individual differences in self-consciousness and mind wandering: {Further} evidence for a dissociation between spontaneous and deliberate mind wandering.
+\emph{Personality and Individual Differences}, \emph{121}, 57--61.
+\url{https://doi.org/10.1016/j.paid.2017.09.022}
+
+\leavevmode\hypertarget{ref-Ventura2015}{}%
+Ventura, M., Salanova, M., \& Llorens, S.
+(2015).
+Professional {Self}-{Efficacy} as a {Predictor} of {Burnout} and {Engagement}: {The} {Role} of {Challenge} and {Hindrance} {Demands}.
+\emph{The Journal of Psychology}, \emph{149}(3), 277--302.
+\url{https://doi.org/10.1080/00223980.2013.876380}
+
+\leavevmode\hypertarget{ref-Vera2004}{}%
+Vera, E.
+M., Shin, R.
+Q., Montgomery, G.
+P., Mildner, C., \& Speight, S.
+L.
+(2004).
+Conflict resolution styles, self-efficacy, self-control, and future orientation of urban adolescents.
+\emph{Professional School Counseling}, \emph{8}(1), 73--80.
+
+\leavevmode\hypertarget{ref-Vera2012}{}%
+Vera, M., Salanova, M., \& Lorente, L.
+(2012).
+The predicting role of self-efficacyin the {Job} {Demands}-{Resources} {Model}: {A} longitudinal study.
+\emph{Studies in Psychology}, \emph{33}(2), 167--178.
+\url{https://doi.org/10.1174/021093912800676439}
+
 \leavevmode\hypertarget{ref-Wiesner2005}{}%
@@
 
+\leavevmode\hypertarget{ref-Xu2021}{}%
+Xu, P., \& Cheng, J.
+(2021).
+Individual differences in social distancing and mask-wearing in the pandemic of {COVID}-19: {The} role of need for cognition, self-control and risk attitude.
+\emph{Personality and Individual Differences}, \emph{175}, 110706.
+\url{https://doi.org/10.1016/j.paid.2021.110706}
+
+\leavevmode\hypertarget{ref-Yang2019}{}%
+Yang, C., Zhou, Y., Cao, Q., Xia, M., \& An, J.
+(2019).
+The relationship between self-control and self-efficacy among patients with substance use sisorders: {R}esilience and self-esteem as mediators.
+\emph{Frontiers in Psychiatry}, \emph{10}.
+\url{https://doi.org/10.3389/fpsyt.2019.00388}
+
 \leavevmode\hypertarget{ref-Zerna2021}{}%
@@
 
+\newpage
+
+\hypertarget{supplementary-material}{%
+\section{Supplementary Material}\label{supplementary-material}}
+
+\hypertarget{s1-items-used-to-assess-covid-burden}{%
+\subsection{S1: Items used to assess Covid burden}\label{s1-items-used-to-assess-covid-burden}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  How burdened do you currently feel by the measures associated with Covid-19?
+\item
+  Are you in a Covid-19 risk group?
+\item
+  Do you have or have you had a Covid-19 infection?
+\item
+  Are or were family members or other people close to you infected with Covid-19?
+\item
+  Do you feel more burdened at work?
+\item
+  Are your worried more?
+\item
+  Do you feel restricted in your current day-to-day life?
+\item
+  Do you currently have additional responsibilities?
+\item
+  How much time do you currently spend on leisure activities?
+\item
+  Do you currently spend more/less time on work-related activities (e.g.~preparing lessons, reading literature, attending trainings for digital teaching)?
+\item
+  Did the current demands within your job change?
+\end{enumerate}
+
+For each response scale, please refer to Excel file with the full list of items and response types on OSF \url{https://osf.io/36ep9/}.
+
+\newpage
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\hypertarget{s2-results-when-excluding-the-outlier-with-very-high-mbi-scores-and-very-low-nfc-scores}{%
+\subsection{S2: Results when excluding the outlier with very high MBI scores and very low NFC scores}\label{s2-results-when-excluding-the-outlier-with-very-high-mbi-scores-and-very-low-nfc-scores}}
+
+\begin{landscape}\begin{table}
+
+\caption{\label{tab:outliercorrelationstable}Spearman correlations and internal consistencies of the questionnaire scores.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{llllllllllllll}
+\toprule
+  & { 1 } & { 2 } & { 3 } & { 4 } & { 5 } & { 6 } & { 7 } & { 8 } & { 9 } & { 10 } & { 11 } & { 12 } & { 13 }\\
+\midrule
+\cellcolor{gray!6}{1.
+MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.91) &  &  &  &  &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{3.
+MBI DP} & \cellcolor{gray!6}{\&nbsp; .74***} & \cellcolor{gray!6}{\&nbsp; .53***} & \cellcolor{gray!6}{\&nbsp; .68(.66)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+4. MBI RPE & \&nbsp; .66*** & \&nbsp; .42*** & \&nbsp; .47*** & \&nbsp; .79(.78) &  &  &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{5.
+ERQ} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{\&nbsp; .05} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+\addlinespace
+6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
+\cellcolor{gray!6}{7.
+ERQ R} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+8. SCS & -.33*** & -.27*** & -.36*** & -.17* & -.04 & -.12 & \&nbsp; .04 & \&nbsp; .85(.85) &  &  &  &  & \\
+\cellcolor{gray!6}{9.
+NFC} & \cellcolor{gray!6}{-.24**} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .15*} & \cellcolor{gray!6}{\&nbsp; .20**} & \cellcolor{gray!6}{\&nbsp; .89(.88)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+10. DTH & \&nbsp; .66*** & \&nbsp; .72*** & \&nbsp; .34*** & \&nbsp; .35*** & \&nbsp; .04 & \&nbsp; .05 & \&nbsp; .00 & -.19** & -.13 & \&nbsp; .73(.72) &  &  & \\
+\addlinespace
+\cellcolor{gray!6}{11.
+DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .35***} & \cellcolor{gray!6}{\&nbsp; .37***} & \cellcolor{gray!6}{\&nbsp; .42***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.15*} & \cellcolor{gray!6}{\&nbsp; .40***} & \cellcolor{gray!6}{\&nbsp; .73(.76)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+12. DRF & -.54*** & -.45*** & -.40*** & -.52*** & -.01 & -.10 & \&nbsp; .09 & \&nbsp; .16* & \&nbsp; .23** & -.41*** & -.55*** & \&nbsp; .77(.75) & \\
+\cellcolor{gray!6}{13.
+COV} & \cellcolor{gray!6}{\&nbsp; .23**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .07} & \cellcolor{gray!6}{\&nbsp; .00} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .14} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{-.12} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden.
+\textit{N} = 179.
+* \textit{p} < .05.
+** \textit{p} < .01.
+*** \textit{p} < .001.
+Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+\end{landscape}
+
+\begin{table}
+
+\caption{\label{tab:outlierobjective1table}Results of the replication of Grass et al. (2018).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Self Control} & \cellcolor{gray!6}{0.132} & \cellcolor{gray!6}{0.047} & \cellcolor{gray!6}{2.804} & \cellcolor{gray!6}{0.005} & \cellcolor{gray!6}{0.042} & \cellcolor{gray!6}{0.226} & \cellcolor{gray!6}{0.217}\\
+\hspace{1em}NFC on Reappraisal & 0.052 & 0.039 & 1.353 & 0.176 & -0.021 & 0.127 & 0.112\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Suppression} & \cellcolor{gray!6}{-0.068} & \cellcolor{gray!6}{0.027} & \cellcolor{gray!6}{-2.519} & \cellcolor{gray!6}{0.012} & \cellcolor{gray!6}{-0.121} & \cellcolor{gray!6}{-0.016} & \cellcolor{gray!6}{-0.188}\\
+\hspace{1em}Self Control on RPE & -0.055 & 0.029 & -1.910 & 0.056 & -0.112 & 0.001 & -0.137\\
+\hspace{1em}\cellcolor{gray!6}{Reappraisal on RPE} & \cellcolor{gray!6}{-0.093} & \cellcolor{gray!6}{0.034} & \cellcolor{gray!6}{-2.707} & \cellcolor{gray!6}{0.007} & \cellcolor{gray!6}{-0.156} & \cellcolor{gray!6}{-0.020} & \cellcolor{gray!6}{-0.177}\\
+\hspace{1em}Suppression on RPE & 0.011 & 0.051 & 0.209 & 0.834 & -0.089 & 0.111 & 0.016\\
+\hspace{1em}\cellcolor{gray!6}{NFC on RPE} & \cellcolor{gray!6}{-0.039} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{-1.994} & \cellcolor{gray!6}{0.046} & \cellcolor{gray!6}{-0.076} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{-0.160}\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}NFC on RPE via Self Control & -0.007 & 0.005 & -1.403 & 0.161 & -0.019 & 0.000 & -0.030\\
+\hspace{1em}\cellcolor{gray!6}{NFC on RPE via Reappraisal} & \cellcolor{gray!6}{-0.005} & \cellcolor{gray!6}{0.004} & \cellcolor{gray!6}{-1.217} & \cellcolor{gray!6}{0.224} & \cellcolor{gray!6}{-0.014} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{-0.020}\\
+\hspace{1em}NFC on RPE via Suppression & -0.001 & 0.004 & -0.191 & 0.848 & -0.009 & 0.006 & -0.003\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}\cellcolor{gray!6}{Total Effect} & \cellcolor{gray!6}{-0.052} & \cellcolor{gray!6}{0.021} & \cellcolor{gray!6}{-2.518} & \cellcolor{gray!6}{0.012} & \cellcolor{gray!6}{-0.090} & \cellcolor{gray!6}{-0.010} & \cellcolor{gray!6}{-0.212}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, $beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:outlierobjective2table}Results of the demand-resource-ratio model.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DTH} & \cellcolor{gray!6}{-0.035} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{-1.789} & \cellcolor{gray!6}{0.074} & \cellcolor{gray!6}{-0.074} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{-0.183}\\
+\hspace{1em}NFC on DTL & -0.020 & 0.015 & -1.287 & 0.198 & -0.050 & 0.010 & -0.152\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DRF} & \cellcolor{gray!6}{0.060} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{2.942} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{0.100} & \cellcolor{gray!6}{0.318}\\
+\hspace{1em}NFC on MBI & 0.024 & 0.151 & 0.161 & 0.872 & -0.272 & 0.320 & 0.010\\
+\hspace{1em}\cellcolor{gray!6}{DTH on MBI} & \cellcolor{gray!6}{11.464} & \cellcolor{gray!6}{2.117} & \cellcolor{gray!6}{5.416} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{7.316} & \cellcolor{gray!6}{15.612} & \cellcolor{gray!6}{0.912}\\
+\hspace{1em}DTL on MBI & 1.951 & 1.565 & 1.247 & 0.212 & -1.115 & 5.018 & 0.106\\
+\hspace{1em}\cellcolor{gray!6}{DRF on MBI} & \cellcolor{gray!6}{-3.565} & \cellcolor{gray!6}{1.020} & \cellcolor{gray!6}{-3.495} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{-5.564} & \cellcolor{gray!6}{-1.566} & \cellcolor{gray!6}{-0.280}\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}NFC on MBI via DTH & -0.403 & 0.230 & -1.754 & 0.079 & -0.853 & 0.047 & -0.167\\
+\hspace{1em}\cellcolor{gray!6}{NFC on MBI via DTL} & \cellcolor{gray!6}{-0.039} & \cellcolor{gray!6}{0.034} & \cellcolor{gray!6}{-1.134} & \cellcolor{gray!6}{0.257} & \cellcolor{gray!6}{-0.106} & \cellcolor{gray!6}{0.028} & \cellcolor{gray!6}{-0.016}\\
+\hspace{1em}NFC on MBI via DRF & -0.215 & 0.104 & -2.070 & 0.038 & -0.418 & -0.011 & -0.089\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}\cellcolor{gray!6}{Total Effect} & \cellcolor{gray!6}{-0.632} & \cellcolor{gray!6}{0.253} & \cellcolor{gray!6}{-2.498} & \cellcolor{gray!6}{0.012} & \cellcolor{gray!6}{-1.128} & \cellcolor{gray!6}{-0.136} & \cellcolor{gray!6}{-0.262}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, $beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error, $N=179$.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
+
+\hypertarget{s3-replication-of-grass-et-al.-2018-when-including-years-spent-teaching}{%
+\subsection{S3: Replication of Grass et al.~(2018) when including years spent teaching}\label{s3-replication-of-grass-et-al.-2018-when-including-years-spent-teaching}}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Manuscript_files/figure-latex/objective1yearsplot-1} \caption{Standardized regression coefficients in the replication of Grass et al.
+(2018) when including years spent teaching.
+* $p<.05$, ** $p<.01$, $N=180$.}\label{fig:objective1yearsplot}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:objective1yearstable}Results of the replication of Grass et al. (2018) when including years spent teaching.}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}rrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Self Control} & \cellcolor{gray!6}{0.168} & \cellcolor{gray!6}{0.052} & \cellcolor{gray!6}{3.258} & \cellcolor{gray!6}{0.001} & \cellcolor{gray!6}{0.064} & \cellcolor{gray!6}{0.267} & \cellcolor{gray!6}{0.280}\\
+\hspace{1em}Years spent teaching on Self Control & 0.145 & 0.044 & 3.299 & 0.001 & 0.054 & 0.230 & 0.223\\
+\hspace{1em}\cellcolor{gray!6}{NFC on Reappraisal} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{0.036} & \cellcolor{gray!6}{1.519} & \cellcolor{gray!6}{0.129} & \cellcolor{gray!6}{-0.016} & \cellcolor{gray!6}{0.125} & \cellcolor{gray!6}{0.123}\\
+\hspace{1em}NFC on Suppression & -0.063 & 0.024 & -2.602 & 0.009 & -0.109 & -0.014 & -0.182\\
+\hspace{1em}\cellcolor{gray!6}{Self Control on RPE} & \cellcolor{gray!6}{-0.069} & \cellcolor{gray!6}{0.030} & \cellcolor{gray!6}{-2.271} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.127} & \cellcolor{gray!6}{-0.010} & \cellcolor{gray!6}{-0.169}\\
+\hspace{1em}Reappraisal on RPE & -0.094 & 0.036 & -2.618 & 0.009 & -0.164 & -0.022 & -0.173\\
+\hspace{1em}\cellcolor{gray!6}{Suppression on RPE} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{0.049} & \cellcolor{gray!6}{0.044} & \cellcolor{gray!6}{0.965} & \cellcolor{gray!6}{-0.093} & \cellcolor{gray!6}{0.101} & \cellcolor{gray!6}{0.003}\\
+\hspace{1em}NFC on RPE & -0.051 & 0.020 & -2.491 & 0.013 & -0.089 & -0.010 & -0.208\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC and years spent teaching on RPE via Self Control} & \cellcolor{gray!6}{-0.021} & \cellcolor{gray!6}{0.011} & \cellcolor{gray!6}{-1.965} & \cellcolor{gray!6}{0.049} & \cellcolor{gray!6}{-0.045} & \cellcolor{gray!6}{-0.002} & \cellcolor{gray!6}{-0.085}\\
+\hspace{1em}NFC on RPE via Reappraisal & -0.005 & 0.004 & -1.325 & 0.185 & -0.014 & 0.002 & -0.021\\
+\hspace{1em}\cellcolor{gray!6}{NFC on RPE via Suppression} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{-0.041} & \cellcolor{gray!6}{0.968} & \cellcolor{gray!6}{-0.008} & \cellcolor{gray!6}{0.006} & \cellcolor{gray!6}{-0.001}\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}Total Effect & -0.078 & 0.025 & -3.164 & 0.002 & -0.124 & -0.027 & -0.315\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, $beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=180$.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
+
+\hypertarget{s4-demand-resource-ratio-model-with-the-mbi-subscale-reduced-personal-efficacy}{%
+\subsection{S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy}\label{s4-demand-resource-ratio-model-with-the-mbi-subscale-reduced-personal-efficacy}}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Manuscript_files/figure-latex/exploratory1plot-1} \caption{Standardized path coefficients of the demand-resource-ratio model with the MBI subscale reduced personal efficacy.
+* $p<.05$, ** $p<.01$, *** $p<.001$.
+NFC = Need for Cognition, DTH = demands too high, DTL = demands too low, DRF = demand resource fit, nfc1-4 = item parcels, dth/dtl/drf1-3 = item indicators, RPE = reduced personal efficacy, $N=180$.}\label{fig:exploratory1plot}
+\end{figure}
+
+\newpage
+
+\hypertarget{s5-exploratory-model-with-all-relevant-variables}{%
+\subsection{S5: Exploratory model with all relevant variables}\label{s5-exploratory-model-with-all-relevant-variables}}
+
+\begin{table}
+
+\caption{\label{tab:explor2table}Results of the exploratory model with Covid burden.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{11}{13}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}rrrrrrr}
+\toprule
+Path & $B$ & $SE$ & $z$-value & $p$-value & CI Lower & CI Upper & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Direct Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{Years on COVB} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{0.024} & \cellcolor{gray!6}{2.327} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{0.102} & \cellcolor{gray!6}{0.168}\\
+\hspace{1em}Years on SCS & 0.137 & 0.045 & 3.037 & 0.002 & 0.049 & 0.226 & 0.212\\
+\hspace{1em}\cellcolor{gray!6}{COVB on DTH} & \cellcolor{gray!6}{0.061} & \cellcolor{gray!6}{0.014} & \cellcolor{gray!6}{4.352} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{0.034} & \cellcolor{gray!6}{0.089} & \cellcolor{gray!6}{0.449}\\
+\hspace{1em}SCS on DTH & -0.015 & 0.005 & -3.069 & 0.002 & -0.025 & -0.005 & -0.217\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DTH} & \cellcolor{gray!6}{-0.038} & \cellcolor{gray!6}{0.014} & \cellcolor{gray!6}{-2.646} & \cellcolor{gray!6}{0.008} & \cellcolor{gray!6}{-0.065} & \cellcolor{gray!6}{-0.010} & \cellcolor{gray!6}{-0.210}\\
+\hspace{1em}SCS on DRF & 0.015 & 0.006 & 2.540 & 0.011 & 0.003 & 0.026 & 0.223\\
+\hspace{1em}\cellcolor{gray!6}{NFC on DRF} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{0.018} & \cellcolor{gray!6}{3.162} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{0.022} & \cellcolor{gray!6}{0.093} & \cellcolor{gray!6}{0.336}\\
+\hspace{1em}DTH on EE & 14.985 & 2.111 & 7.098 & 0.000 & 10.847 & 19.124 & 1.004\\
+\hspace{1em}\cellcolor{gray!6}{COVB on EE} & \cellcolor{gray!6}{-0.294} & \cellcolor{gray!6}{0.136} & \cellcolor{gray!6}{-2.161} & \cellcolor{gray!6}{0.031} & \cellcolor{gray!6}{-0.560} & \cellcolor{gray!6}{-0.027} & \cellcolor{gray!6}{-0.144}\\
+\hspace{1em}DRF on RPE & -4.686 & 0.634 & -7.387 & 0.000 & -5.930 & -3.443 & -0.760\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Indirect Effects}}\\
+\hspace{1em}\cellcolor{gray!6}{NFC and Years on RPE via SCS and DRF} & \cellcolor{gray!6}{-0.279} & \cellcolor{gray!6}{0.084} & \cellcolor{gray!6}{-3.319} & \cellcolor{gray!6}{0.001} & \cellcolor{gray!6}{-0.443} & \cellcolor{gray!6}{-0.114} & \cellcolor{gray!6}{-0.291}\\
+\hspace{1em}NFC and Years on EE via SCS, COVB, and DTH & -0.543 & 0.206 & -2.633 & 0.008 & -0.947 & -0.139 & -0.181\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Total Effect}}\\
+\hspace{1em}\cellcolor{gray!6}{Total Effect} & \cellcolor{gray!6}{-0.821} & \cellcolor{gray!6}{0.256} & \cellcolor{gray!6}{-3.212} & \cellcolor{gray!6}{0.001} & \cellcolor{gray!6}{-1.322} & \cellcolor{gray!6}{-0.320} & \cellcolor{gray!6}{-0.472}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item $B$ = unstandardized regression coefficient, $beta$ = standardized regression coefficient, CI = confidence interval, COVB = Covid Burden, DTH = Demands Too High, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, SCS = Self Control Scale, $SE$ = standard error, Years = Years spent teaching, $N=180$.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
 \end{document}

### 2022-02-23 Manuscript/Analysis.R

@@ -25,9 +25,7 @@
   
   library(renv)
   source(here("Manuscript", "renv", "activate.R"))
-  #renv::activate(here("Manuscript"))
-  #renv::restore(here("Manuscript"))
-  
+
   # the required packages are:
   # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
   # "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "ppcor", "stats", "apa", "GGally"
@@ -386,7 +384,7 @@
 
 ##### Correlations #############################################################
   
-  # The following function for nicely formatted correlation output was taken from
+  # The following function for nicely formatted correlation output was (modified and) taken from
   # https://paulvanderlaken.com/2020/07/28/publication-ready-correlation-matrix-significance-r/
   # on the 5th of August 2021
   
@@ -428,9 +426,9 @@
     # transform correlations to specific character format
     Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)
     
-    # if there are any negative numbers, we want to put a space before the positives to align all
+    # if there are any negative numbers, we want to put a html space before the positives to align all
     if (sum(!is.na(R) & R < 0) > 0) {
-      Rformatted = ifelse(!is.na(R) & R > 0, paste0(" ", Rformatted), Rformatted)
+      Rformatted = ifelse(!is.na(R) & R > 0, paste0("\\&nbsp; ", Rformatted), Rformatted)
     }
     
     # add significance levels if desired
@@ -479,11 +477,11 @@
   consist_diag <- consistencies[c(colnames(correlations))]
   
   # create a vector of consistencies to be used as the diagonal in a table later
-  consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+  consist_diag <- cbind(rep("\\&nbsp; ",10), format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
                         format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
   
   # paste together to create the output "alpha(omega)"
-  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
+  consist_diag <- apply(consist_diag[,c(1:5)], 1 ,paste, collapse = "")
   
[…]

### 2022-02-24 Manuscript/Manuscript.tex
none of the decimal alignments worked and I'm mad

@@
 \cellcolor{gray!6}{1.
-MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.92) &  &  &  &  &  &  &  &  &  &  & \\
+MBI} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+2. MBI EE & .92*** &  &  &  &  &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{3.
-MBI DP} & \cellcolor{gray!6}{\&nbsp; .75***} & \cellcolor{gray!6}{\&nbsp; .54***} & \cellcolor{gray!6}{\&nbsp; .68(.69)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-4. MBI RPE & \&nbsp; .67*** & \&nbsp; .43*** & \&nbsp; .48*** & \&nbsp; .79(.79) &  &  &  &  &  &  &  &  & \\
+MBI DP} & \cellcolor{gray!6}{.75***} & \cellcolor{gray!6}{.54***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+4. MBI RPE & .67*** & .43*** & .48*** &  &  &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{5.
-ERQ} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{\&nbsp; .04} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+ERQ} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{.04} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 \addlinespace
-6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
+6. ERQ S & .05 & -.00 & .17* & .08 & .59*** &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{7.
-ERQ R} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-8. SCS & -.34*** & -.28*** & -.37*** & -.19* & -.03 & -.12 & \&nbsp; .05 & \&nbsp; .85(.86) &  &  &  &  & \\
+ERQ R} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{.71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+8. SCS & -.34*** & -.28*** & -.37*** & -.19* & -.03 & -.12 & .05 &  &  &  &  &  & \\
 \cellcolor{gray!6}{9.
-NFC} & \cellcolor{gray!6}{-.25***} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.22**} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.01} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{\&nbsp; .22**} & \cellcolor{gray!6}{\&nbsp; .89(.89)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-10. DTH & \&nbsp; .67*** & \&nbsp; .72*** & \&nbsp; .35*** & \&nbsp; .36*** & \&nbsp; .03 & \&nbsp; .05 & -.01 & -.21** & -.15* & \&nbsp; .73(.73) &  &  & \\
+NFC} & \cellcolor{gray!6}{-.25***} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.22**} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.01} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{.22**} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+10. DTH & .67*** & .72*** & .35*** & .36*** & .03 & .05 & -.01 & -.21** & -.15* &  &  &  & \\
 \addlinespace
 \cellcolor{gray!6}{11.
-DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .36***} & \cellcolor{gray!6}{\&nbsp; .38***} & \cellcolor{gray!6}{\&nbsp; .43***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.14} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{-.16*} & \cellcolor{gray!6}{\&nbsp; .41***} & \cellcolor{gray!6}{\&nbsp; .73(.75)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-12. DRF & -.55*** & -.46*** & -.41*** & -.53*** & -.00 & -.10 & \&nbsp; .10 & \&nbsp; .18* & \&nbsp; .24** & -.42*** & -.56*** & \&nbsp; .77(.77) & \\
+DTL} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.36***} & \cellcolor{gray!6}{.38***} & \cellcolor{gray!6}{.43***} & \cellcolor{gray!6}{.01} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{-.14} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{-.16*} & \cellcolor{gray!6}{.41***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+12. DRF & -.55*** & -.46*** & -.41*** & -.53*** & -.00 & -.10 & .10 & .18* & .24** & -.42*** & -.56*** &  & \\
 \cellcolor{gray!6}{13.
-COV} & \cellcolor{gray!6}{\&nbsp; .24**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{-.04} & \cellcolor{gray!6}{\&nbsp; .13} & \cellcolor{gray!6}{\&nbsp; .45***} & \cellcolor{gray!6}{\&nbsp; .10} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\
+COV} & \cellcolor{gray!6}{.24**} & \cellcolor{gray!6}{.32***} & \cellcolor{gray!6}{.08} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{-.04} & \cellcolor{gray!6}{.13} & \cellcolor{gray!6}{.45***} & \cellcolor{gray!6}{.10} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{}\\
 \bottomrule
@@
 \cellcolor{gray!6}{1.
-MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.91) &  &  &  &  &  &  &  &  &  &  & \\
+MBI} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+2. MBI EE & .92*** &  &  &  &  &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{3.
-MBI DP} & \cellcolor{gray!6}{\&nbsp; .74***} & \cellcolor{gray!6}{\&nbsp; .53***} & \cellcolor{gray!6}{\&nbsp; .68(.66)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-4. MBI RPE & \&nbsp; .66*** & \&nbsp; .42*** & \&nbsp; .47*** & \&nbsp; .79(.78) &  &  &  &  &  &  &  &  & \\
+MBI DP} & \cellcolor{gray!6}{.74***} & \cellcolor{gray!6}{.53***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+4. MBI RPE & .66*** & .42*** & .47*** &  &  &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{5.
-ERQ} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{\&nbsp; .05} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+ERQ} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{.05} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 \addlinespace
-6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
+6. ERQ S & .05 & -.00 & .17* & .08 & .59*** &  &  &  &  &  &  &  & \\
 \cellcolor{gray!6}{7.
-ERQ R} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-8. SCS & -.33*** & -.27*** & -.36*** & -.17* & -.04 & -.12 & \&nbsp; .04 & \&nbsp; .85(.85) &  &  &  &  & \\
+ERQ R} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{.71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+8. SCS & -.33*** & -.27*** & -.36*** & -.17* & -.04 & -.12 & .04 &  &  &  &  &  & \\
 \cellcolor{gray!6}{9.
-NFC} & \cellcolor{gray!6}{-.24**} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .15*} & \cellcolor{gray!6}{\&nbsp; .20**} & \cellcolor{gray!6}{\&nbsp; .89(.88)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-10. DTH & \&nbsp; .66*** & \&nbsp; .72*** & \&nbsp; .34*** & \&nbsp; .35*** & \&nbsp; .04 & \&nbsp; .05 & \&nbsp; .00 & -.19** & -.13 & \&nbsp; .73(.72) &  &  & \\
+NFC} & \cellcolor{gray!6}{-.24**} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{.15*} & \cellcolor{gray!6}{.20**} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+10. DTH & .66*** & .72*** & .34*** & .35*** & .04 & .05 & .00 & -.19** & -.13 &  &  &  & \\
 \addlinespace
 \cellcolor{gray!6}{11.
-DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .35***} & \cellcolor{gray!6}{\&nbsp; .37***} & \cellcolor{gray!6}{\&nbsp; .42***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.15*} & \cellcolor{gray!6}{\&nbsp; .40***} & \cellcolor{gray!6}{\&nbsp; .73(.76)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
-12. DRF & -.54*** & -.45*** & -.40*** & -.52*** & -.01 & -.10 & \&nbsp; .09 & \&nbsp; .16* & \&nbsp; .23** & -.41*** & -.55*** & \&nbsp; .77(.75) & \\
+DTL} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.35***} & \cellcolor{gray!6}{.37***} & \cellcolor{gray!6}{.42***} & \cellcolor{gray!6}{.01} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.15*} & \cellcolor{gray!6}{.40***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+12. DRF & -.54*** & -.45*** & -.40*** & -.52*** & -.01 & -.10 & .09 & .16* & .23** & -.41*** & -.55*** &  & \\
 \cellcolor{gray!6}{13.
-COV} & \cellcolor{gray!6}{\&nbsp; .23**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .07} & \cellcolor{gray!6}{\&nbsp; .00} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .14} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{-.12} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\
+COV} & \cellcolor{gray!6}{.23**} & \cellcolor{gray!6}{.32***} & \cellcolor{gray!6}{.07} & \cellcolor{gray!6}{.00} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{.14} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.08} & \cellcolor{gray!6}{-.12} & \cellcolor{gray!6}{}\\
 \bottomrule

### 2022-02-24 Manuscript/Analysis.R

@@ -428,7 +428,7 @@
     
     # if there are any negative numbers, we want to put a html space before the positives to align all
     if (sum(!is.na(R) & R < 0) > 0) {
-      Rformatted = ifelse(!is.na(R) & R > 0, paste0("\\&nbsp; ", Rformatted), Rformatted)
+      Rformatted = ifelse(!is.na(R) & R > 0, paste0(" ", Rformatted), Rformatted)
     }
     
     # add significance levels if desired
@@ -477,7 +477,7 @@
   consist_diag <- consistencies[c(colnames(correlations))]
   
   # create a vector of consistencies to be used as the diagonal in a table later
-  consist_diag <- cbind(rep("\\&nbsp; ",10), format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+  consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
                         format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
   
   # paste together to create the output "alpha(omega)"
@@ -996,7 +996,7 @@
   outlier_consist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
   
   # create a vector of consistencies to be used as the diagonal in a table later
-  outlier_consist_diag <- cbind(rep("\\&nbsp; ",10), format(round(t(outlier_consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
+  outlier_consist_diag <- cbind(format(round(t(outlier_consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
                                 format(round(t(outlier_consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
   
   # paste together to create the output "alpha(omega)"

### 2022-03-04 Manuscript/Manuscript.Rmd
changed keywords and reference style

@@
 
-keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
+keywords          : "behaviour, resources, demands, education, Covid-19"
 wordcount         : "~ 5600"
@@
 output            : papaja::apa6_pdf
-csl               : apa.csl
+csl               : sage-harvard.csl
 header-includes   :

### 2022-03-04 Manuscript/Manuscript.tex
changed keywords and reference style

@@
   pdflang={en-EN},
-  pdfkeywords={mediation, resources, demands, structural equation modelling, Covid-19},
+  pdfkeywords={behaviour, resources, demands, education, Covid-19},
   hidelinks,
@@
 \shorttitle{NFC and burnout in teachers}
-\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: ~ 5600}
+\keywords{behaviour, resources, demands, education, Covid-19\newline\indent Word count: ~ 5600}
 \usepackage{lineno}
@@
 
-Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo \& Petty, 1982).
-As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
-NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982; German form: Bless et al., 1994).
-While many studies have found medium sized positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm \& Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
-Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
-These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).
-
-One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli \& Salanova, 2014).
-Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley \& Muramatsu, 2011; Lloyd et al., 2002).
+Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo and Petty, 1982).
+As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm and Ackerman, 2013), and has come to the fore of psychological research in the last years.
+NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo and Petty, 1982; German form: Bless et al., 1994).
+While many studies have found medium sized positive associations of NFC with academic performance (Cazan and Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm and Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
+Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski and Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
+These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe and Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach and Leiter, 2016; Wiesner et al., 2005).
+
+One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli and Salanova, 2014).
+Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley and Muramatsu, 2011; Lloyd et al., 2002).
 Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
@@
 
-Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli \& Salanova, 2014).
-NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
+Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli and Salanova, 2014).
+NFC on the other hand is negatively associated with those variables (Double and Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
 This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
-This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
+This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas and Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
 What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
@@
 Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
-Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
+Since individuals high in NFC are confident in their abilities (Bye and Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski and Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
 And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with \emph{demands too high} and negatively associated with \emph{demand-resource-fit}.
-However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).
-It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
+However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli and Salanova, 2014).
+It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe and Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
 To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.
@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
-Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust \& Barth, 2020), are available at \url{https://osf.io/36ep9/}.
+Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust and Barth, 2020), are available at \url{https://osf.io/36ep9/}.
 The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
@@
 All questionnaires were used in their German form.
-Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI, Büssing \& Perrar, 1992), with items such as ``I don't really care what happens to some recipients'' and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
+Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI, Büssing and Perrar, 1992), with items such as ``I don't really care what happens to some recipients'' and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
 Its subscales \emph{emotional exhaustion}, \emph{depersonalization}, and \emph{reduced personal efficacy} showed acceptable internal consistency (Cronbach's \(\alpha>.70\)) and low retest reliabilities of \(r_{tt}=.60\), \(r_{tt}=.54\), and \(r_{tt}=.57\), respectively, over the span of one year in teachers (Maslach et al., 1997).
-NFC was assessed with the 16-item short version of the German NFC scale (NCS) (Bless et al., 1994), consisting of items (e.g., ``Thinking is not my idea of fun,'' recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+NFC was assessed with the 16-item short version of the German NFC scale (NCS) (Bless et al., 1994), consisting of items (e.g., ``Thinking is not my idea of fun'', recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
 The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\)) (Bless et al., 1994; Fleischhauer et al., 2010) and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks (Fleischhauer et al., 2015).
-Self-control was measured using the short form of the German Self-Control Scale {[}SCS-K-D; Bertrams and Dickhäuser (2009){]} that comprises 13 items (e.g., ``I am able to work effectively toward long-term goals'') with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach's \(\alpha>.80\), 7-week retest reliability \(r_{tt}=.82\)) (Bertrams \& Dickhäuser, 2009).
-Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler \& Kessler, 2009).
+Self-control was measured using the short form of the German Self-Control Scale {[}SCS-K-D; Bertrams and Dickhäuser (2009){]} that comprises 13 items (e.g., ``I am able to work effectively toward long-term goals'') with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach's \(\alpha>.80\), 7-week retest reliability \(r_{tt}=.82\)) (Bertrams and Dickhäuser, 2009).
+Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler and Kessler, 2009).
 The scale has items such as ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (reappraisal) and ``I keep my emotions to myself'' (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)) (Preece et al., 2019).
-Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (Fischer \& Lück, 2014) with items such as ``Sometimes I feel like my work doesn't really matter in my firm,'' which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
-The scale has a split-half reliability of \(r_{tt}=.95\) (Fischer \& Lück, 2014).
+Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (Fischer and Lück, 2014) with items such as ``Sometimes I feel like my work doesn't really matter in my firm'', which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
+The scale has a split-half reliability of \(r_{tt}=.95\) (Fischer and Lück, 2014).
 Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
@@
 The latent factor \emph{demands too high} was indicated by items 4, 8, and 9, \emph{demands too low} by the recoded items 12, 26, and 27, and \emph{demand-resource-fit} by items 17, 22, and 24.
-The items can be translated as follows: 4) ``There is too much pressure on me.'' 8) ``There is often too much being demanded of us at work.'' 9) ``I often feel tired and weary because of my work.'' 12) ``I can realize my ideas here.'' 17) ``I take pleasure in my work.'' 22) ``Does your place of work give you the opportunity to do what you do best?'' 24) ``Does your place of work give you enough opportunities to use your skills?'' 26) ``Are you happy with your promotion prospects?'' and 27) ``Are you happy with your position when comparing it to your skills?''
+The items can be translated as follows: 4) ``There is too much pressure on me.'', 8) ``There is often too much being demanded of us at work.'', 9) ``I often feel tired and weary because of my work.'', 12) ``I can realize my ideas here.'', 17) ``I take pleasure in my work.'', 22) ``Does your place of work give you the opportunity to do what you do best?'', 24) ``Does your place of work give you enough opportunities to use your skills?'', 26) ``Are you happy with your promotion prospects?'', and 27) ``Are you happy with your position when comparing it to your skills?''.
 Model parameters were estimated using the maximum likelihood method with robust standard errors.
@@
 For this descriptive analysis, the variables \emph{demands too high}, \emph{demands too low}, and \emph{demand-resource-fit} were computed as a sum of their item scores, not weighted as in the structural equation model.
-Using traditional cut-off values (Nunnally \& Bernstein, 1994), the Cronbach's Alpha of the three demand-resource-ratios can be considered \emph{acceptable}.
+Using traditional cut-off values (Nunnally and Bernstein, 1994), the Cronbach's Alpha of the three demand-resource-ratios can be considered \emph{acceptable}.
 The more robust MacDonald's Omega (Dunn et al., 2014) did not deviate much from Cronbach's Alpha and indicated \emph{acceptable} to \emph{good} internal consistency.
@@
 The robust Chi-square statistic of \(\chi^2=\) 399.08 (\(p < .001\)) did not indicate good model fit.
-However, since it was in the range of 4 \(df<\chi^2>\) 5 \(df\) the lack of good fit might have been due to the underlying assumption of multivariate normality (Hu \& Bentler, 1999; Schumacker \& Lomax, 2012), which was violated here.
+However, since it was in the range of 4 \(df<\chi^2>\) 5 \(df\) the lack of good fit might have been due to the underlying assumption of multivariate normality (Hu and Bentler, 1999; Schumacker and Lomax, 2012), which was violated here.
 This also held true for the CFI of 0.78, the SRMR of 0.17, and the RMSEA of 0.13, 95\% \(CI\) {[}0.12,0.14{]}.
@@
 We could replicate the relation between the two emotion regulation strategies reappraisal and suppression with \emph{reduced personal efficacy}, but not their association with NFC.
-There is ample evidence that reappraisal is associated with positive outcomes for students (Haga et al., 2007; Levine et al., 2012; Schmidt et al., 2010) and teachers alike (Jiang et al., 2016; Moè \& Katz, 2020; Tsouloupas et al., 2010), so it is suprising that reappraisal did not mediate between NFC and \emph{reduced personal efficacy}.
+There is ample evidence that reappraisal is associated with positive outcomes for students (Haga et al., 2007; Levine et al., 2012; Schmidt et al., 2010) and teachers alike (Jiang et al., 2016; Moè and Katz, 2020; Tsouloupas et al., 2010), so it is suprising that reappraisal did not mediate between NFC and \emph{reduced personal efficacy}.
 Reappraisal did correlate with NFC, as it should appease the preference for cognitive effort in individuals with high NFC, but it was not a mediator in this model.
@@
 The fact that the items that made up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.
-This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands (Lazarus \& Folkman, 1984; Lepine et al., 2005; Podsakoff et al., 2007).
+This individual appraisal has been emphasized as the cause for the ambiguous impact of demands on psychological well-being before, in the form of challenge demands and hindrance demands (Lazarus and Folkman, 1984; Lepine et al., 2005; Podsakoff et al., 2007).
 Challenge demands such as time pressure, responsibility, and workload (Podsakoff et al., 2007) are being positively valued due to their potential to increase personal growth, positive affect, and problem-focused coping (Lepine et al., 2005).
@@
 (2015) found that hindrance but not challenge demands were positively related to burnout in teachers, and teachers who reported high challenge and low hindrance demands also reported higher engagement.
-Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy (Bandura, 1997), so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom (Cherniss, 1993; M.
-Vera et al., 2012).
-Self-efficacy and self-control are closely entwined (Przepiórka et al., 2019; E.
-M.
-Vera et al., 2004; Yang et al., 2019) and both are positively associated with NFC (Bertrams \& Dickhäuser, 2012; Holch \& Marwood, 2020; Naderi et al., 2018; Xu \& Cheng, 2021).
+Whether and to what extent a circumstance is perceived as a challenge or hindrance demand is highly influenced by a person's level of self-efficacy (Bandura, 1997), so much so that a reduction in self-efficacy is considered to be a precurser of burnout, not necessarily a symptom (Cherniss, 1993; Vera et al., 2012).
+Self-efficacy and self-control are closely entwined (Przepiórka et al., 2019; Vera et al., 2004; Yang et al., 2019) and both are positively associated with NFC (Bertrams and Dickhäuser, 2012; Holch and Marwood, 2020; Naderi et al., 2018; Xu and Cheng, 2021).
 Cacioppo et al. (1996) even proposed that higher levels of NFC might develop as a result of a high need for structure or control in those who have the skill, ability, and inclination to do so.
@@
 One possible explanation is that teachers with higher NFC show higher consideration of the consequences and progression of the pandemic, thereby anticipating that it will take a long time until normal teaching can resume, which heightens their feeling of being burdened.
-Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively (Nishiguchi et al., 2018; Vannucci \& Chiorri, 2018), a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
+Although NFC has been shown to be related to more reflective thinking and unrelated to rumination, which are considered healthy and unhealthy thinking styles, respectively (Nishiguchi et al., 2018; Vannucci and Chiorri, 2018), a higher perceived Covid burden itself cannot indicate whether it stems from a realistic view on the pandemic or a feeling of being overwhelmed.
 Teachers with more years of experience also reported higher Covid burden, presumably because older people are less comfortable with technology (Hauk et al., 2018) and therefore stressed by the prospect of online teaching.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-Abler, B., \& Kessler, H.
-(2009).
-Emotion {Regulation} {Questionnaire} -- {Eine} deutschsprachige {Fassung} des {ERQ} von {Gross} und {John}.
-\emph{Diagnostica}, \emph{55}(3), 144--152.
-\url{https://doi.org/10.1026/0012-1924.55.3.144}
+Abler B and Kessler H (2009) Emotion {Regulation} {Questionnaire} -- {Eine} deutschsprachige {Fassung} des {ERQ} von {Gross} und {John}.
+\emph{Diagnostica} 55(3): 144--152.
+DOI: \href{https://doi.org/10.1026/0012-1924.55.3.144}{10.1026/0012-1924.55.3.144}.
 
 \leavevmode\hypertarget{ref-Aust2020}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
+Aust F and Barth M (2020) \emph{{papaja}: {Create} {APA} Manuscripts with {R Markdown}}. Available at: \url{https://github.com/crsh/papaja}.
 
 \leavevmode\hypertarget{ref-Bandura1997}{}%
-Bandura, A. (1997). \emph{Self-{Efficacy}: {The} exercise of control}. Worth Publishers.
+Bandura A (1997) \emph{Self-{Efficacy}: {The} Exercise of Control}. Worth Publishers.
 
 \leavevmode\hypertarget{ref-Bertrams2009a}{}%
-Bertrams, A., \& Dickhäuser, O. (2009). Messung dispositioneller {Selbstkontroll}-{Kapazität}. \emph{Diagnostica}, \emph{55}(1), 2--10. \url{https://doi.org/10.1026/0012-1924.55.1.2}
+Bertrams A and Dickhäuser O (2009) Messung dispositioneller {Selbstkontroll}-{Kapazität}.
+\emph{Diagnostica} 55(1): 2--10.
+DOI: \href{https://doi.org/10.1026/0012-1924.55.1.2}{10.1026/0012-1924.55.1.2}.
 
 \leavevmode\hypertarget{ref-Bertrams2012}{}%
-Bertrams, A., \& Dickhäuser, O. (2012). Passionate thinkers feel better. \emph{Journal of Individual Differences}, \emph{33}(2), 69--75. \url{https://doi.org/10.1027/1614-0001/a000081}
+Bertrams A and Dickhäuser O (2012) Passionate thinkers feel better.
+\emph{Journal of Individual Differences} 33(2): 69--75.
+DOI: \href{https://doi.org/10.1027/1614-0001/a000081}{10.1027/1614-0001/a000081}.
 
 \leavevmode\hypertarget{ref-Bless1994}{}%
-Bless, H., Wänke, M., Bohner, G., Fellhauer, R.
-F., \& Schwarz, N.
-(1994).
-Need for {Cognition}: {Eine} {Skala} zur {Erfassung} von {Engagement} und {Freude} bei {Denkaufgaben}.
-\emph{Zeitschrift für Sozialpsychologie}, \emph{25}.
-\url{https://doi.org/1779110}
+Bless H, Wänke M, Bohner G, et al.
+(1994) Need for {Cognition}: {Eine} {Skala} zur {Erfassung} von {Engagement} und {Freude} bei {Denkaufgaben}.
+\emph{Zeitschrift für Sozialpsychologie} 25.
+DOI: \href{https://doi.org/1779110}{1779110}.
 
 \leavevmode\hypertarget{ref-BoehmKasper2001}{}%
-Böhm-Kasper, O., Bos, O., Körner, S.
-C., \& Weishaupt, H.
-(2001).
-{EBI}.
+Böhm-Kasper O, Bos O, Körner SC, et al.
+(2001) {EBI}.
 {Das} {Erfurter} {Belastungsinventar} zur {Erfassung} von {Belastung} und {Beanspruchung} von {Lehrern} und {Schülern} am {Gymnasium}.
-\emph{Schulforschung Und Schulentwicklung.
-Aktuelle Forschungsbeiträge}, \emph{14}, 35--66.
-\url{https://pub.uni-bielefeld.de/record/1858836}
+\emph{Schulforschung und Schulentwicklung.
+Aktuelle Forschungsbeiträge} 14: 35--66.
+Available at: \url{https://pub.uni-bielefeld.de/record/1858836} (accessed 25 May 2021).
 
 \leavevmode\hypertarget{ref-Brady2021}{}%
-Brady, K.
-J.
-S., Sheldrick, R.
-C., Ni, P., Trockel, M.
-T., Shanafelt, T.
-D., Rowe, S.
-G., \& Kazis, L.
-E.
-(2021).
-Examining the measurement equivalence of the {Maslach} {Burnout} {Inventory} across age, gender, and specialty groups in {US} physicians.
-\emph{Journal of Patient-Reported Outcomes}, \emph{5}(1), 43.
-\url{https://doi.org/10.1186/s41687-021-00312-2}
+Brady KJS, Sheldrick RC, Ni P, et al.
+(2021) Examining the measurement equivalence of the {Maslach} {Burnout} {Inventory} across age, gender, and specialty groups in {US} physicians.
+\emph{Journal of Patient-Reported Outcomes} 5(1): 43.
+DOI: \href{https://doi.org/10.1186/s41687-021-00312-2}{10.1186/s41687-021-00312-2}.
 
 \leavevmode\hypertarget{ref-Buessing1992}{}%
-Büssing, A., \& Perrar, K.-M.
-(1992).
-Die {Messung} von {Burnout}.
+Büssing A and Perrar K-M (1992) Die {Messung} von {Burnout}.
 {Untersuchung} einer deutschen {Fassung} des {Maslach} {Burnout} {Inventory} ({MBI}-{D}).
 {[}{Measuring} burnout: {A} study of a {German} version of the {Maslach} {Burnout} {Inventory} ({MBI}-{D}).{]}.
-\emph{Diagnostica}, \emph{38}(4), 328--353.
+\emph{Diagnostica} 38(4): 328--353.
 
 \leavevmode\hypertarget{ref-Bye2009}{}%
-Bye, D., \& Pushkar, D.
-(2009).
-How need for cognition and perceived control are differentially linked to emotional outcomes in the transition to retirement.
-\emph{Motivation and Emotion}, \emph{33}(3), 320--332.
-\url{https://doi.org/10.1007/s11031-009-9135-3}
+Bye D and Pushkar D (2009) How need for cognition and perceived control are differentially linked to emotional outcomes in the transition to retirement.
+\emph{Motivation and Emotion} 33(3).
+Springer Science; Business Media {LLC}: 320--332.
+DOI: \href{https://doi.org/10.1007/s11031-009-9135-3}{10.1007/s11031-009-9135-3}.
 
 \leavevmode\hypertarget{ref-Cacioppo1982}{}%
-Cacioppo, J. T., \& Petty, R. E. (1982). The {Need} for {Cognition}. \emph{Journal of Personality and Social Psychology}, \emph{42}(1), 116--131. \url{https://doi.org/10.1037//0022-3514.42.1.116}
+Cacioppo JT and Petty RE (1982) The {Need} for {Cognition}.
+\emph{Journal of Personality and Social Psychology} 42(1): 116--131.
+DOI: \href{https://doi.org/10.1037//0022-3514.42.1.116}{10.1037//0022-3514.42.1.116}.
+
+\leavevmode\hypertarget{ref-Cacioppo1984}{}%
+Cacioppo JT, Petty RE and Kao CF (1984) The {Efficient} {Assessment} of {Need} for {Cognition}.
+\emph{Journal of Personality Assessment} 48(3): 306--307.
+DOI: \href{https://doi.org/10.1207/s15327752jpa4803_13}{10.1207/s15327752jpa4803\_13}.
 
 \leavevmode\hypertarget{ref-Cacioppo1996}{}%
-Cacioppo, J.
-T., Petty, R.
-E., Feinstein, J.
-A., \& Jarvis, W.
-B.
-G.
-(1996).
-Dispositional differences in cognitive motivation: {The} life and times of individuals varying in need for cognition.
-\emph{Psychological Bulletin}, \emph{119}(2), 197--253.
-\url{https://doi.org/10.1037/0033-2909.119.2.197}
-
-\leavevmode\hypertarget{ref-Cacioppo1984}{}%
-Cacioppo, J.
-T., Petty, R.
-E., \& Kao, C.
-F.
-(1984).
-The {Efficient} {Assessment} of {Need} for {Cognition}.
-\emph{Journal of Personality Assessment}, \emph{48}(3), 306--307.
-\url{https://doi.org/10.1207/s15327752jpa4803_13}
+Cacioppo JT, Petty RE, Feinstein JA, et al.
+(1996) Dispositional differences in cognitive motivation: {The} life and times of individuals varying in need for cognition.
+\emph{Psychological Bulletin} 119(2): 197--253.
+DOI: \href{https://doi.org/10.1037/0033-2909.119.2.197}{10.1037/0033-2909.119.2.197}.
 
 \leavevmode\hypertarget{ref-Cazan2014}{}%
-Cazan, A.-M., \& Indreica, S.
-E.
-(2014).
-Need for {Cognition} and {Approaches} to {Learning} among {University} {Students}.
-\emph{Procedia - Social and Behavioral Sciences}, \emph{127}, 134--138.
-\url{https://doi.org/10.1016/j.sbspro.2014.03.227}
+Cazan A-M and Indreica SE (2014) Need for {Cognition} and {Approaches} to {Learning} among {University} {Students}.
+\emph{Procedia - Social and Behavioral Sciences} 127.
+The {International} {Conference} {PSYCHOLOGY} {and} {THE} {REALITIES} {OF} {THE} {CONTEMPORARY} {WORLD} -- 4th {edition} - {PSIWORLD} 2013: 134--138.
+DOI: \href{https://doi.org/10.1016/j.sbspro.2014.03.227}{10.1016/j.sbspro.2014.03.227}.
 
 \leavevmode\hypertarget{ref-Champely2020}{}%
-Champely, S. (2020). \emph{Pwr: Basic functions for power analysis}. \url{https://CRAN.R-project.org/package=pwr}
+Champely S (2020) \emph{Pwr: Basic Functions for Power Analysis}. Available at: \url{https://CRAN.R-project.org/package=pwr}.
 
 \leavevmode\hypertarget{ref-Cherniss1993}{}%
-Cherniss, C. (1993). \emph{Professional burnout: Recent developments in theory and research} (W. B. Schaufeli, C. Maslach, \& T. Marek, Eds.; pp. 135--149). Taylor \& Francis.
+Cherniss C (1993) Professional burnout: Recent developments in theory and research. In: Schaufeli WB, Maslach C, and Marek T (eds). Taylor \& Francis, pp. 135--149.
 
 \leavevmode\hypertarget{ref-Dodge2012}{}%
-Dodge, R., Daly, A.
-P., Huyton, J., \& Sanders, L.
-D.
-(2012).
-The challenge of defining wellbeing.
-\emph{International Journal of Wellbeing}, \emph{2}(3).
-\url{https://www.internationaljournalofwellbeing.org/index.php/ijow/article/view/89}
+Dodge R, Daly AP, Huyton J, et al.
+(2012) The challenge of defining wellbeing.
+\emph{International Journal of Wellbeing} 2(3).
+Available at: \url{https://www.internationaljournalofwellbeing.org/index.php/ijow/article/view/89} (accessed 27 April 2021).
 
 \leavevmode\hypertarget{ref-Double2016}{}%
-Double, K.
-S., \& Birney, D.
-P.
-(2016).
-The effects of personality and metacognitive beliefs on cognitive training adherence and performance.
-\emph{Personality and Individual Differences}, \emph{102}, 7--12.
-\url{https://doi.org/10.1016/j.paid.2016.04.101}
+Double KS and Birney DP (2016) The effects of personality and metacognitive beliefs on cognitive training adherence and performance.
+\emph{Personality and Individual Differences} 102: 7--12.
+DOI: \href{https://doi.org/10.1016/j.paid.2016.04.101}{10.1016/j.paid.2016.04.101}.
 
 \leavevmode\hypertarget{ref-Dragano2017}{}%
-Dragano, N., Siegrist, J., Nyberg, S.
-T., Lunau, T., Fransson, E.
-I., Alfredsson, L., Bjorner, J.
-B., Borritz, M., Burr, H., Erbel, R., Fahlén, G., Goldberg, M., Hamer, M., Heikkilä, K., Jöckel, K.-H., Knutsson, A., Madsen, I.
-E.
-H., Nielsen, M.
-L., Nordin, M., \ldots{} Kivimäki, M.
-(2017).
-Effort{{}}reward imbalance at work and incident coronary heart disease.
-\emph{Epidemiology}, \emph{28}(4), 619--626.
-\url{https://doi.org/10.1097/ede.0000000000000666}
+Dragano N, Siegrist J, Nyberg ST, et al.
+(2017) Effort{{}}reward imbalance at work and incident coronary heart disease.
+\emph{Epidemiology} 28(4).
+Ovid Technologies (Wolters Kluwer Health): 619--626.
+DOI: \href{https://doi.org/10.1097/ede.0000000000000666}{10.1097/ede.0000000000000666}.
 
 \leavevmode\hypertarget{ref-Dunn2014}{}%
-Dunn, T.
-J., Baguley, T., \& Brunsden, V.
-(2014).
-From alpha to omega: {A} practical solution to the pervasive problem of internal consistency estimation.
-\emph{British Journal of Psychology}, \emph{105}(3), 399--412.
-\url{https://doi.org/10.1111/bjop.12046}
+Dunn TJ, Baguley T and Brunsden V (2014) From alpha to omega: {A} practical solution to the pervasive problem of internal consistency estimation.
+\emph{British Journal of Psychology} 105(3): 399--412.
+DOI: \href{https://doi.org/10.1111/bjop.12046}{10.1111/bjop.12046}.
+
+\leavevmode\hypertarget{ref-Faul2007}{}%
+Faul F, Erdfelder E, Lang A-G, et al.
+(2007) G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences.
+\emph{Behavior Research Methods} 39(2): 175--191.
+DOI: \href{https://doi.org/10.3758/BF03193146}{10.3758/BF03193146}.
 
 \leavevmode\hypertarget{ref-Faul2009}{}%
-Faul, F., Erdfelder, E., Buchner, A., \& Lang, A.-G.
-(2009).
-Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses.
-\emph{Behavior Research Methods}, \emph{41}(4), 1149--1160.
-\url{https://doi.org/10.3758/BRM.41.4.1149}
-
-\leavevmode\hypertarget{ref-Faul2007}{}%
-Faul, F., Erdfelder, E., Lang, A.-G., \& Buchner, A.
-(2007).
-G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences.
-\emph{Behavior Research Methods}, \emph{39}(2), 175--191.
-\url{https://doi.org/10.3758/BF03193146}
+Faul F, Erdfelder E, Buchner A, et al.
+(2009) Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses.
+\emph{Behavior Research Methods} 41(4): 1149--1160.
+DOI: \href{https://doi.org/10.3758/BRM.41.4.1149}{10.3758/BRM.41.4.1149}.
 
 \leavevmode\hypertarget{ref-Fischer2014}{}%
-Fischer, L., \& Lück, H. E. (2014). Allgemeine {Arbeitszufriedenheit}. \emph{Zusammenstellung Sozialwissenschaftlicher Items Und Skalen (ZIS)}. \url{https://doi.org/10.6102/ZIS1}
+Fischer L and Lück HE (2014) Allgemeine {Arbeitszufriedenheit}. \emph{Zusammenstellung sozialwissenschaftlicher Items und Skalen (ZIS)}. DOI: \href{https://doi.org/10.6102/ZIS1}{10.6102/ZIS1}.
 
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-Fleischhauer, M., Enge, S., Brocke, B., Ullrich, J., Strobel, A., \& Strobel, A.
-(2010).
-Same or different?
+Fleischhauer M, Enge S, Brocke B, et al.
+(2010) Same or different?
 {Clarifying} the relationship of need for cognition to personality and intelligence.
-\emph{Personality \& Social Psychology Bulletin}, \emph{36}(1), 82--96.
-\url{https://doi.org/10.1177/0146167209351886}
+\emph{Personality \& Social Psychology Bulletin} 36(1): 82--96.
+DOI: \href{https://doi.org/10.1177/0146167209351886}{10.1177/0146167209351886}.
+
+\leavevmode\hypertarget{ref-Fleischhauer2015}{}%
+Fleischhauer M, Strobel A and Strobel A (2015) Directly and indirectly assessed {Need for Cognition} differentially predict spontaneous and reflective information processing behavior.
+\emph{Journal of Individual Differences} 36(2).
+Hogrefe Publishing Group: 101--109.
+DOI: \href{https://doi.org/10.1027/1614-0001/a000161}{10.1027/1614-0001/a000161}.
 
 \leavevmode\hypertarget{ref-Fleischhauer2019}{}%
-Fleischhauer, M., Miller, R., Wekenborg, M.
-K., Penz, M., Kirschbaum, C., \& Enge, S.
-(2019).
-Thinking against burnout?
+Fleischhauer M, Miller R, Wekenborg MK, et al.
+(2019) Thinking against burnout?
 {An} individual's tendency to engage in and enjoy thinking as a potential resilience factor of burnout symptoms and burnout-related impairment in executive functioning.
-\emph{Frontiers in Psychology}, \emph{10}, 420.
-\url{https://doi.org/10.3389/fpsyg.2019.00420}
-
-\leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-Fleischhauer, M., Strobel, A., \& Strobel, A.
-(2015).
-Directly and indirectly assessed {Need for Cognition} differentially predict spontaneous and reflective information processing behavior.
-\emph{Journal of Individual Differences}, \emph{36}(2), 101--109.
-\url{https://doi.org/10.1027/1614-0001/a000161}
+\emph{Frontiers in Psychology} 10: 420.
+DOI: \href{https://doi.org/10.3389/fpsyg.2019.00420}{10.3389/fpsyg.2019.00420}.
 
 \leavevmode\hypertarget{ref-Froebe2021}{}%
-Fröbe, A., \& Franco, P.
-(2021).
-Burnout among health care professionals in {COVID19} pandemic.
-\emph{Libri Oncologici}, 40--42.
-\url{https://pesquisa.bvsalud.org/global-literature-on-novel-coronavirus-2019-ncov/resource/pt/covidwho-1282947?lang=en}
+Fröbe A and Franco P (2021) Burnout among health care professionals in {COVID19} pandemic.
+\emph{Libri Oncologici}: 40--42.
+Available at: \url{https://pesquisa.bvsalud.org/global-literature-on-novel-coronavirus-2019-ncov/resource/pt/covidwho-1282947?lang=en} (accessed 4 August 2021).
 
 \leavevmode\hypertarget{ref-Gallivan2020}{}%
-Gallivan, N. (2020). \emph{Behavior feedback and {Need} for {Cognition}: {Factors} affecting coffee beverage consumption} {[}Thesis{]}. \url{https://krex.k-state.edu/dspace/handle/2097/40878}
+Gallivan N (2020) \emph{Behavior feedback and {Need} for {Cognition}: {Factors} affecting coffee beverage consumption}.
+Thesis.
+Available at: \url{https://krex.k-state.edu/dspace/handle/2097/40878} (accessed 16 March 2021).
 
 \leavevmode\hypertarget{ref-Ghorbani2004}{}%
-Ghorbani, N., Davison, H.
-K., Bing, M.
-N., Watson, P.
-J., \& Krauss, S.
-W.
-(2004).
-Private {Self}-{Consciousness} factors: {Relationships} {With} {Need} for {Cognition}, locus of control, and obsessive thinking in {Iran} and the {United} {States}.
-\emph{Journal of Social Psychology}, \emph{144}(4), 359--372.
-\url{http://search.ebscohost.com/login.aspx?direct=true\&db=a9h\&AN=14015824\&site=ehost-live}
+Ghorbani N, Davison HK, Bing MN, et al.
+(2004) Private {Self}-{Consciousness} factors: {Relationships} {With} {Need} for {Cognition}, locus of control, and obsessive thinking in {Iran} and the {United} {States}.
+\emph{Journal of Social Psychology} 144(4): 359--372.
+Available at: \url{http://search.ebscohost.com/login.aspx?direct=true\&db=a9h\&AN=14015824\&site=ehost-live} (accessed 5 March 2018).
 
 \leavevmode\hypertarget{ref-Gignac2016}{}%
-Gignac, G.
-E., \& Szodorai, E.
-T.
-(2016).
-Effect size guidelines for individual differences researchers.
-\emph{Personality and Individual Differences}, \emph{102}, 74--78.
-\url{https://doi.org/10.1016/j.paid.2016.06.069}
+Gignac GE and Szodorai ET (2016) Effect size guidelines for individual differences researchers.
+\emph{Personality and Individual Differences} 102: 74--78.
+DOI: \href{https://doi.org/10.1016/j.paid.2016.06.069}{10.1016/j.paid.2016.06.069}.
+
+\leavevmode\hypertarget{ref-Grass2017}{}%
+Grass J, Strobel A and Strobel A (2017) Cognitive investments in academic success: {The} role of {Need} for {Cognition} at university.
+\emph{Frontiers in Psychology} 8.
+DOI: \href{https://doi.org/10.3389/fpsyg.2017.00790}{10.3389/fpsyg.2017.00790}.
 
 \leavevmode\hypertarget{ref-Grass2018}{}%
-Grass, J., John, N., \& Strobel, A.
-(2018).
-The joy of thinking as the key to success?
+Grass J, John N and Strobel A (2018) The joy of thinking as the key to success?
 {The} importance of {Need} for {Cognition} for subjective experience and achievement in academic studies.
-\emph{Zeitschrift für Padagogische Psychologie}, \emph{32}(3), 145--154.
-\url{https://doi.org/10.1024/1010-0652/a000222}
-
-\leavevmode\hypertarget{ref-Grass2017}{}%
-Grass, J., Strobel, A., \& Strobel, A.
-(2017).
-Cognitive investments in academic success: {The} role of {Need} for {Cognition} at university.
-\emph{Frontiers in Psychology}, \emph{8}.
-\url{https://doi.org/10.3389/fpsyg.2017.00790}
+\emph{Zeitschrift für Padagogische Psychologie} 32(3): 145--154.
+DOI: \href{https://doi.org/10.1024/1010-0652/a000222}{10.1024/1010-0652/a000222}.
 
 \leavevmode\hypertarget{ref-GrayStanley2011}{}%
-Gray-Stanley, J.
-A., \& Muramatsu, N.
-(2011).
-Work stress, burnout, and social and personal resources among direct care workers.
-\emph{Research in Developmental Disabilities}, \emph{32}(3), 1065--1074.
-\url{https://doi.org/10.1016/j.ridd.2011.01.025}
+Gray-Stanley JA and Muramatsu N (2011) Work stress, burnout, and social and personal resources among direct care workers.
+\emph{Research in Developmental Disabilities} 32(3).
+Elsevier {BV}: 1065--1074.
+DOI: \href{https://doi.org/10.1016/j.ridd.2011.01.025}{10.1016/j.ridd.2011.01.025}.
 
 \leavevmode\hypertarget{ref-Gross1998a}{}%
-Gross, J.
-J.
-(1998).
-Antecedent- and response-focused emotion regulation: {Divergent} consequences for experience, expression, and physiology.
-\emph{Journal of Personality and Social Psychology}, \emph{74}(1), 224--237.
-\url{https://doi.org/10.1037//0022-3514.74.1.224}
+Gross JJ (1998) Antecedent- and response-focused emotion regulation: {Divergent} consequences for experience, expression, and physiology.
+\emph{Journal of Personality and Social Psychology} 74(1): 224--237.
+DOI: \href{https://doi.org/10.1037//0022-3514.74.1.224}{10.1037//0022-3514.74.1.224}.
 
 \leavevmode\hypertarget{ref-Haga2007}{}%
-Haga, S.
-M., Kraft, P., \& Corby, E.-K.
-(2007).
-Emotion regulation: Antecedents and well-being outcomes of cognitive reappraisal and expressive suppression in cross-cultural samples.
-\emph{Journal of Happiness Studies}, \emph{10}(3), 271--291.
-\url{https://doi.org/10.1007/s10902-007-9080-3}
+Haga SM, Kraft P and Corby E-K (2007) Emotion regulation: Antecedents and well-being outcomes of cognitive reappraisal and expressive suppression in cross-cultural samples.
+\emph{Journal of Happiness Studies} 10(3).
+Springer Science; Business Media {LLC}: 271--291.
+DOI: \href{https://doi.org/10.1007/s10902-007-9080-3}{10.1007/s10902-007-9080-3}.
 
 \leavevmode\hypertarget{ref-Hauk2018}{}%
-Hauk, N., Hüffmeier, J., \& Krumm, S.
-(2018).
-Ready to be a {Silver Surfer}?
+Hauk N, Hüffmeier J and Krumm S (2018) Ready to be a {Silver Surfer}?
 {A} meta-analysis on the relationship between chronological age and technology acceptance.
-\emph{Computers in Human Behavior}, \emph{84}, 304--319.
-\url{https://doi.org/10.1016/j.chb.2018.01.020}
+\emph{Computers in Human Behavior} 84.
+Elsevier {BV}: 304--319.
+DOI: \href{https://doi.org/10.1016/j.chb.2018.01.020}{10.1016/j.chb.2018.01.020}.
 
 \leavevmode\hypertarget{ref-Heppner1983}{}%
-Heppner, P.
-P., Reeder, B.
-L., \& Larson, L.
-M.
-(1983).
-Cognitive variables associated with personal problem-solving appraisal: {Implications} for counseling.
-\emph{Journal of Counseling Psychology}, \emph{30}(4), 537--545.
-\url{https://doi.org/10.1037/0022-0167.30.4.537}
+Heppner PP, Reeder BL and Larson LM (1983) Cognitive variables associated with personal problem-solving appraisal: {Implications} for counseling.
+\emph{Journal of Counseling Psychology} 30(4): 537--545.
+DOI: \href{https://doi.org/10.1037/0022-0167.30.4.537}{10.1037/0022-0167.30.4.537}.
 
 \leavevmode\hypertarget{ref-Hobfoll1989}{}%
-Hobfoll, S. E. (1989). Conservation of resources: {A} new attempt at conceptualizing stress. \emph{American Psychologist}, \emph{44}(3), 513--524. \url{https://doi.org/10.1037/0003-066X.44.3.513}
+Hobfoll SE (1989) Conservation of resources: {A} new attempt at conceptualizing stress.
+\emph{American Psychologist} 44(3): 513--524.
+DOI: \href{https://doi.org/10.1037/0003-066X.44.3.513}{10.1037/0003-066X.44.3.513}.
 
 \leavevmode\hypertarget{ref-Holch2020}{}%
-Holch, P., \& Marwood, J.
-R.
-(2020).
-{EHealth} literacy in {UK} teenagers and young adults: {Exploration} of predictors and factor structure of the {eHealth} {Literacy} {Scale} ({eHEALS}).
-\emph{JMIR Formative Research}, \emph{4}(9), e14450.
-\url{https://doi.org/10.2196/14450}
+Holch P and Marwood JR (2020) {EHealth} literacy in {UK} teenagers and young adults: {Exploration} of predictors and factor structure of the {eHealth} {Literacy} {Scale} ({eHEALS}).
+\emph{JMIR formative research} 4(9): e14450.
+DOI: \href{https://doi.org/10.2196/14450}{10.2196/14450}.
 
 \leavevmode\hypertarget{ref-Hu1999}{}%
-Hu, L., \& Bentler, P.
-M.
-(1999).
-Cutoff criteria for fit indexes in covariance structure analysis: {Conventional} criteria versus new alternatives.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{6}(1), 1--55.
-\url{https://doi.org/10.1080/10705519909540118}
+Hu L and Bentler PM (1999) Cutoff criteria for fit indexes in covariance structure analysis: {Conventional} criteria versus new alternatives.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal} 6(1): 1--55.
+DOI: \href{https://doi.org/10.1080/10705519909540118}{10.1080/10705519909540118}.
 
 \leavevmode\hypertarget{ref-Jiang2016}{}%
-Jiang, J., Vauras, M., Volet, S., \& Wang, Y.
-(2016).
-Teachers{{}} emotions and emotion regulation strategies: Self- and students{{}} perceptions.
-\emph{Teaching and Teacher Education}, \emph{54}, 22--31.
-\url{https://doi.org/10.1016/j.tate.2015.11.008}
+Jiang J, Vauras M, Volet S, et al.
+(2016) Teachers{{}} emotions and emotion regulation strategies: Self- and students{{}} perceptions.
+\emph{Teaching and Teacher Education} 54.
+Elsevier {BV}: 22--31.
+DOI: \href{https://doi.org/10.1016/j.tate.2015.11.008}{10.1016/j.tate.2015.11.008}.
 
 \leavevmode\hypertarget{ref-Kantas1997}{}%
-Kantas, A., \& Vassilaki, E.
-(1997).
-Burnout in {Greek} teachers: {Main} findings and validity of the {Maslach} {Burnout} {Inventory}.
-\emph{Work \& Stress}, \emph{11}(1), 94--100.
-\url{https://doi.org/10.1080/02678379708256826}
+Kantas A and Vassilaki E (1997) Burnout in {Greek} teachers: {Main} findings and validity of the {Maslach} {Burnout} {Inventory}.
+\emph{Work \& Stress} 11(1).
+Routledge: 94--100.
+DOI: \href{https://doi.org/10.1080/02678379708256826}{10.1080/02678379708256826}.
 
 \leavevmode\hypertarget{ref-Karagiannopoulou2020}{}%
-Karagiannopoulou, E., Milienos, F.
-S., \& Rentzios, C.
-(2020).
-Grouping learning approaches and emotional factors to predict students' academic progress.
-\emph{International Journal of School \& Educational Psychology}, \emph{0}(0), 1--18.
-\url{https://doi.org/10.1080/21683603.2020.1832941}
+Karagiannopoulou E, Milienos FS and Rentzios C (2020) Grouping learning approaches and emotional factors to predict students' academic progress.
+\emph{International Journal of School \& Educational Psychology} 0(0): 1--18.
+DOI: \href{https://doi.org/10.1080/21683603.2020.1832941}{10.1080/21683603.2020.1832941}.
 
 \leavevmode\hypertarget{ref-Klaczynski1996}{}%
-Klaczynski, P.
-A., \& Fauth, J.
-M.
-(1996).
-Intellectual ability, rationality, and intuitiveness as predictors of warranted and unwarranted optimism for future life events.
-\emph{Journal of Youth and Adolescence}, \emph{25}(6), 755--773.
-\url{https://doi.org/10.1007/BF01537452}
+Klaczynski PA and Fauth JM (1996) Intellectual ability, rationality, and intuitiveness as predictors of warranted and unwarranted optimism for future life events.
+\emph{Journal of Youth and Adolescence} 25(6): 755--773.
+DOI: \href{https://doi.org/10.1007/BF01537452}{10.1007/BF01537452}.
 
 \leavevmode\hypertarget{ref-Lackritz2004}{}%
-Lackritz, J.
-R.
-(2004).
-Exploring burnout among university faculty: Incidence, performance, and demographic issues.
-\emph{Teaching and Teacher Education}, \emph{20}(7), 713--729.
-\url{https://doi.org/10.1016/j.tate.2004.07.002}
+Lackritz JR (2004) Exploring burnout among university faculty: Incidence, performance, and demographic issues.
+\emph{Teaching and Teacher Education} 20(7): 713--729.
+DOI: \href{https://doi.org/10.1016/j.tate.2004.07.002}{10.1016/j.tate.2004.07.002}.
 
 \leavevmode\hypertarget{ref-Latimer2007}{}%
-Latimer, A.
-E., Williams‐Piehota, P., Cox, A., Katulak, N.
-A., Salovey, P., \& Mowad, L.
-(2007).
-Encouraging {Cancer} {Patients} to {Talk} to {Their} {Physicians} {About} {Clinical} {Trials}: {Considering} {Patients}' {Information} {Needs1}.
-\emph{Journal of Applied Biobehavioral Research}, \emph{12}(3-4), 178--195.
-\url{https://doi.org/10.1111/j.1751-9861.2008.00020.x}
+Latimer AE, Williams‐Piehota P, Cox A, et al.
+(2007) Encouraging {Cancer} {Patients} to {Talk} to {Their} {Physicians} {About} {Clinical} {Trials}: {Considering} {Patients}' {Information} {Needs1}.
+\emph{Journal of Applied Biobehavioral Research} 12(3-4): 178--195.
+DOI: \href{https://doi.org/10.1111/j.1751-9861.2008.00020.x}{10.1111/j.1751-9861.2008.00020.x}.
 
 \leavevmode\hypertarget{ref-Lavrijsen2021}{}%
-Lavrijsen, J., Preckel, F., Verachtert, P., Vansteenkiste, M., \& Verschueren, K.
-(2021).
-Are motivational benefits of adequately challenging schoolwork related to students' need for cognition, cognitive ability, or both?
-\emph{Personality and Individual Differences}, \emph{171}, 110558.
-\url{https://doi.org/10.1016/j.paid.2020.110558}
+Lavrijsen J, Preckel F, Verachtert P, et al.
+(2021) Are motivational benefits of adequately challenging schoolwork related to students' need for cognition, cognitive ability, or both?
+\emph{Personality and Individual Differences} 171: 110558.
+DOI: \href{https://doi.org/10.1016/j.paid.2020.110558}{10.1016/j.paid.2020.110558}.
 
 \leavevmode\hypertarget{ref-Lazarus1984}{}%
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, {Appraisal}, and {Coping}}. Springer Publsihing Company.
+Lazarus RS and Folkman S (1984) \emph{Stress, {Appraisal}, and {Coping}}. 11 West 42nd Street, New York, NY 10036-8002: Springer Publsihing Company.
 
 \leavevmode\hypertarget{ref-Leiner2019}{}%
-Leiner, D. J. (2019). \emph{{SoSci} {Survey}}. \url{https://www.soscisurvey.de}
+Leiner DJ (2019) {SoSci} {Survey}. Available at: \url{https://www.soscisurvey.de}.
 
 \leavevmode\hypertarget{ref-Lepine2005}{}%
-Lepine, J.
-A., Podsakoff, N.
-P., \& Lepine, M.
-A.
-(2005).
-A meta-analytic test of the {C}hallenge {S}tressor{{}}{H}indrance {S}tressor {F}ramework: {A}n explanation for inconsistent relationships among stressors and performance.
-\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
-\url{https://doi.org/10.5465/amj.2005.18803921}
+Lepine JA, Podsakoff NP and Lepine MA (2005) A meta-analytic test of the {C}hallenge {S}tressor{{}}{H}indrance {S}tressor {F}ramework: {A}n explanation for inconsistent relationships among stressors and performance.
+\emph{Academy of Management Journal} 48(5).
+Academy of Management: 764--775.
+DOI: \href{https://doi.org/10.5465/amj.2005.18803921}{10.5465/amj.2005.18803921}.
 
 \leavevmode\hypertarget{ref-Levine2012}{}%
-Levine, L.
-J., Schmidt, S., Kang, H.
-S., \& Tinti, C.
-(2012).
-Remembering the silver lining: Reappraisal and positive bias in memory for emotion.
-\emph{Cognition {\&} Emotion}, \emph{26}(5), 871--884.
-\url{https://doi.org/10.1080/02699931.2011.625403}
+Levine LJ, Schmidt S, Kang HS, et al.
+(2012) Remembering the silver lining: Reappraisal and positive bias in memory for emotion.
+\emph{Cognition {\&} Emotion} 26(5).
+Informa {UK} Limited: 871--884.
+DOI: \href{https://doi.org/10.1080/02699931.2011.625403}{10.1080/02699931.2011.625403}.
 
 \leavevmode\hypertarget{ref-Little2002}{}%
-Little, T.
-D., Cunningham, W.
-A., Shahar, G., \& Widaman, K.
-F.
-(2002).
-To {Parcel} or {Not} to {Parcel}: {Exploring} the {Question}, {Weighing} the {Merits}.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 151--173.
-\url{https://doi.org/10.1207/S15328007SEM0902_1}
+Little TD, Cunningham WA, Shahar G, et al.
+(2002) To {Parcel} or {Not} to {Parcel}: {Exploring} the {Question}, {Weighing} the {Merits}.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal} 9(2): 151--173.
+DOI: \href{https://doi.org/10.1207/S15328007SEM0902_1}{10.1207/S15328007SEM0902\_1}.
 
 \leavevmode\hypertarget{ref-Lloyd2002}{}%
-Lloyd, C., King, R., \& Chenoweth, L. (2002). Social work, stress and burnout: A review. \emph{Journal of Mental Health}, \emph{11}(3), 255--265. \url{https://doi.org/10.1080/09638230020023642}
+Lloyd C, King R and Chenoweth L (2002) Social work, stress and burnout: A review.
+\emph{Journal of Mental Health} 11(3).
+Informa {UK} Limited: 255--265.
+DOI: \href{https://doi.org/10.1080/09638230020023642}{10.1080/09638230020023642}.
 
 \leavevmode\hypertarget{ref-Madsen2017}{}%
-Madsen, I.
-E.
-H., Nyberg, S.
-T., Hanson, L.
-L.
-M., Ferrie, J.
-E., Ahola, K., Alfredsson, L., Batty, G.
-D., Bjorner, J.
-B., Borritz, M., Burr, H., Chastang, J.-F., Graaf, R.
-de, Dragano, N., Hamer, M., Jokela, M., Knutsson, A., Koskenvuo, M., Koskinen, A., Leineweber, C., \ldots{} Kivimäki, M.
-(2017).
-Job strain as a risk factor for clinical depression: Systematic review and meta-analysis with additional individual participant data.
-\emph{Psychological Medicine}, \emph{47}(8), 1342--1356.
-\url{https://doi.org/10.1017/s003329171600355x}
+Madsen IEH, Nyberg ST, Hanson LLM, et al.
+(2017) Job strain as a risk factor for clinical depression: Systematic review and meta-analysis with additional individual participant data.
+\emph{Psychological Medicine} 47(8).
+Cambridge University Press ({CUP}): 1342--1356.
+DOI: \href{https://doi.org/10.1017/s003329171600355x}{10.1017/s003329171600355x}.
+
+\leavevmode\hypertarget{ref-Maslach2016}{}%
+Maslach C and Leiter M (2016) Burnout.
+In: \emph{Stress: Concepts, Cognition, Emotion, and Behavior}.
+Elsevier, pp.
+351--357.
+DOI: \href{https://doi.org/10.1016/b978-0-12-800951-2.00044-3}{10.1016/b978-0-12-800951-2.00044-3}.
 
 \leavevmode\hypertarget{ref-Maslach1997}{}%
-Maslach, C., Jackson, S.
-E., \& Leiter, M.
-P.
-(1997).
-Maslach {Burnout} {Inventory}: {Third} edition.
-In C.
-P.
-Zalaquett \& R.
-J.
-Wood (Eds.), \emph{Evaluating stress: A book of resources} (pp.
-191--218).
-Scarecrow Education.
-
-\leavevmode\hypertarget{ref-Maslach2016}{}%
-Maslach, C., \& Leiter, M. (2016). Burnout. In \emph{Stress: Concepts, cognition, emotion, and behavior} (pp. 351--357). Elsevier. \url{https://doi.org/10.1016/b978-0-12-800951-2.00044-3}
+Maslach C, Jackson SE and Leiter MP (1997) Maslach {Burnout} {Inventory}: {Third} edition.
+In: Zalaquett CP and Wood RJ (eds) \emph{Evaluating Stress: A Book of Resources}.
+Lanham, MD, US: Scarecrow Education, pp.
+191--218.
 
 \leavevmode\hypertarget{ref-Moe2020}{}%
-Moè, A., \& Katz, I.
-(2020).
-Emotion regulation and need satisfaction shape a motivating teaching style.
-\emph{Teachers and Teaching}, \emph{27}(5), 370--387.
-\url{https://doi.org/10.1080/13540602.2020.1777960}
+Moè A and Katz I (2020) Emotion regulation and need satisfaction shape a motivating teaching style.
+\emph{Teachers and Teaching} 27(5).
+Informa {UK} Limited: 370--387.
+DOI: \href{https://doi.org/10.1080/13540602.2020.1777960}{10.1080/13540602.2020.1777960}.
 
 \leavevmode\hypertarget{ref-Naderi2018}{}%
-Naderi, Z., Bakhtiari, S., Momennasab, M., Abootalebi, M., \& Mirzaei, T.
-(2018).
-Prediction of academic burnout and academic performance based on the need for cognition and general self-efficacy: {A} cross-sectional analytical study.
-\emph{Latinoamericana de Hipertensión}, \emph{13}(6).
-\url{http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958}
+Naderi Z, Bakhtiari S, Momennasab M, et al.
+(2018) Prediction of academic burnout and academic performance based on the need for cognition and general self-efficacy: {A} cross-sectional analytical study.
+\emph{Latinoamericana de Hipertensión} 13(6).
+Available at: \url{http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958} (accessed 22 March 2021).
 
 \leavevmode\hypertarget{ref-Nishiguchi2018}{}%
-Nishiguchi, Y., Mori, M., \& Tanno, Y.
-(2018).
-Need for {Cognition} promotes adaptive style of self-focusing with the mediation of {Effortful} {Control}.
-\emph{Japanese Psychological Research}, \emph{60}(1), 54--61.
-\url{https://doi.org/10.1111/jpr.12167}
+Nishiguchi Y, Mori M and Tanno Y (2018) Need for {Cognition} promotes adaptive style of self-focusing with the mediation of {Effortful} {Control}.
+\emph{Japanese Psychological Research} 60(1): 54--61.
+DOI: \href{https://doi.org/10.1111/jpr.12167}{10.1111/jpr.12167}.
 
 \leavevmode\hypertarget{ref-Nowlin2017}{}%
-Nowlin, E., Walker, D., Deeter-Schmelz, D.
-R., \& Haas, A.
-(2017).
-Emotion in sales performance: Affective orientation and {Need} for {Cognition} and the mediating role of motivation to work.
-\emph{Journal of Business \& Industrial Marketing}, \emph{33}(1), 107--116.
-\url{https://doi.org/10.1108/JBIM-06-2016-0136}
+Nowlin E, Walker D, Deeter-Schmelz DR, et al.
+(2017) Emotion in sales performance: Affective orientation and {Need} for {Cognition} and the mediating role of motivation to work.
+\emph{Journal of Business \& Industrial Marketing} 33(1): 107--116.
+DOI: \href{https://doi.org/10.1108/JBIM-06-2016-0136}{10.1108/JBIM-06-2016-0136}.
 
 \leavevmode\hypertarget{ref-Nunnally1994}{}%
-Nunnally, J., \& Bernstein, I. (1994). \emph{Psychometric {Theory}}. McGraw-Hill Companies,Incorporated.
+Nunnally J and Bernstein I (1994) \emph{Psychometric {Theory}}. McGraw-Hill Companies,Incorporated.
 
 \leavevmode\hypertarget{ref-Oliva2019}{}%
-Oliva, A., Antolín-Suárez, L., \& Rodríguez-Meirinhos, A.
-(2019).
-Uncovering the link between self-control, age, and psychological maladjustment among {Spanish} adolescents and young adults.
-\emph{Psychosocial Intervention}, \emph{28}(1), 49--55.
-\url{https://doi.org/10.5093/pi2019a1}
+Oliva A, Antolín-Suárez L and Rodríguez-Meirinhos A (2019) Uncovering the link between self-control, age, and psychological maladjustment among {Spanish} adolescents and young adults.
+\emph{Psychosocial Intervention} 28(1).
+Colegio Oficial de Psicologos de Madrid: 49--55.
+DOI: \href{https://doi.org/10.5093/pi2019a1}{10.5093/pi2019a1}.
 
 \leavevmode\hypertarget{ref-Osberg1987}{}%
-Osberg, T.
-M.
-(1987).
-The convergent and discriminant validity of the {Need} for {Cognition} {Scale}.
-\emph{Journal of Personality Assessment}, \emph{51}(3), 441--450.
-\url{https://doi.org/10.1207/s15327752jpa5103_11}
+Osberg TM (1987) The convergent and discriminant validity of the {Need} for {Cognition} {Scale}.
+\emph{Journal of Personality Assessment} 51(3): 441--450.
+DOI: \href{https://doi.org/10.1207/s15327752jpa5103_11}{10.1207/s15327752jpa5103\_11}.
 
 \leavevmode\hypertarget{ref-Podsakoff2007}{}%
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential {Challenge Stressor-Hindrance Stressor} relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438--454.
-\url{https://doi.org/10.1037/0021-9010.92.2.438}
+Podsakoff NP, LePine JA and LePine MA (2007) Differential {Challenge Stressor-Hindrance Stressor} relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology} 92(2).
+American Psychological Association ({APA}): 438--454.
+DOI: \href{https://doi.org/10.1037/0021-9010.92.2.438}{10.1037/0021-9010.92.2.438}.
 
 \leavevmode\hypertarget{ref-Preece2019}{}%
-Preece, D.
-A., Becerra, R., Robinson, K., \& Gross, J.
-J.
-(2019).
-{The Emotion Regulation Questionnaire: Psychometric} properties in general community samples.
-\emph{Journal of Personality Assessment}, \emph{102}(3), 348--356.
-\url{https://doi.org/10.1080/00223891.2018.1564319}
+Preece DA, Becerra R, Robinson K, et al.
+(2019) {The Emotion Regulation Questionnaire: Psychometric} properties in general community samples.
+\emph{Journal of Personality Assessment} 102(3).
+Informa {UK} Limited: 348--356.
+DOI: \href{https://doi.org/10.1080/00223891.2018.1564319}{10.1080/00223891.2018.1564319}.
 
 \leavevmode\hypertarget{ref-Przepiorka2019}{}%
-Przepiórka, A., Błachnio, A., \& Siu, N.
-Y.-F.
-(2019).
-The relationships between self-efficacy, self-control, chronotype, procrastination and sleep problems in young adults.
-\emph{Chronobiology International}, \emph{36}(8), 1025--1035.
-\url{https://doi.org/10.1080/07420528.2019.1607370}
+Przepiórka A, Błachnio A and Siu NY-F (2019) The relationships between self-efficacy, self-control, chronotype, procrastination and sleep problems in young adults.
+\emph{Chronobiology International} 36(8).
+Informa {UK} Limited: 1025--1035.
+DOI: \href{https://doi.org/10.1080/07420528.2019.1607370}{10.1080/07420528.2019.1607370}.
 
 \leavevmode\hypertarget{ref-RCT2020}{}%
-R Core Team. (2020). \emph{R: {A} language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+R Core Team (2020) \emph{R: {A} Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. Available at: \url{https://www.R-project.org/}.
 
 \leavevmode\hypertarget{ref-Reijseger2013}{}%
-Reijseger, G., Schaufeli, W.
-B., Peeters, M.
-C.
-W., Taris, T.
-W., Beek, I.
-van, \& Ouweneel, E.
-(2013).
-Watching the paint dry at work: Psychometric examination of the {Dutch} {Boredom} {Scale}.
-\emph{Anxiety, Stress, \& Coping}, \emph{26}(5), 508--525.
-\url{https://doi.org/10.1080/10615806.2012.720676}
+Reijseger G, Schaufeli WB, Peeters MCW, et al.
+(2013) Watching the paint dry at work: Psychometric examination of the {Dutch} {Boredom} {Scale}.
+\emph{Anxiety, Stress, \& Coping} 26(5): 508--525.
+DOI: \href{https://doi.org/10.1080/10615806.2012.720676}{10.1080/10615806.2012.720676}.
 
 \leavevmode\hypertarget{ref-Revelle2021}{}%
-Revelle, W. (2021). \emph{Psych: {P}rocedures for psychological, psychometric, and personality research}. Northwestern University. \url{https://CRAN.R-project.org/package=psych}
+Revelle W (2021) \emph{Psych: {P}rocedures for Psychological, Psychometric, and Personality Research}.
+Evanston, Illinois: Northwestern University.
+Available at: \url{https://CRAN.R-project.org/package=psych}.
 
 \leavevmode\hypertarget{ref-Rosen2020}{}%
-Rosen, C.
-C., Gabriel, A.
-S., Lee, H.
-W., Koopman, J., \& Johnson, R.
-E.
-(2020).
-When lending an ear turns into mistreatment: {An} episodic examination of leader mistreatment in response to venting at work.
-\emph{Personnel Psychology}, 1--21.
-\url{https://doi.org/10.1111/peps.12418}
+Rosen CC, Gabriel AS, Lee HW, et al.
+(2020) When lending an ear turns into mistreatment: {An} episodic examination of leader mistreatment in response to venting at work.
+\emph{Personnel Psychology}: 1--21.
+DOI: \href{https://doi.org/10.1111/peps.12418}{10.1111/peps.12418}.
 
 \leavevmode\hypertarget{ref-Rosseel2012}{}%
-Rosseel, Y. (2012). {lavaan}: {A}n {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. \url{https://www.jstatsoft.org/v48/i02/}
+Rosseel Y (2012) {lavaan}: {A}n {R} package for structural equation modeling. \emph{Journal of Statistical Software} 48(2): 1--36. Available at: \url{https://www.jstatsoft.org/v48/i02/}.
 
 \leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-RStudio Team. (2020). \emph{{RStudio}: {Integrated} development for {R}}. RStudio, PBC. \url{http://www.rstudio.com}
+RStudio Team (2020) {RStudio}: {Integrated} development for {R}. Boston, MA: RStudio, PBC. Available at: \url{http://www.rstudio.com}.
 
 \leavevmode\hypertarget{ref-Salanova2006}{}%
-Salanova, M., Bakker, A.
-B., \& Llorens, S.
-(2006).
-Flow at {Work}: {Evidence} for an {Upward} {Spiral} of {Personal} and {Organizational} {Resources}*.
-\emph{Journal of Happiness Studies}, \emph{7}(1), 1--22.
-\url{https://doi.org/10.1007/s10902-005-8854-8}
+Salanova M, Bakker AB and Llorens S (2006) Flow at {Work}: {Evidence} for an {Upward} {Spiral} of {Personal} and {Organizational} {Resources}*.
+\emph{Journal of Happiness Studies} 7(1): 1--22.
+DOI: \href{https://doi.org/10.1007/s10902-005-8854-8}{10.1007/s10902-005-8854-8}.
+
+\leavevmode\hypertarget{ref-Schaufeli2014}{}%
+Schaufeli W and Salanova M (2014) Burnout, boredom and engagement at the workplace.
+In: Peeters M, Jonge J de, and Taris T (eds) \emph{People at Work: {An} {Introduction} to {Contemporary} {Work} {Psychology}}.
+Wiley Blackwell; Chichester, pp.
+293--320.
+Available at: \url{https://lirias.kuleuven.be/retrieve/307889} (accessed 25 June 2021).
 
 \leavevmode\hypertarget{ref-Schaufeli2001}{}%
-Schaufeli, W., Bakker, A.
-B., Hoogduin, K., Schaap, C., \& Kladler, A.
-(2001).
-On the clinical validity of the {Maslach} {Burnout} {Inventory} and the burnout measure.
-\emph{Psychology \& Health}, \emph{16}(5), 565--582.
-\url{https://doi.org/10.1080/08870440108405527}
-
-\leavevmode\hypertarget{ref-Schaufeli2014}{}%
-Schaufeli, W., \& Salanova, M.
-(2014).
-Burnout, boredom and engagement at the workplace.
-In M.
-Peeters, J.
-de Jonge, \& T.
-Taris (Eds.), \emph{People at work: {An} {Introduction} to {Contemporary} {Work} {Psychology}} (pp.
-293--320).
-Wiley Blackwell; Chichester.
-\url{https://lirias.kuleuven.be/retrieve/307889}
+Schaufeli W, Bakker AB, Hoogduin K, et al.
+(2001) On the clinical validity of the {Maslach} {Burnout} {Inventory} and the burnout measure.
+\emph{Psychology \& Health} 16(5).
+Routledge: 565--582.
+DOI: \href{https://doi.org/10.1080/08870440108405527}{10.1080/08870440108405527}.
 
 \leavevmode\hypertarget{ref-Schmidt2010}{}%
-Schmidt, S., Tinti, C., Levine, L.
-J., \& Testa, S.
-(2010).
-Appraisals, emotions and emotion regulation: An integrative approach.
-\emph{Motivation and Emotion}, \emph{34}(1), 63--72.
-\url{https://doi.org/10.1007/s11031-010-9155-z}
+Schmidt S, Tinti C, Levine LJ, et al.
+(2010) Appraisals, emotions and emotion regulation: An integrative approach.
+\emph{Motivation and Emotion} 34(1).
+Springer Science; Business Media {LLC}: 63--72.
+DOI: \href{https://doi.org/10.1007/s11031-010-9155-z}{10.1007/s11031-010-9155-z}.
 
 \leavevmode\hypertarget{ref-Schumacker2012}{}%
-Schumacker, R. E., \& Lomax, R. G. (2012). \emph{A {Beginner}'s {Guide} to {Structural} {Equation} {Modeling}: {Third} {Edition}}. Routledge.
+Schumacker RE and Lomax RG (2012) \emph{A {Beginner}'s {Guide} to {Structural} {Equation} {Modeling}: {Third} {Edition}}. Routledge.
 
 \leavevmode\hypertarget{ref-Simmons2012}{}%
-Simmons, J.
-P., Nelson, L.
-D., \& Simonsohn, U.
-(2012).
-\emph{A 21 word solution} (\{SSRN\} \{Scholarly\} \{Paper\} ID 2160588).
-Social Science Research Network.
-\url{https://doi.org/10.2139/ssrn.2160588}
+Simmons JP, Nelson LD and Simonsohn U (2012) \emph{A 21 word solution}.
+ID 2160588, \{SSRN\} \{Scholarly\} \{Paper\}, October.
+Rochester, NY: Social Science Research Network.
+DOI: \href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.
 
 \leavevmode\hypertarget{ref-Steptoe2013}{}%
-Steptoe, A., \& Kivimäki, M.
-(2013).
-Stress and cardiovascular disease: An update on current knowledge.
-\emph{Annual Review of Public Health}, \emph{34}(1), 337--354.
-\url{https://doi.org/10.1146/annurev-publhealth-031912-114452}
+Steptoe A and Kivimäki M (2013) Stress and cardiovascular disease: An update on current knowledge.
+\emph{Annual Review of Public Health} 34(1).
+Annual Reviews: 337--354.
+DOI: \href{https://doi.org/10.1146/annurev-publhealth-031912-114452}{10.1146/annurev-publhealth-031912-114452}.
 
 \leavevmode\hypertarget{ref-Strobel2017}{}%
-Strobel, A., Anacker, K., \& Strobel, A.
-(2017).
-Cognitive engagement mediates the relationship between positive life events and positive emotionality.
-\emph{Frontiers in Psychology}, \emph{8}.
-\url{https://doi.org/10.3389/fpsyg.2017.01861}
+Strobel A, Anacker K and Strobel A (2017) Cognitive engagement mediates the relationship between positive life events and positive emotionality.
+\emph{Frontiers in Psychology} 8.
+DOI: \href{https://doi.org/10.3389/fpsyg.2017.01861}{10.3389/fpsyg.2017.01861}.
 
 \leavevmode\hypertarget{ref-Stumm2013}{}%
-Stumm, S. von, \& Ackerman, P. L. (2013). Investment and intellect: A review and meta-analysis. \emph{Psychological Bulletin}, \emph{139}(4), 841--869. \url{https://doi.org/10.1037/a0030746}
+Stumm S von and Ackerman PL (2013) Investment and intellect: A review and meta-analysis.
+\emph{Psychological Bulletin} 139(4).
+American Psychological Association ({APA}): 841--869.
+DOI: \href{https://doi.org/10.1037/a0030746}{10.1037/a0030746}.
 
 \leavevmode\hypertarget{ref-Taber2018}{}%
-Taber, K.
-S.
-(2018).
-The use of {Cronbach}'s {Alpha} when developing and reporting research instruments in science education.
-\emph{Research in Science Education}, \emph{48}(6), 1273--1296.
-\url{https://doi.org/10.1007/s11165-016-9602-2}
+Taber KS (2018) The use of {Cronbach}'s {Alpha} when developing and reporting research instruments in science education.
+\emph{Research in Science Education} 48(6): 1273--1296.
+DOI: \href{https://doi.org/10.1007/s11165-016-9602-2}{10.1007/s11165-016-9602-2}.
 
 \leavevmode\hypertarget{ref-Tolentino1990}{}%
-Tolentino, E., Curry, L., \& Leak, G.
-(1990).
-Further validation of the short form of the {Need} for {Cognition} {Scale}.
-\emph{Psychological Reports}, \emph{66}(1), 321--322.
-\url{https://doi.org/10.2466/pr0.1990.66.1.321}
+Tolentino E, Curry L and Leak G (1990) Further validation of the short form of the {Need} for {Cognition} {Scale}.
+\emph{Psychological Reports} 66(1).
+SAGE Publications Inc: 321--322.
+DOI: \href{https://doi.org/10.2466/pr0.1990.66.1.321}{10.2466/pr0.1990.66.1.321}.
 
 \leavevmode\hypertarget{ref-Tsouloupas2010}{}%
-Tsouloupas, C.
-N., Carson, R.
-L., Matthews, R., Grawitch, M.
-J., \& Barber, L.
-K.
-(2010).
-Exploring the association between teachers' perceived student misbehaviour and emotional exhaustion: The importance of teacher efficacy beliefs and emotion regulation.
-\emph{Educational Psychology}, \emph{30}(2), 173--189.
-\url{https://doi.org/10.1080/01443410903494460}
+Tsouloupas CN, Carson RL, Matthews R, et al.
+(2010) Exploring the association between teachers' perceived student misbehaviour and emotional exhaustion: The importance of teacher efficacy beliefs and emotion regulation.
+\emph{Educational Psychology} 30(2).
+Informa {UK} Limited: 173--189.
+DOI: \href{https://doi.org/10.1080/01443410903494460}{10.1080/01443410903494460}.
 
 \leavevmode\hypertarget{ref-ValdiviaVazquez2021}{}%
-Valdivia Vázquez, J.
-A., Hernández Castillo, G.
-D., \& Maiz García, S.
-I.
-(2021).
-Burnout in {Police} {Officers} from {Northern} {Mexico}: {A} validity study of the {Maslach} {Burnout} {Inventory}.
+Valdivia Vázquez JA, Hernández Castillo GD and Maiz García SI (2021) Burnout in {Police} {Officers} from {Northern} {Mexico}: {A} validity study of the {Maslach} {Burnout} {Inventory}.
 \emph{Journal of Police and Criminal Psychology}.
-\url{https://doi.org/10.1007/s11896-021-09452-z}
+DOI: \href{https://doi.org/10.1007/s11896-021-09452-z}{10.1007/s11896-021-09452-z}.
 
 \leavevmode\hypertarget{ref-Vannucci2018}{}%
-Vannucci, M., \& Chiorri, C.
-(2018).
-Individual differences in self-consciousness and mind wandering: {Further} evidence for a dissociation between spontaneous and deliberate mind wandering.
-\emph{Personality and Individual Differences}, \emph{121}, 57--61.
-\url{https://doi.org/10.1016/j.paid.2017.09.022}
+Vannucci M and Chiorri C (2018) Individual differences in self-consciousness and mind wandering: {Further} evidence for a dissociation between spontaneous and deliberate mind wandering.
+\emph{Personality and Individual Differences} 121: 57--61.
+DOI: \href{https://doi.org/10.1016/j.paid.2017.09.022}{10.1016/j.paid.2017.09.022}.
 
 \leavevmode\hypertarget{ref-Ventura2015}{}%
-Ventura, M., Salanova, M., \& Llorens, S.
-(2015).
-Professional {Self}-{Efficacy} as a {Predictor} of {Burnout} and {Engagement}: {The} {Role} of {Challenge} and {Hindrance} {Demands}.
-\emph{The Journal of Psychology}, \emph{149}(3), 277--302.
-\url{https://doi.org/10.1080/00223980.2013.876380}
+Ventura M, Salanova M and Llorens S (2015) Professional {Self}-{Efficacy} as a {Predictor} of {Burnout} and {Engagement}: {The} {Role} of {Challenge} and {Hindrance} {Demands}.
+\emph{The Journal of Psychology} 149(3): 277--302.
+DOI: \href{https://doi.org/10.1080/00223980.2013.876380}{10.1080/00223980.2013.876380}.
 
 \leavevmode\hypertarget{ref-Vera2004}{}%
-Vera, E.
-M., Shin, R.
-Q., Montgomery, G.
-P., Mildner, C., \& Speight, S.
-L.
-(2004).
-Conflict resolution styles, self-efficacy, self-control, and future orientation of urban adolescents.
-\emph{Professional School Counseling}, \emph{8}(1), 73--80.
+Vera EM, Shin RQ, Montgomery GP, et al. (2004) Conflict resolution styles, self-efficacy, self-control, and future orientation of urban adolescents. \emph{Professional School Counseling} 8(1): 73--80.
 
 \leavevmode\hypertarget{ref-Vera2012}{}%
-Vera, M., Salanova, M., \& Lorente, L.
-(2012).
-The predicting role of self-efficacyin the {Job} {Demands}-{Resources} {Model}: {A} longitudinal study.
-\emph{Studies in Psychology}, \emph{33}(2), 167--178.
-\url{https://doi.org/10.1174/021093912800676439}
+Vera M, Salanova M and Lorente L (2012) The predicting role of self-efficacyin the {Job} {Demands}-{Resources} {Model}: {A} longitudinal study.
+\emph{Studies in Psychology} 33(2): 167--178.
+DOI: \href{https://doi.org/10.1174/021093912800676439}{10.1174/021093912800676439}.
 
 \leavevmode\hypertarget{ref-Wiesner2005}{}%
-Wiesner, M., Windle, M., \& Freeman, A.
-(2005).
-Work stress, substance use, and depression among young adult workers: An examination of main and moderator effect model.
-\emph{Journal of Occupational Health Psychology}, \emph{10}(2), 83--96.
-\url{https://doi.org/10.1037/1076-8998.10.2.83}
+Wiesner M, Windle M and Freeman A (2005) Work stress, substance use, and depression among young adult workers: An examination of main and moderator effect model.
+\emph{Journal of Occupational Health Psychology} 10(2).
+American Psychological Association ({APA}): 83--96.
+DOI: \href{https://doi.org/10.1037/1076-8998.10.2.83}{10.1037/1076-8998.10.2.83}.
 
 \leavevmode\hypertarget{ref-Xu2021}{}%
-Xu, P., \& Cheng, J.
-(2021).
-Individual differences in social distancing and mask-wearing in the pandemic of {COVID}-19: {The} role of need for cognition, self-control and risk attitude.
-\emph{Personality and Individual Differences}, \emph{175}, 110706.
-\url{https://doi.org/10.1016/j.paid.2021.110706}
+Xu P and Cheng J (2021) Individual differences in social distancing and mask-wearing in the pandemic of {COVID}-19: {The} role of need for cognition, self-control and risk attitude.
+\emph{Personality and Individual Differences} 175: 110706.
+DOI: \href{https://doi.org/10.1016/j.paid.2021.110706}{10.1016/j.paid.2021.110706}.
 
 \leavevmode\hypertarget{ref-Yang2019}{}%
-Yang, C., Zhou, Y., Cao, Q., Xia, M., \& An, J.
-(2019).
-The relationship between self-control and self-efficacy among patients with substance use sisorders: {R}esilience and self-esteem as mediators.
-\emph{Frontiers in Psychiatry}, \emph{10}.
-\url{https://doi.org/10.3389/fpsyt.2019.00388}
+Yang C, Zhou Y, Cao Q, et al.
+(2019) The relationship between self-control and self-efficacy among patients with substance use sisorders: {R}esilience and self-esteem as mediators.
+\emph{Frontiers in Psychiatry} 10.
+Frontiers Media {SA}.
+DOI: \href{https://doi.org/10.3389/fpsyt.2019.00388}{10.3389/fpsyt.2019.00388}.
 
 \leavevmode\hypertarget{ref-Zerna2021}{}%
-Zerna, J., Strobel, A., \& Strobel, A.
-(2021).
-\emph{The role of {Need} for {Cognition} in wellbeing -- {A} review of associations and potential underlying mechanisms}.
-\url{https://doi.org/10.31234/osf.io/p6gwh}
+Zerna J, Strobel A and Strobel A (2021) The role of {Need} for {Cognition} in wellbeing -- {A} review of associations and potential underlying mechanisms.
+PsyArXiv.
+DOI: \href{https://doi.org/10.31234/osf.io/p6gwh}{10.31234/osf.io/p6gwh}.
 
 \leavevmode\hypertarget{ref-Zheng2020}{}%
-Zheng, A., Briley, D., Jacobucci, R., Harden, K.
-P., \& Tucker-Drob, E.
-(2020).
-\emph{Incremental {Validity} of {Character} {Measures} {Over} the {Big} {Five} and {Fluid} intelligence in {Predicting} {Academic} {Achievement}}.
-\url{https://doi.org/10.31234/osf.io/652qz}
+Zheng A, Briley D, Jacobucci R, et al.
+(2020) Incremental {Validity} of {Character} {Measures} {Over} the {Big} {Five} and {Fluid} intelligence in {Predicting} {Academic} {Achievement}.
+PsyArXiv.
+DOI: \href{https://doi.org/10.31234/osf.io/652qz}{10.31234/osf.io/652qz}.
 

### 2022-03-25 Manuscript/Manuscript.Rmd
shortened abstract to 150 words

@@
 abstract: |
-  The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
-  While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
+  Burnout has become more prevalent, mainly in social jobs, but little is known about the personality traits that promote or protect against burnout.
   One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
-  In the present study, we analyzed questionnaire data of N = 180 teachers that had been collected in spring of 2020.
-  Firstly, we aimed to replicate results by Grass et al.
-(2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
-  With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
-  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
-  The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to their demands.
+  We analyzed data of N = 180 teachers to replicate results by Grass et al.
+(2018), who reported a mediation of NFC and the burnout subscale reduced personal efficacy by habitual reappraisal, but not by habitual suppression or self-control.
+  With our data, self-control became a significant mediator when taking teaching experience into account, but neither reappraisal nor suppression did.
+  We also investigated whether NFC and burnout were associated via different ratios of demands and resources, and included other variables in an exploratory approach.
+  The results indicated that teachers with higher NFC and self-control have lower burnout because they experience their resources as fitting to the demands.
 

### 2022-03-25 Manuscript/Manuscript.Rmd
submission stage

@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no

### 2022-07-20 Manuscript/Manuscript.Rmd
corrected typo modincides -> modindices

@@
 We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
-Then we modified the structure of the model using the *modincides()*-function in *lavaan* in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
+Then we modified the structure of the model using the *modindices()*-function in *lavaan* in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
 The final model is illustrated in Figure 3, the total, direct, and indirect effects are listed in *Supplementary Material S5*.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Added Revision Letter

---
title       : "NFC and burnout in teachers - A replication and extension study"
authors     : "Josephine Zerna, Nicole ENgelmann, Anja Strobel & Alexander Strobel"
journal     : "Health Psychology Open"
manuscript  : "HPO-22-0057"

class       : "draft"
output      : papaja::revision_letter_pdf
---

Dear Dr. McParland,

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
In the following we address your and each reviewers' concerns point-by-point.

# Reviewer \#1

\RC{Difference between the samples of Grass et al. (2018) and this study

- The authors should clearly mark the difference between their teacher sample and Grass et al.’s (2018) student teacher sample.
This includes designating Grass et al.’s sample as “student teachers” (on p.3 and p.20), not “teacher trainees”. This is more precise (the latter could easily be confounded with 2nd teacher education phase, called “Referendariat”) and corresponds to Grass et al.’s own use. Additionally, “replication/replicated” should be qualified as “replication/replicated in a teacher sample” throughout the manuscript. This would also mark the novelty of this paper.

- Furthermore, the authors should consider and discuss implications of the different professional situations of the two samples.
This includes considering question like “Are there difference in how personal efficacy is perceived among students compared with in-service teachers?”, “What are the implications for burnout, need for cognition and other key concepts/variables with reference to the difference between academic learning and working in a school?” Literature dealing with these questions should be included.
}

This is our response

\Assignment{First Author}
\WorkInProgress
\Easy

\RC{Focus on the burnout characteristic reduced personal efficacy (RPE), cf. Table 3

I don’t see the point of focusing only on the significant correlations and mediations from Grass et al. (2018). Non-significant results are also findings. In Grass et al. (2018), they analyzed the other two characteristics emotional exhaustion and depersonalization, too. There, they focused on RPE in further mediation analysis apparently because it was more strongly related to NFC and Self-control. Obviously, correlations and mediations are different in this study (which might be due to investigating a different population). This justifies analyses of all assessed variables. Therefore, analyses of associations of the two other burnout characteristics (emotional exhaustion and depersonalization) should be included.

Furthermore, RPE can not the most important burnout characteristic. On the contrary, it frequently has the lowest correlation with burnout (MBI score) among the three subscales. Additionally, it is the subscale that receives less attention in research on teachers’ health, in the sense that if only certain burnout subscales are investigated, then those are usually emotional exhaustion and depersonalization (e.g.,

- Bermejo-Toro, L., Prieto-Ursúa, M., \& Hernández, V. (2016). Towards a model of teacher well-being: Personal and job resources involved in teacher burnout and engagement. *Educational Psychology, 36*(3), 481–501. https://doi.org/10.1080/01443410.2015.1005006
- Dicke, T., Parker, P. D., Marsh, H. W., Kunter, M., Schmeck, A., \& Leutner, D. (2014). Self-efficacy in classroom management, classroom disturbances, and emotional exhaustion: A moderated mediation analysis of teacher candidates. *Journal of Educational Psychology, 106(2)*, 569–583. https://doi.org/10.1037/a0035504)

This means that further analyses of the two other subscales would increase relevance of this paper in the scientific field.

When using the term “burnout”, the manuscript should carefully distinguish between burnout characteristic RPE and burnout as the commonly used concept including EE and DP. Mostly, this is accomplished successfully, but not in the discussion (p.19: “we replicated findings of mediators between Need for Cognition and burnout” when only mediations between NFC and RPE were investigated), and conclusion (first two sentences p.25), for example.
}

This is our response.

> This is a section quoted from the revised manuscript to illustrate the change.

\Assignment{Second Author}
\AlmostDone
\Medium

\RC
This is a reviewer comment

This is our response

\Assignment{First Author}
\Done
\TimeConsuming
\Hard
\NotEstimated

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@
 title       : "NFC and burnout in teachers - A replication and extension study"
-authors     : "Josephine Zerna, Nicole ENgelmann, Anja Strobel & Alexander Strobel"
+authors     : "Josephine Zerna, Nicole Engelmann, Anja Strobel & Alexander Strobel"
 journal     : "Health Psychology Open"
@@
 thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
+We would like to thank the reviewers for their efforts to thoughly assess our manuscript.
 In the following we address your and each reviewers' concerns point-by-point.
+We hope that we could adequately address all the issues raised.
 
@@
 
-\Assignment{Second Author}
+\Assignment{Which Author?}
 \AlmostDone
@@
 
-\RC
-This is a reviewer comment
+\RC{Abstract: “little is known about the personality traits that promote or protect against burnout”
+
+- This phrase is unfortunate.
+The readers might doubt whether the authors are aware of, for example, the more than a thousand times cited meta-analyses that exist on this topic and the literature they themselves cite later that elucidates this issue.
+If promoting and protecting in the narrowed sense of having shown predictive validity in longitudinal studies is meant, then, the presented study does not add insights because it is cross-sectional.
+Please clarify what was meant.}
 
@@
 \Assignment{First Author}
-\Done
+\WorkInProgress
 \TimeConsuming
@@
 
+\RC{p.17 typo: the lavaan function should be spelled modindices(), not modincides()}
+
+Thank you for noticing this typo. We have corrected it.
+
+\Assignment{Last Author}
+\Done
+
+\RC{p.19/23 somewhere it should be conceded that the positive relation Covid burden and years of experience is influenced or confounded by item number 2 of the Covid burden questionnaire (“Are you in a Covid-19 risk group?”).
+Persons that do not belong to the risk group of old people (50+) can by default not have the highest years of experience.
+}
+
+This is our response.
+
+\RC{p.21 “The mediator that did not reach significance was the perception of own resources exceeding the job demands.
+As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al.
+(2013.)”
+
+- The authors might want to deepen the discussion with the possible explanation that boredom is less prevalent in the teaching profession (including a suitable reference) than in professions where you can “watch the paint dry” as Reijseger et al.
+describe.
+For some readers it might be counterintuitive that teachers experience boredom in the form of resources exceeding demands at all.
+Teaching appears to be an activity that could always address more individual needs and a class of app.
+20 students seems to always have the potential to keep their teachers busy.}
+
+This is our response.
+
+\RC{supplementary material S2
+
+For me, the numbering of supplementary material headings, table and figure numbers was confusing.
+I would find a system that links supplemental topic and table/figure numbering with each other much more intuitive and easier to navigate, e.g., heading S2, table S2a, table S2b,… or heading S2, table S2.1, table S2.2,….}
+
+This is our response.
+
+\Assignment{First or Last Author}
+\WorkInProgress
+
+# Reviewer \#2
+
+\RC{Thank you so much for providing me with an opportunity to review this manuscript. I enjoyed reading it.
+In brief, this study replicates the findings of mediation between NFC and burnout, investigates the effect of different demand resource ratios on the relationship between NFC and burnout, and explores the impact of other variables such as perceived burden by the pandemic.
+
+The introduction is well-written and follows a logical order in explaining the literature and the gap to explore the other variables mediating the relationship between NFC and burnout.
+The method seems to be clear and concise enough to explain the sample, procedure, and data analysis strategies.
+However, I was wondering if the authors have checked the reliability of the last scale used to assess the Covid-19 pandemic burden.
+
+The results have also been presented in detail and clearly according to the appropriate methods of analysis and have been properly discussed.
+
+The only weak point of the study is the use of self-reports, which limits taking causal conclusions.
+However, this point along with others has been presented in the limitation of the study and nothing can be done now.
+Overall, I found the study interesting with significant results to share and enjoy good quality. Therefore, I suggest acceptance.}
+
+We like to thank the reviewer very much for this positive assessment of our manuscript.
+In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p.XX.
+
+\Assignment{JZ}
+
+# Reviewer \#3
+
+\RC{Page 1.
+
+The abstract needs to be rewritten as it does not clearly present the variables of interest and their relations  (“we analysed…” fails to delineate the outcome variabel, predictor, mediator).
+Also the Grass et al.
+study should be fully references in the abstract.}
+
+This is our response.
+
+\RC{Page 2.
+
+- “small to large” implies that the effect sizes vary. 
+- “always in conflict” often?}
+
+This is our response.
+
+\RC{Page 3. 
+How is NFC related to other constructs like neuroticism, self-esteem, and locus of control? And would NFC provide incremental validity in predicting burnout?
+“adults” in which context?
+
+please provide more information on the Grass et al. study in terms of sample, context, and sample size. Why was this study the focus of a replication?
+}
+
+This is our response.
+
+\RC{Page 4
+
+how are demands too high, demands too low, and demand-resources fit related to each other?}
+
+This is our response.
+
+\RC{Page 5.
+
+Are data also shared openly for further research?
+
+Note that I couldn’t assess the preregistration, but that the OSF offers a way to anonymise preregistrations for peer review.}
+
+This is our response.
+
+\RC{Page 6.
+
+Which nominal Alpha level is used? .01 or .05? Please explicate all deviations from the preregistration.}
+
+This is our response.
+
+\RC{Page 7.
+
+Note that reliabilities are not characteristic of scales as they are also a function of variation of true scores in the samples.}
+
+This is our response.
+
+\RC{Page 8.
+
+Why did the authors choose (preregister?) to use parcels instead of the five and seven-point items scores as input in the SEMs?
+The mean and variance corrected WLS estimator in Lavaan should be able to handle the raw item data well as long as the model is not too large.
+
+How were bootstrapped fit measures computed?}
+
+This is our response.
+
+\RC{Page 9.
+
+How are the three demand factors related to each other? shouldn’t they be allowed to covary in the SEMs? why do the authors assume that NFC completely accounts for their covariation?}
+
+This is our response.
+
+\RC{Page 10.
+
+Unfortunately, the appendix does not present fit measures of the model without the outlier.}
+
+This is our response.
+
+\RC{Page 13.
+
+How is the RSMEA computed? My computation with RMSEA=SQRT((chisq-df)/(df(n-1)))  gives a value around .14 instead of .000}
+
+\RC{Pages 15-16.
+
+please provide the DF of the model alongside the Chi-square.
+The model doesn’t fit very well and it is not clear that non-normality accounts for this as the authors are using robust chi-square.
+Please consider potential model revisions of the model in figure 2 using modification indices and clearly report these as an exploratory analysis.
+My expectation is that much of the misfit is created by additional covariances between the DTH, DTL, and DRF factors.}
+
+This is our response.
+
+\RC{Page 18.
+
+Here the authors do present another exploratory model that did consider ad hoc revisions using the modification indices, but they also added additional variables to the model instead of choosing to revise the original model in Figure 2.
+Actually, in the new model the authors changed the entire outcome variable from burnout to a study of EE and RPE (but without DP).
+For this reason, the text and study loose much of their focus: wouldn’t it be better to focus on an overarching model that incorporates all relevant prior expectation and/or compares different (nested) models to pit ideas against each other?}
+
+This is our response.
+
+\RC{Pages 20-24.
+
+In their discussion, the  authors also focus on different aspects, namely the replication of Grass et al, the demand-resource ratio model, and the exploratory analyses with personal efficacy and covid burden.
+A more general framework would probably work much better in interpreting the results and relating them to the wider literature.}
+
+This is our response.
 \newpage

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 abstract: |
-  Burnout has become more prevalent, mainly in social jobs, but little is known about the personality traits that promote or protect against burnout.
+  Burnout has become more prevalent, mainly in social jobs.
+While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.
   One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@
 
-This is our response
+This is our response.
 
-\Assignment{First Author}
+\Assignment{JZ}
 \WorkInProgress
@@
 
-\Assignment{Which Author?}
+\Assignment{JZ}
 \AlmostDone
@@
 
-This is our response
+We acknowledge that this sentence was unfortunate. We changed it accordingly and now write in the abstract:
 
-\Assignment{First Author}
-\WorkInProgress
-\TimeConsuming
-\Hard
-\NotEstimated
+> While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.
+
+\Assignment{AS}
+\Done
 
@@
 
-\RC{p.21 “The mediator that did not reach significance was the perception of own resources exceeding the job demands.
+\Assignment{JZ}
+\WorkInProgress
+\Easy
+
+\RC{p.
+21 “The mediator that did not reach significance was the perception of own resources exceeding the job demands.
 As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al.
@@
 
+\Assignment{JZ}
+\WorkInProgress
+\Easy
+
 \RC{supplementary material S2
@@
 
-\Assignment{First or Last Author}
+\Assignment{JZ}
 \WorkInProgress
+\Easy
 
@@
 We like to thank the reviewer very much for this positive assessment of our manuscript.
-In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p.XX.
+In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p.
+XX.
 

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
   One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
-  We analyzed data of N = 180 teachers to replicate results by Grass et al.
-(2018), who reported a mediation of NFC and the burnout subscale reduced personal efficacy by habitual reappraisal, but not by habitual suppression or self-control.
+  We analyzed data of $N=180$ teachers to replicate previous results on a mediation of NFC and the burnout subscale reduced personal efficacy by habitual reappraisal, but not by habitual suppression or self-control.
   With our data, self-control became a significant mediator when taking teaching experience into account, but neither reappraisal nor suppression did.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@
 
+\RC{...
+the goals of the study and the theoretical framework it uses switch multiple times as the manuscript progresses.
+Notably, the different models presented on the same dataset are clearly different (in terms of structure, predictors, and outcome variables) and are not clearly related to each other.
+So the theoretical focus needs to be improved to increase readability and clarity.
+Specifically, the different models need to be related to other in a theoretical and empirical manner.
+Also, the main model in figure 2 did not fit well possibly because it assumed conditional independence between three main DTH, DTL, and DRF factors that are expected to covary even after controlling for NFC.}
+
+This is our response.
+
+\Assignment{JZ}
+\WorkInProgress
+\TimeConsuming
+
 \RC{Page 1.
@@
 
-This is our response.
+[address frist sentence] We deleted the reference to Grass et al. because referencing it fully would have exceeded the word limit for the abstract.
 

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
-To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.
+To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
 

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision_Letter.Rmd
Update Revision Letter

@@
 
-[address frist sentence] We deleted the reference to Grass et al. because referencing it fully would have exceeded the word limit for the abstract.
+[address frist sentence] We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.
 
@@
 
-This is our response.
+We rewrote the respective sentences as the phrasing obviously was misleading. The respective sentences now read:
+
+> "with these associations being in a small to medium range."
+
+> "... because the worker is often in conflict ..."
 
@@
 How is NFC related to other constructs like neuroticism, self-esteem, and locus of control? And would NFC provide incremental validity in predicting burnout?
+
 “adults” in which context?
@@
 
-\RC{Page 4
+\Assignment{JZ}
+# Comment: see Table 2 in Fleischhauer et al. (2019)
+
+\RC{Page 4.
 
@@
 This is our response.
+
+\Assignment{JZ}
 
@@
 
-This is our response.
+We are aware that the double-blind review process somewhat interferes with Open Science issues.
+We learned how OSF projects can be anonymized only after submission of our manuscript.
+We apologize that we did not give the reviewer the opportunity to check our preregistration/data/code.
+Of course, we share our data and code openly on OSF and also provide a license for re-use (CC-4.0-BY).
 

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 While many studies have found medium sized positive associations of NFC with academic performance [@Cazan2014; @Stumm2013; @Grass2017; @Lavrijsen2021; @Zheng2020], recent investigations have also looked at NFC as a personal resource in academic and work contexts.
-Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020], with these associations being small to medium sized by and large.
+Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020], with these associations being in a small to medium range.
 These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological consequences [@Madsen2017; @Maslach2016; @Wiesner2005].

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly [@Schaufeli2014].
-Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer [@GrayStanley2011; @Lloyd2002].
+Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is often in conflict between advocating for their client and meeting the goals set by the employer [@GrayStanley2011; @Lloyd2002].
 Lackritz [-@Lackritz2004] found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
@@
 Burnout was assessed using the 21-item Maslach Burnout Inventory [MBI, @Buessing1992], with items such as "I don't really care what happens to some recipients" and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
-Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and low retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
+Its subscales *emotional exhaustion*, *depersonalization*, and *reduced personal efficacy* showed acceptable internal consistency (Cronbach’s $\alpha>.70$) and retest reliabilities of $r_{tt}=.60$, $r_{tt}=.54$, and $r_{tt}=.57$, respectively, over the span of one year in teachers [@Maslach1997].
 NFC was assessed with the 16-item short version of the German NFC scale (NCS) [@Bless1994], consisting of items (e.g., "Thinking is not my idea of fun", recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
-Following Grass et al. [-@Grass2018], bootstrapped confidence with $N=2,000$ replicates were computed to account for deviations from normality.
+Following Grass et al.
+[-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" -->w ere computed to account for deviations from normality.
 Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).
@@
 For this descriptive analysis, the variables *demands too high*, *demands too low*, and *demand-resource-fit* were computed as a sum of their item scores, not weighted as in the structural equation model.
-Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
+Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios in this sample were *acceptable*.
 The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@
 
-This is our response.
+This is our response (resolve inconsistency in tables).
 
@@
 
-This is our response.
+We revised the respective sentence that now reads:
+
+> "... the Cronbach's Alpha of the three demand-resource-ratios in this sample were *acceptable*."
+
+\Assignment{JZ}
 
@@
 
-This is our response.
+[add comment on parcelling]. We used the standard bootstrapping algorithm implemented in *lavaan*. To make our procedure more transparent, we now also provide the seed and the random number generator.
+
+\Assignment{JZ}
 
@@
 
+\Assignment{JZ}
+
 \RC{Page 10.
@@
 
+\Assignment{JZ}
+
 \RC{Page 13.
@@
 How is the RSMEA computed? My computation with RMSEA=SQRT((chisq-df)/(df(n-1))) gives a value around .14 instead of .000}
+
+\Assignment{JZ \& AS}
 
@@
 This is our response.
+
 \newpage

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

@@
 Following Grass et al.
-[-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" -->w ere computed to account for deviations from normality.
+[-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" --> were computed to account for deviations from normality.
 Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).

### 2022-07-20 Manuscript/Manuscript.Rmd
replaced trainees with student teachers

@@
 NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
-This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
+This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and student teachers [@Grass2018].
 However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
@@
 The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
-The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
+The participants in the study by Grass et al. [-@Grass2018] were student teachers with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
 Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.

### 2022-07-20 Manuscript/Manuscript.Rmd
added replication 'in a teacher sample'

@@
 [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
-One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
+One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] in a teacher sample using a multiple mediation model on cross-sectional self-report data of teachers.
 We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.
@@
 It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
-To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
+To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout in a teacher sample, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
 
@@
 
-### Replication of Grass et al. (2018)
+### Replication of Grass et al. (2018) in a teacher sample
 Items were reverse coded according to the scale manuals.
@@
 
-```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
+```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018) in a teacher sample"}
 
@@
     knitr::kable(replic_table,
-        caption = "Results of the replication of Grass et al. (2018).",
+        caption = "Results of the replication of Grass et al. (2018) in a teacher sample.",
         booktabs = T, # no vertical lines
@@
 
-## Replication of Grass et al. (2018)
+## Replication of Grass et al. (2018) in a teacher sample
 
@@
 
-```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al. (2018). * $p<.05$, ** $p<.01$."}
+```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al.
+(2018) in a teacher sample.
+* $p<.05$, ** $p<.01$."}
 
@@
 The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
-To achieve this, we replicated findings of mediators between Need for Cognition and burnout, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+To achieve this, we replicated findings of mediators between Need for Cognition and burnout in a teacher sample, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
 In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
@@
 
-```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}
+```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018) in a teacher sample"}
 
@@
     knitr::kable(outlierreplic_table,
-        caption = "Results of the replication of Grass et al. (2018).",
+        caption = "Results of the replication of Grass et al. (2018) in a teacher sample.",
         booktabs = T, # no vertical lines

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision_Letter.Rmd
answered comment about MBI subscales

@@
 thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
-We would like to thank the reviewers for their efforts to thoughly assess our manuscript.
-In the following we address your and each reviewers' concerns point-by-point.
+We would like to thank the reviewers for their efforts to thoroughly assess our manuscript. In the following we address your and each reviewer's concerns point-by-point.
 We hope that we could adequately address all the issues raised.
@@
 
-This is our response.
+Thank you for pointing this out.
+We changed the term "teacher trainees" to "student teachers" to make clear that the participants in the Grass et al. sample were still attending university.
+We also emphasized that the replication was done in a teacher sample in the respective parts of the manuscript.
 
@@
 \WorkInProgress
-\Easy
 
@@
 
-This is our response.
+Thank you for this suggestion.
+Our intention was not to focus on the significant mediations of Grass et al. (2018), but to deepen the understanding of the role of NFC in burnout.
+Therefore, we focussed on RPE, because it is likely the most relevant subscale of the MBI scale in the context of NFC (as Grass et al. also argued).
+While Grass et al.
+(2018) did not find significant correlations between NFC and the subscales DP and EE, Naderi et al.
+(2018, http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958) showed that in students, NFC was significantly correlated with DP and EE, but less so than with RPE.
+It has been shown that NFC is positively associated with higher self-efficacy (Rooij et al.
+(2017), https://doi.org/10.1080/13596748.2017.1381301, and Tan et al.
+(2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
+As can be seen in the correlation table (Table 2), NFC was equally related to all MBI subscales in our teacher sample.
+We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
+Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
+Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have theory-driven hypotheses regarding these associations,  we do not believe that such analyses would contribute to the goals of the paper.
+A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.
 

### 2022-07-20 Manuscript/Manuscript.Rmd
changed burnout into RPE where applicable

@@
 It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
-To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout in a teacher sample, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
+To sum up, this study had three aims: Replicating findings of mediation between NFC and reduced personal efficacy in a teacher sample, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
 
@@
 The translated Covid-19 items can be found in the *Supplementary Material S1*.
-Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.
+Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and reduced personal efficacy by active and passive coping.
 
@@
 The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
-To achieve this, we replicated findings of mediators between Need for Cognition and burnout in a teacher sample, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
+To achieve this, we replicated findings of mediators between Need for Cognition and reduced personal efficacy in a teacher sample, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
 In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
@@
 
-Our study showed that self-control mediated between NFC and burnout when teaching experience was being taken into account.
-Contrary to prior studies, neither habitual use of reappraisal nor use of suppression mediated between NFC and burnout.
+Our study showed that self-control mediated between NFC and reduced personal efficacy when teaching experience was being taken into account.
+Contrary to prior studies, neither habitual use of reappraisal nor use of suppression mediated between NFC and reduced personal efficacy.
 However, a crucial role in the relation of NFC and burnout seemed to be the perceived ratio of personal resources and demands, specifically, a resource-demand-fit was associated with lower and excessive demands were associated with higher burnout scores.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
added sentence to comment 2

@@
 (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
-As can be seen in the correlation table (Table 2), NFC was equally related to all MBI subscales in our teacher sample.
+And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
 We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.

### 2022-07-20 Manuscript/Revision_Letter.Rmd
answered age and covid burden

@@
 
-> This is a section quoted from the revised manuscript to illustrate the change.
-
 \Assignment{JZ}
-\AlmostDone
-\Medium
+\Done
 
@@
 
-This is our response.
+We do not agree that this item justifies claims for a confounding of Covid burden and years of experience.
+Firstly, years of experience cannot be equated with age, as some teachers are lateral entry employees.
+Secondly, age itself is not the only risk factor for Covid, but one of a long list of risk factors according to the Center for Disease Control and Prevention, such as disability, asthma, cancer, chronic heart disease, diabetes, HIV, weak immune function, obesity, mental disorders, pregnancy, physical inactivity, etc.
+Since the item does not specify the kind of risk factor, there is no need to correct for any confound between Covid burden and years of experience.
 
 \Assignment{JZ}
-\WorkInProgress
-\Easy
+\Done
 

### 2022-07-20 Manuscript/Revision_Letter.Rmd
started arguing the teacher-boredom case

@@
 
-This is our response.
+Thank you for addressing this.
+We do not consider "being busy" to be the same as "not being bored", because while an employee might have a high workload, the tasks in question might not be interesting or stimulating at all.
+In the case of teachers it might be grading essays on a topic they have read about many times, or staying at work until the late evening for parent-teacher conferences.
+We looked into the literature on boredom in teachers and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al.
+2019, https://doi.org/10.1111/bjep.12309), and teachers have a strong feeling of mission and responsibility but lack the opportunities to implement these priorities (Tuisk 2007, https://doi.org/10.2478/v10099-009-0011-8).
 

### 2022-07-20 Manuscript/Manuscript.Rmd
put in comment for boredom thingy

@@
 As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. [-@Reijseger2013.].
+<!--Here we apparently need a source saying that teachers are less likely to be bored-->
 The fact that the items that made up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.

### 2022-07-21 Manuscript/Revision_Letter.Rmd
responded to boredom-question

@@
 (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
-And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
+And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to also focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
 We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
 Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
-Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have theory-driven hypotheses regarding these associations,  we do not believe that such analyses would contribute to the goals of the paper.
+Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we do not believe that such analyses would contribute to the goals of the paper.
 A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.
@@
 
-\Assignment{Last Author}
+\Assignment{AS}
 \Done
@@
 We do not consider "being busy" to be the same as "not being bored", because while an employee might have a high workload, the tasks in question might not be interesting or stimulating at all.
-In the case of teachers it might be grading essays on a topic they have read about many times, or staying at work until the late evening for parent-teacher conferences.
-We looked into the literature on boredom in teachers and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al.
+In the case of teachers it might be grading essays on the same topic they have taught year after year, or staying at work until the late evening for parent-teacher conferences.
+We looked into the literature on boredom in teachers, which is unfortunately quite sparse, and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al.
 2019, https://doi.org/10.1111/bjep.12309), and teachers have a strong feeling of mission and responsibility but lack the opportunities to implement these priorities (Tuisk 2007, https://doi.org/10.2478/v10099-009-0011-8).
+Therefore, we cannot claim that boredom is less prevalent in the teaching profession.
+As the distinction between "being busy" and "not being bored" is reflected in the positive correlation between DTH and DTL, we have added a more in-depth discussion of this correlation in the manuscript (see also our response to the fifth comment of Reviewer 3):
+
+> However, the positive association of *demands too high* and *demands too low* in the correlation analysis suggests that boredom and burnout are not mutually exclusive.
+A teacher can have a very high workload, which is reflected in an elevated *demands too high* score, but the work in question might not be intellectually stimulating at all or might not appeal to their ideals and goals, which increases their *demands too low* score.
+Both of these variables were correlated with higher MBI scores, but in this model, high demands appear to have contributed more to explaining variance in MBI scores than low demands, suggesting that the perceived workload is more important in the burnout context than how stimulating the work is.
 
 \Assignment{JZ}
-\WorkInProgress
-\Easy
+\Done
 

### 2022-07-21 Manuscript/Manuscript.Rmd
added paragraph on DTH-DTL association

--- 2022-07-20 Manuscript/Manuscript.Rmd
@@
 As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. [-@Reijseger2013.].
+However, the positive association of *demands too high* and *demands too low* in the correlation analysis suggests that boredom and burnout are not mutually exclusive.
+A teacher can have a very high workload, which is reflected in an elevated *demands too high* score, but the work in question might not be intellectually stimulating at all or might not appeal to their ideals and goals, which increases their *demands too low* score.
+Both of these variables were correlated with higher MBI scores, but in this model, high demands appear to have contributed more to explaining variance in MBI scores than low demands, suggesting that the perceived workload is more important in the burnout context than how stimulating the work is.
 The fact that the items that made up the demand-resource-ratios were about the subjective perception and not about objective measures, supports the idea that the individual appraisal of one's own circumstances plays a crucial role in the development of burnout.

### 2022-07-21 Manuscript/Manuscript.Rmd
changed section counter

@@
 \renewcommand\thesection{\Alph{section}}
+\renewcommand\thesubsection{\arabic{subsection}}
 \counterwithout{figure}{section}
@@
 \newpage
+\setcounter{section}{19}
+\counterwithin{subsection}{section}
+\setcounter{subsection}{0}
+\counterwithin{figure}{subsection}
+\counterwithin{table}{subsection}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 
-# Supplementary Material
-
-## S1: Items used to assess Covid burden
+\section{Supplementary Material}
+\subsection{Items used to assess Covid burden}
 
@@
 \newpage
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{0}
 
-## S2: Results when excluding the outlier with very high MBI scores and very low NFC scores
+\subsection{Results when excluding the outlier with very high MBI scores and very low NFC scores}
 
@@
 
-## S3: Replication of Grass et al. (2018) when including years spent teaching
+\subsection{Replication of Grass et al. (2018) when including years spent teaching}
 
@@
 
-## S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy
+\subsection{Demand-resource-ratio model with the MBI subscale reduced personal efficacy}
 
@@
 
-## S5: Exploratory model with all relevant variables
+\subsection{Exploratory model with all relevant variables}
 

### 2022-07-21 Manuscript/Revision_Letter.Rmd
answered abstract comment

@@
 
-> While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.
+> Burnout has become more prevalent, mainly in social jobs, and there is evidence that certain personality traits promote or protect against burnout.
+Only recently, studies have focused on investment traits like Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
 
@@
 
-This is our response.
+Thank you for this suggestion.
+We have changed the numbering of the supplementary material into a S2.1, S2.2, ... notation.
 
 \Assignment{JZ}
-\WorkInProgress
-\Easy
+\Done
 
@@
 We like to thank the reviewer very much for this positive assessment of our manuscript.
-In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p.
-XX.
+In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p. XX.
+In our initial submission, there was an error in the code creating the table, so the diagonal with Cronbach's $\alpha$ and MacDonald's $\omega$ was missing.
 
 \Assignment{JZ}
+\Done
 
@@
 
-[address frist sentence] We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.
+Thank you for pointing this out.
+We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.
+In fact, the limit of 150 words is so small that we cannot include all variable names, so we rewrote the abstract to better explain the three aims of the study.
+It now reads as follows:
+
+> Burnout has become more prevalent, mainly in social jobs, and there is evidence that certain personality traits promote or protect against burnout.
+Only recently, studies have focused on investment traits like Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
+This study had three aims: First, replicating findings of NFC and the burnout subscale reduced personal efficacy in student teachers in a sample of N = 180 teachers, second, investigating the role of perceived ratios of demands and resources in the context of NFC and burnout, and finally, creating an exploratory model as a starting point for future research.
+The results indicated that unlike the student sample, the teachers’ association of NFC and reduced personal efficacy was mediated by self-control but not reappraisal.
+Teachers with higher NFC and self-control also had lower burnout because they experienced their resources as fitting to the demands.
 

### 2022-07-21 Manuscript/Revision_Letter.Rmd
replied to more from rev3

@@
 
-\Assignment{JZ}
-\Done
-
 \RC{Abstract: “little is known about the personality traits that promote or protect against burnout”
@@
 
-\Assignment{AS}
-\Done
-
 \RC{p.17 typo: the lavaan function should be spelled modindices(), not modincides()}
@@
 Thank you for noticing this typo. We have corrected it.
-
-\Assignment{AS}
-\Done
 
@@
 Since the item does not specify the kind of risk factor, there is no need to correct for any confound between Covid burden and years of experience.
-
-\Assignment{JZ}
-\Done
 
@@
 
-\Assignment{JZ}
-\Done
-
 \RC{supplementary material S2
@@
 We have changed the numbering of the supplementary material into a S2.1, S2.2, ... notation.
-
-\Assignment{JZ}
-\Done
 
@@
 In our initial submission, there was an error in the code creating the table, so the diagonal with Cronbach's $\alpha$ and MacDonald's $\omega$ was missing.
-
-\Assignment{JZ}
-\Done
 
@@
 
-This is our response.
+We have added the correlations of NFC with neuroticism, self-esteem, and locus of control in the manuscript:
 
-\Assignment{JZ}
-# Comment: see Table 2 in Fleischhauer et al. (2019)
+> NFC on the other hand shows opposite associations with those variables (r = -.19 with passive coping (Grass et al., 2018), r = -.19–-.33 with neuroticism (Fleischhauer et al., 2019), r = .42 with self-esteem (Osberg, 1987), r = .32 with internal locus of control (Fletcher et al.
+1986)), suggesting that people high in NFC are less prone to experience burnout.
+
+In the study done by Fleischhauer et al.
+(2019, https://doi.org/10.3389/fpsyg.2019.00420, Table 2), NFC could provide incremental validity in predicting the MBI score and its subscales over and above the Five Factor model.
+The adults in this study were a population-based sample of over 4,100 participants from different work backgrounds.
+
+Thank you for suggesting to provide more information on the characteristics of the Grass et al. sample.
+We have added the following information to the manuscript:
+
+> Grass et al.
+(2018) investigated such a mediation in a sample of 167 students, who were studying to become teachers in primary, secondary, special needs, or vocational schools, and who had been studying for M ± SD = 5.13 ± 2.63 semesters.
+
+We wanted to replicate the findings of Grass et al.
+(2018) in a sample of teachers to investigate the different mechanisms that influence the development of burnout in different life/career stages within the same profession.
+As burnout mostly affects social jobs and theories of person-environment fit have been discussed for quite some time, it begs the question whether the structure of social jobs causes burnout or whether the type of employee in social jobs is more prone to burnout.
+Studying the same profession in different stages can shed light on this issue.
 
@@
 
-This is our response.
+We did not have specific hypotheses about the relations of the demand-resource-ratios to each other.
+Initially it would stand to reason that they are not substantially correlated at all, since each participant might have a unique level of demands and resources, so they should score high in one of the variables and rather low in the other two.
+However, as they correlation table (Table 2) shows, this is not the case.
+DTH and DTL are positively correlated, and both are negatively correlated with DRF.
+Although initially counterintuitive, these associations are quite likely in practise: A teacher can have a very high workload in a strict time frame (high DTH) but the work itself might not be interesting or cognitively stimulating at all (high DTL), such as teaching the same material year after year, not being able to influence the syllabus, teaching at a much lower standard than what the teacher learned at university, keeping notorious troublemakers under control, having parent-teacher conferences until the late evening, etc.
+So a surplus of demands and a surplus of resources can co-exist, but not together with a demand-resource-fit.
+We have added the following section to the discussion:
 
-\Assignment{JZ}
+> However, the positive association of *demands too high* and *demands too low* in the correlation analysis suggests that boredom and burnout are not mutually exclusive.
+A teacher can have a very high workload, which is reflected in an elevated *demands too high* score, but the work in question might not be intellectually stimulating at all or might not appeal to their ideals and goals, which increases their *demands too low* score.
+Both of these variables were correlated with higher MBI scores, but in this model, high demands appear to have contributed more to explaining variance in MBI scores than low demands, suggesting that the perceived workload is more important in the burnout context than how stimulating the work is.
 

### 2022-07-22 Manuscript/Analysis.R
included full model

@@ -859,7 +859,78 @@
   
   explor2_table[2:ncol(explor2_table)] <- format(round(explor2_table[2:ncol(explor2_table)], digits = 3), nsmall = 2)
   
+#### Fully saturated model #####################################################
+  
+  fullysat_model <- '
+  # measurement model
+    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+    DTH =~ dth1 + dth2 + dth3
+    DRF =~ drf1 + drf2 + drf3
+    DTL =~ dtl1 + dtl2 + dtl3
+    MBI =~ mbi_ee + mbi_dp + mbi_rpe
+    SC =~ scs
+    COV =~ covb
+    YST =~ years
 
+  # structural model
+    
+    DTH ~ hnfc * NFC + hsc * SC + hcov * COV + hyst * YST
+    DTL ~ lnfc * NFC + lsc * SC + lcov * COV + lyst * YST
+    DRF ~ fnfc * NFC + fsc * SC + fcov * COV + fyst * YST
+    MBI ~ mdth * DTH + mdtl * DTL + mdrf * DRF
+    
+    mbi_ee ~~ mbi_rpe
+    mbi_ee ~~ mbi_dp
+    mbi_dp ~~ mbi_rpe
+    
+    NFC ~~ YST
+    NFC ~~ SC
+    NFC ~~ COV
+    SC ~~ COV
+    SC ~~ YST
+    YST ~~ COV
+
+    DTH ~~ DTL
+    DTH ~~ DRF
+    DRF ~~ DTL
+    
+    dth1 ~~ dth2
+    dth1 ~~ dth3
+    dth2 ~~ dth3
+
+    drf1 ~~ drf2
+    drf1 ~~ drf3
+    drf2 ~~ drf3
+    
+    dtl1 ~~ dtl2
+    dtl1 ~~ dtl3
+    dtl2 ~~ dtl3
+    
+  # Indirect effects
+    Indirect1 := hnfc * mdth + hsc * mdth + hcov * mdth + hyst * mdth
+    Indirect2 := lnfc * mdtl + lsc * mdtl + lcov * mdtl + lyst * mdtl
+    Indirect3 := fnfc * mdrf + fsc * mdrf + fcov * mdrf + fyst * mdrf
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+         
+  # total effect
[…]

### 2022-07-25 Manuscript/Revision_Letter.Rmd
answered question about alpha level

@@
 
-This is our response (resolve inconsistency in tables).
+Thank you for identifying this lack of clarity.
+The original data collection was done in the context of a thesis with different hypotheses than this study.
+Therefore, the sample size calculation of the original data collection reads as follows:
+
+> The initial study was aiming to recruit a sample of N ≥ 287 teachers as determined using the R package pwr (Champely, 2020), assuming a small to medium correlation of r = .20 between the measures of interest and targeting at a power of 1 − β = .80 at α = .01.
+
+And the post-hoc power analysis of the current study is presented at the end of the same paragraph:
+
+> Using the smallest standardized indirect effect from the mediation in Grass et al.
+(2018) in a post hoc power analysis with G*Power (Faul et al., 2007, 2009) yielded a power of 1 − β = .85 for linear multiple regression, given α = .05, N = 180, and f² = .05.
+
+This is the alpha-level we had preregistered and have adhered to in the manuscript.
 
 \Assignment{JZ}
+\Done
 

### 2022-07-25 Manuscript/Revision_Letter.Rmd
answered bootstrapping/parcelling question

@@
 \Assignment{JZ}
+\Done
 
@@
 
-[add comment on parcelling]. We used the standard bootstrapping algorithm implemented in *lavaan*. To make our procedure more transparent, we now also provide the seed and the random number generator.
+Parcelling items for SEMs has been shown to increase goodness-of-fit, reduce bias, and alleviate the effects of non-normally distributed data (e.g.
+Bandalos (2009, https://doi.org/10.1207/S15328007SEM0901_5), Hall et al.
+(1999, https://doi.org/10.1177/109442819923002), Matsanuga (2008, https://doi.org/10.1080/19312450802458935)).
+To benefit from these effects and reduce the number of parameters, especially given the sample size of N = 180, we wanted to use item parcelling for the Need for Cognition Scale.
+Additionally, because the MBI was also modelled in a way similar to item parcels (i.e.
+the three subscales were used as indicators), modelling the NFC scale with item parcels gives in a more balanced model.
+
+We used the standard bootstrapping algorithm implemented in *lavaan*.
+To make our procedure more transparent, we now also provide the seed and the random number generator.
+
+> Following Grass et al.
+(2018), bootstrapped confidence with *N* = 2,000 replicates and the seed 13 were computed with the Bollen-Stine bootstrapping of *lavaan()* to account for deviations from normality.
 

### 2022-07-25 Manuscript/Analysis.R
corrected error for diagonal insertion

@@ -23,7 +23,7 @@
   # load reproducible environment library to get all packages with correct versions form the renv.lock file
   # install renv by calling install.packages("renv") if necessary
   
-  library(renv)
+  #library(renv)
 
   # the required packages are:
   # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
@@ -476,8 +476,8 @@
   consist_diag <- consistencies[c(colnames(correlations))]
   
   # create a vector of consistencies to be used as the diagonal in a table later
-  consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
-                        format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
+  consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",13),
+                        format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",13))
   
   # paste together to create the output "alpha(omega)"
   consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
@@ -1066,8 +1066,8 @@
   outlier_consist_diag <- outlierconsistencies[c(colnames(outliercorrelations))]
   
   # create a vector of consistencies to be used as the diagonal in a table later
-  outlier_consist_diag <- cbind(format(round(t(outlier_consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
-                                format(round(t(outlier_consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))
+  outlier_consist_diag <- cbind(format(round(t(outlier_consist_diag[2,]), digits = 2), nsmall = 2), rep("(",13),
+                                format(round(t(outlier_consist_diag[5,]), digits = 2), nsmall = 2), rep(")",13))
   
   # paste together to create the output "alpha(omega)"
   outlier_consist_diag <- apply(outlier_consist_diag[,c(1:4)], 1 ,paste, collapse = "")

### 2022-07-25 Manuscript/Revision_Letter.Rmd
responded to model fit in supplement

@@
 
-\Assignment{JZ}
+\Assignment{JZ \& AS}
 
@@
 
-This is our response.
+That is right, thank you for pointing it out.
+We have added the fit measures of the replication of Grass et al.
+(2018) and of the demand-resource-ratio model without the outlier in the supplementary material below Table S2.2 and Table S2.3, respectively.
 
 \Assignment{JZ}
+\Done
 
@@
 
-This is our response.
+That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic.
 

### 2022-07-25 Manuscript/Analysis.R
added drr model with covariance

@@ -1205,4 +1205,49 @@
   # format the numbers to three digits after the decimal point
   
   outlierdrr_table[2:ncol(outlierdrr_table)] <- format(round(outlierdrr_table[2:ncol(outlierdrr_table)], digits = 3), nsmall = 2)
+
+#### DRR model with covariance as suggested by reviewer ####################
+  
+  sem_cov_model <- '
+  # measurement model
+    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+    DTH =~ dth1 + dth2 + dth3
+    DTL =~ dtl1 + dtl2 + dtl3
+    DRF =~ drf1 + drf2 + drf3
+    MBI =~ mbi_ee + mbi_dp + mbi_rpe
+
+  # structural model
+    DTH ~ a1 * NFC
+    DTL ~ a2 * NFC
+    DRF ~ a3 * NFC
+    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF
+  
+  # covariances
+    DTH ~~ DTL
+    DTL ~~ DRF
+    DRF ~~ DTH
+
+  # indirect effects
+    Indirect1 := a1 * b1
+    Indirect2 := a2 * b2
+    Indirect3 := a3 * b3
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+         
+  # total effect
+    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'
+  
+  # Determine the model fit
+  
+  fit2_cov <- lavaan::sem(
+    model = sem_cov_model,
+    data  = score_data,
+    estimator = "MLR"
+  )
+  
+  # Get summary
+  
+  fit2_cov_summ <- lavaan::summary(fit2_cov, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
+                               estimates = TRUE, ci = TRUE)
   

### 2022-07-25 Manuscript/Revision_Letter.Rmd
responded to covariance suggestion

@@
 
-That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic.
+That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic in the manuscript.
+We have also added the analysis code for the demand-resource-ratio model with covariance between DTH, DRL, and DRF to our *Analysis.R* script.
+The results indicate that the improvement in fit measures is very marginal: From CFI = .775, SRMR = .173, and RMSEA = .131 (model without covariance) to CFI = .831, SRMR = .091, and RMSEA = .114 (model with covariance).
+None of the fit measures indicate good fit.
+Therefore, we would like to refrain from including this model as yet another exploratory/supplementary analyis.
 
 \Assignment{JZ}
+\Done
 

### 2022-07-25 Manuscript/Revision_Letter.Rmd
explained full model failure

@@
 
-This is our response.
+We did start the exploratory model with the intention of using a full model, but lavaan was not able to compute it.
+For transparency, we have added the intended code of the full model into our *Analyis.R* script:
+
+> fullysat_model <- '
+  # measurement model
+    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
+    DTH =~ dth1 + dth2 + dth3
+    DRF =~ drf1 + drf2 + drf3
+    DTL =~ dtl1 + dtl2 + dtl3
+    MBI =~ ee + dp + rpe
+    SC =~ scs
+    COV =~ covb
+    YST =~ years
+
+  # structural model
+
+    DTH ~ hnfc * NFC + hsc * SC + hcov * COV + hyst * YST
+    DTL ~ lnfc * NFC + lsc * SC + lcov * COV + lyst * YST
+    DRF ~ fnfc * NFC + fsc * SC + fcov * COV + fyst * YST
+    MBI ~ mdth * DTH + mdtl * DTL + mdrf * DRF
+
+    ee ~~ rpe
+    ee ~~ dp
+    dp ~~ rpe
+
+    NFC ~~ YST
+    NFC ~~ SC
+    NFC ~~ COV
+    SC ~~ COV
+    SC ~~ YST
+    YST ~~ COV
+
+    DTH ~~ DTL
+    DTH ~~ DRF
+    DRF ~~ DTL
+
+    dth1 ~~ dth2
+    dth1 ~~ dth3
+    dth2 ~~ dth3
+
+    drf1 ~~ drf2
+    drf1 ~~ drf3
+    drf2 ~~ drf3
+
+    dtl1 ~~ dtl2
+    dtl1 ~~ dtl3
+    dtl2 ~~ dtl3
+
+  # Indirect effects
+    Indirect1 := hnfc * mdth + hsc * mdth + hcov * mdth + hyst * mdth
+    Indirect2 := lnfc * mdtl + lsc * mdtl + lcov * mdtl + lyst * mdtl
+    Indirect3 := fnfc * mdrf + fsc * mdrf + fcov * mdrf + fyst * mdrf
+
+  # contrast (if significant, the effects differ)
+    Contrast := Indirect1 - Indirect2 - Indirect3
+
+  # total effect
+    Total := Indirect1 + Indirect2 + Indirect3
+'
+However, this code yielded multiple error messages: *lavaan* was not able to compute standard errors as the model might not be identified, it could not invert the information matrix, and estimated some latent variables with negative variances.
+In short, the model could not be computed, so we used the *modindices()* function to modify it step by step, starting with the modifications with the biggest impact on model fit, but implementing only those that were contentually meaningful.
+We did not document this process, which would have been a good choice in hindsight.
+We adapted the explanation in the results section as follows:
+
+> We started with a full model with all variables except for the ERQ and its subscales as they had hardly any correlations with the other variables.
+This model could not be computed by *lavaan*, so we modified the structure using the *modindices()*-function in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
 
@@
 This is our response.
-
-\newpage
-
-# References
-
-::: {#refs custom-style="Bibliography"}
-:::

### 2022-07-25 Manuscript/Revision_Letter.Rmd
wrote some answer to the last comment

@@
 
+\Assignment{JZ}
+\Done
+
 \RC{Pages 20-24.
@@
 
-This is our response.
+Thank you for this suggestion.
+The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
+Each part is relevant but not "long enough" to warrant its own paper.
+
+\Assignment{JZ \& AS \& AS}
+\WorkInProgress

### 2022-07-26 Manuscript/Revision_Letter.Rmd
answered sample differences

@@
 
+Thank you for suggesting a more elaborate consideration of sample differences.
+We have added the following paragraph to the discussion:
+
+> Overall, the differences between Grass et al.
+(2018) and the present analysis suggest that burnout is being mediated by different factors in student teachers than in teachers.
+In a classroom context, controlling oneself and one’s emotional expression might be more relevant in dealing with the workload than in a university context, where a person is responsible for themselves first and foremost.
+This could even imply a different interpretation of the concept of personal efficacy in these two samples – student teachers might focus on how well they can follow lectures, complete work on time, and schedule their tasks efficiently, while teachers might focus on how well they can manage their students and whether they get good grades.
+Therefore, the understanding of personal efficacy could change from one’s own success to one’s students’ success depending on the career stage.
+
 \Assignment{JZ}
-\WorkInProgress
+\Done
 

### 2022-07-26 Manuscript/Revision_Letter.Rmd
removed assignment tag
answered first comm by rev 3

@@
 Therefore, the understanding of personal efficacy could change from one’s own success to one’s students’ success depending on the career stage.
-
-\Assignment{JZ}
-\Done
 
@@
 We like to thank the reviewer very much for this positive assessment of our manuscript.
-In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p. XX.
+In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see Table 2.
 In our initial submission, there was an error in the code creating the table, so the diagonal with Cronbach's $\alpha$ and MacDonald's $\omega$ was missing.
@@
 
-This is our response.
+Thank you for this assessment.
+It is true that the theoretical framework shifts within the manuscript, but this is absolutely intentional.
+We wanted to use one data set to investigate multiple aims that each have a right to exist but are not "long" enough for papers of their own.
+And as the investigation of demands and resources in the context of Need for Cognition is very new, a smaller confirmatory model and a larger exploratory model likely contribute more to developing this approach than a highly complex and long paper with a theoretical framework that is still in its infancy.
+The overarching framework in this manuscript is the role of Need for Cognition in burnout or burnout subscales, and depending on which specific aim the reader is interested in, they may skim over the others.
+We have added subheadings to the introduction and expanded the last paragraph before the methods section to better convey these three aims:
 
-\Assignment{JZ}
-\WorkInProgress
-\TimeConsuming
+> To sum up, this study used one questionnaire data set to investigate three aims: Firstly, replicating findings of mediation between NFC and reduced personal efficacy in a teacher sample to identify possible differences between teachers and student teachers.
+Secondly, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout to see whether teachers with high NFC tend to overestimate their own resources or underestimate the current demands, respectively.
+And lastly, exploring the impact of other variables in the burnout context, such as the perceived burden by the pandemic, to create a starting point for future research.
 

### 2022-07-26 Manuscript/Revision_Letter.Rmd
finished answers

@@
 We hope that we could adequately address all the issues raised.
+In this revision, we have also updated the figures, they are now created with Inkscape rather than RStudio, which gives a more elegant result.
+The content of the figures did not change.
 
@@
 
+Regarding the covariation of DTH, DTL, and DRF, please see our response to your comment about pages 15-16 below.
+
 \RC{Page 1.
@@
 
-\Assignment{JZ}
-\Done
-
 \RC{Page 7.
@@
 > "... the Cronbach's Alpha of the three demand-resource-ratios in this sample were *acceptable*."
-
-\Assignment{JZ}
-\Done
 
@@
 
-\Assignment{JZ}
-\Done
-
 \RC{Page 9.
@@
 
-This is our response.
+We do not assume that NFC completely accounts for their covariation.
+We have computed an exploratory model which includes the covariation of the three factors as you suggested in the comment below, and it was not superior to the confirmatory model regarding fit measures (please see our response to your comment about pages 15-16).
 
@@
 
-\Assignment{JZ}
-\Done
-
 \RC{Page 13.
@@
 
-\Assignment{JZ \& AS}
+The *lavaan*-function *fitMeasures()* calls the function *lav_fit_measures()*, which uses the robust RMSEA formula by Broseau-Liard, Savalei, and Li(2012, doi: 10.1080/00273171.2012.715252, equation 8).
+It corrects for nonnormality of the data, which might be the reason why RMSEA=SQRT((chisq-df)/(df(n-1))) gives a slightly different result.
 
@@
 Therefore, we would like to refrain from including this model as yet another exploratory/supplementary analyis.
-
-\Assignment{JZ}
-\Done
 
@@
 
-\Assignment{JZ}
-\Done
-
 \RC{Pages 20-24.
@@
 Each part is relevant but not "long enough" to warrant its own paper.
-
-\Assignment{JZ \& AS \& AS}
-\WorkInProgress
+(As we have provided an answer to this issue in our response to your first comment, we would kindly refer to it here.)

### 2022-07-29 Manuscript/Revision_Letter.Rmd
added anonymous link
implemented Anjas comments

@@
 Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
-Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we do not believe that such analyses would contribute to the goals of the paper.
+Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we would like to refrain from including these analyses in the paper in order not to report analyses that are less well-reasoned and not pre-registered.
 A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.
@@
 
-We do not agree that this item justifies claims for a confounding of Covid burden and years of experience.
+Although one can assume that Covid burden and years of experience are associated, there is a variety of factors that may also play a role.
 Firstly, years of experience cannot be equated with age, as some teachers are lateral entry employees.
@@
 Thank you for this assessment.
-It is true that the theoretical framework shifts within the manuscript, but this is absolutely intentional.
-We wanted to use one data set to investigate multiple aims that each have a right to exist but are not "long" enough for papers of their own.
-And as the investigation of demands and resources in the context of Need for Cognition is very new, a smaller confirmatory model and a larger exploratory model likely contribute more to developing this approach than a highly complex and long paper with a theoretical framework that is still in its infancy.
+It is true that the theoretical framework shifts within the manuscript.
+This is motivated by the three different aims of the paper.
+As the investigation of demands and resources in the context of Need for Cognition is very new, a smaller confirmatory model and a larger exploratory model likely contribute more to developing this approach than a highly complex and long paper with a theoretical framework that is still in its infancy.
 The overarching framework in this manuscript is the role of Need for Cognition in burnout or burnout subscales, and depending on which specific aim the reader is interested in, they may skim over the others.
@@
 Of course, we share our data and code openly on OSF and also provide a license for re-use (CC-4.0-BY).
+The anonymized link is: https://osf.io/36ep9/?view_only=5169a1624e6d40c193bdc96121266ea9.
 
@@
 The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
-Each part is relevant but not "long enough" to warrant its own paper.
 (As we have provided an answer to this issue in our response to your first comment, we would kindly refer to it here.)

### 2022-08-31 Manuscript/Analysis.R
added analyses of DP and EE subscales

@@ -542,13 +542,13 @@
                                         "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
                                         "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                         "Total Effect"),
-                             "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
-                             "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
+                             "$B$" = c(fit_summ$pe$est[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "$SE$" = c(fit_summ$pe$se[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "$z$-value" = c(fit_summ$pe$z[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "$p$-value" = c(fit_summ$pe$pvalue[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "CI Lower" = c(fit_summ$pe$ci.lower[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "CI Upper" = c(fit_summ$pe$ci.upper[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
+                             "$\\beta$" = c(fit_summ$pe$std.all[fit_summ$pe$label != "" & fit_summ$pe$label != "Contrast"]),
                              check.names = FALSE)
   
[…]
